### 2024-05-24 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
get scripts in there

---
title: "MS Prelim Data K23"
author: "Erica Baller"
date: "2/25/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(stringr)
#functions
source("~/BBL/msanxiety/scripts/ms_functions.R")
```

## MS anxiety analyses

## R Markdown

The first chunk here is reading in appropriate data frames and preprocessing. Two big data frames are read in. The first is the demographic, drug, lab info for the MS patients (from the DAC pull). The second is the data frame of fascicle proportion affected for people with good mimosa (# volume affected/total volume of fascicle). The most important preprocessing occurs in a series of mutate commands. These essentially add new columns to the data frame that can later be used. The thrust of these mutate commands is to define who has depression and who does not.

Of note, in prior iterations of this analysis, we did not consider psychiatric medications in determining group inclusion/exclusion. Turns out it makes a difference, as a lot of people on psychotropic medications were counted as "controls/healthy" in previous analyses. For these preliminary analysis, our inclusion/exclusion are more stringent. Of note, the graph below is irrespective of whether they had good/bad MIMoSA. As such, the MIMoSA subset is smaller. It does however highlight the

<img width="70%" src="/Users/eballer/BBL/msdepression/data/drugs_data/MS_Patient_Depression_Categorizations.png"/>

Inclusion criteria below:

Inclusion MS Criteria (dataframe read in here has already been filtered down using the exclusions below previously)
  1) Scanned under MS protocol (42K)
  2) MS Diagnosis (17K)
  3) Seen by MS doctor (16K)

Inclusion criteria for Anxious Group
  1) Have an ICD10 F3* code (in our sample, people have F41.1; 41.3; 41.8; 41.9)
        (may use this later)- https://www.nami.org/About-Mental-Illness/Treatments/Mental-Health-Medications

Inclusion criteria for Healthy Group
  1) No F* diagnoses
  2) At least 1 PHQ2 or PHQ9 with a documented 0
  3) Free of psychiatric medications per NAMI website

Exclusions
  If you received the MS protocol or had a diagnosis of MS but never actually saw an MS provider, we cannot be sure that the diagnosis of MS is truly valid, as it is hard to diagnose anyway.
  If you did not have a diagnosis of depression and never completed a PHQ2 or 9, and had no history of medications, we could not safely confirm nor deny the presence of depression. These subjects were excluded from future analyses. We could consider adding these to the healthy group maybe, but not too inclined to do that right now.

Imaging exclusion
  We are currently only using people who had good MIMOSA (75 or 100). That severely limits our numbers, but that is okay! When we re-QC, we will probably get a lot more into this group.

Final N demographics 
  Anxious: 
  Super clean healthy: 604 (148 unique)

(unique, with good MIMoSA):

```{r read_in_df_and_subset}
homedir <- "/Users/eballer/BBL/msanxiety/"
columns_to_make_integer <- c("ACCESSION_NUM", "PAT_AGE_AT_EXAM","MRI_ENC_AGE","CURRENT_AGE","hemoglobin", "WBC","RBC","B12","FOLATE", "TSH", "RPR","CSFAPPEAR1","CSFAPPEAR4","CSFCOLOR1",       "CSFCOLOR4","CSFTUBE","CSFTUBE4","PHQ.2","PHQ.9") #removed "VitD", not in new pull for some reason

#open Rds
data_2023_pull <- readRDS(paste0(homedir, "/data/data_2023_pull_with_curated_icd10_codes.rds"))

#Get med info in
#read in BCP info, names of meds, est and prog and doses
bcp <- read.csv("/Users/eballer/BBL/medication_data/BCP_est_and_prog_levels_and_doses_all_brands.csv", sep = ",", header = TRUE)
bcp$bcp_name <- toupper(bcp$bcp_name)

#read in ms med info, names of meds, mechanism, and whether or not dmt
msmeds <- read.csv("/Users/eballer/BBL/medication_data/ms_medications_brand_and_generic.csv", sep = ",", header = TRUE)
msmeds$Medication <- toupper(msmeds$Medication)

#depression/psych meds from NAMI website 
psych_meds <- read.csv("/Users/eballer/BBL/medication_data/nami_psych_meds_antidepressants.csv", sep = ",", header = TRUE)
psych_meds$Medication.Name <- toupper(psych_meds$Medication.Name)

#anxiety meds from chatgpt (cross referenced with psych meds)
anxiety_meds <- read.csv("/Users/eballer/BBL/medication_data/antianxiety_medications.csv", sep = ",", header = TRUE)
anxiety_meds$Medication <- toupper(anxiety_meds$Medication)
anxiety_meds_no_beta_blocker <- anxiety_meds %>% filter(Class != "Beta_blocker")

##########################
### some preprocessing ###
##########################
#we need to keep scans from people seen by an MS provider (n = 17067) who have an MS diagnostic code (n=16,830)
#we make a bunch of columns from character to integer, binarize sex and race, and put date into a nice format YYYYMMDD, the %m%d%y indicates what it started out as

#goal is to keep people who were seen by 
 data_empi_acc_f_phq <-data_2023_pull %>% 
   mutate(across(.cols = columns_to_make_integer, .fns = as.integer)) %>%
   mutate(sex_binarized = ifelse(SEX == "MALE", 1, 2)) %>%
   mutate(osex = ordered(sex_binarized,levels = c(1,2), labels = c("Male","Female"))) %>%
   mutate(race_binarized = ifelse(RACE == "WHITE", 1, 2)) %>%
   mutate(orace = ordered(race_binarized,levels = c(1,2), labels = c("White","Non-white"))) %>%
   mutate(EXAM_DATE = as.Date(BEGIN_EXAM_DTTM, format = "%m/%d/%y")) %>% 
   mutate(EXAM_DATE = gsub(EXAM_DATE, pattern = "-", replacement = "")) %>%
   mutate(BEGIN_EXAM_DTTM = as.Date(BEGIN_EXAM_DTTM, format = "%m/%d/%y")) %>% #make sure to actually save it as date object for later processing
   mutate(EMPI = as.factor(EMPI)) %>%
   mutate(number_of_dx = ifelse(!is.na(ICD10), (str_count(ICD10, ";") + 1), 0)) %>%
   mutate(number_of_dx_extended = ifelse(!is.na(all_icd10_dx), str_count(all_icd10_dx, ";") + 1, 0)) %>%
   mutate(number_of_psychiatric_comorbidities_extended = ifelse(!is.na(all_icd10_dx), str_count(all_icd10_dx, "F"), 0)) %>%
   mutate(number_of_anxiety_comorbidities_extended = ifelse(!is.na(all_icd10_dx), str_count(all_icd10_dx, "F4"), 0)) %>%
   mutate(number_of_depression_comorbidities_extended = ifelse(!is.na(all_icd10_dx), str_count(all_icd10_dx, "F3"), 0)) %>%
   mutate(number_of_medications = ifelse(!is.na(Medication), str_count(Medication, ";") + 1, 0)) %>%
   mutate(On.Bcp = ifelse(str_detect(Medication, paste(bcp$bcp_name, collapse = "|")), 1, 0)) %>%
   mutate(On.Psych.Meds = ifelse(str_detect(Medication, paste(psych_meds$Medication, collapse = "|")), 1, 0)) %>%
   mutate(On.Antidepressants = ifelse(str_detect(Medication, paste(psych_meds$Medication[psych_meds$Antidepressant == "t"], collapse = "|")), 1, 0)) %>%
   mutate(On.Anxiolytics = ifelse(str_detect(Medication, paste(anxiety_meds$Medication, collapse = "|")), 1, 0)) %>%
   mutate(On.Anxiolytics_no_beta_blocker = ifelse(str_detect(Medication, paste(anxiety_meds_no_beta_blocker$Medication, collapse = "|")), 1, 0)) %>%
   mutate(On.Benzos = ifelse(str_detect(Medication, paste(anxiety_meds$Medication[anxiety_meds$Class == "Benzodiazepine"], collapse = "|")), 1, 0)) %>%
   mutate(On.Anti_cd20 = ifelse(str_detect(Medication, paste(msmeds$Medication[msmeds$Mechanism == "anti-cd20"], collapse = "|")), 1, 0)) %>%
   mutate(On.Interferon = ifelse(str_detect(Medication, paste(msmeds$Medication[msmeds$Mechanism == "Interferon"], collapse = "|")), 1, 0)) %>%
   mutate(On.Steroids = ifelse(str_detect(Medication, paste(msmeds$Medication[msmeds$Mechanism == "Steroid"], collapse = "|")), 1, 0)) %>%
   mutate(On.Dmt = ifelse(str_detect(Medication, paste(msmeds$Medication[msmeds$DMT == "y"], collapse = "|")), 1, 0)) %>%
   mutate(Has.PHQ2 = ifelse(PHQ.2 != "NULL", 1, 0)) %>%
   mutate(Has.PHQ9 = ifelse(PHQ.9 != "NULL", 1, 0)) %>%
   mutate(Has.depdx = ifelse(grepl("F3", all_icd10_dx), 1, 0)) %>%
   mutate(Has.anxietydx = ifelse(grepl("F4", all_icd10_dx), 1, 0)) %>%
   mutate(Has.depANDanx.dx = ifelse(Has.depdx & Has.anxietydx, 1, 0)) %>%
   mutate(PHQ.2_modsev_dep_sxs = ifelse(Has.PHQ2 & PHQ.2 >= 3, 1, 0)) %>%
   mutate(PHQ.9_modsev_dep_sxs = ifelse(Has.PHQ9 & PHQ.9 >= 10, 1, 0)) %>%
   mutate(PHQ.2_mild_dep_sxs = ifelse(Has.PHQ2 & PHQ.2 > 0 & PHQ.2 < 3, 1, 0)) %>%
   mutate(PHQ.9_mild_dep_sxs = ifelse(Has.PHQ9 & PHQ.9 > 0 & PHQ.9 < 10, 1, 0)) %>%
   mutate(PHQ.2_zero = ifelse(Has.PHQ2 & PHQ.2 == 0, 1, 0)) %>%
   mutate(PHQ.9_zero = ifelse(Has.PHQ9 & PHQ.9 == 0, 1, 0)) %>%
   mutate(dep_by_dx_phq = ifelse((Has.depdx | PHQ.2_modsev_dep_sxs | PHQ.9_modsev_dep_sxs),1,0)) %>%
   mutate(dep_by_dx_phq_antidep = ifelse((Has.depdx | On.Antidepressants | PHQ.2_modsev_dep_sxs | PHQ.9_modsev_dep_sxs),1,0)) %>%
   mutate(true_healthy = ifelse((!Has.depdx & !On.Psych.Meds & (PHQ.2_zero | PHQ.9_zero)), 1, 0)) %>%
   mutate(dep_by_dx_phq_meds_healthy_phq0_no_psych_meds = ifelse(dep_by_dx_phq_antidep | true_healthy, 1, 0)) %>%
   rowwise(ACCESSION_NUM) %>%
   mutate(depGroupVar =
            sum(c(dep_by_dx_phq_meds_healthy_phq0_no_psych_meds,dep_by_dx_phq_antidep))) %>%#you get an extra point if you are in the depression group, so the end result is dep = 2, healthy = 1, 0 for exclude
   ungroup() #n=3,737 unique people, n= 16,830 total

##########################################################
#             Read in Fascicle info             #
##########################################################

fascicle_proportions <- read.csv(paste0(homedir, "/results/fascicle_volumes_all_subjects_roi_n2336.csv"), header = T, sep = ",") #n = 2336

#fascicle names are contained in all but the first 2 columns of the fascicle_proportions df
fascicle_names <- names(fascicle_proportions[3:dim(fascicle_proportions)[2]])

write.table(fascicle_names,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names.csv", row.names = F, quote = F, col.names = F)

########
#fascicle volumes in depression network
########
fascicle_volumes_dep <- read.csv(paste0(homedir, "results/streamline_volume_within_dep_network.csv"), header = T, sep = ",")

#add column to indicate whether does not meet criteria for inclusion in dep mask (0), any overlapping voxels (1), or >10% overlapping voxels (2)
fascicle_volumes_dep_network <- fascicle_volumes_dep %>%
  replace(is.na(.), 0) %>%
  mutate(inDepMask=case_when(prop_in_mask == 0 ~ 0, (prop_in_mask > 0 & prop_in_mask < 0.1) ~ 1, prop_in_mask >= 0.1 ~ 2))

write.table(fascicle_volumes_dep_network, paste0(homedir,  "/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_grouping.csv"), sep = ",", col.names=T)#, row.names = F, quote = F, col.names = T)

fascicle_names_nondep_network<- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask == 0)]

fascicle_names_dep_network_all <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask > 0)]

#fascicle_names_dep_network_all <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask == 1)]
#write.table(fascicle_names_dep_network_all,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_all.csv", row.names = F, quote = F, col.names = F)

fascicle_names_dep_network_10_percent <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask == 2)] #n=15
#write.table(fascicle_names_dep_network_10_percent,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_10_percent.csv", row.names = F, quote = F, col.names = F)

fascicle_names_dep_network_5_percent <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$prop_in_mask >= 0.05)] #n=24

#fascicle_mapping, returns numerical mapping as well as names of tracts, and whether in or out of dep network
fascicle_bundle_mapping <- get_fascicle_bundle_mapping()

##########################################################
#             Merge with data_empi              #
##########################################################
df_demo_and_fascicles <- merge(data_empi_acc_f_phq, fascicle_proportions, by = c("EMPI", "EXAM_DATE")) #n = 2962

##########################################################
#                 Histos                        #
##########################################################
##### Histograms for PHQ2/9 healthy and depressed

hist(df_demo_and_fascicles$PHQ.2[which(!is.na(df_demo_and_fascicles$PHQ.2))], main = paste0("PHQ-2 In Good Mimosa Group : n = ", length(which(!is.na(df_demo_and_fascicles$PHQ.2)))), xlab = "PHQ-2", breaks = 8)

hist(df_demo_and_fascicles$PHQ.9[which(!is.na(df_demo_and_fascicles$PHQ.9))], main = paste0("PHQ-9 In Good Mimosa Group : n = ", length(which(!is.na(df_demo_and_fascicles$PHQ.9)))), xlab = "PHQ-9", breaks = 8)

phq2_and_dep <- df_demo_and_fascicles %>% filter(depGroupVar == 2) %>% drop_na(PHQ.2) 
phq9_and_dep <- df_demo_and_fascicles %>% filter(depGroupVar == 2) %>% drop_na(PHQ.9) 
phq2_and_healthy <- df_demo_and_fascicles %>% filter(Has.depdx == 0) %>% drop_na(PHQ.2) 
phq9_and_healthy <- df_demo_and_fascicles %>% filter(Has.depdx == 0) %>% drop_na(PHQ.9)

hist(phq2_and_dep$PHQ.2, main = paste0("PHQ-2/Depressed In Good Mimosa Group : n = ", dim(phq2_and_dep)[1]), xlab = "PHQ-2", breaks = 8)

hist(phq9_and_dep$PHQ.9, main = paste0("PHQ-9/Depressed In Good Mimosa Group : n = ", dim(phq9_and_dep)[1]), xlab = "PHQ-9", breaks = 8)

hist(phq2_and_healthy$PHQ.2, main = paste0("PHQ-2/Healthy In Good Mimosa Group : n = ", dim(phq2_and_healthy)[1]), xlab = "PHQ-2", breaks = 8)
hist(phq9_and_healthy$PHQ.9, main = paste0("PHQ-9/Healthy In Good Mimosa Group : n = ", dim(phq9_and_healthy)[1]), xlab = "PHQ-9", breaks = 8)

######## Histograms for depression network
#this histogram helps contextualize the number of streamlines with varying degrees of proportions affected
hist(x=fascicle_volumes_dep$prop_in_mask, main = "Histogram Affected Streamlines in Dep Net", xlab = "Proportion Streamlines per Fascicle Affected", breaks = 20)

```

## Depression versus healthy analysis

```{r demographics}

#this will display a demographics table comparing age, race, sex between healthy and depressed groups, using the first presentation to treatment

make_demographics_table_ms(data_frame = data_empi_acc_f_phq)

df_unique_empi <- data_empi_acc_f_phq %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

make_demographics_table_ms(data_frame = df_unique_empi)

df_just_healthy_and_depressed <- df_unique_empi %>% filter(depGroupVar != 0)

make_demographics_table_ms(data_frame = df_just_healthy_and_depressed)

#just people with good mimosa
df_good_mimosa <- df_demo_and_fascicles %>% filter(depGroupVar != 0)
make_demographics_table_ms(data_frame = df_good_mimosa)

df_good_mimosa_unique <- df_demo_and_fascicles %>% 
  filter(depGroupVar != 0) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup() 
make_demographics_table_ms(data_frame = df_good_mimosa_unique)
```

```{r proof_of_concept}

#this section creates histograms looking at the proportion of volume lost in each fascicle across subjects
#we recapitulate earlier work and show that higher volume loss with our method reflects regions previously known to have higher volume loss
#These findings suggest that the streamline filtering approach could be a reasonable approach for this analysis

#have to pull out just the pieces I'm interested in
just_dep_and_empi <- subset(data_empi_acc_f_phq, select = c("EMPI", "depGroupVar"))
added_dep_to_fascicles <- merge(just_dep_and_empi, fascicle_proportions, by = c("EMPI"))
melted_df <- melt(added_dep_to_fascicles, id.vars = c("EMPI", "EXAM_DATE", "depGroupVar"))

#exclude regions where there was no lesion at all
lesioned <- subset(melted_df, value > 0)

#only include people in healthy or depressed group
lesioned_dx <- subset(lesioned, depGroupVar != 0)

#separate out healthy and depressed
healthy <- subset(lesioned, depGroupVar == 1)
depressed <- subset(lesioned, depGroupVar == 2)

q<-ggplot(lesioned, aes(x=value, fill=depGroupVar)) + geom_histogram() + facet_wrap(~variable)
r<-ggplot(lesioned_dx, aes(x=value, fill=depGroupVar)) + geom_histogram() + facet_wrap(~variable)
r_color<-ggplot(lesioned_dx, aes(x=value, color=factor(depGroupVar))) + geom_histogram() + facet_wrap(~variable)
x<-ggplot(lesioned, aes(x=value)) + geom_histogram() + facet_wrap(~variable)
y<-ggplot(healthy, aes(x=value)) + geom_histogram() + facet_wrap(~variable)
z<-ggplot(depressed, aes(x=value)) + geom_histogram() + facet_wrap(~variable)

#print(q)
#print(r)
print(r_color)
#print(x)
#print(y)
#print(z)
```

```{r age_effects_fascicles_unique}
########### age effect whole group

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% 
  filter(depGroupVar != 0)  %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

#### age histo ###
hist(dep_and_healthy_groups_for_ICD_analysis$PAT_AGE_AT_EXAM,
main = paste0("Age In Good Mimosa Group : n = ", dim(dep_and_healthy_groups_for_ICD_analysis)[1]), xlab = "Age", breaks = 10)

#lm
fascicle_age_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PAT_AGE_AT_EXAM, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_age_lm) <- fascicle_names

#anova
fascicle_age_anova <- lapply(fascicle_age_lm, anova)

#fdr corrected
fascicle_age_anova_fdr <- fdr_anova_generic(fascicle_age_anova, 1)
print(fascicle_age_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_age_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#visreg
#sapply(fascicle_age_lm,visreg)
visreg(fascicle_age_lm$AF_R,ylab = "Proportion of Affected Streamlines", xlab = "Age in Years",
       line=list(col="red"),
       points=list(col="black"))

```

```{r sex_effects_fascicles_unique}

### really not interesting at all. 3 areas that are uncorrected: SCP, CPT_O_R, OR_R

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% filter(depGroupVar != 0)  %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

#### sex histo ###
hist(dep_and_healthy_groups_for_ICD_analysis$sex_binarized,
main = paste0("Sex In Good Mimosa Group : n (M/F)= ", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1), "/", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)),  xlab = "Sex", breaks = 2)

#lm
fascicle_sex_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ osex, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_sex_lm) <- fascicle_names

#anova
fascicle_sex_anova <- lapply(fascicle_sex_lm, anova)

#fdr corrected
fascicle_sex_anova_fdr <- fdr_anova_generic(fascicle_sex_anova, 1)
print(fascicle_sex_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sex_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_sex_anova_p <- sapply(fascicle_sex_anova, function(v) v$"Pr(>F)"[1])
fascicle_sex_anova_p05_unc <- as.data.frame(fascicle_sex_anova_p[fascicle_sex_anova_p < 0.05])
print(fascicle_sex_anova_p05_unc)

```

```{r depression_unique_all_fascicles_together_in_dep_networks}

#isolate out only the depressed group and healthy group, make a column that sums up the total prop lost)
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
  mutate(total_fascicle_prop_lost_indepnet_10_percent =
           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
   mutate(total_fascicle_prop_lost_indepnet_5_percent =
           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
  mutate(total_fascicle_prop_lost_nondep_network =
           rowMeans(across(fascicle_names_nondep_network))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

dep_vs_healthy <- lm(total_fascicle_prop_lost ~ depGroupVar, data = dep_and_healthy_groups_for_ICD_analysis)
summary(dep_vs_healthy) #p=0.494, cohen d = 0.2

#power analysis to predict sample required for K, u = num df, v = denom df, f2=0.01 (cohen d = 0.02/2) 
#prop in each fascicle predicting dep (87), number of predictors (age, sex, ef, ess?) = 4, u = 87-4 = 83
pwr.f2.test(u=83, f2 = 0.02, sig.level = 0.5, power = 0.8)

#test whether proportion lost overall different between depressed and healthy- yes, p = 0.049
total_volume_lost_dep_vs_healthy_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 27%, mean non_dep = 24%, p = 0.049

df_for_visreg <- as.data.frame(cbind(c(dep_and_healthy_groups_for_ICD_analysis$EMPI, dep_and_healthy_groups_for_ICD_analysis$EMPI), c(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]), c(rep(1,298), rep(2,298))))
names(df_for_visreg) <- c("EMPI", "prop_lost", "Diagnosis")
df_for_visreg$Diagnosis <- as.factor(df_for_visreg$Diagnosis)

plot <- ggplot(df_for_visreg, aes(x=Diagnosis, y = prop_lost, col=Diagnosis)) +
  geom_violin() + 
  geom_jitter(shape=16, position=position_jitter(0.05)) + 
  geom_boxplot(width=0.1) + theme_minimal() + 
  stat_summary(fun.y=median, geom="point", size=2, color="black") + 
  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed"))

print(plot)

#bar plot
Diagnosis <- c("MS w/Depression", "MS No Depression")
value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]))

sem <- c((sd(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==2))),
           (sd(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==1))))

data <- data.frame(Diagnosis,value, sem)
#data$Fascicle <- pretty_names

# Grouped
barplot <- ggplot(data, aes(x=Diagnosis,fill=Diagnosis, y=value)) + 
  geom_bar(stat="identity", position=position_dodge(0.9)) + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
  ylab("Proportion of Fascicles Affected") +
  ylim(0,0.5) +
  theme(axis.text = element_text(size = 12, colour = "black"))

print(barplot)

# Grouped
barplot <- ggplot(data, aes(x=reorder(Diagnosis, -value),fill=Diagnosis, y=value)) + 
  geom_bar(stat="identity", colour="black", width=0.8, size=1.5) + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9), size=1.5) +
  scale_fill_manual(values = c("#cdcdcd", "#FFFFFF")) + #comment out if you want colored graph
  ylab("Proportion of Fascicles Affected") +
  theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=20),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        panel.background = element_rect(colour = "white", fill = "white")) + #comment out if you want pretty 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.52)) #comment out if you want colored graph

print(barplot)

#look at within depression network specifically - trend, p = 0.059
total_volume_lost_dep_vs_healthy_unique_in_dep_network <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 36%, mean non_dep = 32%, p = 0.071

#look at within depression network in fascicles where at least 10% of the volume of the fascicle was in dep network
#yes, p = 0.048
total_volume_lost_dep_vs_healthy_unique_in_dep_network_10percent <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_10_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_10_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 33%, mean non_dep = 27%, p = 0.048

#look at within depression network in fascicles where at least 5% of the volume of the fascicle was in dep network
#yes, 
total_volume_lost_dep_vs_healthy_unique_in_dep_network_5percent <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_5_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_5_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 32%, mean non_dep = 27%, p = 0.056

#look at outside depression network, yes p = 0.037
total_volume_lost_dep_vs_healthy_unique_in_nondep_network <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 18%, mean non_dep = 16%, p = 0.037

### Age actually makes things worse
#dep_vs_healthy_w_age <- lm(total_fascicle_prop_lost ~ depGroupVar + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)
#summary(dep_vs_healthy_w_age)

#df for visreg - actually not using visreg. Just a nice way to see that there is significantly more loss in depression network versus outside depression network

```

```{r depressed_versus_healthy_unique_subjs_indiv_fascicle}
##### repeat above analysis but use only the first instance of each EMPI, sorted by date
df_unique_empi <- df_demo_and_fascicles %>% 
  filter(depGroupVar != 0) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

#lm
fascicle_lm_unique <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ depGroupVar + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_unique_empi)
})
names(fascicle_lm_unique) <- fascicle_names

#anova
fascicle_anova_unique <- lapply(fascicle_lm_unique, anova)

#fdr corrected
fascicle_anova_unique_fdr <- fdr_anova_generic(fascicle_anova_unique, 1)
print(fascicle_anova_unique_fdr)#anova values < 0.05, uncorrected

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_anova_unique[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#fdr corrected only dep network
fascicle_anova_w_fiber_mapping <- fascicle_anova_unique[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr)

#fdr corrected only dep 10% mask
fascicle_anova_w_fiber_mapping <- fascicle_anova_unique[which(fascicle_bundle_mapping$inDepNetwork_vector ==2)]
fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr)

#fdr corrected only dep 5% mask
fascicle_anova_w_fiber_mapping <- fascicle_anova_unique[which(fascicle_volumes_dep_network$prop_in_mask >= 0.05)]
fascicle_anova_fdr<- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr)

#uncorrected
fascicle_anova_unique_p <- sapply(fascicle_anova_unique, function(v) v$"Pr(>F)"[1])
fascicle_anova_unique_p05_unc <- as.data.frame(fascicle_anova_unique_p[fascicle_anova_unique_p < 0.05])
print(fascicle_anova_unique_p05_unc)

### plot AF_R

df_for_visreg <- as.data.frame(cbind(c(dep_and_healthy_groups_for_ICD_analysis$EMPI, dep_and_healthy_groups_for_ICD_analysis$EMPI), c(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]), c(rep(1,298), rep(2,298))))
names(df_for_visreg) <- c("EMPI", "prop_lost", "Diagnosis")
df_for_visreg$Diagnosis <- as.factor(df_for_visreg$Diagnosis)

plot <- ggplot(df_for_visreg, aes(x=Diagnosis, y = prop_lost, col=Diagnosis)) +
  ggtitle("Arcuate Fasciculus R") + 
 # geom_violin() + 
  geom_jitter(shape=16, position=position_jitter(0.05)) + 
  geom_boxplot(width=0.1) + theme_minimal() + 
  stat_summary(fun.y=median, geom="point", size=2, color="black") + 
  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed"))

print(plot)

### Plot OR_R	0.69024050
df_for_visreg <- as.data.frame(cbind(c(dep_and_healthy_groups_for_ICD_analysis$EMPI, dep_and_healthy_groups_for_ICD_analysis$EMPI), c(dep_and_healthy_groups_for_ICD_analysis$OR_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$OR_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]), c(rep(1,298), rep(2,298))))
names(df_for_visreg) <- c("EMPI", "prop_lost", "Diagnosis")
df_for_visreg$Diagnosis <- as.factor(df_for_visreg$Diagnosis)

plot <- ggplot(df_for_visreg, aes(x=Diagnosis, y = prop_lost, col=Diagnosis)) +
  ggtitle("Optic Radiation R") + 
 # geom_violin() + 
  geom_jitter(shape=16, position=position_jitter(0.05)) + 
  geom_boxplot(width=0.1) + theme_minimal() + 
  stat_summary(fun.y=median, geom="point", size=2, color="black") + 
  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed")) 
print(plot)

### grouped bar plot

Diagnosis <- c(rep("Depressed" , 2) , rep("Non-Depressed" , 2))
Fascicle <- rep(c("Depression Network (AF)" , "Region Outside Depression Network (C_PH)"), 2)
value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$C_PH_L[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]),
           mean(dep_and_healthy_groups_for_ICD_analysis$C_PH_L[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]))

sem <- c((sd(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==2))),
           (sd(dep_and_healthy_groups_for_ICD_analysis$C_PH_L[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==2))),
           (sd(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==1 ))),
          (sd(dep_and_healthy_groups_for_ICD_analysis$C_PH_L[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==1 ))))

data <- data.frame(Diagnosis,Fascicle,value, sem)
#data$Fascicle <- pretty_names

# Grouped
barplot <- ggplot(data, aes(fill=Diagnosis, y=value, x=Fascicle)) + 
    geom_bar(position="dodge", stat="identity") + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
  ylab("Proportion of Fascicles Affected") +
  theme(axis.text = element_text(size = 12, colour = "black"), axis.title.x = element_blank())

print(barplot)

# Grouped
barplot <- ggplot(data, aes(fill=Diagnosis, y=value, x=Fascicle)) + 
    geom_bar(position="dodge", stat="identity") + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
  ylab("Proportion of Fascicles Affected") +
  theme(axis.text = element_text(size = 12, colour = "black"), axis.title.x = element_blank())

print(barplot)

barplot2 <- ggplot(data, aes(fill=Diagnosis, y=value, x=Fascicle)) + 
    geom_bar(position="dodge", stat="identity", colour = "black", width=0.9,size=1.5) + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9), size=1) + 
    scale_fill_manual(values = c("#cdcdcd", "#FFFFFF", "#cdcdcd", "#FFFFFF")) + #comment out if you want colored graph

    ylab("Proportion of Fascicles Affected") +
    theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
          axis.title.y = element_text(size=20),
          axis.line = element_line(size = 1.5, colour = "black", linetype=1),
          panel.background = element_rect(colour = "white", fill = "white")) + #comment out if you want pretty graph
    scale_y_continuous(expand = c(0, 0), limits = c(0, 0.52)) #comment out if you want colored graph

print(barplot2)

```

```{r testing_whether_ms_disease_more_likely_in_depression_mask_unique}
### tests whether there is higher proportion of vertices lost in depression network versus not

dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
  mutate(total_fascicle_prop_lost_indepnet_10_percent =
           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
  mutate(total_fascicle_prop_lost_indepnet_5_percent =
           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
  mutate(total_fascicle_prop_lost_nondep_network =
           rowMeans(across(fascicle_names_nondep_network))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ### when I filter and remove fascicles where there was no loss at all, the depression vs healthy findings go away
#  filter(total_fascicle_prop_lost > 0) %>%
  ungroup()

#test whether there is differentially more volume loss in depression versus nondepression network
volume_lost_dep_vs_nondep_network_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network, var.equal = F) #mean dep_net = 35%, mean non_dep_net =  17%, p 2.2 x 10^-16

volume_lost_dep10_vs_nondep_network_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_10_percent,
dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network, var.equal = F) #mean dep net = 31%, mean non_dep_net = 17%, p 2.2 * 10^-16

volume_lost_dep5_vs_nondep_network_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_5_percent,
dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network, var.equal = F) #mean dep net = 30%, mean non_dep_net = 17%, p 2.2 * 10^-16

#df for visreg - actually not using visreg. Just a nice way to see that there is significantly more loss in depression network versus outside depression network
df_for_visreg <- as.data.frame(cbind(c(dep_and_healthy_groups_for_ICD_analysis$EMPI, dep_and_healthy_groups_for_ICD_analysis$EMPI), c(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network), c(rep(1,298), rep(2,298))))
names(df_for_visreg) <- c("EMPI", "prop_lost", "network")
df_for_visreg$network <- as.factor(df_for_visreg$network)

plot <- ggplot(df_for_visreg, aes(x=network, y = prop_lost, col=network)) +
  geom_violin() + 
  geom_jitter(shape=16, position=position_jitter(0.05)) + 
  geom_boxplot(width=0.1) + theme_minimal() + 
  stat_summary(fun.y=median, geom="point", size=2, color="red") + 
  scale_x_discrete(labels=c("1" = "Depression Network", "2" = "Non-Depression Network")) + 
  ylab("Proportion of Fascicles Affected") + 
  theme(axis.text =element_text(size=14), axis.title.x = element_blank())

print(plot)

########## Bar plot
Network <- c("Depression Network","Non-Depression Network")
value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet),
           mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network))

sem <- c((sd(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet)/sqrt(dim(dep_and_healthy_groups_for_ICD_analysis)[1])),
           (sd(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network)/sqrt(dim(dep_and_healthy_groups_for_ICD_analysis)[1])))

data <- data.frame(Network,value,sem)
#data$Fascicle <- pretty_names

# Grouped
barplot <- ggplot(data, aes(x=Network,fill=Network, y=value)) + 
  geom_bar(stat="identity", position=position_dodge(0.9)) + 
  geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
  ylab("Proportion of Fascicles Affected") +
  ylim(0,0.5) +
  theme(axis.text = element_text(size = 12, colour = "black"))

print(barplot)
# Black and white
barplot <- ggplot(data, aes(x=Network,fill=Network, y=value)) + 
  geom_bar(stat="identity", colour="black", width=0.8, size=1.5) + 
  geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9), size=1.5) +
  scale_fill_manual(values = c("#cdcdcd", "#FFFFFF")) + #comment out if you want colored graph
  ylab("Proportion of Fascicles Affected") +
  theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=20),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        panel.background = element_rect(colour = "white", fill = "white")) + #comment out if you want pretty 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.52)) #comment out if you want colored graph

print(barplot)

###### Depression network x depression group interaction - It is there, depression always worse. 
#these lms largely match up with the t.tests above. Sig differences between depressed (more disease) within and outside of mask

loss_in_dep_network <- lm(total_fascicle_prop_lost_indepnet~depGroupVar, data = dep_and_healthy_groups_for_ICD_analysis) #non sig, p = 0.061
loss_in_dep_network_10_percent <- lm(total_fascicle_prop_lost_indepnet_10_percent~depGroupVar, data = dep_and_healthy_groups_for_ICD_analysis) #p = 0.0492
loss_in_nondep_network <- lm(total_fascicle_prop_lost_nondep_network~depGroupVar, data = dep_and_healthy_groups_for_ICD_analysis) #p=0.037
```

```{r phq9_correlation_fascicles}

####### NOTHING SIGNIFICANT!!!! ########3
#isolate out only the depressed group and healthy group
with_phq9 <- df_demo_and_fascicles %>%
  filter(depGroupVar != 0) %>%
  filter(!is.na(PHQ.9)) %>%
  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
  mutate(total_fascicle_prop_lost_indepnet_10_percent =
           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
  mutate(total_fascicle_prop_lost_indepnet_5_percent =
           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
  mutate(total_fascicle_prop_lost_nondep_network =
           rowMeans(across(fascicle_names_nondep_network))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

#lm
fascicle_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PHQ.9, list(i = as.name(x))), data = with_phq9)
})
names(fascicle_lm) <- fascicle_names

#anova
fascicle_anova <- lapply(fascicle_lm, anova)

#fdr corrected
fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
print(fascicle_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#fdr corrected only dep network
fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
fascicle_anova_fdr<- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr)

#fdr corrected only dep 10% mask
fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$inDepNetwork_vector == 2)]
fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr)

#uncorrected
fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
fascicle_anova_p05_unc <- fascicle_anova_p[!is.na(fascicle_anova_p) & fascicle_anova_p < 0.05]
print(fascicle_anova_p05_unc)

######### overall fascicle proportion affected - nothing is significant
overall_prop_affected <- lm(total_fascicle_prop_lost~PHQ.9, data=with_phq9)
overall_prop_affected_depnet <- lm(total_fascicle_prop_lost_indepnet~PHQ.9, data=with_phq9)
overall_prop_affected_depnet_10percent <- lm(total_fascicle_prop_lost_indepnet_10_percent~PHQ.9, data=with_phq9)
overall_prop_affected_depnet_5percent <- lm(total_fascicle_prop_lost_indepnet_5_percent~PHQ.9, data=with_phq9)
overall_prop_affected_nondep <- lm(total_fascicle_prop_lost_nondep_network~PHQ.9, data=with_phq9)
```

```{r phq9_regressions_just_dep_group}
##### NOTHING SIGNIFICANT ########
##################################
## Just within depression group ##
##################################
#isolate out only the depressed group and healthy group
with_phq9 <- df_demo_and_fascicles %>%
  filter(depGroupVar == 2) %>%
  filter(!is.na(PHQ.9)) %>%
  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
  mutate(total_fascicle_prop_lost_indepnet_10_percent =
           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
  mutate(total_fascicle_prop_lost_indepnet_5_percent =
           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
  mutate(total_fascicle_prop_lost_nondep_network =
           rowMeans(across(fascicle_names_nondep_network))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()
#lm
fascicle_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PHQ.9, list(i = as.name(x))), data = with_phq9)
})
names(fascicle_lm) <- fascicle_names

#anova
fascicle_anova <- lapply(fascicle_lm, anova)

#fdr corrected
fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
print(fascicle_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#fdr corrected only dep network
fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
fascicle_anova_fdr<- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr)

#fdr corrected only dep 10% mask
fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$inDepNetwork_vector == 2)]
fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr)

#uncorrected
fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
fascicle_anova_p05_unc <- fascicle_anova_p[!is.na(fascicle_anova_p) & fascicle_anova_p < 0.05]
print(fascicle_anova_p05_unc)

######### overall fascicle proportion affected - nothing is significant
overall_prop_affected <- lm(total_fascicle_prop_lost~PHQ.9, data=with_phq9)
overall_prop_affected_depnet <- lm(total_fascicle_prop_lost_indepnet~PHQ.9, data=with_phq9)
overall_prop_affected_depnet_10percent <- lm(total_fascicle_prop_lost_indepnet_10_percent~PHQ.9, data=with_phq9)
overall_prop_affected_depnet_5percent <- lm(total_fascicle_prop_lost_indepnet_5_percent~PHQ.9, data=with_phq9)
overall_prop_affected_nondep <- lm(total_fascicle_prop_lost_nondep_network~PHQ.9, data=with_phq9)

#visreg
#sapply(fascicle_lm, visreg)
```
All the mixed models are below
```{r age_effects_indiv_fascicles_mm}

### This subscript compares proportion of fascicles lost across age for each fascicle of the 80+. Looks lonly at the people in the depressed versus healthy group. Importantly, I ran this looking at everyone, at the results are the same.
### Separately considers findings just within the association cortex

#isolate out only the depressed group and healthy group
df_mm <- df_demo_and_fascicles %>% filter(depGroupVar != 0)
#n depressed = 859, healthy = 604, total n = 1463

#lm
fascicle_lm_mm <- lapply(fascicle_names, function(x) 
{
  lmerTest::lmer(substitute(i ~ PAT_AGE_AT_EXAM + (1 | EMPI), list(i = as.name(x))), data = df_mm)
})
names(fascicle_lm_mm) <- fascicle_names

#anova
fascicle_anova_mm <- lapply(fascicle_lm_mm, anova)

#fdr corrected
fascicle_anova_mm_fdr <- fdr_anova_generic(fascicle_anova_mm, 1)
print(fascicle_anova_mm_fdr)#anova values < 0.05, uncorrected

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#fdr corrected only dep network
fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#fdr corrected only dep network 10%
fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$inDepNetwork_vector == 2)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_anova_mm_p <- sapply(fascicle_anova_mm, function(v) v$"Pr(>F)"[1])
fascicle_anova_mm_p05_unc <- as.data.frame(fascicle_anova_mm_p[fascicle_anova_mm_p < 0.05])
print(fascicle_anova_mm_p05_unc)

```

```{r sex_effects_fascicles_mm}
########### sex effect whole group

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% filter(depGroupVar != 0) 
#healthhy = 713, total n = 1106

#### sex histo ###
hist(dep_and_healthy_groups_for_ICD_analysis$sex_binarized,
main = paste0("Sex In Good Mimosa Group : n (M/F)= ", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1), "/", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)),  xlab = "Sex", breaks = 2)

#lm
fascicle_sex_lm <- lapply(fascicle_names, function(x) 
{
  lmerTest::lmer(substitute(i ~ osex + (1|EMPI), list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_sex_lm) <- fascicle_names

#anova
fascicle_sex_anova <- lapply(fascicle_sex_lm, anova)

#fdr corrected
fascicle_sex_anova_fdr <- fdr_anova_generic(fascicle_sex_anova, 1)
print(fascicle_sex_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#visreg
#sapply(fascicle_sex_lm,visreg)
```

```{r depressed_versus_healthy_indiv_fascicles_mm}

### This subscript compares proportion of fascicles lost for each fascicle of the 80+ between those in the depressed and the clean healthy group. Done as both a mixed model as well as using unique individuals alone.

#Of note, adding age into this model makes things WORSE

### Separately considers findings just within the association cortex
#isolate out only the depressed group and healthy group
df_mm <- df_demo_and_fascicles %>% filter(depGroupVar != 0)
#n depressed = 859, healthy = 604, total n = 1463

#lm
fascicle_lm_mm <- lapply(fascicle_names, function(x) 
{
  lmerTest::lmer(substitute(i ~ depGroupVar + (1 | EMPI), list(i = as.name(x))), data = df_mm)
})
names(fascicle_lm_mm) <- fascicle_names

#anova
fascicle_anova_mm <- lapply(fascicle_lm_mm, anova)

#fdr corrected
fascicle_anova_mm_fdr <- fdr_anova_generic(fascicle_anova_mm, 1)
print(fascicle_anova_mm_fdr)#anova values < 0.05, uncorrected

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#fdr corrected only dep network
fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#fdr corrected only dep network 10%
fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$inDepNetwork_vector == 2)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_anova_mm_p <- sapply(fascicle_anova_mm, function(v) v$"Pr(>F)"[1])
fascicle_anova_mm_p05_unc <- as.data.frame(fascicle_anova_mm_p[fascicle_anova_mm_p < 0.05])
print(fascicle_anova_mm_p05_unc)

```

Lastly, this section will explore interactions (age * dep), (sex * dep)

```{r age_by_depression_unique}

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>%
  filter(depGroupVar != 0)  %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

#lm
fascicle_agedep_lm <- lapply(fascicle_names, function(x) 
{
   lm(substitute(i ~ PAT_AGE_AT_EXAM*depGroupVar, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
# lm(substitute(i ~ depGroupVar + PAT_AGE_AT_EXAM + osex, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_agedep_lm) <- fascicle_names

#anova
fascicle_agedep_anova <- lapply(fascicle_agedep_lm, anova)

#fdr corrected - depression alone
fascicle_agedep_anova_fdr <- fdr_anova_generic(fascicle_agedep_anova, 2)
print(fascicle_agedep_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_agedep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,2)
print(fascicle_anova_fdr_association)

#fdr corrected - interaction
fascicle_agedep_anova_fdr <- fdr_anova_generic(fascicle_agedep_anova, 3)
print(fascicle_agedep_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_agedep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
print(fascicle_anova_fdr_association)

#fdr corrected only dep network
fascicle_anova_w_fiber_mapping <- fascicle_agedep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
print(fascicle_anova_fdr_association)

#fdr corrected only dep network 10%
fascicle_anova_w_fiber_mapping <- fascicle_agedep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector == 2)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_anova_p <- sapply(fascicle_agedep_anova, function(v) v$"Pr(>F)"[3])
fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
print(fascicle_anova_p05_unc)
```

```{r sex_by_depression_unique}

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>%
  filter(depGroupVar != 0)  %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

#lm
fascicle_sexdep_lm <- lapply(fascicle_names, function(x) 
{
   lm(substitute(i ~ osex*depGroupVar, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)

})
names(fascicle_sexdep_lm) <- fascicle_names

#anova
fascicle_sexdep_anova <- lapply(fascicle_sexdep_lm, anova)

#fdr corrected - depression alone
fascicle_sexdep_anova_fdr <- fdr_anova_generic(fascicle_sexdep_anova, 2)
print(fascicle_sexdep_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,2)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_anova_p <- sapply(fascicle_sexdep_anova, function(v) v$"Pr(>F)"[2])
fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
print(fascicle_anova_p05_unc)

#fdr corrected - interaction
fascicle_sexdep_anova_fdr <- fdr_anova_generic(fascicle_sexdep_anova, 3)
print(fascicle_sexdep_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
print(fascicle_anova_fdr_association)

#fdr corrected only dep network
fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
print(fascicle_anova_fdr_association)

#fdr corrected only dep network 10%
fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector == 2)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_anova_p <- sapply(fascicle_sexdep_anova, function(v) v$"Pr(>F)"[3])
fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
print(fascicle_anova_p05_unc)
```
Interaction models below

```{r sexdep_effects_fascicles_unique}

### Trying to figure out if there are any sex * depression effects, covarying for age given that men tend to get worse over time. dep*sex uncorrected in SLF1_L and CNVIII_R p< 0.05)

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% filter(depGroupVar != 0)  %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

#### sex histo ###
hist(dep_and_healthy_groups_for_ICD_analysis$sex_binarized,
main = paste0("Sex In Good Mimosa Group : n (M/F)= ", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1), "/", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)),  xlab = "Sex", breaks = 2)

#lm
fascicle_sexdep_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ depGroupVar*osex + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_sexdep_lm) <- fascicle_names

#anova
fascicle_sexdep_anova <- lapply(fascicle_sexdep_lm, anova)

##### depGroupVar ####
### 12 areas, nearly identical to reg model

#fdr corrected
fascicle_sexdep_anova_fdr <- fdr_anova_generic(fascicle_sexdep_anova, 1)
print(fascicle_sexdep_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_sexdep_anova_p <- sapply(fascicle_sexdep_anova, function(v) v$"Pr(>F)"[1])
fascicle_sexdep_anova_p05_unc <- as.data.frame(fascicle_sexdep_anova_p[fascicle_sexdep_anova_p < 0.05])
print(fascicle_sexdep_anova_p05_unc) ### CNVIII p < 0.05

##### sex differences ####
## same as above, just add in CNVIII_R

#fdr corrected
fascicle_sexdep_anova_fdr <- fdr_anova_generic(fascicle_sexdep_anova, 2)
print(fascicle_sexdep_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,2)
print(fascicle_anova_fdr_association)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,2)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_sexdep_anova_p <- sapply(fascicle_sexdep_anova, function(v) v$"Pr(>F)"[2])
fascicle_sexdep_anova_p05_unc <- as.data.frame(fascicle_sexdep_anova_p[fascicle_sexdep_anova_p < 0.05])
print(fascicle_sexdep_anova_p05_unc) ### CNVIII p < 0.05

#######interaction ####

### SLF1_L and CNVIII_R

#fdr corrected interaction
fascicle_sexdep_anova_fdr <- fdr_anova_generic(fascicle_sexdep_anova, 4)
print(fascicle_sexdep_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,4)
print(fascicle_anova_fdr_association)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,4)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_sexdep_anova_p <- sapply(fascicle_sexdep_anova, function(v) v$"Pr(>F)"[4])
fascicle_sexdep_anova_p05_unc <- as.data.frame(fascicle_sexdep_anova_p[fascicle_sexdep_anova_p < 0.05])
print(fascicle_sexdep_anova_p05_unc) #p uncorrected slf1_L p = 0.0488, CNVIII_R 0.01)

### grouped bar and line plot

Diagnosis <- c(rep("Depressed" , 2) , rep("Non-Depressed" , 2))
Sex <- rep(c("Male" , "Female"), 2)
value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)]),
           mean(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)]),
           mean(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)]),
           mean(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)]))

sem <- c((sd(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)])/sqrt(sum((dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)))),
         (sd(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)])/sqrt(sum((dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)))),
         (sd(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)])/sqrt(sum((dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)))),
         (sd(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)])/sqrt(sum((dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)))))

data <- data.frame(Diagnosis,Sex,value, sem)
#data$Fascicle <- pretty_names

# Grouped
barplot <- ggplot(data, aes(fill=Sex, y=value, x=Diagnosis)) + 
    geom_bar(position="dodge", stat="identity") + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
  ylab("Proportion of SLF Affected") +
  theme(axis.text = element_text(size = 12, colour = "black"), axis.title.x = element_blank())

print(barplot)

lineplot <- ggplot(data=data, aes(fill=Sex, y=value, x=Diagnosis, group = Sex)) +

    geom_line(aes(color=Sex, size=0.9)) +
    geom_point(aes(color=Sex, size=0.9)) +
    ylim(0.05,0.30)+
    ylab("Proportion of SLF Affected") +
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1) + 
    theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank())

print(lineplot)

```

### 2024-05-24 scripts/clean_dac_pull_icd10_codes_and_make_clean_df.R

@@ -1,0 +1,154 @@
+### Clean data frame up
+
+##pre: dac pulls from 2023 with full psychiatric ICD10 codes
+##post: rds that contains beautifully curated all_icd10_dx column. 
+## uses: Takes the dac pull, combines csvs, adds column with beautifully curated icd10 codes
+## dependencies: dplyr
+
+library(dplyr)
+
+
+######################
+## FUNCTIONS #########
+######################
+####Extract unique ICD10 codes
+### takes an empi, returns all the unique diagnostic codes.
+### steps: 1) filter data frame by EMPI; 2) separate into 1 column per diagnosis; 3) remove doubles; 4) combine/paste into 1 column separated by semicolons; 5) return
+get_all_unique_ICD10_diagnoses <- function(indiv_empi) {
+  data_frame<-data_pull
+  all_unique_diagnoses <- data_frame %>% 
+    filter(str_detect(EMPI, indiv_empi)) %>% 
+    dplyr::select(ICD10) %>%
+    separate_rows(ICD10, sep = ";") %>%
+    summarize(all_icd_codes = paste(unique(ICD10), collapse = ";"))
+  print(all_unique_diagnoses$all_icd_codes)
+  return(all_unique_diagnoses$all_icd_codes)
+}
+
+
+######################
+## CODE ##############
+######################
+
+#this goes through dac pulls, combines them, cleans them, and saves them as rds that can be loaded in other analyses. To clean up. 
+
+#############################################################################################################################
+### ***** MUST CHANGE THE HOMEDIR  AND THE PATHS TO DATA AND OUTPUT IN ORDER FOR THIS TO WORK ON A NEW PULL> THIS IS REALLY IMPORTANT ###
+#############################################################################################################################
+
+homedir <- "/Users/eballer/BBL/msanxiety/"
+
+#data from dac pull with full icd10 lists
[…]

### 2024-05-24 scripts/ms_functions.R

@@ -1,0 +1,1431 @@
+require('visreg')
+require('mgcv')
+require('tableone')
+require('dplyr')
+require('plm')
+require('MatchIt')
+require('tidyr')
+require('ggplot2')
+require('reshape')
+require('emmeans')
+require('cowplot')
+require('stringr')
+require('visreg')
+require('rasterVis')
+require('lattice')
+require('circlize')
+## set directories ##
+#local_wkdir <- '~/Google Drive/TDSlab/SCZ_gene_imaging/'
+#remote_wkdir <- '~/Desktop/BBL/data/joy/BBL/studies/pnc/'
+
+#############################
+###Make Demographics Table###
+#############################
+
+#############################
+####### Demographics ########
+#############################
+
+
+#######Matched group all clusters ##############
+make_demographics_table_ms_Hydra_k2<- function(data_frame) {
+  #subset demographics
+  
+  listVars <- c("Race", 
+                "Sex",
+                "Age",
+                "Depression",
+                "Hydra_k2",
+                "PHQ2",
+                "PHQ9",
+                "Has.depdx", 
+                "On.Antidepressants",
+                "on_anti_cd20",
+                "on_interferon",
+                "on_steroids",
+                "on_dmt",
+                "number_of_dx",
+                "number_of_dx_extended",
+                "number_of_psychiatric_comorbidities_extended",
+                "number_of_anxiety_comorbidities_extended",
+                "number_of_medications",
+                "on_bcp",
+                "volume_of_mimosa_lesions", 
+                "sum_fascicle_vol_lost",
+                "proportion_volume_lost_per_total_network_size_sum",
+                "sum_fascicle_vol_lost_indepnet_top_quartile", 
+                "proportion_volume_lost_dep_net_by_network_size_sum",
+                "sum_fascicle_vol_lost_nondep_bottom_3_quartiles", 
+                "proportion_volume_lost_nondep_net_by_network_size_sum") #Race 1 = caucasian, Sex 1 = M age = years
+
+  #for_parse <- paste0("data.frame(data_frame$race_binarized, data_frame$sex_binarized, data_frame$PAT_AGE_AT_EXAM, data_frame$depGroupVar, data_frame$PHQ.2, data_frame$PHQ.9)")
[…]

### 2024-05-24 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
Add files via upload

@@
 
-```{r read_in_df_and_subset}
+```{r read_in_df}
 homedir <- "/Users/eballer/BBL/msanxiety/"
-columns_to_make_integer <- c("ACCESSION_NUM", "PAT_AGE_AT_EXAM","MRI_ENC_AGE","CURRENT_AGE","hemoglobin", "WBC","RBC","B12","FOLATE", "TSH", "RPR","CSFAPPEAR1","CSFAPPEAR4","CSFCOLOR1",       "CSFCOLOR4","CSFTUBE","CSFTUBE4","PHQ.2","PHQ.9") #removed "VitD", not in new pull for some reason
 
@@
 data_2023_pull <- readRDS(paste0(homedir, "/data/data_2023_pull_with_curated_icd10_codes.rds"))
-
-#Get med info in
-#read in BCP info, names of meds, est and prog and doses
-bcp <- read.csv("/Users/eballer/BBL/medication_data/BCP_est_and_prog_levels_and_doses_all_brands.csv", sep = ",", header = TRUE)
-bcp$bcp_name <- toupper(bcp$bcp_name)
-
-#read in ms med info, names of meds, mechanism, and whether or not dmt
-msmeds <- read.csv("/Users/eballer/BBL/medication_data/ms_medications_brand_and_generic.csv", sep = ",", header = TRUE)
-msmeds$Medication <- toupper(msmeds$Medication)
-
-#depression/psych meds from NAMI website 
-psych_meds <- read.csv("/Users/eballer/BBL/medication_data/nami_psych_meds_antidepressants.csv", sep = ",", header = TRUE)
-psych_meds$Medication.Name <- toupper(psych_meds$Medication.Name)
-
-#anxiety meds from chatgpt (cross referenced with psych meds)
-anxiety_meds <- read.csv("/Users/eballer/BBL/medication_data/antianxiety_medications.csv", sep = ",", header = TRUE)
-anxiety_meds$Medication <- toupper(anxiety_meds$Medication)
-anxiety_meds_no_beta_blocker <- anxiety_meds %>% filter(Class != "Beta_blocker")
-
-##########################
-### some preprocessing ###
-##########################
-#we need to keep scans from people seen by an MS provider (n = 17067) who have an MS diagnostic code (n=16,830)
-#we make a bunch of columns from character to integer, binarize sex and race, and put date into a nice format YYYYMMDD, the %m%d%y indicates what it started out as
-
-#goal is to keep people who were seen by 
- data_empi_acc_f_phq <-data_2023_pull %>% 
-   mutate(across(.cols = columns_to_make_integer, .fns = as.integer)) %>%
-   mutate(sex_binarized = ifelse(SEX == "MALE", 1, 2)) %>%
-   mutate(osex = ordered(sex_binarized,levels = c(1,2), labels = c("Male","Female"))) %>%
-   mutate(race_binarized = ifelse(RACE == "WHITE", 1, 2)) %>%
-   mutate(orace = ordered(race_binarized,levels = c(1,2), labels = c("White","Non-white"))) %>%
-   mutate(EXAM_DATE = as.Date(BEGIN_EXAM_DTTM, format = "%m/%d/%y")) %>% 
-   mutate(EXAM_DATE = gsub(EXAM_DATE, pattern = "-", replacement = "")) %>%
-   mutate(BEGIN_EXAM_DTTM = as.Date(BEGIN_EXAM_DTTM, format = "%m/%d/%y")) %>% #make sure to actually save it as date object for later processing
-   mutate(EMPI = as.factor(EMPI)) %>%
-   mutate(number_of_dx = ifelse(!is.na(ICD10), (str_count(ICD10, ";") + 1), 0)) %>%
-   mutate(number_of_dx_extended = ifelse(!is.na(all_icd10_dx), str_count(all_icd10_dx, ";") + 1, 0)) %>%
-   mutate(number_of_psychiatric_comorbidities_extended = ifelse(!is.na(all_icd10_dx), str_count(all_icd10_dx, "F"), 0)) %>%
-   mutate(number_of_anxiety_comorbidities_extended = ifelse(!is.na(all_icd10_dx), str_count(all_icd10_dx, "F4"), 0)) %>%
-   mutate(number_of_depression_comorbidities_extended = ifelse(!is.na(all_icd10_dx), str_count(all_icd10_dx, "F3"), 0)) %>%
-   mutate(number_of_medications = ifelse(!is.na(Medication), str_count(Medication, ";") + 1, 0)) %>%
-   mutate(On.Bcp = ifelse(str_detect(Medication, paste(bcp$bcp_name, collapse = "|")), 1, 0)) %>%
-   mutate(On.Psych.Meds = ifelse(str_detect(Medication, paste(psych_meds$Medication, collapse = "|")), 1, 0)) %>%
-   mutate(On.Antidepressants = ifelse(str_detect(Medication, paste(psych_meds$Medication[psych_meds$Antidepressant == "t"], collapse = "|")), 1, 0)) %>%
-   mutate(On.Anxiolytics = ifelse(str_detect(Medication, paste(anxiety_meds$Medication, collapse = "|")), 1, 0)) %>%
-   mutate(On.Anxiolytics_no_beta_blocker = ifelse(str_detect(Medication, paste(anxiety_meds_no_beta_blocker$Medication, collapse = "|")), 1, 0)) %>%
-   mutate(On.Benzos = ifelse(str_detect(Medication, paste(anxiety_meds$Medication[anxiety_meds$Class == "Benzodiazepine"], collapse = "|")), 1, 0)) %>%
-   mutate(On.Anti_cd20 = ifelse(str_detect(Medication, paste(msmeds$Medication[msmeds$Mechanism == "anti-cd20"], collapse = "|")), 1, 0)) %>%
-   mutate(On.Interferon = ifelse(str_detect(Medication, paste(msmeds$Medication[msmeds$Mechanism == "Interferon"], collapse = "|")), 1, 0)) %>%
-   mutate(On.Steroids = ifelse(str_detect(Medication, paste(msmeds$Medication[msmeds$Mechanism == "Steroid"], collapse = "|")), 1, 0)) %>%
-   mutate(On.Dmt = ifelse(str_detect(Medication, paste(msmeds$Medication[msmeds$DMT == "y"], collapse = "|")), 1, 0)) %>%
-   mutate(Has.PHQ2 = ifelse(PHQ.2 != "NULL", 1, 0)) %>%
-   mutate(Has.PHQ9 = ifelse(PHQ.9 != "NULL", 1, 0)) %>%
-   mutate(Has.depdx = ifelse(grepl("F3", all_icd10_dx), 1, 0)) %>%
-   mutate(Has.anxietydx = ifelse(grepl("F4", all_icd10_dx), 1, 0)) %>%
-   mutate(Has.depANDanx.dx = ifelse(Has.depdx & Has.anxietydx, 1, 0)) %>%
-   mutate(PHQ.2_modsev_dep_sxs = ifelse(Has.PHQ2 & PHQ.2 >= 3, 1, 0)) %>%
-   mutate(PHQ.9_modsev_dep_sxs = ifelse(Has.PHQ9 & PHQ.9 >= 10, 1, 0)) %>%
-   mutate(PHQ.2_mild_dep_sxs = ifelse(Has.PHQ2 & PHQ.2 > 0 & PHQ.2 < 3, 1, 0)) %>%
-   mutate(PHQ.9_mild_dep_sxs = ifelse(Has.PHQ9 & PHQ.9 > 0 & PHQ.9 < 10, 1, 0)) %>%
-   mutate(PHQ.2_zero = ifelse(Has.PHQ2 & PHQ.2 == 0, 1, 0)) %>%
-   mutate(PHQ.9_zero = ifelse(Has.PHQ9 & PHQ.9 == 0, 1, 0)) %>%
-   mutate(dep_by_dx_phq = ifelse((Has.depdx | PHQ.2_modsev_dep_sxs | PHQ.9_modsev_dep_sxs),1,0)) %>%
-   mutate(dep_by_dx_phq_antidep = ifelse((Has.depdx | On.Antidepressants | PHQ.2_modsev_dep_sxs | PHQ.9_modsev_dep_sxs),1,0)) %>%
-   mutate(true_healthy = ifelse((!Has.depdx & !On.Psych.Meds & (PHQ.2_zero | PHQ.9_zero)), 1, 0)) %>%
-   mutate(dep_by_dx_phq_meds_healthy_phq0_no_psych_meds = ifelse(dep_by_dx_phq_antidep | true_healthy, 1, 0)) %>%
-   rowwise(ACCESSION_NUM) %>%
-   mutate(depGroupVar =
-            sum(c(dep_by_dx_phq_meds_healthy_phq0_no_psych_meds,dep_by_dx_phq_antidep))) %>%#you get an extra point if you are in the depression group, so the end result is dep = 2, healthy = 1, 0 for exclude
-   ungroup() #n=3,737 unique people, n= 16,830 total
-
+```
+
+```{r read_in_mimosa_qc}
+#This section checks how many unique individuals had QA data, and then how many met MIMoSA QC. Some additional people lost at registration.
+
+#1 Total unique individuals who also have MS - 890
+#2 Total unique who had good MIMoSA - 786
+#3 Total unique with bad MIMoSA - 890-786 = 104
+#4 Total lost in streamline filtering - 3
+#5 Final N going into inclusion/exclusion - 783
+
+#read in mimosa data
+mimosa_qc <- read.csv("/Users/eballer/BBL/msdepression/data/melissa_martin_files/csv/mimosa_dataframe", sep = ",", header = FALSE) #n=2840
+
+#preprocess data frame to extract dates, empis, and score
+empis_with_qc <- mimosa_qc %>% 
+  mutate(EMPI = as.factor(gsub(x = V5, pattern = ".*sub-(.*)/ses-.*/.*", replacement="\\1", perl = TRUE))) %>%
+  mutate(EXAM_DATE = gsub(x=V5, pattern = ".*/ses-(.{8})/.*", replacement = "\\1\\2\\3")) %>% 
+  mutate(score = V3)
+
+#merge with whole data frame to make sure we exclude people w/out MS
+mimosa_qc_df <- merge(data_2023_pull, empis_with_qc, by = c("EMPI", "EXAM_DATE")) #n = 3592
+
+#get list of unique patients, n = 890
+mimosa_qc_unique <- mimosa_qc_df %>%
+  group_by(EMPI) %>%
+  arrange(EXAM_DATE) %>%
+  slice(1) %>%
+  ungroup #n=890
+
+#get list of unique patients with good QC, n = 867
+mimosa_unique_score_gre_75 <- mimosa_qc_unique %>%
+  filter(score >= 75) %>%
+  group_by(EMPI) %>%
+  arrange(EXAM_DATE) %>%
+  mutate(EXAM_DATA = as.character(EXAM_DATE)) %>%
+  mutate(EMPI = as.character(EMPI)) %>%
+  dplyr::select(EMPI, EXAM_DATE, score) %>%
+  slice(1) %>%
+  ungroup #n=786
+```
+
+```{r merge_df_with_mimosa}
+
+#n=867
+df_people_with_good_mimosa <- data_2023_pull %>% 
+  group_by(EMPI, EXAM_DATE) %>%
+  slice(1) %>%
+  left_join(mimosa_unique_score_gre_75, by = c("EMPI", "EXAM_DATE")) %>%
+  filter(!is.na(score))
+```
+
+```{r read_in_fascicle_info}
 ##########################################################
@@
 
-fascicle_proportions <- read.csv(paste0(homedir, "/results/fascicle_volumes_all_subjects_roi_n2336.csv"), header = T, sep = ",") #n = 2336
+fascicle_proportions <- read.csv(paste0("/Users/eballer/BBL/msdepression//results/fascicle_volumes_all_subjects_roi_n2336.csv"), header = T, sep = ",") #n = 2336
+fascicle_proportions <- fascicle_proportions %>%
+  mutate(EMPI = as.character(EMPI)) %>%
+  mutate(EXAM_DATE = as.character(EXAM_DATE))
 
@@
 
-write.table(fascicle_names,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names.csv", row.names = F, quote = F, col.names = F)
+fascicle_names_no_cranial_nerves <- fascicle_names[grep("CN", fascicle_names, invert = TRUE)] #n=77, drop cranial nerves
+
+#write.table(fascicle_names,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names.csv", row.names = F, quote = F, col.names = F)
 
@@
 ########
-fascicle_volumes_dep <- read.csv(paste0(homedir, "results/streamline_volume_within_dep_network.csv"), header = T, sep = ",")
+fascicle_volumes_dep <- read.csv("/Users/eballer/BBL/msdepression/results/streamline_volume_within_dep_network.csv", header = T, sep = ",")
 
@@
 
-write.table(fascicle_volumes_dep_network, paste0(homedir,  "/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_grouping.csv"), sep = ",", col.names=T)#, row.names = F, quote = F, col.names = T)
+#write.table(fascicle_volumes_dep_network, paste0(homedir,  "/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_grouping.csv"), sep = ",", col.names=T)#, row.names = F, quote = F, col.names = T)
 
@@
 fascicle_names_dep_network_all <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask > 0)]
-
-#fascicle_names_dep_network_all <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask == 1)]
-#write.table(fascicle_names_dep_network_all,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_all.csv", row.names = F, quote = F, col.names = F)
-
-fascicle_names_dep_network_10_percent <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask == 2)] #n=15
-#write.table(fascicle_names_dep_network_10_percent,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_10_percent.csv", row.names = F, quote = F, col.names = F)
-
-fascicle_names_dep_network_5_percent <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$prop_in_mask >= 0.05)] #n=24
 
@@
 ##########################################################
-df_demo_and_fascicles <- merge(data_empi_acc_f_phq, fascicle_proportions, by = c("EMPI", "EXAM_DATE")) #n = 2962
-
+
+ #n = 823
+df_demo_and_fascicles <- df_people_with_good_mimosa %>% 
+  left_join(fascicle_proportions, by = c("EMPI", "EXAM_DATE")) %>%
+  filter(!is.na(Has.MS.Provider))
+
+```
+
+#Compare disease burden by anxiety comorbidity
+```{r compare_disease_burden_by_anxiety_comorbidity}
+
+#lm
+fascicle_number_of_anxiety_dx_lm <- lapply(fascicle_names_no_cranial_nerves, function(x) 
+{
+  lm(substitute(i ~ number_of_anxiety_comorbidities_extended, list(i = as.name(x))), data = df_demo_and_fascicles)
+})
+names(fascicle_number_of_anxiety_dx_lm) <- fascicle_names_no_cranial_nerves
+fascicle_number_of_anxiety_dx_anova <- lapply(fascicle_number_of_anxiety_dx_lm, anova)
+
+#fdr corrected
+fascicle_number_of_anxiety_dx_anova_fdr <- fdr_anova_generic(fascicle_number_of_anxiety_dx_anova, 1)
+print(fascicle_number_of_anxiety_dx_anova_fdr)
+
+```
+#Has depression AND anxiety diagnoses
+```{r compare_disease_burden_by_dep_AND_anxiety_comorbidity}
+
+#lm
+fascicle_depANDanx_dx_lm <- lapply(fascicle_names_no_cranial_nerves, function(x) 
+{
+  lm(substitute(i ~ Has.depANDanx.dx, list(i = as.name(x))), data = df_demo_and_fascicles)
+})
+names(fascicle_depANDanx_dx_lm) <- fascicle_names_no_cranial_nerves
+fascicle_depANDanx_dx_anova <- lapply(fascicle_depANDanx_dx_lm, anova)
+
+#fdr corrected
+fascicle_depANDanx_dx_anova_fdr <- fdr_anova_generic(fascicle_depANDanx_dx_anova, 1)
+print(fascicle_depANDanx_dx_anova_fdr)
+
+```
+
+#compare disease burden by psychiatric comorbidity
+```{r compare_disease_burden_between_anxiety_and_no_psych_dx}
+
+#lm
+fascicle_number_of_psychiatric_dx_lm <- lapply(fascicle_names_no_cranial_nerves, function(x) 
+{
+  lm(substitute(i ~ number_of_psychiatric_comorbidities_extended, list(i = as.name(x))), data = df_demo_and_fascicles)
+})
+names(fascicle_number_of_psychiatric_dx_lm) <- fascicle_names_no_cranial_nerves
+
+fascicle_number_of_psychiatric_dx_anova <- lapply(fascicle_number_of_psychiatric_dx_lm, anova)
+
+#fdr corrected
+fascicle_number_of_psychiatric_dx_anova_fdr <- fdr_anova_generic(fascicle_number_of_psychiatric_dx_anova, 1)
+print(fascicle_number_of_psychiatric_dx_anova_fdr)
+```
+
+# Yeo network analysis attempts
+###Read in fascicle info
+```{r read_in_fascicle_info}
 ##########################################################
-#                 Histos                        #
+#             Read in Fascicle info             #
 ##########################################################
-##### Histograms for PHQ2/9 healthy and depressed
-
-hist(df_demo_and_fascicles$PHQ.2[which(!is.na(df_demo_and_fascicles$PHQ.2))], main = paste0("PHQ-2 In Good Mimosa Group : n = ", length(which(!is.na(df_demo_and_fascicles$PHQ.2)))), xlab = "PHQ-2", breaks = 8)
-
-hist(df_demo_and_fascicles$PHQ.9[which(!is.na(df_demo_and_fascicles$PHQ.9))], main = paste0("PHQ-9 In Good Mimosa Group : n = ", length(which(!is.na(df_demo_and_fascicles$PHQ.9)))), xlab = "PHQ-9", breaks = 8)
-
-phq2_and_dep <- df_demo_and_fascicles %>% filter(depGroupVar == 2) %>% drop_na(PHQ.2) 
-phq9_and_dep <- df_demo_and_fascicles %>% filter(depGroupVar == 2) %>% drop_na(PHQ.9) 
-phq2_and_healthy <- df_demo_and_fascicles %>% filter(Has.depdx == 0) %>% drop_na(PHQ.2) 
-phq9_and_healthy <- df_demo_and_fascicles %>% filter(Has.depdx == 0) %>% drop_na(PHQ.9)
-
-hist(phq2_and_dep$PHQ.2, main = paste0("PHQ-2/Depressed In Good Mimosa Group : n = ", dim(phq2_and_dep)[1]), xlab = "PHQ-2", breaks = 8)
-
-hist(phq9_and_dep$PHQ.9, main = paste0("PHQ-9/Depressed In Good Mimosa Group : n = ", dim(phq9_and_dep)[1]), xlab = "PHQ-9", breaks = 8)
-
-hist(phq2_and_healthy$PHQ.2, main = paste0("PHQ-2/Healthy In Good Mimosa Group : n = ", dim(phq2_and_healthy)[1]), xlab = "PHQ-2", breaks = 8)
-hist(phq9_and_healthy$PHQ.9, main = paste0("PHQ-9/Healthy In Good Mimosa Group : n = ", dim(phq9_and_healthy)[1]), xlab = "PHQ-9", breaks = 8)
-
-######## Histograms for depression network
-#this histogram helps contextualize the number of streamlines with varying degrees of proportions affected
-hist(x=fascicle_volumes_dep$prop_in_mask, main = "Histogram Affected Streamlines in Dep Net", xlab = "Proportion Streamlines per Fascicle Affected", breaks = 20)
+########
+#fascicle volumes in yeo networks
+########
+
+#read in file with proportions
+#fascicle_volumes_yeo_7 <- read.csv(paste0(homedir, "results/yeo_7_network_overlap_proportions.txt"), header = T, sep = ",", na.strings="0")
+
+#make titles nice
+#names(fascicle_volumes_yeo_7) <-gsub("prop_in_mask_", "prop_", names(fascicle_volumes_yeo_7))
+
+#make Nas into 0
+#fascicle_volumes_yeo_7[is.na(fascicle_volumes_yeo_7)]=0
+
+#read in file with binarized yes/no 
+fascicle_volumes_yeo_7_binarized <- read.csv(paste0(homedir_msdep, "results/yeo_7_network_overlap_proportions_binarized.txt"), header = T, sep = ",")
+
+#drop cranial nerves
+fascicle_volumes_yeo_7_binarized_no_cranial_nerves <- fascicle_volumes_yeo_7_binarized %>% filter(!grepl('CN', fascicle))
+
+#check that order of df is same as yeo networks
+new_df <- gsub(pattern = "_vol", replacement = "", x = names(df_demo_and_fascicles_prop_and_vol[grep(pattern = "_vol", x = names(df_demo_and_fascicles_prop_and_vol))]))
+
+combined_df <- data.frame(cbind(new_df, fascicle_volumes_yeo_7_binarized_no_cranial_nerves$fascicle))
+names(combined_df) <- c("df", "yeo")
+
+#they match
+combined_df$match <- combined_df$df == combined_df$yeo
+```
+
+### Calc healthy volume of yeo networks
+```{r calc_healthy_volume_of_yeo_networks}
+#multiply with the binary yeo maps to get absolute volumes of healthy
+fascicle_volumes_yeo_7_full_volumes <- fascicle_volumes_yeo_7_binarized_no_cranial_nerves %>% 
+  tibble::remove_rownames() %>%
+  tibble::column_to_rownames(var = 'fascicle') %>%
+  mutate(across(everything()) * fiber_volume_values_no_cranial_nerves$volume_full) %>%
+  rename_with(~ str_c(.x, "_vol"), everything())
+
+#sum the volumes of each network to get total. 
+sums_of_volume_of_healthy_fascicles_by_network <- fascicle_volumes_yeo_7_full_volumes %>%
+  summarise(across(everything(), ~ sum(., na.rm = TRUE)))
+
+```
+
+###Calculate injury to networks for each subject
+```{r calculate_injury_to_network}
+
+#grab names of networks, get rid of first element which is "fasiscle"
+yeo_network_names <- names(fascicle_volumes_yeo_7_binarized_no_cranial_nerves)[-1]
+
+df_w_yeo_volume_info <- dep_and_healthy_groups_for_ICD_analysis_with_hydra_prop %>%
+  filter(Hydra_k2 != -1)  %>% 
+ # mutate(total_fascicle_vol_lost = rowMeans(across(all_of(fascicle_names_w_vol_suffix)))) %>%
+  group_by(EMPI) %>% 
+  arrange(EXAM_DATE) %>% 
+  slice(1) %>% 
+  dplyr::select(EMPI, Hydra_k2, ends_with("_vol")) %>%
+  ungroup()
+
+#add columns to data frame for each network
+df_w_yeo_volume_info[,yeo_network_names] = 0
+
+#this has been checked with eyeballs and works. You CAN trust the df_w_yeo_vol_info
+for (network in yeo_network_names) {
+
+  for (subj in 1:dim(df_w_yeo_volume_info)[1]) {
+      # multiply the binary vector of the network with the fascicle volumes of injury, sum, and store in data frame
+      text_to_eval <- paste0("df_w_yeo_volume_info$", network,"[", subj,"]=sum(fascicle_volumes_yeo_7_binarized_no_cranial_nerves$", network,
+      "*df_w_yeo_volume_info[",subj,",2:(dim(df_w_yeo_volume_info)[2] - 7)])")
+      eval(parse(text=text_to_eval))
+  }
+}
+
+### going to add 7 more columns to the data frame that contain the volume of injury/total healthy volume
+df_w_yeo_volume_info_with_prop_of_network <- tibble(df_w_yeo_volume_info) %>% 
+  mutate(across(all_of(yeo_network_names), 
+    .names = "{.col}_prop_net"
+
+  ))
+
+#go through each subject, and divide their total volume of injury within each network by the overall volume of the network
+for (subj in 1:dim(df_w_yeo_volume_info_with_prop_of_network)[1]){
+  df_w_yeo_volume_info_with_prop_of_network[subj, grepl(x = names(df_w_yeo_volume_info_with_prop_of_network), pattern = "_prop_net")] = df_w_yeo_volume_info_with_prop_of_network[subj, grepl(x = names(df_w_yeo_volume_info_with_prop_of_network), pattern = "_prop_net")]/sums_of_volume_of_healthy_fascicles_by_network
+}
 
@@
 
-make_demographics_table_ms(data_frame = data_empi_acc_f_phq)
+make_demographics_table_ms(data_frame = data_2023_pull)
 

### 2024-05-24 scripts/clean_dac_pull_icd10_codes_and_make_clean_df.R

@@ -38,6 +38,9 @@ get_all_unique_ICD10_diagnoses <- function(indiv_empi) {
 
 homedir <- "/Users/eballer/BBL/msanxiety/"
 
+## output directory
+output_file <- paste0(homedir, "/data/data_2023_pull_with_curated_icd10_codes.rds")
+
 #data from dac pull with full icd10 lists
 data_pt1 <- read.csv(paste0(homedir, "/data/dac/investigatingpatientsms2010to2023_full_psych_codes_pt1.csv"), sep = ",", header = TRUE) 
 data_pt2 <- read.csv(paste0(homedir, "/data/dac/investigatingpatientsms2010to2023_full_psych_codes_pt2.csv"), sep = ",", header = TRUE) 
@@ -56,10 +59,6 @@ unique_empi_with_ms_providers <- empi_and_provider %>%
   mutate(EMPI = as.character(EMPI)) %>%
   group_by(EMPI) %>%
   slice(1)
-
-  
-## output directory
-output_file <- paste0(homedir, "/data/data_2023_pull_with_curated_icd10_codes.rds")
 
 #combine data frames
 data_pull <- rbind(data_pt1, data_pt2) %>% 

### 2024-05-24 scripts/ms_functions.R

@@ -1195,9 +1195,9 @@ get_community_names <- function(num_communities) {
 get_fascicle_bundle_mapping <- function(){
   # returns vector with association (34 tracts) = 1; cerebellum (7 t) = 2
   # cranial nerves(10) = 3; projection (34) = 4; commissural (2) = 5
-  dep_network_grouping <- read.csv(paste0(homedir,"/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_grouping.csv"), header = T, sep = ",")
-  yeo_7_network <- fascicle_volumes_yeo_7_binarized <- read.csv(paste0(homedir, "results/yeo_7_network_overlap_proportions.txt"), header = T, sep = ",")
-  yeo_7_network_binarized <- fascicle_volumes_yeo_7_binarized <- read.csv(paste0(homedir, "results/yeo_7_network_overlap_proportions_binarized.txt"), header = T, sep = ",")
+  dep_network_grouping <- read.csv("/Users/eballer/BBL/msdepression//templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_grouping.csv", header = T, sep = ",")
+  yeo_7_network <- fascicle_volumes_yeo_7_binarized <- read.csv("/Users/eballer/BBL/msdepression/results/yeo_7_network_overlap_proportions.txt", header = T, sep = ",")
+  yeo_7_network_binarized <- fascicle_volumes_yeo_7_binarized <- read.csv("/Users/eballer/BBL/msdepression//results/yeo_7_network_overlap_proportions_binarized.txt", header = T, sep = ",")
   numerical_vector <- c(rep(1,34), rep(2,7), rep(3,10), rep(4,34), rep(5,2))
   name_vector <- c(rep("association",34), 
                    rep("cerebellum",7), 

### 2024-05-28 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
adding yeo things

@@
 
+### Read in fascicle info, use this to determine proportion and volume of injury within each fascicle, and save it in the df_demo_and_fascicles_df
 ```{r read_in_fascicle_info}
+
+### by the end of this chunk, the df should include 77 columns each for proportion of injury and volume of injury in each fascicle
+
 ##########################################################
@@
 
-#fascicle names are contained in all but the first 2 columns of the fascicle_proportions df
-fascicle_names <- names(fascicle_proportions[3:dim(fascicle_proportions)[2]])
-
-fascicle_names_no_cranial_nerves <- fascicle_names[grep("CN", fascicle_names, invert = TRUE)] #n=77, drop cranial nerves
-
-#write.table(fascicle_names,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names.csv", row.names = F, quote = F, col.names = F)
-
-########
-#fascicle volumes in depression network
-########
-fascicle_volumes_dep <- read.csv("/Users/eballer/BBL/msdepression/results/streamline_volume_within_dep_network.csv", header = T, sep = ",")
-
-#add column to indicate whether does not meet criteria for inclusion in dep mask (0), any overlapping voxels (1), or >10% overlapping voxels (2)
-fascicle_volumes_dep_network <- fascicle_volumes_dep %>%
-  replace(is.na(.), 0) %>%
-  mutate(inDepMask=case_when(prop_in_mask == 0 ~ 0, (prop_in_mask > 0 & prop_in_mask < 0.1) ~ 1, prop_in_mask >= 0.1 ~ 2))
-
-#write.table(fascicle_volumes_dep_network, paste0(homedir,  "/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_grouping.csv"), sep = ",", col.names=T)#, row.names = F, quote = F, col.names = T)
-
-fascicle_names_nondep_network<- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask == 0)]
-
-fascicle_names_dep_network_all <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask > 0)]
-
-#fascicle_mapping, returns numerical mapping as well as names of tracts, and whether in or out of dep network
-fascicle_bundle_mapping <- get_fascicle_bundle_mapping()
-
+```
+
+## Merge data with good mimosa
+```{r merge_with_good_mimosa}
 ##########################################################
@@
 
-#Compare disease burden by anxiety comorbidity
-```{r compare_disease_burden_by_anxiety_comorbidity}
-
-#lm
-fascicle_number_of_anxiety_dx_lm <- lapply(fascicle_names_no_cranial_nerves, function(x) 
-{
-  lm(substitute(i ~ number_of_anxiety_comorbidities_extended, list(i = as.name(x))), data = df_demo_and_fascicles)
-})
-names(fascicle_number_of_anxiety_dx_lm) <- fascicle_names_no_cranial_nerves
-fascicle_number_of_anxiety_dx_anova <- lapply(fascicle_number_of_anxiety_dx_lm, anova)
-
-#fdr corrected
-fascicle_number_of_anxiety_dx_anova_fdr <- fdr_anova_generic(fascicle_number_of_anxiety_dx_anova, 1)
-print(fascicle_number_of_anxiety_dx_anova_fdr)
-
-```
-#Has depression AND anxiety diagnoses
-```{r compare_disease_burden_by_dep_AND_anxiety_comorbidity}
-
-#lm
-fascicle_depANDanx_dx_lm <- lapply(fascicle_names_no_cranial_nerves, function(x) 
-{
-  lm(substitute(i ~ Has.depANDanx.dx, list(i = as.name(x))), data = df_demo_and_fascicles)
-})
-names(fascicle_depANDanx_dx_lm) <- fascicle_names_no_cranial_nerves
-fascicle_depANDanx_dx_anova <- lapply(fascicle_depANDanx_dx_lm, anova)
-
-#fdr corrected
-fascicle_depANDanx_dx_anova_fdr <- fdr_anova_generic(fascicle_depANDanx_dx_anova, 1)
-print(fascicle_depANDanx_dx_anova_fdr)
-
-```
-
-#compare disease burden by psychiatric comorbidity
-```{r compare_disease_burden_between_anxiety_and_no_psych_dx}
-
-#lm
-fascicle_number_of_psychiatric_dx_lm <- lapply(fascicle_names_no_cranial_nerves, function(x) 
-{
-  lm(substitute(i ~ number_of_psychiatric_comorbidities_extended, list(i = as.name(x))), data = df_demo_and_fascicles)
-})
-names(fascicle_number_of_psychiatric_dx_lm) <- fascicle_names_no_cranial_nerves
-
-fascicle_number_of_psychiatric_dx_anova <- lapply(fascicle_number_of_psychiatric_dx_lm, anova)
-
-#fdr corrected
-fascicle_number_of_psychiatric_dx_anova_fdr <- fdr_anova_generic(fascicle_number_of_psychiatric_dx_anova, 1)
-print(fascicle_number_of_psychiatric_dx_anova_fdr)
+```{r add_suffix_to_each_measure}
+
+#########################################
+## Get vectors with names of fascicles ##
+#########################################
+
+#fascicle names are contained in all but the first 2 columns of the fascicle_proportions df
+fascicle_names <- names(fascicle_proportions[3:dim(fascicle_proportions)[2]])
+fascicle_names_no_cranial_nerves <- fascicle_names[grep("CN", fascicle_names, invert = TRUE)] #n=77, drop cranial nerves
+
+fascicle_names_w_prop_suffix <- gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE, x = fascicle_names_no_cranial_nerves)
+fascicle_names_w_vol_suffix <- gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE, x = fascicle_names_no_cranial_nerves)
+
+#write.table(fascicle_names,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names.csv", row.names = F, quote = F, col.names = F)
+
+#read in volumes of fascicles and make columns reflecting volume of disease injured per fascicle
+
+##########################################################
+#  Add columns for volume and change proportion names    #
+##########################################################
+
+#read in fiber volume values
+fiber_volume_values <- read.csv("/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fiber_volume_values.csv", sep=",", header = T)
+
+#remove cranial nerves
+fiber_volume_values_no_cranial_nerves <- fiber_volume_values %>% filter(fascicle %in% fascicle_names_no_cranial_nerves) %>%
+  slice(order(factor(fascicle, levels = fascicle_names_no_cranial_nerves)))
+
+#extract data frame that only includes the fascicle proportion lost
+df_fascicles_prop <- df_demo_and_fascicles[ , (names(df_demo_and_fascicles) %in% fascicle_names_no_cranial_nerves)] 
+df_everything_else <- df_demo_and_fascicles[ , !(names(df_demo_and_fascicles) %in% fascicle_names_no_cranial_nerves)]
+
+#multiply each row by the vector of total volumes to extract volume of disease within fascicle
+df_fascicles_volumes <- sweep(x = df_fascicles_prop, MARGIN = 2,                        # Sweep with Complex STATS
+                  STATS = fiber_volume_values_no_cranial_nerves$volume_full, FUN = "*") %>%
+  mutate_if(is.numeric, round) #round all values
+
+# change name of df_fascicle_volumes to have the suffix, and add a suffix for the proportion measures
+names(df_fascicles_prop) <- fascicle_names_w_prop_suffix
+names(df_fascicles_volumes) <- fascicle_names_w_vol_suffix
+
+#combine back with data_fram
+#df_demo_and_fascicle_volumes_full <- cbind(df_everything_else, df_fascicle_volumes)
+df_demo_and_fascicles <- cbind(df_everything_else, df_fascicles_prop, df_fascicles_volumes)
 ```
@@
 ###Read in fascicle info
-```{r read_in_fascicle_info}
+```{r read_in_yeo_fascicle_info}
 ##########################################################
@@
 #read in file with binarized yes/no 
-fascicle_volumes_yeo_7_binarized <- read.csv(paste0(homedir_msdep, "results/yeo_7_network_overlap_proportions_binarized.txt"), header = T, sep = ",")
+fascicle_volumes_yeo_7_binarized <- read.csv("/Users/eballer/BBL/msdepression/results/yeo_7_network_overlap_proportions_binarized.txt", header = T, sep = ",")
 
@@
 #check that order of df is same as yeo networks
-new_df <- gsub(pattern = "_vol", replacement = "", x = names(df_demo_and_fascicles_prop_and_vol[grep(pattern = "_vol", x = names(df_demo_and_fascicles_prop_and_vol))]))
+new_df <- gsub(pattern = "_vol", replacement = "", x = names(df_demo_and_fascicles[grep(pattern = "_vol", x = names(df_demo_and_fascicles))]))
 
@@
 
-df_w_yeo_volume_info <- dep_and_healthy_groups_for_ICD_analysis_with_hydra_prop %>%
-  filter(Hydra_k2 != -1)  %>% 
+df_w_yeo_volume_info <- df_demo_and_fascicles %>%
   # mutate(total_fascicle_vol_lost = rowMeans(across(all_of(fascicle_names_w_vol_suffix)))) %>%
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  dplyr::select(EMPI, Hydra_k2, ends_with("_vol")) %>%
+  dplyr::select(EMPI, ends_with("_vol")) %>%
   ungroup()
@@
 
-#this has been checked with eyeballs and works. You CAN trust the df_w_yeo_vol_info
+#this has been checked with eyeballs and works. You CAN trust the df_w_yeo_volume_info
 for (network in yeo_network_names) {
@@
       text_to_eval <- paste0("df_w_yeo_volume_info$", network,"[", subj,"]=sum(fascicle_volumes_yeo_7_binarized_no_cranial_nerves$", network,
-      "*df_w_yeo_volume_info[",subj,",2:(dim(df_w_yeo_volume_info)[2] - 7)])")
+      "*df_w_yeo_volume_info[",subj,",3:(dim(df_w_yeo_volume_info)[2] - 7)])")
+     # print(text_to_eval)
       eval(parse(text=text_to_eval))
@@
 }
+
+### rename the whole new data frame df_demo_and_fascicles
+df_demo_and_fascicles <- df_w_yeo_volume_info_with_prop_of_network %>% 
+  dplyr::select(-contains('_vol')) %>% #removes all columns with volume, leaving only the exam date, empi, and yeo values
+  right_join(df_demo_and_fascicles, by = c("EXAM_DATE", "EMPI")) #combine with demo_and_fascicles
+
+```
+
+#summarize means across all fascicles
+```{r make_summary_measures_of_fascicle_burden}
+
+df_demo_and_fascicles <- df_demo_and_fascicles %>%
+  mutate(total_fascicle_prop_lost_no_cranial_nerves = rowMeans(across(fascicle_names_w_prop_suffix))) %>%
+  mutate(total_fascicle_volume_lost_no_cranial_nerves = rowMeans(across(fascicle_names_w_vol_suffix)))
+```
+
+#Compare disease burden by anxiety comorbidity
+```{r compare_disease_burden_by_anxiety_comorbidity}
+
+#lm
+fascicle_number_of_anxiety_dx_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
+{
+  lm(substitute(i ~ number_of_anxiety_comorbidities_extended, list(i = as.name(x))), data = df_demo_and_fascicles)
+})
+names(fascicle_number_of_anxiety_dx_lm) <- fascicle_names_w_prop_suffix
+fascicle_number_of_anxiety_dx_anova <- lapply(fascicle_number_of_anxiety_dx_lm, anova)
+
+#fdr corrected
+fascicle_number_of_anxiety_dx_anova_fdr <- fdr_anova_generic(fascicle_number_of_anxiety_dx_anova, 1)
+print(fascicle_number_of_anxiety_dx_anova_fdr)
+
+## limbic area disease by anxiety diagnosis
+
+yeo_lim_no_anxiety <- lm(LIM~number_of_anxiety_comorbidities_extended, data = df_demo_and_fascicles) #nothing
+
+```
+#Has depression AND anxiety diagnoses
+```{r compare_disease_burden_by_dep_AND_anxiety_comorbidity}
+
+#lm
+fascicle_depANDanx_dx_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
+{
+  lm(substitute(i ~ Has.depANDanx.dx, list(i = as.name(x))), data = df_demo_and_fascicles)
+})
+names(fascicle_depANDanx_dx_lm) <- fascicle_names_w_prop_suffix
+fascicle_depANDanx_dx_anova <- lapply(fascicle_depANDanx_dx_lm, anova)
+
+#fdr corrected
+fascicle_depANDanx_dx_anova_fdr <- fdr_anova_generic(fascicle_depANDanx_dx_anova, 1)
+print(fascicle_depANDanx_dx_anova_fdr)
+
+```
+
+#compare disease burden by psychiatric comorbidity
+```{r compare_disease_burden_between_anxiety_and_no_psych_dx}
+
+#lm
+fascicle_number_of_psychiatric_dx_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
+{
+  lm(substitute(i ~ number_of_psychiatric_comorbidities_extended, list(i = as.name(x))), data = df_demo_and_fascicles)
+})
+names(fascicle_number_of_psychiatric_dx_lm) <- fascicle_names_w_prop_suffix
+
+fascicle_number_of_psychiatric_dx_anova <- lapply(fascicle_number_of_psychiatric_dx_lm, anova)
+
+#fdr corrected
+fascicle_number_of_psychiatric_dx_anova_fdr <- fdr_anova_generic(fascicle_number_of_psychiatric_dx_anova, 1)
+print(fascicle_number_of_psychiatric_dx_anova_fdr)
+
+## yeo
+#lm
+psych_comorbidity_lm_yeo <- lapply(yeo_network_names, function(x) 
+{
+  lm(substitute(i ~ number_of_psychiatric_comorbidities_extended, list(i = as.name(x))), data = anxiety_vs_no_psych)
+})
+names(psych_comorbidity_lm_yeo) <- yeo_network_names
+
+psych_comorbidity_yeo_anova <- lapply(psych_comorbidity_lm_yeo, anova)
+
+#fdr corrected
+psych_comorbidity_yeo_anova_fdr <- fdr_anova_generic(psych_comorbidity_yeo_anova, 1)
+print(psych_comorbidity_yeo_anova_fdr)
+
+```
+
+##compare disease in anxiety versus patients with no psychiatric comorbidity
+```{r anxiety_vs_healthy_ish}
+
+anxiety_vs_no_psych <- df_demo_and_fascicles %>%
+  mutate(anxietyGroupVar = ifelse(Has.anxietydx, 2, ifelse(healthy_ish, 1, 0))) %>% #complicated, if they have an anxiety disorder, they get a 2, if they are health-ish, no psych dx or meds, 1, otherwise, exclude
+  filter(anxietyGroupVar != 0) %>% #get rid of the people who are not anxious and not healthy_ish, n =650, lost n=173
+  group_by(EMPI) %>%
+  arrange(EXAM_DATE) %>%
+  slice(1) %>%
+  ungroup
+
+#lm
+anxiety_vs_no_psych_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
+{
+  lm(substitute(i ~ anxietyGroupVar, list(i = as.name(x))), data = anxiety_vs_no_psych)
+})
+names(anxiety_vs_no_psych_lm) <- fascicle_names_w_prop_suffix
+
+anxiety_vs_no_psych_lm_anova <- lapply(anxiety_vs_no_psych_lm, anova)
+
+#fdr corrected
+anxiety_vs_no_psych_lm_anova_fdr <- fdr_anova_generic(anxiety_vs_no_psych_lm_anova, 1)
+print(anxiety_vs_no_psych_lm_anova_fdr)
+
+## yeo
+#lm
+anxiety_vs_no_psych_lm_yeo <- lapply(yeo_network_names, function(x) 
+{
+  lm(substitute(i ~ anxietyGroupVar, list(i = as.name(x))), data = anxiety_vs_no_psych)
+})
+names(anxiety_vs_no_psych_lm_yeo) <- yeo_network_names
+
+anxiety_vs_no_psych_yeo_anova <- lapply(anxiety_vs_no_psych_lm_yeo, anova)
+
+#fdr corrected
+anxiety_vs_no_psych_yeo_anova_fdr <- fdr_anova_generic(anxiety_vs_no_psych_yeo_anova, 1)
+print(anxiety_vs_no_psych_yeo_anova_fdr)
 

### 2024-05-28 scripts/clean_dac_pull_icd10_codes_and_make_clean_df.R

@@ -6,6 +6,8 @@
 ## dependencies: dplyr
 
 library(dplyr)
+library(tidyr)
+library(stringr)
 
 
 ######################
@@ -70,7 +72,7 @@ for(row in 1:dim(data_pull)[1]) {
   data_pull$all_icd10_dx[row] <- get_all_unique_ICD10_diagnoses(data_pull$EMPI[row])
 }
 
-columns_to_make_integer <- c("ACCESSION_NUM", "PAT_AGE_AT_EXAM","MRI_ENC_AGE","CURRENT_AGE","hemoglobin", "WBC","RBC","B12","FOLATE", "TSH", "RPR","CSFAPPEAR1","CSFAPPEAR4","CSFCOLOR1",       "CSFCOLOR4","CSFTUBE","CSFTUBE4","PHQ.2","PHQ.9") #removed "VitD", not in new pull for some reason
+columns_to_make_integer <- c("ACCESSION_NUM", "PAT_AGE_AT_EXAM","MRI_ENC_AGE","CURRENT_AGE","hemoglobin", "WBC","RBC","B12","FOLATE", "TSH", "RPR","CSFAPPEAR1","CSFAPPEAR4","CSFCOLOR1", "CSFCOLOR4","CSFTUBE","CSFTUBE4","PHQ.2","PHQ.9") #removed "VitD", not in new pull for some reason
 
 #Get med info in
 #read in BCP info, names of meds, est and prog and doses
@@ -140,7 +142,8 @@ data_final_rds <-data_pull %>%
   mutate(PHQ.9_zero = ifelse(Has.PHQ9 & PHQ.9 == 0, 1, 0)) %>%
   mutate(dep_by_dx_phq = ifelse((Has.depdx | PHQ.2_modsev_dep_sxs | PHQ.9_modsev_dep_sxs),1,0)) %>%
   mutate(dep_by_dx_phq_antidep = ifelse((Has.depdx | On.Antidepressants | PHQ.2_modsev_dep_sxs | PHQ.9_modsev_dep_sxs),1,0)) %>%
-  mutate(true_healthy = ifelse((!Has.depdx & !On.Psych.Meds & (PHQ.2_zero | PHQ.9_zero)), 1, 0)) %>%
+  mutate(healthy_ish = ifelse(((number_of_psychiatric_comorbidities_extended == 0) & !On.Psych.Meds), 1, 0)) %>% #just like true healthy but doesn't require a phq screen
[…]

### 2024-05-28 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
made some changes to anxiety dx

@@
   filter(anxietyGroupVar != 0) %>% #get rid of the people who are not anxious and not healthy_ish, n =650, lost n=173
+  filter(is.na(depGroupVar)) %>% #exclude people with depression (87 have both depression and anxiety), n = 563, anxiety = 101, nonanxious = 462)
   group_by(EMPI) %>%

### 2024-05-29 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
Add files via upload

--- 2024-05-28 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
@@
 
- #n = 823
+ #n = 812
 df_demo_and_fascicles <- df_people_with_good_mimosa %>% 
   left_join(fascicle_proportions, by = c("EMPI", "EXAM_DATE")) %>%
-  filter(!is.na(Has.MS.Provider))
+  filter(!is.na(Has.MS.Provider)) %>% #remove people who don't have MS provider
+  filter(!is.na(CNII_L)) #this is a sample fascicle that should have a value. if it does not, it means something is usually wrong with whole person. Remove rows with NAs
 
@@
 
-# Yeo network analysis attempts
+##YEO Networks
 ###Read in fascicle info
@@
 
+#make names with _prop_net for use later to grap columns of proportions and not volumes
+yeo_network_names_prop <- paste(yeo_network_names, 'prop_net', sep = '_')
+
 df_w_yeo_volume_info <- df_demo_and_fascicles %>%
@@
 
+#n=812
 df_demo_and_fascicles <- df_demo_and_fascicles %>%
-  mutate(total_fascicle_prop_lost_no_cranial_nerves = rowMeans(across(fascicle_names_w_prop_suffix))) %>%
-  mutate(total_fascicle_volume_lost_no_cranial_nerves = rowMeans(across(fascicle_names_w_vol_suffix)))
+  mutate(total_fascicle_prop_lost_no_cranial_nerves = rowMeans(across(all_of(fascicle_names_w_prop_suffix)))) %>%
+  mutate(total_fascicle_volume_lost_no_cranial_nerves = rowMeans(across(all_of(fascicle_names_w_vol_suffix))))
 ```
@@
 
+##uncorrected
+p_anova <- as.data.frame(sapply(fascicle_number_of_anxiety_dx_anova, function(v) v$"Pr(>F)"[1]) )
+
+#extract values that are significant
+p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
+
+#print BEFORE FDR correction 
+print(p_anova_unc)
+
 #fdr corrected
@@
 
+##uncorrected
+p_anova <- as.data.frame(sapply(fascicle_depANDanx_dx_anova, function(v) v$"Pr(>F)"[1]) )
+
+#extract values that are significant
+p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
+
+#print BEFORE FDR correction 
+print(p_anova_unc)
+
 #fdr corrected
@@
 
+#Pull p-values
+p_anova <- as.data.frame(sapply(fascicle_number_of_psychiatric_dx_anova, function(v) v$"Pr(>F)"[1]) )
+
+#extract values that are significant
+p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
+
+#print BEFORE FDR correction 
+print(p_anova_unc)
+
 #fdr corrected
@@
 {
-  lm(substitute(i ~ number_of_psychiatric_comorbidities_extended, list(i = as.name(x))), data = anxiety_vs_no_psych)
+  lm(substitute(i ~ number_of_psychiatric_comorbidities_extended, list(i = as.name(x))), data = df_demo_and_fascicles)
 })
@@
 psych_comorbidity_yeo_anova <- lapply(psych_comorbidity_lm_yeo, anova)
+
+#uncorrected
+#Pull p-values
+p_anova <- as.data.frame(sapply(psych_comorbidity_yeo_anova, function(v) v$"Pr(>F)"[1]) )
+
+#extract values that are significant
+p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
+
+#print BEFORE FDR correction 
+print(p_anova_unc)
 
@@
   mutate(anxietyGroupVar = ifelse(Has.anxietydx, 2, ifelse(healthy_ish, 1, 0))) %>% #complicated, if they have an anxiety disorder, they get a 2, if they are health-ish, no psych dx or meds, 1, otherwise, exclude
-  filter(anxietyGroupVar != 0) %>% #get rid of the people who are not anxious and not healthy_ish, n =650, lost n=173
+  filter(anxietyGroupVar != 0) %>% #get rid of the people who are not anxious and not healthy_ish, n =643, lost n=169
+  filter(is.na(depGroupVar)) %>% #exclude people with depression (87 have both depression and anxiety), n = 557, anxiety = 101, nonanxious = 456)
   group_by(EMPI) %>%
@@
 anxiety_vs_no_psych_lm_anova <- lapply(anxiety_vs_no_psych_lm, anova)
+
+#uncorrected
+#Pull p-values
+p_anova <- as.data.frame(sapply(anxiety_vs_no_psych_lm_anova, function(v) v$"Pr(>F)"[1]) )
+
+#extract values that are significant
+p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
+
+#print BEFORE FDR correction 
+print(p_anova_unc)
 
@@
 
+#uncorrected
+#Pull p-values
+p_anova <- as.data.frame(sapply(anxiety_vs_no_psych_yeo_anova, function(v) v$"Pr(>F)"[1]) )
+
+#extract values that are significant
+p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
+
+#print BEFORE FDR correction 
+print(p_anova_unc)
+
 #fdr corrected
@@
 print(anxiety_vs_no_psych_yeo_anova_fdr)
+
+```
+### Run analysis again but include in anxiety group people on anti-anxiety meds
+```{r anxiety_oranxiety_meds_vs_healthy_ish}
+
+anxiety_vs_no_psych <- df_demo_and_fascicles %>%
+  mutate(anxietyGroupVar = ifelse((Has.anxietydx | On.Anxiolytics_no_beta_blocker), 2, ifelse(healthy_ish, 1, 0))) %>% #complicated, if they have an anxiety disorder, they get a 2, if they are health-ish, no psych dx or meds, 1, otherwise, exclude
+  filter(anxietyGroupVar != 0) %>% #get rid of the people who are not anxious and not healthy_ish, n =643, lost n=169
+  filter(is.na(depGroupVar)) %>% #exclude people with depression (87 have both depression and anxiety), n = 557, anxiety = 101, nonanxious = 456)
+  group_by(EMPI) %>%
+  arrange(EXAM_DATE) %>%
+  slice(1) %>%
+  ungroup
+
+#lm
+anxiety_vs_no_psych_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
+{
+  lm(substitute(i ~ anxietyGroupVar, list(i = as.name(x))), data = anxiety_vs_no_psych)
+})
+names(anxiety_vs_no_psych_lm) <- fascicle_names_w_prop_suffix
+
+anxiety_vs_no_psych_lm_anova <- lapply(anxiety_vs_no_psych_lm, anova)
+
+#uncorrected
+#Pull p-values
+p_anova <- as.data.frame(sapply(anxiety_vs_no_psych_lm_anova, function(v) v$"Pr(>F)"[1]) )
+
+#extract values that are significant
+p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
+
+#print BEFORE FDR correction 
+print(p_anova_unc)
+
+#fdr corrected
+anxiety_vs_no_psych_lm_anova_fdr <- fdr_anova_generic(anxiety_vs_no_psych_lm_anova, 1)
+print(anxiety_vs_no_psych_lm_anova_fdr)
+
+## yeo
+#lm
+anxiety_vs_no_psych_lm_yeo <- lapply(yeo_network_names, function(x) 
+{
+  lm(substitute(i ~ anxietyGroupVar, list(i = as.name(x))), data = anxiety_vs_no_psych)
+})
+names(anxiety_vs_no_psych_lm_yeo) <- yeo_network_names
+
+anxiety_vs_no_psych_yeo_anova <- lapply(anxiety_vs_no_psych_lm_yeo, anova)
+
+#uncorrected
+#Pull p-values
+p_anova <- as.data.frame(sapply(anxiety_vs_no_psych_yeo_anova, function(v) v$"Pr(>F)"[1]) )
+
+#extract values that are significant
+p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
+
+#print BEFORE FDR correction 
+print(p_anova_unc)
+
+#fdr corrected
+anxiety_vs_no_psych_yeo_anova_fdr <- fdr_anova_generic(anxiety_vs_no_psych_yeo_anova, 1)
+print(anxiety_vs_no_psych_yeo_anova_fdr)
+
+```
+
+### Send anxiety groups to HYDRA (diagnosis only, no on meds)
+```{r anxiety_group_prep_for_hydra}
+### remake data frame from above
+
+anxiety_vs_no_psych <- df_demo_and_fascicles %>%
+  mutate(anxietyGroupVar = ifelse(Has.anxietydx, 2, ifelse(healthy_ish, 1, 0))) %>% #complicated, if they have an anxiety disorder, they get a 2, if they are health-ish, no psych dx or meds, 1, otherwise, exclude
+  filter(anxietyGroupVar != 0) %>% #get rid of the people who are not anxious and not healthy_ish, n =643, lost n=169
+  filter(is.na(depGroupVar)) %>% #exclude people with depression (87 have both depression and anxiety), n = 557, anxiety = 101, nonanxious = 456)
+  mutate(anxietyHydraVar = ifelse(anxietyGroupVar == 2, 1, -1)) %>%
+  group_by(EMPI) %>%
+  arrange(EXAM_DATE) %>%
+  slice(1) %>%
+  ungroup
+
+#pull out EMPI, proportion, and anxiety group var
+anxiety_vs_no_psych_features_for_hydra <- anxiety_vs_no_psych %>%
+  dplyr::select(EMPI, fascicle_names_w_prop_suffix, anxietyHydraVar)
+
+write.csv(file=paste0(homedir, "/hydra/data/Features_ms_fascicle_dysconnectome_anxiety_prop.csv"),x=anxiety_vs_no_psych_features_for_hydra, quote = F, row.names = F)
+
+#pull out age, age + sex covariates
+anxiety_age <- anxiety_vs_no_psych %>%
+  dplyr::select(EMPI, PAT_AGE_AT_EXAM)
+
+write.csv(file=paste0(homedir, "/hydra/data/Covariates_age.csv"),x=anxiety_age, quote = F, row.names = F)
+
+anxiety_age_and_sex <- anxiety_vs_no_psych %>%
+  dplyr::select(EMPI, PAT_AGE_AT_EXAM, sex_binarized)
+
+write.csv(file=paste0(homedir, "/hydra/data/Covariates_age_and_sex.csv"),x=anxiety_age_and_sex, quote = F, row.names = F)
+
+#pull out yeo proportions
+anxiety_vs_no_psych_yeo_features_for_hydra <- anxiety_vs_no_psych %>%
+  dplyr::select(EMPI, yeo_network_names_prop, anxietyHydraVar)
+
+write.csv(file=paste0(homedir, "/hydra/data/Features_ms_fascicle_dysconnectome_anxiety_yeo_prop.csv"),x=anxiety_vs_no_psych_yeo_features_for_hydra, quote = F, row.names = F)
 

### 2024-05-29 scripts/clean_dac_pull_icd10_codes_and_make_clean_df.R

@@ -87,6 +87,11 @@ msmeds$Medication <- toupper(msmeds$Medication)
 psych_meds <- read.csv("/Users/eballer/BBL/medication_data/nami_psych_meds_antidepressants.csv", sep = ",", header = TRUE)
 psych_meds$Medication.Name <- toupper(psych_meds$Medication.Name)
 
+#depression/psych meds from NAMI website + neurontin, gabapentin, elavil, amitriptyline
+psych_meds_extended <- read.csv("/Users/eballer/BBL/medication_data/nami_psych_meds_antidepressants_plus_gabapentin_and_amitriptyline.csv", sep = ",", header = TRUE)
+psych_meds_extended$Medication.Name <- toupper(psych_meds_extended$Medication.Name)
+
+
 #anxiety meds from chatgpt (cross referenced with psych meds)
 anxiety_meds <- read.csv("/Users/eballer/BBL/medication_data/antianxiety_medications.csv", sep = ",", header = TRUE)
 anxiety_meds$Medication <- toupper(anxiety_meds$Medication)
@@ -120,6 +125,7 @@ data_final_rds <-data_pull %>%
   mutate(number_of_medications = ifelse(!is.na(Medication), str_count(Medication, ";") + 1, 0)) %>%
   mutate(On.Bcp = ifelse(str_detect(Medication, paste(bcp$bcp_name, collapse = "|")), 1, 0)) %>%
   mutate(On.Psych.Meds = ifelse(str_detect(Medication, paste(psych_meds$Medication, collapse = "|")), 1, 0)) %>%
+  mutate(On.Psych.Meds.Extended = ifelse(str_detect(Medication, paste(psych_meds_extended$Medication, collapse = "|")), 1, 0)) %>% #extended includes amitriptyline and gabapentin (and brands) in med list
   mutate(On.Antidepressants = ifelse(str_detect(Medication, paste(psych_meds$Medication[psych_meds$Antidepressant == "t"], collapse = "|")), 1, 0)) %>%
   mutate(On.Anxiolytics = ifelse(str_detect(Medication, paste(anxiety_meds$Medication, collapse = "|")), 1, 0)) %>%
[…]

### 2024-06-07 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
adding all sorts of things for within/bet network
After using neurosynth maps

@@
 
+## Read in lesion volume size
+```{r read_in_lesion_volumes}
+##########################################################
+#             Read in Lesion Volumes                     #
+##########################################################
+
+# contains the volume of lesioned voxels, i.e. a sum of all the areas of each individual's binary mask that are 1
+
+lesion_volumes <- read.csv("/Users/eballer/BBL/msdepression/results/mimosa_binary_masks_hcp_space_20211026_n2336_volumes", sep = ",", header = TRUE) #n=958 unique, identical to fascicle unique
+lesion_volumes <- lesion_volumes %>%
+  mutate(EMPI = as.character(EMPI)) %>%
+  mutate(EXAM_DATE = as.character(EXAM_DATE))
+
+```
+
+## Merge with data frame with good mimosas
+```{r merge_lesion_volume_w_mimosa_df}
+##########################################################
+#             Merge lesion volumes with mimosa df        #
+##########################################################
+#merge whole data set with fascicle proportions, n = 812
+df_demo_and_fascicles <- df_demo_and_fascicles %>%
+  left_join(lesion_volumes, by = c("EMPI", "EXAM_DATE"))
+
+```
+
+## Make separate columns for proportional injury (prop), total volume injury (vol)
 ```{r add_suffix_to_each_measure}
+
+########################################
+## Read in Fiber Volume Values        ##
+########################################
+
+#read in fiber volume values
+fiber_volume_values <- read.csv("/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fiber_volume_values.csv", sep=",", header = T)
 
@@
 
-#read in volumes of fascicles and make columns reflecting volume of disease injured per fascicle
-
 ##########################################################
@@
 ##########################################################
-
-#read in fiber volume values
-fiber_volume_values <- read.csv("/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fiber_volume_values.csv", sep=",", header = T)
 
@@
 ```
-
-#summarize means across all fascicles
-```{r make_summary_measures_of_fascicle_burden}
-
-#n=812
+##Anxiety Network from neurosynth (association, not uniformity)
+###read in file with fasciclexanxiety overlap, and define anxiety network
+```{r read_in_neurosynth_anxiety_network}
+neurosynth_anxiety_network_fascicle_overlap <- read.csv("/Users/eballer/BBL/msanxiety/results/streamline_volume_within_anxiety_network_association_neuro_maps_FDR_01.csv", header = T, sep = ",") %>% 
+  filter(fascicle %in% fascicle_names_no_cranial_nerves) %>%
+  slice(order(factor(fascicle, levels = fascicle_names_no_cranial_nerves))) #get rid of cranial nerves up front
+
+fascicles_with_any_anxiety_overlap <- neurosynth_anxiety_network_fascicle_overlap %>%
+  filter(!is.na(prop_in_mask))  #n = 43
+
+#top 25% 
+number_of_brain_regions_in_top_25 <- round((dim(fascicles_with_any_anxiety_overlap)[1]/4)) #n=11
+
+fascicles_with_vol_top_25_percent_anxiety_overlap <- neurosynth_anxiety_network_fascicle_overlap %>%
+  filter(!is.na(prop_in_mask)) %>%
+  arrange(desc(non_zero_voxels_in_anxiety_map)) %>%
+  slice(1:number_of_brain_regions_in_top_25)
+
+fascicles_with_prop_top_25_percent_anxiety_overlap <- neurosynth_anxiety_network_fascicle_overlap %>%
+  filter(!is.na(prop_in_mask)) %>%
+  arrange(desc(prop_in_mask)) %>%
+  slice(1:number_of_brain_regions_in_top_25)
+
+#name vectors to use later
+fascicle_names_any_anxiety_overlap_vol <- fascicles_with_any_anxiety_overlap$fascicle 
+fascicle_names_top_25_vol <- fascicles_with_vol_top_25_percent_anxiety_overlap$fascicle 
+fascicle_names_bottom_75_vol <- fascicles_with_any_anxiety_overlap %>% filter(!(fascicle %in% fascicle_names_top_25_vol)) %>% pull(fascicle)
+
+fascicle_names_any_anxiety_overlap_prop <- fascicles_with_any_anxiety_overlap$fascicle
+fascicle_names_top_25_prop <-fascicles_with_prop_top_25_percent_anxiety_overlap$fascicle 
+fascicle_names_bottom_75_prop <- fascicles_with_any_anxiety_overlap %>% filter(!(fascicle %in% fascicle_names_top_25_prop)) %>% pull(fascicle)
+
+##add vol/prop
+fascicle_names_any_anxiety_overlap_vol_w_suff <- fascicle_names_any_anxiety_overlap_vol %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
+fascicle_names_top_25_vol_w_suff <- fascicle_names_top_25_vol %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
+fascicle_names_bottom_75_vol_w_suff <- fascicle_names_bottom_75_vol  %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in
+
+fascicle_names_any_anxiety_overlap_prop_w_suff <- fascicle_names_any_anxiety_overlap_prop %>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
+fascicle_names_top_25_prop_w_suff <- fascicle_names_top_25_prop %>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
+fascicle_names_bottom_75_prop_w_suff <- fascicle_names_bottom_75_prop %>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
+
+# Total volume of injury within each anxiety network, double checked that : top_25_total_volume + bottom_75_total_volume
+total_fascicle_volume <- sum(neurosynth_anxiety_network_fascicle_overlap$num_voxels_total)
+any_anxiety_overlap_total_volume <- sum(fascicles_with_any_anxiety_overlap$num_voxels_total) # vol = 1093606
+top_25_total_volume <-sum(fascicles_with_vol_top_25_percent_anxiety_overlap$num_voxels_total) # vol = 548305
+bottom_75_total_volume <- sum(fascicles_with_any_anxiety_overlap$num_voxels_total[fascicles_with_any_anxiety_overlap$fascicle %in% fascicle_names_bottom_75_vol]) #vol = 548305
+
+```
+
+###Add columns in the main data frame indicating overall injury in the whole network, in the top 25 network (vol and prop), and bottom 75%
+```{r add_anxiety_network_details_to_data_frame}
+
+#all of this has been checked - making sure prop * vol network = sum of damage
+
 df_demo_and_fascicles <- df_demo_and_fascicles %>%
-  mutate(total_fascicle_prop_lost_no_cranial_nerves = rowMeans(across(all_of(fascicle_names_w_prop_suffix)))) %>%
-  mutate(total_fascicle_volume_lost_no_cranial_nerves = rowMeans(across(all_of(fascicle_names_w_vol_suffix))))
-```
-
-#Compare disease burden by anxiety comorbidity
+
+  mutate(mean_fascicle_prop_lost_no_cranial_nerves = rowMeans(across(all_of(fascicle_names_w_prop_suffix)))) %>%
+  mutate(mean_fascicle_volume_lost_no_cranial_nerves = rowMeans(across(all_of(fascicle_names_w_vol_suffix)))) %>%
+
+  #sum of total volume lost and proportion of volume lost 
+  mutate(sum_fascicle_vol_lost = rowSums(across(all_of(fascicle_names_w_vol_suffix)))) %>%
+  mutate(proportion_volume_lost_per_total_network_size_sum = sum_fascicle_vol_lost/total_fascicle_volume) %>%
+
+  #sum of total volume lost in anxiety network and proportion of volume lost in anxietyn network (volume lost/network volume size) 
+  mutate(sum_fascicle_vol_lost_inanxietynet_all = 
+           rowSums(across(all_of(fascicle_names_any_anxiety_overlap_vol_w_suff)))) %>%
+  mutate(proportion_volume_lost_anxiety_net_by_network_size_sum = sum_fascicle_vol_lost_inanxietynet_all/any_anxiety_overlap_total_volume) %>%
+
+  #sum of total volume lost in anxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) 
+  mutate(sum_fascicle_vol_lost_inanxietynet_top_quartile = 
+           rowSums(across(all_of(fascicle_names_top_25_vol_w_suff)))) %>%
+  mutate(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 = sum_fascicle_vol_lost_inanxietynet_top_quartile/top_25_total_volume) %>%
+
+  #sum of total volume lost in nonanxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) 
+  mutate(sum_fascicle_vol_lost_nonanxiety_net_bottom_3_quartiles = 
+           rowSums(across(all_of(fascicle_names_bottom_75_vol_w_suff)))) %>%
+  mutate(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 = sum_fascicle_vol_lost_nonanxiety_net_bottom_3_quartiles/bottom_75_total_volume) %>%
+
+  ungroup()
+
+#neurosynth_anxiety_network_fascicle_overlap
+```
+
+## Anxiety within/outside network interaction
+```{r anxiety_net_intx}
+
+#clean up data frame
+df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
+  filter(anxietyGroupVar != 0) %>% #lose 93, n now 719
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = ifelse(anxietyGroupVar==1, "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
+  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
+  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
+  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
+  mutate(Network = as.factor(Network)) %>%
+  ungroup()
+
+#simple t test, disease within versus outside anxiety network; mean within anxiety net: 0.5426694 affected, mean outside anxiety network = 0.3062429, T=57.44, p<2.2*10^-16, 95% CI 0.22-0.24
+
+hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"])
+hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"])
+
+within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
+summary(within_vs_outside_anxiety_net_t)
+
+ #simple lmer, confirms T
+disease_within_vs_outside_anxiety_net_lmer <- lmer(proportion_affected ~ Network + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_lmer)
+
+#diagnosis: Anxiety > nonanxiety T = 2.4, p = 0.015; Network dep>nondep = T=12.4, p = 2*10^-16; intx = T = 2.3, p = 0.020
+diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
+summary(diagnosis_by_network_interaction_lmer)
+
+#Diagnosis: MS+ > MS- 0.011-0.1; Network dep>nondep -.104--.076; intx: -0.040--0.003
+confint(diagnosis_by_network_interaction_lmer)
+
+```
+# Compare anxiety burden (presence of condition, number of anxiety comorbidities) by fascicle, by overall injury, and by volume of lesions
+```{r compare_anxiety_burden_by_fascicle_injury_lesion_volume}
+
+```
+
+## Compare disease burden by anxiety comorbidity by fascicle
 ```{r compare_disease_burden_by_anxiety_comorbidity}
 
+#### in each fascicle
 #lm
@@
 ```
-#Has depression AND anxiety diagnoses
+
+## Has depression AND anxiety diagnoses
 ```{r compare_disease_burden_by_dep_AND_anxiety_comorbidity}
@@
 
+### total lesion burden
+
+### lesion volume
+
 ```
@@
 anxiety_vs_no_psych <- df_demo_and_fascicles %>%
-  mutate(anxietyGroupVar = ifelse((Has.anxietydx | On.Anxiolytics_no_beta_blocker), 2, ifelse(healthy_ish, 1, 0))) %>% #complicated, if they have an anxiety disorder, they get a 2, if they are health-ish, no psych dx or meds, 1, otherwise, exclude
-  filter(anxietyGroupVar != 0) %>% #get rid of the people who are not anxious and not healthy_ish, n =643, lost n=169
+  mutate(anxietyGroupVar = ifelse((Has.anxietydx | On.Anxiolytics_no_beta_blocker), 2, ifelse(healthy_ish, 1, 0))) %>% #complicated, if they have an anxiety disorder, they get a 2, if they are health-ish, no psych dx or meds, 1, otherwise, exclude; n anxiety = 271, healthyish = 448, unclassified = 93
+  mutate(anxietyGroupVar_ordered = ordered(anxietyGroupVar,levels = c(0,1,2), labels = c("unclassified", "healthyish", "anxiety"))) %>%
+  filter(anxietyGroupVar_ordered != "unclassified") %>% #get rid of the people who are not anxious and not healthy_ish, n =541, lost n=93
   filter(is.na(depGroupVar)) %>% #exclude people with depression (87 have both depression and anxiety), n = 557, anxiety = 101, nonanxious = 456)
@@
 print(anxiety_vs_no_psych_yeo_anova_fdr)
+
+```
+
+## Compare total disease burden and lesion volume by anxiety comorbidity
+```{r total_burden_and_lesion_volume_by_anxiety_comorbdity}
+
+total_burden_by_anxietydx_lm <- lm(anxietyGroupVar~total_fascicle_volume_lost_no_cranial_nerves, data = anxiety_vs_no_psych)
+print(summary(total_burden_by_anxietydx_lm))
+
+total_burden_by_anxiety_lm <- lm(number_of_anxiety_comorbidities_extended~total_fascicle_volume_lost_no_cranial_nerves, data = anxiety_vs_no_psych)
+print(summary(total_burden_by_anxiety_lm))
+
+total_lesion_volume_by_anxietydx_lm <- lm(anxietyGroupVar ~volume_of_mimosa_lesions, data = anxiety_vs_no_psych)
+print(summary(total_lesion_volume_by_anxietydx_lm))
+
+total_lesion_volume_by_anxiety_lm <- lm(number_of_anxiety_comorbidities_extended ~volume_of_mimosa_lesions, data = anxiety_vs_no_psych)
+print(summary(total_lesion_volume_by_anxiety_lm))
 

### 2024-06-07 scripts/clean_dac_pull_icd10_codes_and_make_clean_df.R

@@ -134,12 +134,11 @@ data_final_rds <-data_pull %>%
   mutate(On.Interferon = ifelse(str_detect(Medication, paste(msmeds$Medication[msmeds$Mechanism == "Interferon"], collapse = "|")), 1, 0)) %>%
   mutate(On.Steroids = ifelse(str_detect(Medication, paste(msmeds$Medication[msmeds$Mechanism == "Steroid"], collapse = "|")), 1, 0)) %>%
   mutate(On.Dmt = ifelse(str_detect(Medication, paste(msmeds$Medication[msmeds$DMT == "y"], collapse = "|")), 1, 0)) %>%
-  mutate(Has.PHQ2 = ifelse(PHQ.2 != "NULL", 1, 0)) %>%
-  mutate(Has.PHQ9 = ifelse(PHQ.9 != "NULL", 1, 0)) %>%
+  mutate(Has.PHQ2 = ifelse((PHQ.2 != "NULL" & !is.na(PHQ.2)), 1, 0)) %>%
+  mutate(Has.PHQ9 = ifelse((PHQ.9 != "NULL" & !is.na(PHQ.9)), 1, 0)) %>%
   mutate(Has.depdx = ifelse(grepl("F3[2:4]", all_icd10_dx), 1, 0)) %>%
   mutate(Has.anxietydx = ifelse(grepl("F4", all_icd10_dx), 1, 0)) %>%
   mutate(Has.CannabisUsedx = ifelse(grepl("F12", all_icd10_dx), 1, 0)) %>%
-  mutate(Has.depANDanx.dx = ifelse(Has.depdx & Has.anxietydx, 1, 0)) %>%
   mutate(Has.Anxietydx.Or.Antianxietymed = ifelse(Has.anxietydx | On.Anxiolytics,1,0)) %>%
   mutate(PHQ.2_modsev_dep_sxs = ifelse(Has.PHQ2 & PHQ.2 >= 3, 1, 0)) %>%
   mutate(PHQ.9_modsev_dep_sxs = ifelse(Has.PHQ9 & PHQ.9 >= 10, 1, 0)) %>%
@@ -156,8 +155,13 @@ data_final_rds <-data_pull %>%
   rowwise(ACCESSION_NUM) %>%
   mutate(depGroupVar =
[…]

### 2024-06-07 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
with age/sex

@@
   filter(fascicle %in% fascicle_names_no_cranial_nerves) %>%
-  slice(order(factor(fascicle, levels = fascicle_names_no_cranial_nerves))) #get rid of cranial nerves up front
+  slice(order(factor(fascicle, levels = fascicle_names_no_cranial_nerves))) %>% #get rid of cranial nerves up front 
+  replace(is.na(.), 0)
 
 fascicles_with_any_anxiety_overlap <- neurosynth_anxiety_network_fascicle_overlap %>%
-  filter(!is.na(prop_in_mask))  #n = 43
+  filter(prop_in_mask > 0)  #n = 43
 
 #top 25% 
-number_of_brain_regions_in_top_25 <- round((dim(fascicles_with_any_anxiety_overlap)[1]/4)) #n=11
+#number_of_brain_regions_in_top_25 <- round((dim(fascicles_with_any_anxiety_overlap)[1]/4)) #n=11
+number_of_brain_regions_in_top_25 <- round((dim(neurosynth_anxiety_network_fascicle_overlap)[1]/4)) #n=19
 
@@
 fascicle_names_top_25_vol <- fascicles_with_vol_top_25_percent_anxiety_overlap$fascicle 
-fascicle_names_bottom_75_vol <- fascicles_with_any_anxiety_overlap %>% filter(!(fascicle %in% fascicle_names_top_25_vol)) %>% pull(fascicle)
+fascicle_names_bottom_75_vol <- neurosynth_anxiety_network_fascicle_overlap %>% filter(!(fascicle %in% fascicle_names_top_25_vol)) %>% pull(fascicle)
 
@@
 fascicle_names_top_25_prop <-fascicles_with_prop_top_25_percent_anxiety_overlap$fascicle 
-fascicle_names_bottom_75_prop <- fascicles_with_any_anxiety_overlap %>% filter(!(fascicle %in% fascicle_names_top_25_prop)) %>% pull(fascicle)
+fascicle_names_bottom_75_prop <- neurosynth_anxiety_network_fascicle_overlap %>% filter(!(fascicle %in% fascicle_names_top_25_prop)) %>% pull(fascicle)
 
@@
 top_25_total_volume <-sum(fascicles_with_vol_top_25_percent_anxiety_overlap$num_voxels_total) # vol = 548305
-bottom_75_total_volume <- sum(fascicles_with_any_anxiety_overlap$num_voxels_total[fascicles_with_any_anxiety_overlap$fascicle %in% fascicle_names_bottom_75_vol]) #vol = 548305
+bottom_75_total_volume <- sum(neurosynth_anxiety_network_fascicle_overlap$num_voxels_total[neurosynth_anxiety_network_fascicle_overlap$fascicle %in% fascicle_names_bottom_75_vol]) #vol = 548305
 
@@
 
+#t test, t = 63.621, df = 718, p-value < 2.2e-16; 95 percent confidence interval:0.2349467 0.2499088, mean diff: 0.2424277 
 within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
@@
 
- #simple lmer, confirms T
+ #simple lmer, confirms T; -63.62   <2e-16 ***
 disease_within_vs_outside_anxiety_net_lmer <- lmer(proportion_affected ~ Network + (1|subject), data = df_empi_dx_network_proportions)
@@
 
-#diagnosis: Anxiety > nonanxiety T = 2.4, p = 0.015; Network dep>nondep = T=12.4, p = 2*10^-16; intx = T = 2.3, p = 0.020
+ #Net by sex, confirms T; -63.62   <2e-16, but no sex differences (p=0.179)
+disease_within_vs_outside_anxiety_net_sex_lmer <- lmer(proportion_affected ~ Network +osex + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_sex_lmer)
+
+ #simple lmer, confirms network: -63.621  < 2e-16 , Pat age: 6.338 4.12e-10
+disease_within_vs_outside_anxiety_net_age_lmer <- lmer(proportion_affected ~ Network + PAT_AGE_AT_EXAM + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_age_lmer)
+
+#Age * network interaction, don't know if this is valid at all. outside > w/in net: -12.718  < 2e-16 ***; pat age = 6.837  1.6e-11 ***, NetworkNonanxiety_network:PAT_AGE_AT_EXAM -2.852  0.00447 
+disease_within_vs_outside_anxiety_net_age_intx_lmer <- lmer(proportion_affected ~ Network*PAT_AGE_AT_EXAM + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_age_intx_lmer)
+
+#diagnosis: NS
 diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
@@
 
-#Diagnosis: MS+ > MS- 0.011-0.1; Network dep>nondep -.104--.076; intx: -0.040--0.003
+#Diagnosis: NS
 confint(diagnosis_by_network_interaction_lmer)

### 2024-06-11 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
adding a lot more anxiety/dep stuff

@@
 Final N demographics
-  Anxious: 
-  Super clean healthy: 604 (148 unique)
 
 (unique, with good MIMoSA):
+
+#findings
 
@@
 
+### Get dep network data
+```{r depression_network_injury}
+#take depression network from the BP paper, and find names of fascicles in each group
+
+#read in depression network overlap by volume data frame
+dep_net_overlap_from_bp_paper <- read.csv("/Users/eballer/BBL/msdepression/results/df_fascicles_sorted_by_volume_in_mask_for_eTable3.csv", sep = ",", header = TRUE)
+
+dep_net_top_25_percent <- dep_net_overlap_from_bp_paper$fascicle[1:round((dim(dep_net_overlap_from_bp_paper)[1]/4),0)]
+dep_net_top_25_percent_w_suff <- dep_net_top_25_percent %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
+
+top_25_total_volume_dep <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[1:round((dim(dep_net_overlap_from_bp_paper)[1]/4),0)])
+
+nondep_net_bottom_75_percent <- dep_net_overlap_from_bp_paper$fascicle[(round(dim(dep_net_overlap_from_bp_paper)[1]/4,0) +1):dim(dep_net_overlap_from_bp_paper)[1]]
+nondep_net_bottom_75_percent_w_suff <- nondep_net_bottom_75_percent %>%gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
+
+bottom_75_total_volume_nondep <- sum(dep_net_overlap_from_bp_paper$non_zero_voxels_in_dep_map[(round(dim(dep_net_overlap_from_bp_paper)[1]/4,0) +1):dim(dep_net_overlap_from_bp_paper)[1]])
+
+```
+
+### find names of fascicles in anxiety + dep network, unique to dep net, and unique to anxiety net
+```{r find_names_and_overlaps_of_dep_and_anxiety_networks}
+
+#I want to figure out what the volume is in all voxels within the overlap of depression and anxiety network, as well as within the nonoverlapping networks
+#the depression net overlap from bp paper contains a colum (num_voxels_total) that has the full voxel sizes of all of the fascicles. Will use this to help find the "total volume size"
+
+#total volume = 1545449
+#checked to make sure that dep_only_net_vol + anxiety_only_net_vol + dep_and_anxiety_net_overlap_net_volume = dep_and_anxiety_net_unique_net_volume
+
+dep_and_anxiety_combined <- c(fascicle_names_top_25_vol, dep_net_top_25_percent) #n = 38
+
+dep_and_anxiety_net_unique_names <- dep_and_anxiety_combined %>% unique() #n=34
+dep_and_anxiety_net_unique_net_volume <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_and_anxiety_net_unique_names]) #vol = 1048643
+
+dep_and_anxiety_net_overlap_names <- dep_and_anxiety_combined[dep_and_anxiety_combined %>% duplicated()] #n=4
+dep_and_anxiety_net_overlap_net_volume <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_and_anxiety_net_overlap_names]) #vol = 486260
+
+dep_only_names <- dep_and_anxiety_net_unique_names[!(dep_and_anxiety_net_unique_names %in% fascicle_names_top_25_vol)] #n=15
+dep_only_net_vol <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_only_names]) #vol = 370747
+
+anxiety_only_names <-dep_and_anxiety_net_unique_names[!(dep_and_anxiety_net_unique_names %in% dep_net_top_25_percent)] #n=15
+anxiety_only_net_vol <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% anxiety_only_names]) #vol = 191636
+
+### add suffix
+dep_and_anxiety_net_unique_names_w_suff <- dep_and_anxiety_net_unique_names  %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in
+
+dep_and_anxiety_net_overlap_names_w_suff <- dep_and_anxiety_net_overlap_names %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in
+
+dep_only_names_w_suff <- dep_only_names %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in
+
+anxiety_only_names_w_suff <- anxiety_only_names %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in 
+```
+
 ###Add columns in the main data frame indicating overall injury in the whole network, in the top 25 network (vol and prop), and bottom 75%
-```{r add_anxiety_network_details_to_data_frame}
+```{r add_anxiety_and_dep_network_details_to_data_frame}
 
@@
 
-  #sum of total volume lost in anxiety network and proportion of volume lost in anxietyn network (volume lost/network volume size) 
+  #sum of total volume lost in anxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) 
   mutate(sum_fascicle_vol_lost_inanxietynet_all = 
@@
 
-  #sum of total volume lost in anxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) 
+  #sum of total volume lost in anxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) top quartile
   mutate(sum_fascicle_vol_lost_inanxietynet_top_quartile = 
@@
 
-  #sum of total volume lost in nonanxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) 
+  #sum of total volume lost in nonanxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) bottom 3 quartiles
   mutate(sum_fascicle_vol_lost_nonanxiety_net_bottom_3_quartiles = 
@@
 
+  ##sum of total volume lost in depression network and proportion of volume lost in depression network (volume lost/network volume size) top quartile
+  mutate(sum_fascicle_vol_lost_indepressionnet_top_quartile = 
+           rowSums(across(all_of(dep_net_top_25_percent_w_suff)))) %>%
+  mutate(proportion_volume_lost_depression_net_by_network_size_sum_top_25 = sum_fascicle_vol_lost_indepressionnet_top_quartile/top_25_total_volume_dep) %>%
+
+  #sum of total volume lost in nondepression network and proportion of volume lost in depression network (volume lost/network volume size) bottom 3 quartiles
+  mutate(sum_fascicle_vol_lost_nondepression_net_bottom_3_quartiles = 
+           rowSums(across(all_of(nondep_net_bottom_75_percent_w_suff)))) %>%
+  mutate(proportion_volume_lost_nondepression_net_by_network_size_sum_bottom_75 = sum_fascicle_vol_lost_nondepression_net_bottom_3_quartiles/bottom_75_total_volume_nondep) %>%
+
+  ##sum of total volume lost in depression + anxiety network and proportion of volume lost in network (volume lost/network volume size) top quartile
+  mutate(sum_fascicle_vol_lost_indep_and_anxiety_net_combined = 
+           rowSums(across(all_of(dep_and_anxiety_net_unique_names_w_suff)))) %>%
+  mutate(proportion_fascicle_vol_lost_indep_and_anxiety_net_combined = sum_fascicle_vol_lost_indep_and_anxiety_net_combined/dep_and_anxiety_net_unique_net_volume) %>%
+
+  ##sum of total volume lost in areas of overlap between depression + anxiety network and proportion of volume lost in network (volume lost/network volume size) top quartile
+  mutate(sum_fascicle_vol_lost_indep_and_anxiety_net_overlap = 
+           rowSums(across(all_of(dep_and_anxiety_net_overlap_names_w_suff)))) %>%
+  mutate(proportion_fascicle_vol_lost_indep_and_anxiety_net_overlap = sum_fascicle_vol_lost_indep_and_anxiety_net_overlap/dep_and_anxiety_net_overlap_net_volume) %>%
+
+  ##sum of total volume lost in depression, no overlap with anxiety network and proportion of volume lost in network (volume lost/network volume size) top quartile
+  mutate(sum_fascicle_vol_lost_indepressionnet_no_anxiety_overlap = 
+           rowSums(across(all_of(dep_only_names_w_suff)))) %>%
+  mutate(proportion_fascicle_vol_lost_indepressionnet_no_anxiety_overlap = sum_fascicle_vol_lost_indepressionnet_no_anxiety_overlap/dep_only_net_vol) %>%
+
+    ##sum of total volume lost in anxiety, no depression overlap network and proportion of volume lost in network (volume lost/network volume size) top quartile
+  mutate(sum_fascicle_vol_lost_inanxietynet_no_depression_overlap = 
+           rowSums(across(all_of(anxiety_only_names_w_suff)))) %>%
+  mutate(proportion_fascicle_vol_lost_inanxietynet_no_depression_overlap = sum_fascicle_vol_lost_inanxietynet_no_depression_overlap/anxiety_only_net_vol) %>%
+
   ungroup()
@@
 ```{r anxiety_net_intx}
+
+## demographics
+
+### BEST SPLIT IS STRATIFYING ON ANXIETY MEDS!!!! Better than on variable that includes anxietyGroupVar(meds + anxiety diagnoses), or anxiety diagnosis alone
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietyGroupVar!= 0,])
 
@@
   mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
+  mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker, "On.Anxiolytics", "Off.Anxiolytics")) %>%
+  mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
+  mutate(Benzo_status = ifelse(On.Benzos, "On.Benzos", "Off.Benzos")) %>%
+  mutate(Benzo_status = as.factor(Benzo_status)) %>%
   mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
   mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
-  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
-  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
+  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, Anxiolytics_status, Has.anxietydx, Benzo_status, PAT_AGE_AT_EXAM) %>% 
+  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -Anxiolytics_status, -Has.anxietydx, -Benzo_status) %>% #this is like a melt.
+Keeps empi and depGroupVar out of the melt
   mutate(Network = as.factor(Network)) %>%
@@
 #simple t test, disease within versus outside anxiety network; mean within anxiety net: 0.5426694 affected, mean outside anxiety network = 0.3062429, T=57.44, p<2.2*10^-16, 95% CI 0.22-0.24
-
+#MS+Anxiety, MS-Anxiety, meds + anxiety dx, true normal = 0.3850697; MS+ anxiety: ; MS-anxiety: 0.3672053
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"])
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])
+
+#Anxiety dx vs no anxiety dx
+#anxiety dx: 0.3785979; no anxiety dx: 0.3723245
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.anxietydx==1])
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.anxietydx==0])
+
+#On.Anxiolytics vs Off.Anxiolytics
+#on anxiolytics: 0.415625; off anxiolytics:0.3664898
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Anxiolytics_status=="On.Anxiolytics"])
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Anxiolytics_status=="Off.Anxiolytics"])
+
+#On.Benzos vs Off.Benzos
+#on benzos: 0.4022933; off benzos:0.372135
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Benzo_status=="On.Benzos"])
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Benzo_status=="Off.Benzos"])
+
+#histos
 hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"])
 hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"])
+
+## Means of separate groups:
 
@@
 
-```
-# Compare anxiety burden (presence of condition, number of anxiety comorbidities) by fascicle, by overall injury, and by volume of lesions
-```{r compare_anxiety_burden_by_fascicle_injury_lesion_volume}
-
+## Anxiety network x anxiolytics status
+#Network (nonanxiety <anxiety network) : T = -58.141   <2e-16 ***; Anxiolytic status: On.anxiolytics>off.anxiolytics; T= 2.473   0.0136 *  
+#Mean prop affected: on anxiolytics: 0.415625;  off anxioloytics: 0.3664898
+
+disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer <- lmer(proportion_affected ~ Network*Anxiolytics_status + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
+confint(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
+
+## Anxiety network x benzo status
+#Network (nonanxiety <anxiety network) : T = -54.535   <2e-16***; Anxiety status: T = 0.462    P = 0.645
+
+disease_within_vs_outside_anxiety_net_by_benzo_lmer <- lmer(proportion_affected ~ Network*Benzo_status + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
+confint(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
+
+## Anxiety network x anxiety diagnosis
+#Network (nonanxiety <anxiety network) : T = -54.535   <2e-16***; Anxiety status: T = 0.462    P = 0.645
+
+disease_within_vs_outside_anxiety_net_by_anxietydx_lmer <- lmer(proportion_affected ~ Network*Has.anxietydx + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
+confint(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
 ```

### 2024-06-11 scripts/clean_dac_pull_icd10_codes_and_make_clean_df.R

@@ -159,6 +159,7 @@ data_final_rds <-data_pull %>%
   mutate(Has.Anxiety.No.Depression = ifelse((anxietyGroupVar == 2 & depGroupVar != 2), 1, 0)) %>%
   mutate(Has.Depression.No.Anxiety = ifelse((anxietyGroupVar != 2 & depGroupVar == 2), 1, 0)) %>%
   mutate(Has.Depression.And.Anxiety = ifelse((anxietyGroupVar == 2 & depGroupVar == 2), 1, 0)) %>%
+  mutate(Anxiety.And.Dep.GroupVar = ifelse(healthy_ish, 1, ifelse(Has.Anxiety.No.Depression, 2, ifelse(Has.Depression.No.Anxiety, 3, ifelse(Has.Depression.And.Anxiety, 4, 0))))) %>% #healthy = 1, anxiety alone = 2, dep no anxiety only = 3, dep + anxiety = 4, exclude 0) 
   ungroup() #n=3,737 unique people, n= 16,830 total
 
 

### 2024-06-11 scripts/ms_functions.R

@@ -26,6 +26,120 @@ require('circlize')
 ####### Demographics ########
 #############################
 
+#### anxiety demographics
+make_demographics_table_ms_anxiety<- function(data_frame) {
+  #subset demographics
+  
+  listVars <- c("Race", 
+                "Sex",
+                "Age",
+                "Anxiety",
+                "Anxiety.And.Dep.GroupVar",
+                "PHQ2",
+                "PHQ9",
+                "Has.depdx", 
+                "Has.anxietydx", 
+                "On.Antidepressants",
+                "On.Anxiolytics_no_beta_blocker",
+                "on_anti_cd20",
+                "on_interferon",
+                "on_steroids",
+                "on_dmt",
+                "number_of_dx",
+                "number_of_dx_extended",
+                "number_of_psychiatric_comorbidities_extended",
+                "number_of_anxiety_comorbidities_extended",
+                "number_of_medications",
+                "on_bcp",
+                "volume_of_mimosa_lesions", 
+                "sum_fascicle_vol_lost",
+                "proportion_volume_lost_per_total_network_size_sum",
+                "sum_fascicle_vol_lost_inanxietynet_all",
+                "proportion_volume_lost_anxiety_net_by_network_size_sum",
+                "sum_fascicle_vol_lost_inanxietynet_top_quartile",
+                "proportion_volume_lost_anxiety_net_by_network_size_sum_top_25", 
+                "sum_fascicle_vol_lost_nonanxiety_net_bottom_3_quartiles",
+                "proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75",
+                "proportion_volume_lost_depression_net_by_network_size_sum_top_25",
+                "proportion_volume_lost_nondepression_net_by_network_size_sum_bottom_75",
+                "proportion_fascicle_vol_lost_indep_and_anxiety_net_combined",
+                "proportion_fascicle_vol_lost_indep_and_anxiety_net_overlap",
+                "proportion_fascicle_vol_lost_indepressionnet_no_anxiety_overlap",
+                "proportion_fascicle_vol_lost_inanxietynet_no_depression_overlap") #Race 1 = caucasian, Sex 1 = M age = years
+
+  
[…]

### 2024-06-12 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
Add files via upload

@@
 
-bottom_75_total_volume_nondep <- sum(dep_net_overlap_from_bp_paper$non_zero_voxels_in_dep_map[(round(dim(dep_net_overlap_from_bp_paper)[1]/4,0) +1):dim(dep_net_overlap_from_bp_paper)[1]])
+bottom_75_total_volume_nondep <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[(round(dim(dep_net_overlap_from_bp_paper)[1]/4,0) +1):dim(dep_net_overlap_from_bp_paper)[1]])
 
@@
 ### BEST SPLIT IS STRATIFYING ON ANXIETY MEDS!!!! Better than on variable that includes anxietyGroupVar(meds + anxiety diagnoses), or anxiety diagnosis alone
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietyGroupVar!= 0,])
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietyGroupVar != 0,])
 
@@
   mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
-  mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker, "On.Anxiolytics", "Off.Anxiolytics")) %>%
+  mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
   mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
-  mutate(Benzo_status = ifelse(On.Benzos, "On.Benzos", "Off.Benzos")) %>%
+  mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
   mutate(Benzo_status = as.factor(Benzo_status)) %>%

### 2024-06-12 scripts/clean_dac_pull_icd10_codes_and_make_clean_df.R

@@ -124,8 +124,8 @@ data_final_rds <-data_pull %>%
   mutate(number_of_mood_comorbidities_extended = ifelse(!is.na(all_icd10_dx), str_count(all_icd10_dx, "F3"), 0)) %>%
   mutate(number_of_medications = ifelse(!is.na(Medication), str_count(Medication, ";") + 1, 0)) %>%
   mutate(On.Bcp = ifelse(str_detect(Medication, paste(bcp$bcp_name, collapse = "|")), 1, 0)) %>%
-  mutate(On.Psych.Meds = ifelse(str_detect(Medication, paste(psych_meds$Medication, collapse = "|")), 1, 0)) %>%
-  mutate(On.Psych.Meds.Extended = ifelse(str_detect(Medication, paste(psych_meds_extended$Medication, collapse = "|")), 1, 0)) %>% #extended includes amitriptyline and gabapentin (and brands) in med list
+  mutate(On.Psych.Meds = ifelse(str_detect(Medication, paste(psych_meds$Medication.Name, collapse = "|")), 1, 0)) %>%
+  mutate(On.Psych.Meds.Extended = ifelse(str_detect(Medication, paste(psych_meds_extended$Medication.Name, collapse = "|")), 1, 0)) %>% #extended includes amitriptyline and gabapentin (and brands) in med list
   mutate(On.Antidepressants = ifelse(str_detect(Medication, paste(psych_meds$Medication[psych_meds$Antidepressant == "t"], collapse = "|")), 1, 0)) %>%
   mutate(On.Anxiolytics = ifelse(str_detect(Medication, paste(anxiety_meds$Medication, collapse = "|")), 1, 0)) %>%
   mutate(On.Anxiolytics_no_beta_blocker = ifelse(str_detect(Medication, paste(anxiety_meds_no_beta_blocker$Medication, collapse = "|")), 1, 0)) %>%
@@ -139,27 +139,26 @@ data_final_rds <-data_pull %>%
   mutate(Has.depdx = ifelse(grepl("F3[2:4]", all_icd10_dx), 1, 0)) %>%
[…]

### 2024-06-12 scripts/ms_functions.R

@@ -33,10 +33,8 @@ make_demographics_table_ms_anxiety<- function(data_frame) {
   listVars <- c("Race", 
                 "Sex",
                 "Age",
-                "Anxiety",
+                "AnxietyGroupVar",
                 "Anxiety.And.Dep.GroupVar",
-                "PHQ2",
-                "PHQ9",
                 "Has.depdx", 
                 "Has.anxietydx", 
                 "On.Antidepressants",
@@ -45,6 +43,8 @@ make_demographics_table_ms_anxiety<- function(data_frame) {
                 "on_interferon",
                 "on_steroids",
                 "on_dmt",
+                "PHQ2",
+                "PHQ9",
                 "number_of_dx",
                 "number_of_dx_extended",
                 "number_of_psychiatric_comorbidities_extended",
@@ -74,8 +74,6 @@ make_demographics_table_ms_anxiety<- function(data_frame) {
                       data_frame$PAT_AGE_AT_EXAM, 
                       data_frame$anxietyGroupVar,
                       data_frame$Anxiety.And.Dep.GroupVar,
-                      data_frame$PHQ.2, 
-                      data_frame$PHQ.9, 
                       data_frame$Has.depdx, 
                       data_frame$Has.anxietydx, 
                       data_frame$On.Antidepressants,
@@ -84,6 +82,8 @@ make_demographics_table_ms_anxiety<- function(data_frame) {
                       data_frame$On.Interferon,
                       data_frame$On.Steroids,
                       data_frame$On.Dmt,
+                      data_frame$PHQ.2, 
+                      data_frame$PHQ.9, 
                       data_frame$number_of_dx, 
                       data_frame$number_of_dx_extended, 
                       data_frame$number_of_psychiatric_comorbidities_extended,
@@ -119,11 +119,11 @@ make_demographics_table_ms_anxiety<- function(data_frame) {
   
   
   #Define Categorical Variables
-  cat_variables <- c("Race", "Sex", "Anxiety", "Has.anxietydx,", "On.Anxiolytics_no_beta_blockers","Has.depdx", "On.Antidepressants", "on_anti_cd20", "on_interferon", "on_steroids", "on_dmt", "on_bcp")
[…]

### 2024-06-20 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
Add files via upload

@@
 library(stringr)
+library(MatchIt)
 #functions
@@
 
-###Calculate injury to networks for each subject
+###Calculate injury to yeo networks for each subject
 ```{r calculate_injury_to_network}
@@
 bottom_75_total_volume <- sum(neurosynth_anxiety_network_fascicle_overlap$num_voxels_total[neurosynth_anxiety_network_fascicle_overlap$fascicle %in% fascicle_names_bottom_75_vol]) #vol = 548305
+
+### Sort all the fascicles by %overlap, in decreasing order (so highest overlap at the top), and then take names of the top quartile, save for making binary maps later
+anxiety_network_names_top_quartile_no_cranial_nerves<- (neurosynth_anxiety_network_fascicle_overlap[order(neurosynth_anxiety_network_fascicle_overlap$non_zero_voxels_in_anxiety_map, decreasing = TRUE),])$fascicle[1:number_of_brain_regions_in_top_25]
+
+write.table(anxiety_network_names_top_quartile_no_cranial_nerves, paste0(homedir, "/results/anxiety_network_names_top_quartile_no_cranial_nerves_by_vol.txt"), row.names = F, col.names = F, quote = F)
+
+df_for_making_binary_color_maps_vol <- neurosynth_anxiety_network_fascicle_overlap %>% dplyr::select(fascicle, non_zero_voxels_in_anxiety_map)
+
+write.table(df_for_making_binary_color_maps_vol, paste0(homedir, "/results/volume_of_overlap_w_anxiety_net_n77.csv"), row.names = F, col.names = F, quote = F, sep = ",")
+
+df_for_making_binary_color_maps_prop <- neurosynth_anxiety_network_fascicle_overlap %>% dplyr::select(fascicle, prop_in_mask)
+
+write.table(df_for_making_binary_color_maps_prop, paste0(homedir, "/results/proportion_of_overlap_w_anxiety_net_n77.csv"), row.names = F, col.names = F, quote = F, sep = ",")
 
@@
   mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
+  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, Anxiolytics_status, Has.anxietydx, Benzo_status, PAT_AGE_AT_EXAM) %>% 
+  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -Anxiolytics_status, -Has.anxietydx, -Benzo_status) %>% #this is like a melt.
+Keeps empi and depGroupVar out of the melt
+  mutate(Network = as.factor(Network)) %>%
+  ungroup()
+
+#simple t test, disease within versus outside anxiety network; mean within anxiety net: 0.5426694 affected, mean outside anxiety network = 0.3062429, T=57.44, p<2.2*10^-16, 95% CI 0.22-0.24
+#MS+Anxiety, MS-Anxiety, meds + anxiety dx, true normal = 0.3850697; MS+ anxiety: ; MS-anxiety: 0.3672053
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"])
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])
+
+#Anxiety dx vs no anxiety dx
+#anxiety dx: 0.3785979; no anxiety dx: 0.3723245
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.anxietydx==1])
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.anxietydx==0])
+
+#On.Anxiolytics vs Off.Anxiolytics
+#on anxiolytics: 0.415625; off anxiolytics:0.3664898
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Anxiolytics_status=="On.Anxiolytics"])
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Anxiolytics_status=="Off.Anxiolytics"])
+
+#On.Benzos vs Off.Benzos
+#on benzos: 0.4022933; off benzos:0.372135
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Benzo_status=="On.Benzos"])
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Benzo_status=="Off.Benzos"])
+
+#histos
+hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], main = "Anxiety Network Injury", xlab = "Proportion Affected")
+hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], main = "Nonanxiety Network Injury", xlab = "Proportion Affected")
+
+## Means of separate groups:
+
+#t test, t = 63.621, df = 718, p-value < 2.2e-16; 95 percent confidence interval:0.2349467 0.2499088, mean diff: 0.2424277 
+within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
+summary(within_vs_outside_anxiety_net_t)
+
+ #simple lmer, confirms T; -63.62   <2e-16 ***
+disease_within_vs_outside_anxiety_net_lmer <- lmer(proportion_affected ~ Network + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_lmer)
+
+ #Net by sex, confirms T; -63.62   <2e-16, but no sex differences (p=0.179)
+disease_within_vs_outside_anxiety_net_sex_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_sex_lmer)
+
+ #simple lmer, confirms network: -63.621  < 2e-16 , Pat age: 6.338 4.12e-10
+disease_within_vs_outside_anxiety_net_age_lmer <- lmer(proportion_affected ~ Network + PAT_AGE_AT_EXAM + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_age_lmer)
+
+#Age * network interaction, don't know if this is valid at all. outside > w/in net: -12.718  < 2e-16 ***; pat age = 6.837  1.6e-11 ***, NetworkNonanxiety_network:PAT_AGE_AT_EXAM -2.852  0.00447 
+disease_within_vs_outside_anxiety_net_age_intx_lmer <- lmer(proportion_affected ~ Network*PAT_AGE_AT_EXAM + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_age_intx_lmer)
+
+#diagnosis: NS
+diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
+summary(diagnosis_by_network_interaction_lmer)
+
+#Diagnosis: NS
+confint(diagnosis_by_network_interaction_lmer)
+
+## Anxiety network x anxiolytics status
+#Network (nonanxiety <anxiety network) : T = -58.141   <2e-16 ***; Anxiolytic status: On.anxiolytics>off.anxiolytics; T= 2.473   0.0136 *  
+#Mean prop affected: on anxiolytics: 0.415625;  off anxioloytics: 0.3664898
+
+disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer <- lmer(proportion_affected ~ Network*Anxiolytics_status + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
+confint(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
+
+## Anxiety network x benzo status
+#Network (nonanxiety <anxiety network) : T = -54.535   <2e-16***; Anxiety status: T = 0.462    P = 0.645
+
+disease_within_vs_outside_anxiety_net_by_benzo_lmer <- lmer(proportion_affected ~ Network*Benzo_status + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
+confint(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
+
+## Anxiety network x anxiety diagnosis
+#Network (nonanxiety <anxiety network) : T = -54.535   <2e-16***; Anxiety status: T = 0.462    P = 0.645
+
+disease_within_vs_outside_anxiety_net_by_anxietydx_lmer <- lmer(proportion_affected ~ Network*Has.anxietydx + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
+confint(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
+```
+
+### Anxiety network interaction, matching groups 
+```{r anxiety_net_intx}
+
+## demographics
+
+### BEST SPLIT IS STRATIFYING ON ANXIETY MEDS!!!! Better than on variable that includes anxietyGroupVar(meds + anxiety diagnoses), or anxiety diagnosis alone
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietyGroupVar != 0,])
+
+#clean up data frame
+df_prematched <- df_demo_and_fascicles %>%
+  filter(anxietyGroupVar != 0) %>% #lose 93, n now 719
+  mutate(anxietyGroupVar = as.factor(anxietyGroupVar)) %>%
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = ifelse(anxietyGroupVar==1, "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
+  mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
+  mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
+  mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
+  mutate(Benzo_status = as.factor(Benzo_status)) %>%
+  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
+  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
+  ungroup()
+
+#Do the match
+### first, check the prematched data, can play with which variable I want to match on, Has.anxietydx, anxietyGroupVar, Anxiolytics_status
+m.out.prematched <- matchit(anxietyGroupVar ~ sex_binarized + PAT_AGE_AT_EXAM , data = df_prematched,
+                 method = NULL, distance = "glm")
+summary(m.out.prematched)
+
+#then, do the match with the "nearest" method
+m.out.matched <-  matchit(anxietyGroupVar ~ sex_binarized + PAT_AGE_AT_EXAM , data = df_prematched,
+                 method = "nearest", distance = "glm")
+
+#display output
+summary(m.out.matched, un = FALSE)
+
+#add column for keeping to the prematched data frame
+df_prematched$keep <- m.out.matched$weights
+
+#drop values to not keep
+
+df_matched <- df_prematched %>% filter(keep == 1)
+
+### check demographics
+make_demographics_table_ms_anxiety(data_frame = df_matched)
+
+df_empi_dx_network_proportions <-  df_matched %>%
   dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, Anxiolytics_status, Has.anxietydx, Benzo_status, PAT_AGE_AT_EXAM) %>% 

### 2024-06-20 scripts/make_binary_colored_anxiety_net_maps.R

@@ -1,0 +1,43 @@
+#### Welcome to make_binary_colored_depression_net_maps! ####
+
+### I developed this script because I wanted to make my own RGB color palettes for DSI studio. 
+### In short, I want to color each fascicle according to whether or not it is in the depression map. Yellow is dep map, blue is non dep map (though this is flexible)
+
+### Pre: File of fascicle overlap with depression network proportions
+### Post: Output of RGB values in colors
+### Uses: Opens up proportions, sorts by overlap to get a name of a vector in top quartile
+###       iterate through each fascicle, if in the top quartile, color will be first color, if not, will be second color
+###       **** If you change colors!!! CHANGE SUFFIX***
+### Dependencies: Any R will do, need the names of the fibers in the depression network, and a file with proportions
+
+
+homedir="/Users/eballer/BBL/msanxiety/"
+
+anxiety_network_names_top_quartile_no_cranial_nerves_by_vol <- read.csv(file = paste0(homedir, "/results/anxiety_network_names_top_quartile_no_cranial_nerves_by_vol.txt"), header = F)
+
+files = c("proportion_of_overlap_w_anxiety_net_n77", "volume_of_overlap_w_anxiety_net_n77") #c("fascicle_proportion_overlap_with_depression_network_n77")
+
+color_anxiety_net = "132 29 226" #purple
+#color_nonanxiety_net = "123 226 29" #green
+color_nonanxiety_net = "211 211 211" #light grey
+#color_nonanxiety_net = "0 255 255" #light blue
+#color_anxiety_net = "255 255 0" #yellow
+#color_nonanxiety_net = "0 0 255" #blue
+
+for (filename in files) {
+  #suffix, CHANGE IF YOU WANT A DIFFERENT FLAG
+  suffix = "purple_grey"
+  
+  #read in file with fascicle name and proportion
+  fascicle_name_and_prop <- read.csv(paste0(homedir, "/results/", filename, ".csv"), sep = ",", header = F)
+  names(fascicle_name_and_prop) <- c("fascicle", "proportion")
+  
+  #output color file (77 lines, each represents a color), and color name vector. Not sure how to do 1:1 assignments rather than manually, but I'll see if I can figure that out!
+  fascicle_name_and_prop_rgb_only <- fascicle_name_and_prop %>%
[…]

### 2024-07-11 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
making more grouping variables
Really trying to figure out how best to carve the EMR anxiety space

@@
 
+dep_and_anxiety_net_overlap_names_no_CC <- dep_and_anxiety_net_overlap_names[dep_and_anxiety_net_overlap_names != "CC"]
+dep_and_anxiety_net_overlap_net_volume_no_CC <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_and_anxiety_net_overlap_names_no_CC]) #vol = 95659
+
 dep_only_names <- dep_and_anxiety_net_unique_names[!(dep_and_anxiety_net_unique_names %in% fascicle_names_top_25_vol)] #n=15
@@
 dep_and_anxiety_net_overlap_names_w_suff <- dep_and_anxiety_net_overlap_names %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in
+
+dep_and_anxiety_net_overlap_names_w_suff_no_CC <- dep_and_anxiety_net_overlap_names_no_CC %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in
 
@@
 
+  ##sum of total volume lost in areas of overlap between depression + anxiety network and proportion of volume lost in network (volume lost/network volume size), no CC
+  mutate(sum_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC = 
+           rowSums(across(all_of(dep_and_anxiety_net_overlap_names_w_suff_no_CC)))) %>%
+  mutate(proportion_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC = sum_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC/dep_and_anxiety_net_overlap_net_volume_no_CC) %>%
+
   ##sum of total volume lost in depression, no overlap with anxiety network and proportion of volume lost in network (volume lost/network volume size) top quartile
@@
 make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietyGroupVar != 0,])
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$Has.Anxietydx.AND.AntianxietymedGroupVar != 0,])
 
@@
 
+#Has.Anxietydx.Or.Antianxietymed
+#on benzos: 0.4022933; off benzos:0.372135
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.Anxietydx.Or.Antianxietymed=="On.Benzos"])
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.Anxietydx.Or.Antianxietymed=="Off.Benzos"])
+
 #histos
@@
 #Network (nonanxiety <anxiety network) : T = -54.535   <2e-16***; Anxiety status: T = 0.462    P = 0.645
+
+disease_within_vs_outside_anxiety_net_by_anxietydx_lmer <- lmer(proportion_affected ~ Network*Has.anxietydx + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
+confint(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
+```
+
+#Anxiety network interactions and uncinate alone
+```{r anxiety_net_intx}
+
+## demographics
+
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$Has.Anxietydx.AND.AntianxietymedGroupVar != 0,])
+
+#clean up data frame
+cleaned_df <- df_demo_and_fascicles %>%
+  filter(Has.Anxietydx.AND.AntianxietymedGroupVar != 0) %>% #lose 93, n now 719
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = ifelse(Has.Anxietydx.AND.AntianxietymedGroupVar==1, "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
+  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
+  mutate(mean_uncinate_injury = (UF_L_prop + UF_R_prop)/2) %>%
+  mutate(mean_uncinate_and_fornix_injury = (UF_L_prop + UF_R_prop + F_R_prop + F_L_prop)/2) %>%
+  ungroup()
+
+df_empi_dx_network_proportions <- cleaned_df %>%
+  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
+  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
+  mutate(Network = as.factor(Network)) %>%
+  ungroup()
+
+#histos
+hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], main = "Anxiety Network Injury", xlab = "Proportion Affected")
+hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], main = "Nonanxiety Network Injury", xlab = "Proportion Affected")
+hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS+Anxiety"], main = "Uncinate Injury in Anxious Patients", xlab = "Proportion Affected")
+hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS-Anxiety"], main = "Uncinate Injury in Healthyish Patients", xlab = "Proportion Affected")
+
+## Means of separate groups:
+
+#t test, 
+within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
+within_vs_outside_anxiety_net_t
+
+#diagnosis: 
+diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
+summary(diagnosis_by_network_interaction_lmer)
+confint(diagnosis_by_network_interaction_lmer)
+
+#Net by sex, confirms T; -63.62   <2e-16, but no sex differences (p=0.179)
+disease_within_vs_outside_anxiety_net_sex_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_sex_lmer)
+
+#t test uncinate alone
+mean_uncinate_by_dx_t <- t.test(cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
+mean_uncinate_by_dx_t
+
+#diagnosisxmean_uncinate: 
+diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_injury ~ Diagnosis, data = cleaned_df)
+summary(diagnosis_by_network_interaction_lmer)
+confint(diagnosis_by_network_interaction_lmer)
+
+#diagnosisxmean_uncinate+fornix: 
+diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_and_fornix_injury ~ Diagnosis, data = cleaned_df)
+summary(diagnosis_by_network_interaction_lmer)
+confint(diagnosis_by_network_interaction_lmer)
+
+#### if I decide later I want to look at L and right uncinate alone
+
+#t test uncinate alone, Left,
+l_uncinate_by_dx_t <- t.test(cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
+l_uncinate_by_dx_t
+
+#t test uncinate alone, right, remember everybody is double counted!!!! so this needs to be fixed.
+r_uncinate_by_dx_t <- t.test(cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
+r_uncinate_by_dx_t
+
+```
+
+## Anxiety burden severity T test ranking
+
+I am wondering here if, as my brain wants to think, that things in the chart reflect severity of anxiety.
+For example, I'd expect people with dep and anxiety comorbidity and on meds would be the sickest, followed by anxiety + on meds, then on meds, then anxiety dx, then healthyish.
+I am going to do a t-test comparing proportion of disease over whole brain, over anxiety net, and over uncinate in each of those groups as compared to the healthy group, and rank the T to see if that pattern bears out.
+And if it does, do some sort of regression.
+```{r anxiety_burden_severity_ranking }
+#variables_to_evaluate <- c("Has.Anxietydx.AND.AntianxietymedGroupVar")
+df_disease_burden_unc_and_anx_net <- df_demo_and_fascicles %>%
+  filter(oAnxiety.And.Dep.And.AnxietyMedsGroupVar != "unclassified") %>%
+  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxiety.And.Dep.And.AnxietyMedsGroupVar, osex)
+
+tibble_n <- df_disease_burden_unc_and_anx_net %>% 
+  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>% 
+  summarise(n())
+
+tibble_overall_disease <- 
+  df_disease_burden_unc_and_anx_net %>% 
+  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
+  summarize(mean_size = mean(proportion_volume_lost_per_total_network_size_sum))
+
+tibble_overall_summaries <- 
+  df_disease_burden_unc_and_anx_net %>% 
+  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+tibble_overall_summaries
+
+tibble_overall_summaries_by_sex <- 
+  df_disease_burden_unc_and_anx_net %>% 
+  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar, osex) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+  tibble_overall_summaries_by_sex
+
+  tibble_overall_summaries_females <- 
+  df_disease_burden_unc_and_anx_net %>% 
+  filter(osex == "Female") %>%
+  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+  tibble_overall_summaries_females
+
+    tibble_overall_summaries_males <- 
+  df_disease_burden_unc_and_anx_net %>% 
+  filter(osex == "Male") %>%
+  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+  tibble_overall_summaries_males
+
+  ### analyses
+
+```
+
+###Collapse anxiety dx and antianxiety meds with those plus depression
+```{r group_anxietydx_meds_and_dep_comorbidity}
+
+#this collapses anxiety group + meds with those with anxiety group + meds + with/without depression
+
+df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
+  filter(oAnxietydx.Meds.Inc.Dep.Collapsed != "unclassified") %>%
+  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxietydx.Meds.Inc.Dep.Collapsed, osex)
+
+ tibble_overall_summaries <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+tibble_overall_summaries
+
+tibble_overall_summaries_by_sex <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed, osex) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+  tibble_overall_summaries_by_sex
+
+  tibble_overall_summaries_females <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  filter(osex == "Female") %>%
+  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+  tibble_overall_summaries_females
+
+    tibble_overall_summaries_males <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  filter(osex == "Male") %>%
+  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+  tibble_overall_summaries_males
+
+  #mean disease
+  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_mean_disease_lm)
+
+  anxietyGrouping_by_sex_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_by_sex_mean_disease_lm)
+
+  #anxiety network
+  anxietyGrouping_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_anxiety_net_lm)
+
+  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_by_sex_anxiety_net_lm)
+
+  #UF R
+  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_UF_R_lm)
+
+  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_UF_R_by_sex_lm)
+
+  #UF L
+  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_UF_L_lm)
+
+  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_UF_L_by_sex_lm)
+
+  #burden of anxiety by network
+  #clean up data frame
+  df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
+  #filter(oAnxietydx.Meds.Inc.Dep.Collapsed != "unclassified") %>%
+  filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>% 
+  #filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "Has.anxietydx")) %>%  #-> doesn't work
+ # filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "On.Anxiolytics")) %>% #-> doesn't work
+  mutate(subject = as.factor(EMPI)) %>%
+#  mutate(Diagnosis = oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oAnxietydx.Meds.Inc.Dep.Collapsed=="healthy_ish", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  #mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
+  #mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
+  #mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
+  ##mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
+  #mutate(Benzo_status = as.factor(Benzo_status)) %>%
+  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
+  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
+  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
+  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
+  mutate(Network = as.factor(Network)) %>%
+  ungroup()
+
+## Means of separate groups:
+
+#t test, t, t = 37.378, df = 271, p-value < 2.2e-16, anxiety net: 0.4974984; nonanxiety net: 0.256347
+within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
+summary(within_vs_outside_anxiety_net_t)
+
+#t test, between diagnoses, NS, mean MS+ANXIETY = .40, MS-Anxiety = 0.37
+between_dx_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])
+summary(between_dx_t)
+
+#means
+
+#mean = 0.5381082
+mean_anxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
+mean_anxiety_dx_anx_net
+
+#mean = 0.2681277
+mean_anxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
+mean_anxiety_dx_nonanx_net
+
+#mean = 0.4911045
+mean_nonanxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
+mean_nonanxiety_dx_anx_net
+
+#mean = 0.2544921
+mean_nonanxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
+mean_nonanxiety_dx_nonanx_net
+
+ #simple lmer, NetworkNonanxiety_network  -0.241926   0.003943 661.000022  -61.36   <2e-16 ***
+disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
+
+#Network confit:NetworkNonanxiety_network -0.2496593 -0.23419230
+confint(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
+```
+
+### Plot within vs outside network
+```{r plottting_bar_graph}
+
+#Within vs outside network
+anxiety_net_group <- c(rep("Anxiety Network", times = dim(df_demo_and_fascicles)[1]), rep("Nonanxiety Network",times =dim(df_demo_and_fascicles)[1]))
+net_values <- c(df_demo_and_fascicles$proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, df_demo_and_fascicles$proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75)
+
+newdf <- data.frame(anxiety_net_group, net_values)
+
+newdf <- newdf %>%
+  mutate( anxiety_net_group=factor(anxiety_net_group,levels=c( "Nonanxiety Network", "Anxiety Network")))
+
+violin_within_vs_outside_network_sum_proportion_scaled_by_network_size <- ggplot(newdf, aes(x=anxiety_net_group, y=net_values, fill=anxiety_net_group)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  ggtitle(paste0("Volume of Fascicle Disease Burden")) +
+  ylab("Proportion of network affected") +
+  ylim(0,1) + 
+  scale_fill_manual(values=c("#D3D3D3", "#841DE2")) +
+  theme(plot.title = element_text(size=16, hjust = 0.55),
+        axis.text = element_text(size = 16, colour = "black"), axis.title.y  = element_blank(), 
+        axis.title.x = element_text(size=16),
+        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
+        legend.position = "none",
+        aspect.ratio=4/7,
+        panel.background = element_rect(colour = "white", fill = "white")) + 
+  coord_flip()
+
+#display
+violin_within_vs_outside_network_sum_proportion_scaled_by_network_size
+```
+
+### AnxietydxANDbenzoGroupVar within/outside network
+```{r anxiety_net_intx}
+
+## demographics
+
+### demographics
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietydxANDbenzoGroupVar != 0,])
+
+#clean up data frame
+df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
+  filter(anxietydxANDbenzoGroupVar != 0) %>% #lose 150, n now 662
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = ifelse(anxietydxANDbenzoGroupVar==1, "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
+  mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
+  mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
+  mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
+  mutate(Benzo_status = as.factor(Benzo_status)) %>%
+  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
+  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
+  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, Anxiolytics_status, Has.anxietydx, Benzo_status, PAT_AGE_AT_EXAM) %>% 
+  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -Anxiolytics_status, -Has.anxietydx, -Benzo_status) %>% #this is like a melt.
+Keeps empi and depGroupVar out of the melt
+  mutate(Network = as.factor(Network)) %>%
+  ungroup()
+
+#MS+Anxiety, MS-Anxiety, benzos + anxiety dx, true normal = 0.3782694; MS+ anxiety: ; MS-anxiety: 0.3672053
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"])
+mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])
+t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
+
+#histos
+hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], main = "Anxiety Network Injury", xlab = "Proportion Affected")
+hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], main = "Nonanxiety Network Injury", xlab = "Proportion Affected")
+
+## Means of separate groups:
+
+#t test, t; t = 61.356, df = 661, p-value < 2.2e-16; 95 percent confidence interval:0.2341835 0.2496681
+within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
+summary(within_vs_outside_anxiety_net_t)
+
+ #simple lmer, NetworkNonanxiety_network  -0.241926   0.003943 661.000022  -61.36   <2e-16 ***
+disease_within_vs_outside_anxiety_net_lmer <- lmer(proportion_affected ~ Network + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_lmer)
+
+#Network confit:NetworkNonanxiety_network -0.2496593 -0.23419230
+confint(disease_within_vs_outside_anxiety_net_lmer)
+
+#diagnosis: NS; DiagnosisMS+Anxiety T=  0.811, p=    0.418    ; NetworkNonanxiety_network T= -49.984   p<2e-16 ***
+diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
+summary(diagnosis_by_network_interaction_lmer)
+
+#Diagnosis: NS
+confint(diagnosis_by_network_interaction_lmer)
+
+## Anxiety network x anxiolytics status
+#Network (nonanxiety <anxiety network) : 
+# anxiolytic status: Anxiolytics_statusOn.Anxiolytics 0.064088   0.031256 736.439692    2.05   0.0407 *  
+#Mean prop affected:
+
+disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer <- lmer(proportion_affected ~ Network*Anxiolytics_status + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
+confint(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
+
+## Anxiety network x benzo status
+#Network (nonanxiety <anxiety network) -59.082   <2e-16; Anxiety status: T = 1.210    P = 0.227
+
+disease_within_vs_outside_anxiety_net_by_benzo_lmer <- lmer(proportion_affected ~ Network*Benzo_status + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
+confint(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
+
+## Anxiety network x anxiety diagnosis
+#Network (nonanxiety <anxiety network) :  -51.733   <2e-16 *** ; Anxiety status:  0.721    0.471
 
@@
 
+### Plot within vs outside network, matched groups
+```{r plottting_bar_graph_matched}
+
+#Within vs outside network
+anxiety_net_group <- c(rep("Anxiety Network", times = dim(df_matched)[1]), rep("Nonanxiety Network",times =dim(df_matched)[1]))
+net_values <- c(df_matched$proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, df_matched$proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75)
+
+newdf <- data.frame(anxiety_net_group, net_values)
+
+newdf <- newdf %>%
+  mutate( anxiety_net_group=factor(anxiety_net_group,levels=c( "Nonanxiety Network", "Anxiety Network")))
+
+violin_within_vs_outside_network_sum_proportion_scaled_by_network_size_matched <- ggplot(newdf, aes(x=anxiety_net_group, y=net_values, fill=anxiety_net_group)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  ggtitle(paste0("Volume of Fascicle Disease Burden")) +
+  ylab("Proportion of network affected") +
+  ylim(0,1) + 
+  scale_fill_manual(values=c("#D3D3D3", "#841DE2")) +
+  theme(plot.title = element_text(size=16, hjust = 0.55),
+        axis.text = element_text(size = 16, colour = "black"), axis.title.y  = element_blank(), 
+        axis.title.x = element_text(size=16),
+        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
+        legend.position = "none",
+        aspect.ratio=4/7,
+        panel.background = element_rect(colour = "white", fill = "white")) + 
+  coord_flip()
+
+#display
+violin_within_vs_outside_network_sum_proportion_scaled_by_network_size_matched
+```
+
 ## Compare disease burden by anxiety comorbidity by fascicle
@@
 write.csv(file=paste0(homedir, "/hydra/data/Features_ms_fascicle_dysconnectome_anxiety_yeo_prop.csv"),x=anxiety_vs_no_psych_yeo_features_for_hydra, quote = F, row.names = F)
+
+```
+
+### Send anxiety groups to HYDRA ((diagnosis only + benzos)
+```{r anxiety_group_prep_for_hydra}
+### remake data frame from above
+
+anxiety_vs_no_psych <- df_demo_and_fascicles %>%
+  filter(anxietydxANDbenzoGroupVar != 0) %>% #get rid of the people who are not anxious and not healthy_ish, n =662, lost n=150
+  filter(depGroupVar!=2) %>% #exclude people with depression , n =568, lost 104
+  mutate(anxietyHydraVar = ifelse(anxietyGroupVar == 2, 1, -1)) %>%
+  group_by(EMPI) %>%
+  arrange(EXAM_DATE) %>%
+  slice(1) %>%
+  ungroup
+
+#pull out EMPI, proportion, and anxiety group var
+anxiety_vs_no_psych_features_for_hydra <- anxiety_vs_no_psych %>%
+  dplyr::select(EMPI, fascicle_names_w_prop_suffix, anxietyHydraVar)
+
+write.csv(file=paste0(homedir, "/hydra/data/Features_anxietydxANDbenzo_prop.csv"),x=anxiety_vs_no_psych_features_for_hydra, quote = F, row.names = F)
+
+#pull out age, age + sex covariates
+anxiety_age <- anxiety_vs_no_psych %>%
+  dplyr::select(EMPI, PAT_AGE_AT_EXAM)
+
+write.csv(file=paste0(homedir, "/hydra/data/Covariates_anxietydxANDbenzo_age.csv"),x=anxiety_age, quote = F, row.names = F)
+
+anxiety_age_and_sex <- anxiety_vs_no_psych %>%
+  dplyr::select(EMPI, PAT_AGE_AT_EXAM, sex_binarized)
+
+write.csv(file=paste0(homedir, "/hydra/data/Covariates_anxietydxANDbenzo_age_and_sex.csv"),x=anxiety_age_and_sex, quote = F, row.names = F)
+
+#pull out yeo proportions
+anxiety_vs_no_psych_yeo_features_for_hydra <- anxiety_vs_no_psych %>%
+  dplyr::select(EMPI, yeo_network_names_prop, anxietyHydraVar)
+
+write.csv(file=paste0(homedir, "/hydra/data/Features_anxietydxANDbenzo_yeo_prop.csv"),x=anxiety_vs_no_psych_yeo_features_for_hydra, quote = F, row.names = F)
 

### 2024-07-11 scripts/clean_dac_pull_icd10_codes_and_make_clean_df.R

@@ -140,6 +140,7 @@ data_final_rds <-data_pull %>%
   mutate(Has.anxietydx = ifelse(grepl("F4", all_icd10_dx), 1, 0)) %>%
   mutate(Has.CannabisUsedx = ifelse(grepl("F12", all_icd10_dx), 1, 0)) %>%
   mutate(Has.Anxietydx.Or.Antianxietymed = ifelse((Has.anxietydx==1) | (On.Anxiolytics==1),1,0)) %>%
+  mutate(Has.Anxietydx.AND.Antianxietymed = ifelse((Has.anxietydx==1) & (On.Anxiolytics==1),1,0)) %>%
   mutate(PHQ.2_modsev_dep_sxs = ifelse((Has.PHQ2==1) & PHQ.2 >= 3, 1, 0)) %>%
   mutate(PHQ.9_modsev_dep_sxs = ifelse((Has.PHQ9==1) & PHQ.9 >= 10, 1, 0)) %>%
   mutate(PHQ.2_mild_dep_sxs = ifelse((Has.PHQ2==1) & PHQ.2 > 0 & PHQ.2 < 3, 1, 0)) %>%
@@ -155,12 +156,18 @@ data_final_rds <-data_pull %>%
   rowwise(ACCESSION_NUM) %>%
   mutate(depGroupVar = ifelse(dep_by_dx_phq_antidep==1, 2, ifelse(dep_by_dx_phq_meds_healthy_phq0_no_psych_meds == 1, 1, 0))) %>% # dep = 2, healthy = 1, 0 for exclude
   mutate(anxietyGroupVar = ifelse(((Has.anxietydx==1) | (On.Anxiolytics_no_beta_blocker==1)), 2, ifelse(healthy_ish, 1, 0))) %>%
+  mutate(anxietydxANDbenzoGroupVar = ifelse(((Has.anxietydx==1) | (On.Benzos==1)), 2, ifelse(healthy_ish, 1, 0))) %>%
+  mutate(Has.Anxietydx.AND.AntianxietymedGroupVar = ifelse((Has.Anxietydx.AND.Antianxietymed==1), 2, ifelse(healthy_ish, 1, 0))) %>% #0 if excluded, 1 if healthyish, 2 if has anxiety dx AND on med
   mutate(Has.Anxiety.No.Depression = ifelse((anxietyGroupVar == 2 & depGroupVar != 2), 1, 0)) %>%
[…]

### 2024-07-12 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
Add files via upload

@@
 library(MatchIt)
+library(ggpubr)
 #functions
@@
 
-## Anxiety burden severity T test ranking
+## Anxiety burden severity ranking
 
@@
 
-###Collapse anxiety dx and antianxiety meds with those plus depression
-```{r group_anxietydx_meds_and_dep_comorbidity}
-
-#this collapses anxiety group + meds with those with anxiety group + meds + with/without depression
-
-df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
-  filter(oAnxietydx.Meds.Inc.Dep.Collapsed != "unclassified") %>%
-  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxietydx.Meds.Inc.Dep.Collapsed, osex)
-
- tibble_overall_summaries <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
-  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
+#### plots
+```{r}
+  #proportion injured over whole brain
+prop_injured_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=proportion_volume_lost_per_total_network_size_sum, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_by_anxiety_burden_plot
+
+  #proportion injured over anxiety net
+prop_injured_anxiety_net_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_anxiety_net_by_anxiety_burden_plot
+
+  #proportion injured over nonanxiety net
+prop_injured_nonanxiety_net_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_nonanxiety_net_by_anxiety_burden_plot
+
+  #proportion injured over R Uncinate prop
+prop_injured_R_uncinate_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=UF_R_prop, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_R_uncinate_by_anxiety_burden_plot
+
+  #proportion injured over L Uncinate prop
+prop_injured_L_uncinate_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=UF_L_prop, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_L_uncinate_by_anxiety_burden_plot
+
+prop_injured_by_anxiety_burden_and_sex_plot <- ggboxplot(df_disease_burden_unc_and_anx_net, x = "oAnxiety.And.Dep.And.AnxietyMedsGroupVar", y = "proportion_volume_lost_per_total_network_size_sum", color = "osex",
+          palette = c("#00AFBB", "#E7B800")) +
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_by_anxiety_burden_and_sex_plot
+
+```
+
+#Anxiety network interactions and uncinate alone, TRUE HEALTHY
+```{r anxiety_net_intx}
+
+## demographics
+
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar != "unclassified",])
+
+#clean up data frame
+cleaned_df <- df_demo_and_fascicles %>%
+  filter(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar != "unclassified") %>% #lose 93, n now 719
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = ifelse(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
+  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
+  mutate(mean_uncinate_injury = (UF_L_prop + UF_R_prop)/2) %>%
+  mutate(mean_uncinate_and_fornix_injury = (UF_L_prop + UF_R_prop + F_R_prop + F_L_prop)/2) %>%
+  ungroup()
+
+df_empi_dx_network_proportions <- cleaned_df %>%
+  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
+  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
+  mutate(Network = as.factor(Network)) %>%
+  ungroup()
+
+#histos
+hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], main = "Anxiety Network Injury", xlab = "Proportion Affected")
+hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], main = "Nonanxiety Network Injury", xlab = "Proportion Affected")
+hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS+Anxiety"], main = "Uncinate Injury in Anxious Patients", xlab = "Proportion Affected")
+hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS-Anxiety"], main = "Uncinate Injury in Healthyish Patients", xlab = "Proportion Affected")
+
+## Means of separate groups:
+
+#t test, 
+within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
+within_vs_outside_anxiety_net_t
+
+#diagnosis: 
+diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
+summary(diagnosis_by_network_interaction_lmer)
+confint(diagnosis_by_network_interaction_lmer)
+
+#Net by sex, confirms T; -63.62   <2e-16, but no sex differences (p=0.179)
+disease_within_vs_outside_anxiety_net_sex_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_sex_lmer)
+
+#t test uncinate alone
+mean_uncinate_by_dx_t <- t.test(cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
+mean_uncinate_by_dx_t
+
+#diagnosisxmean_uncinate: 
+diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_injury ~ Diagnosis, data = cleaned_df)
+summary(diagnosis_by_network_interaction_lmer)
+confint(diagnosis_by_network_interaction_lmer)
+
+#diagnosisxmean_uncinate+fornix: 
+diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_and_fornix_injury ~ Diagnosis, data = cleaned_df)
+summary(diagnosis_by_network_interaction_lmer)
+confint(diagnosis_by_network_interaction_lmer)
+
+#### if I decide later I want to look at L and right uncinate alone
+
+#t test uncinate alone, Left,
+l_uncinate_by_dx_t <- t.test(cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
+l_uncinate_by_dx_t
+
+#t test uncinate alone, right, remember everybody is double counted!!!! so this needs to be fixed.
+r_uncinate_by_dx_t <- t.test(cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
+r_uncinate_by_dx_t
+
+```
+
+## Anxiety burden severity ranking true healthy
+
+I am wondering here if, as my brain wants to think, that things in the chart reflect severity of anxiety.
+For example, I'd expect people with dep and anxiety comorbidity and on meds would be the sickest, followed by anxiety + on meds, then on meds, then anxiety dx, then healthyish.
+I am going to do a t-test comparing proportion of disease over whole brain, over anxiety net, and over uncinate in each of those groups as compared to the healthy group, and rank the T to see if that pattern bears out.
+And if it does, do some sort of regression.
+```{r anxiety_burden_severity_ranking }
+#variables_to_evaluate <- c("Has.Anxietydx.AND.AntianxietymedGroupVar")
+df_disease_burden_unc_and_anx_net_true_healthy <- df_demo_and_fascicles %>%
+  filter(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar != "unclassified") %>%
+  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, osex)
+
+tibble_n <- df_disease_burden_unc_and_anx_net_true_healthy %>% 
+  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>% 
+  summarise(n())
+
+tibble_overall_disease <- 
+  df_disease_burden_unc_and_anx_net_true_healthy %>% 
+  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
+  summarize(mean_size = mean(proportion_volume_lost_per_total_network_size_sum))
+
+tibble_overall_summaries <- 
+  df_disease_burden_unc_and_anx_net_true_healthy %>% 
+  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
   summarize(n(),
@@
 
-tibble_overall_summaries_by_sex <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
-  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed, osex) %>%
+tibble_overall_summaries_by_sex <- 
+  df_disease_burden_unc_and_anx_net_true_healthy %>% 
+  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, osex) %>%
   summarize(n(),
@@
 
-  tibble_overall_summaries_females <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  tibble_overall_summaries_females <- 
+  df_disease_burden_unc_and_anx_net_true_healthy %>% 
   filter(osex == "Female") %>%
-  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
+  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
   summarize(n(),
@@
 
-    tibble_overall_summaries_males <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+    tibble_overall_summaries_males <- 
+  df_disease_burden_unc_and_anx_net_true_healthy %>% 
   filter(osex == "Male") %>%
-  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
+  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
   summarize(n(),
@@
 
+  ### analyses
+
+```
+
+#### plots
+```{r}
+  #proportion injured over whole brain
+prop_injured_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=proportion_volume_lost_per_total_network_size_sum, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_by_anxiety_burden_true_healty_plot
+
+  #proportion injured over anxiety net
+prop_injured_anxiety_net_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_anxiety_net_by_anxiety_burden_true_healty_plot
+
+  #proportion injured over nonanxiety net
+prop_injured_nonanxiety_net_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_nonanxiety_net_by_anxiety_burden_true_healty_plot
+
+  #proportion injured over R Uncinate prop
+prop_injured_R_uncinate_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=UF_R_prop, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_R_uncinate_by_anxiety_burden_true_healty_plot
+
+  #proportion injured over L Uncinate prop
+prop_injured_L_uncinate_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=UF_L_prop, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_L_uncinate_by_anxiety_burden_true_healty_plot
+
+prop_injured_by_anxiety_burden_and_sex_true_healty_plot <- ggboxplot(df_disease_burden_unc_and_anx_net_true_healthy, x = "oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar", y = "proportion_volume_lost_per_total_network_size_sum", color = "osex",
+          palette = c("#00AFBB", "#E7B800")) +
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_by_anxiety_burden_and_sex_true_healty_plot
+
+```
+
+##Collapse anxiety dx and antianxiety meds with those plus depression
+```{r group_anxietydx_meds_and_dep_comorbidity}
+
+#this collapses anxiety group + meds with those with anxiety group + meds + with/without depression
+
+df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
+  filter(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)
+
+ tibble_overall_summaries <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  group_by(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+tibble_overall_summaries
+
+tibble_overall_summaries_by_sex <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  group_by(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+  tibble_overall_summaries_by_sex
+
+  tibble_overall_summaries_females <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  filter(osex == "Female") %>%
+  group_by(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+  tibble_overall_summaries_females
+
+    tibble_overall_summaries_males <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  filter(osex == "Male") %>%
+  group_by(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+  tibble_overall_summaries_males
+
   #mean disease
-  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
+  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
   summary(anxietyGrouping_mean_disease_lm)
 
-  anxietyGrouping_by_sex_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
+  anxietyGrouping_by_sex_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
   summary(anxietyGrouping_by_sex_mean_disease_lm)
@@
   #anxiety network
-  anxietyGrouping_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
+  anxietyGrouping_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
   summary(anxietyGrouping_anxiety_net_lm)
 
-  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
+  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
   summary(anxietyGrouping_by_sex_anxiety_net_lm)
@@
   #UF R
-  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
+  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
   summary(anxietyGrouping_UF_R_lm)
 
-  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
+  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
   summary(anxietyGrouping_UF_R_by_sex_lm)
@@
   #UF L
-  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
+  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
   summary(anxietyGrouping_UF_L_lm)
 
-  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
+  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
   summary(anxietyGrouping_UF_L_by_sex_lm)
@@
   df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
-  #filter(oAnxietydx.Meds.Inc.Dep.Collapsed != "unclassified") %>%
-  filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>% 
+  #filter(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed == c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>% 
   #filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "Has.anxietydx")) %>%  #-> doesn't work
@@
 #  mutate(Diagnosis = oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
-  mutate(Diagnosis = ifelse(oAnxietydx.Meds.Inc.Dep.Collapsed=="healthy_ish", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = ifelse(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
   mutate(Diagnosis = as.factor(Diagnosis)) %>%
@@
   mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
-  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
-  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
+  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol) %>% 
+  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
   mutate(Network = as.factor(Network)) %>%
@@
 
-#mean = 0.4911045
+#mean = 0.4762486
 mean_nonanxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
@@
 
-#mean = 0.2544921
+#mean = 0.2444919
 mean_nonanxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
@@
 
- #simple lmer, NetworkNonanxiety_network  -0.241926   0.003943 661.000022  -61.36   <2e-16 ***
+ #simple lmer, NetworkNonanxiety_network   -0.23176    0.01462 85.00000 -15.855   <2e-16 ***; NetworkNonanxiety_network:DiagnosisMS+Anxiety -0.03822    0.02241 85.00000  -1.705   0.0918 .
 disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject), data = df_empi_dx_network_proportions)
@@
 confint(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
-```
-
-### Plot within vs outside network
+
+#do anova instead
+
+disease_within_vs_outside_anxiety_net_by_dx_groups_anova <- aov(proportion_affected ~ Network+Diagnosis + Network:Diagnosis, data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_dx_groups_anova)
+
+#do lm UF*Diagnosis
+ #UF_R_vol -> NS
+disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis, data = df_empi_dx_network_proportions)
+summary(disease_UF_R_vol_lm)
+
+ #UF_L_vol -> NS
+disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis, data = df_empi_dx_network_proportions)
+summary(disease_UF_L_vol_lm)
+
+```
+
+###plots
+```{r}
+prop_injured_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x= oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed , y=proportion_volume_lost_per_total_network_size_sum, fill= oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed )) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_by_anxiety_burden_collapsed_vars_plot
+
+  #proportion injured over anxiety net
+prop_injured_anxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_anxiety_net_by_anxiety_burden_collapsed_vars_plot
+
+  #proportion injured over nonanxiety net
+prop_injured_nonanxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_nonanxiety_net_by_anxiety_burden_collapsed_vars_plot
+
+  #proportion injured over R Uncinate prop
+prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_R_prop, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot
+
+  #proportion injured over L Uncinate prop
+prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_L_prop, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot
+
+prop_injured_by_anxiety_burden_and_sex_true_healty_collapsed_plot <- ggboxplot(df_disease_burden_unc_and_anx_net_collapsed_variables, x = "oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed", y = "proportion_volume_lost_per_total_network_size_sum", color = "osex",
+          palette = c("#00AFBB", "#E7B800")) +
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_by_anxiety_burden_and_sex_true_healty_collapsed_plot
+```
+
+##Collapse anxiety dx and antianxiety meds with those plus depression, and anxiety dx OR on anxiety meds into 1 group -->> THIS IS THE MONEY
+```{r group_anxietydx_meds_and_dep_comorbidity}
+
+#this collapses anxiety group + meds with those with anxiety group + meds + with/without depression
+
+df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)
+
+ tibble_overall_summaries <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  group_by(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+tibble_overall_summaries
+
+tibble_overall_summaries_by_sex <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  group_by(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+  tibble_overall_summaries_by_sex
+
+  tibble_overall_summaries_females <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  filter(osex == "Female") %>%
+  group_by(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+  tibble_overall_summaries_females
+
+    tibble_overall_summaries_males <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  filter(osex == "Male") %>%
+  group_by(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  summarize(n(),
+            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
+            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
+            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
+            mean_UF_L = mean(UF_L_prop),
+            mean_UF_R = mean(UF_R_prop))
+  tibble_overall_summaries_males
+
+  #mean disease
+  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_mean_disease_lm)
+
+  anxietyGrouping_by_sex_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_by_sex_mean_disease_lm)
+
+  #anxiety network
+  anxietyGrouping_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_anxiety_net_lm)
+
+  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_by_sex_anxiety_net_lm)
+
+  #UF R
+  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_UF_R_lm)
+
+  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_UF_R_by_sex_lm)
+
+  #UF L
+  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_UF_L_lm)
+
+  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
+  summary(anxietyGrouping_UF_L_by_sex_lm)
+
+  #burden of anxiety by network
+  #clean up data frame
+  df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>% 
+  #filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "Has.anxietydx")) %>%  #-> doesn't work
+ # filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "On.Anxiolytics")) %>% #-> doesn't work
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  #mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
+  #mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
+  #mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
+  ##mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
+  #mutate(Benzo_status = as.factor(Benzo_status)) %>%
+  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
+  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
+  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol) %>% 
+  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
+  mutate(Network = as.factor(Network)) %>%
+  ungroup()
+
+## Means of separate groups:
+
+#t test, t, t = 37.378, df = 271, p-value < 2.2e-16, anxiety net: 0.4974984; nonanxiety net: 0.256347
+within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
+summary(within_vs_outside_anxiety_net_t)
+
+#t test
+between_dx_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])
+summary(between_dx_t)
+
+#means
+
+#mean = 0.5381082
+mean_anxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
+mean_anxiety_dx_anx_net
+
+#mean = 0.2681277
+mean_anxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
+mean_anxiety_dx_nonanx_net
+
+#mean = 0.4762486
+mean_nonanxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
+mean_nonanxiety_dx_anx_net
+
+#mean = 0.2444919
+mean_nonanxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
+mean_nonanxiety_dx_nonanx_net
+
+ #simple lmer
+disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
+
+#Network confit:NetworkNonanxiety_network -0.2496593 -0.23419230
+confint(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
+
+#do anova instead
+
+disease_within_vs_outside_anxiety_net_by_dx_groups_anova <- aov(proportion_affected ~ Network+Diagnosis + Network:Diagnosis, data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_dx_groups_anova)
+
+#do lm UF*Diagnosis
+ #UF_R_vol -> NS
+disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis, data = df_empi_dx_network_proportions)
+summary(disease_UF_R_vol_lm)
+
+ #UF_L_vol -> NS
+disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis, data = df_empi_dx_network_proportions)
+summary(disease_UF_L_vol_lm)
+
+## sex diff
+
+## net by sex 
+ #simple lmer
+disease_within_vs_outside_anxiety_net_by_sex_diff_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_sex_diff_lmer)
+
+#Network confit:
+confint(disease_within_vs_outside_anxiety_net_by_sex_diff_lmer)
+
+## diagnosis by sex 
+ #simple lmer
+disease_diagnosis_by_sex_diff_lm <- lm(proportion_affected ~ Diagnosis*osex, data = df_empi_dx_network_proportions)
+summary(disease_diagnosis_by_sex_diff_lm)
+
+#Network confit:
+confint(disease_diagnosis_by_sex_diff_lm)
+
+#network * diagnosis + sex
+ #simple lmer
+disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer <- lmer(proportion_affected ~ Network*Diagnosis + osex + (1|subject), data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer)
+
+#Network confit:NetworkNonanxiety_network -0.2496593 -0.23419230
+confint(disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer)
+
+```
+
+###plots
+```{r}
+prop_injured_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x= oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed , y=proportion_volume_lost_per_total_network_size_sum, fill= oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed )) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_by_anxiety_burden_collapsed_vars_plot
+
+  #proportion injured over anxiety net
+prop_injured_anxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_anxiety_net_by_anxiety_burden_collapsed_vars_plot
+
+  #proportion injured over nonanxiety net
+prop_injured_nonanxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_nonanxiety_net_by_anxiety_burden_collapsed_vars_plot
+
+  #proportion injured over R Uncinate prop
+prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_R_prop, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot
+
+  #proportion injured over L Uncinate prop
+prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_L_prop, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot
+```
+
+##Plot within vs outside network
 ```{r plottting_bar_graph}
@@
 
-### AnxietydxANDbenzoGroupVar within/outside network
+## AnxietydxANDbenzoGroupVar within/outside network
 ```{r anxiety_net_intx}
@@
 
-### Anxiety network interaction, matching groups 
+## Anxiety network interaction, matching groups 
 ```{r anxiety_net_intx}

### 2024-07-12 scripts/clean_dac_pull_icd10_codes_and_make_clean_df.R

@@ -150,7 +150,7 @@ data_final_rds <-data_pull %>%
   mutate(dep_by_dx_phq = ifelse(((Has.depdx==1) | (PHQ.2_modsev_dep_sxs==1) | (PHQ.9_modsev_dep_sxs==1)),1,0)) %>%
   mutate(dep_by_dx_phq_antidep = ifelse(((Has.depdx==1) | (On.Antidepressants==1) | (PHQ.2_modsev_dep_sxs==1) | (PHQ.9_modsev_dep_sxs==1)),1,0)) %>%
   mutate(healthy_ish = ifelse(((number_of_psychiatric_comorbidities_extended == 0) & (On.Psych.Meds.Extended==0)), 1, 0)) %>% #just like true healthy but doesn't require a phq screen
-  mutate(true_healthy = ifelse(((number_of_psychiatric_comorbidities_extended == 0) & (On.Psych.Meds.Extended==0) & ((PHQ.2_zero==1) | (PHQ.9_zero==1))), 1, 0)) %>%
+  mutate(true_healthy = ifelse(((number_of_psychiatric_comorbidities_extended == 0) & (On.Psych.Meds.Extended==0) & ((Has.PHQ2==1 | Has.PHQ9==1) & ((PHQ.2_zero==1) | (PHQ.9_zero==1)))), 1, 0)) %>% # we can do this because we know that a person will either have a PHQ2 OR 9, not both
   mutate(dep_by_dx_phq_meds_healthy_phq0_no_psych_meds = ifelse((dep_by_dx_phq_antidep==1) | (true_healthy==1), 1, 0)) %>%
   left_join(unique_empi_with_ms_providers, by = "EMPI") %>% 
   rowwise(ACCESSION_NUM) %>%
@@ -167,6 +167,19 @@ data_final_rds <-data_pull %>%
   mutate(Anxietydx.Meds.And.Dep.Collapsed = oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>% #copy values from oanxiety_group
[…]

### 2024-07-12 scripts/ms_functions.R

@@ -34,11 +34,17 @@ make_demographics_table_ms_anxiety<- function(data_frame) {
                 "Sex",
                 "Age",
                 "AnxietyGroupVar",
+                "AnxietydxANDbenzoGroupVar",
                 "Anxiety.And.Dep.GroupVar",
+                "Has.Anxietydx.Or.Antianxietymed",
+                "Has.Anxietydx.AND.Antianxietymed",
+                "Has.Anxietydx.AND.AntianxietymedGroupVar",
+                "oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar",
                 "Has.depdx", 
                 "Has.anxietydx", 
                 "On.Antidepressants",
                 "On.Anxiolytics_no_beta_blocker",
+                "On.Benzos",
                 "on_anti_cd20",
                 "on_interferon",
                 "on_steroids",
@@ -64,6 +70,7 @@ make_demographics_table_ms_anxiety<- function(data_frame) {
                 "proportion_volume_lost_nondepression_net_by_network_size_sum_bottom_75",
                 "proportion_fascicle_vol_lost_indep_and_anxiety_net_combined",
                 "proportion_fascicle_vol_lost_indep_and_anxiety_net_overlap",
+                "proportion_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC",
                 "proportion_fascicle_vol_lost_indepressionnet_no_anxiety_overlap",
                 "proportion_fascicle_vol_lost_inanxietynet_no_depression_overlap") #Race 1 = caucasian, Sex 1 = M age = years
 
@@ -73,11 +80,17 @@ make_demographics_table_ms_anxiety<- function(data_frame) {
                       data_frame$sex_binarized, 
                       data_frame$PAT_AGE_AT_EXAM, 
                       data_frame$anxietyGroupVar,
+                      data_frame$anxietydxANDbenzoGroupVar,
                       data_frame$Anxiety.And.Dep.GroupVar,
+                      data_frame$Has.Anxietydx.Or.Antianxietymed,
+                      data_frame$Has.Anxietydx.AND.Antianxietymed,
+                      data_frame$Has.Anxietydx.AND.AntianxietymedGroupVar,
+                      data_frame$oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar,
[…]

### 2024-07-16 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
playing with new groups, adding gams

@@
   slice(1) %>%
-  ungroup #n=786
+  ungroup 
 ```
@@
 
-##Collapse anxiety dx and antianxiety meds with those plus depression, and anxiety dx OR on anxiety meds into 1 group -->> THIS IS THE MONEY
+#COLLAPSE anxiety dx and antianxiety meds with those plus depression, and anxiety dx OR on anxiety meds into 1 group -->> THIS IS THE MONEY
 ```{r group_anxietydx_meds_and_dep_comorbidity}
-
 #this collapses anxiety group + meds with those with anxiety group + meds + with/without depression
+
+#demo
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
+
+make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[((df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
 
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>% 
-  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)
+  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex, anxiety_dose)
 
@@
   #mean disease
-  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
+
+  df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>% filter (anxiety_dose != 3) #3 is unclassified, 0 is no anxiety, 1 is diagnosis or on meds, 2 is diagnosis AND on meds
+
+  #mean disease by anxiety dose: anxiety_dose  0.03606    0.01493   2.416   0.0162 *
+  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_mean_disease_lm)
 
-  anxietyGrouping_by_sex_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
+  ### gam instead
+    anxietyGrouping_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_mean_disease_gam)
+
+  #mean disease with sex in model : anxiety_dose         anxiety_dose     0.0356677  0.0150093   2.376  0.01800 *  
+  anxietyGrouping_by_sex_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_by_sex_mean_disease_lm)
 
+  #gam: anxiety_dose  0.03692    0.01496   2.468    0.014 *  
+      anxietyGrouping_by_sex_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + osex+ s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+      summary(anxietyGrouping_by_sex_mean_disease_gam)
+
   #anxiety network
-  anxietyGrouping_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
+
+  ###  anxiety_dose    0.036474   0.017586   2.074 0.038768 *  ; PAT_AGE_AT_EXAM 0.004132   0.001058   3.905 0.000112 ***
+  anxietyGrouping_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_anxiety_net_lm)
 
-  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
+  #gam
+   anxietyGrouping_anxiety_net_gam<- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_anxiety_net_gam)
+
+  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.053407   0.021365   2.500   0.0129 *  
+  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_by_sex_anxiety_net_lm)
 
-  #UF R
-  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
+  #gam
+  anxietyGrouping_by_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_by_sex_anxiety_net_gam)
+
+  #volume lost in anxiety net by anxiety dose + sex + PAT_AGE_AT_EXAM: anxiety_dose     0.037282   0.017629   2.115   0.0351 *
+  anxietyGrouping_cov_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_cov_sex_anxiety_net_lm)
+
+  #gam
+   anxietyGrouping_cov_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_cov_sex_anxiety_net_gam)
+
+########UF R - just looking at uncinate by anxiety dose; anxiety_dose      369.72     187.93   1.967   0.0499 *  ***********
+  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_UF_R_lm)
 
-  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
+  #gam, anxiety_dose    357.0      188.8   1.891   0.0594 .
+  anxietyGrouping_UF_R_gam <- gam(UF_R_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_UF_R_gam)
+
+  #UF _ R anxiety_dose          anxiety_dose      377.35     188.43   2.003    0.046 *********   
+  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_UF_R_by_sex_lm)
 
-  #UF L
-  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
+  #gam, anxiety_dose    364.2      189.3   1.924   0.0552 .  
+    anxietyGrouping_UF_R_by_sex_gam <- gam(UF_R_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_UF_R_by_sex_gam)
+
+  #UF L - anxiety_dose     222.193    133.138   1.669    0.096 .  
+  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_UF_L_lm)
 
-  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
+   #gam, anxiety_dose    220.1      133.7   1.646    0.101    
+  anxietyGrouping_UF_L_gam <- gam(UF_L_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_UF_L_gam)
+
+  #UF_L anxiety_dose:         anxiety_dose     232.210    133.294   1.742   0.0823 .  
+  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_UF_L_by_sex_lm)
+
+   #gam, anxiety_dose    229.9      133.9   1.717   0.0868 .  
+  anxietyGrouping_UF_L_by_sex_gam <- gam(UF_L_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_UF_L_by_sex_gam)
 
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>% 
-  #filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "Has.anxietydx")) %>%  #-> doesn't work
- # filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "On.Anxiolytics")) %>% #-> doesn't work
   mutate(subject = as.factor(EMPI)) %>%
@@
   mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  #mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
-  #mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
-  #mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
-  ##mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
-  #mutate(Benzo_status = as.factor(Benzo_status)) %>%
   mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
@@
 
-#means
-
-#mean = 0.5381082
+######means
+
+#mean = 0.5665159
 mean_anxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
@@
 
-#mean = 0.2681277
+#mean = 0.310777
 mean_anxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
@@
 
-#mean = 0.4762486
+#mean =  0.4652665
 mean_nonanxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
@@
 
-#mean = 0.2444919
+#mean = 0.2106967
 mean_nonanxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
@@
  #simple lmer
-disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject), data = df_empi_dx_network_proportions)
+
+##NetworkNonanxiety_network                      -0.254570   0.013575  92.000000 -18.753  < 2e-16 ***
+##DiagnosisMS+Anxiety                             0.108710   0.040130 103.092356   2.709  0.00791 ** 
+disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
 summary(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
@@
 
-#do anova instead
-
-disease_within_vs_outside_anxiety_net_by_dx_groups_anova <- aov(proportion_affected ~ Network+Diagnosis + Network:Diagnosis, data = df_empi_dx_network_proportions)
+###do anova instead
+##Network             1  3.059  3.0587  82.472  < 2e-16 ***
+##Diagnosis           1  0.473  0.4728  12.749 0.000455 ***
+
+disease_within_vs_outside_anxiety_net_by_dx_groups_anova <- aov(proportion_affected ~ Network+Diagnosis + Network:Diagnosis + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
 summary(disease_within_vs_outside_anxiety_net_by_dx_groups_anova)
@@
 #do lm UF*Diagnosis
- #UF_R_vol -> NS
-disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis, data = df_empi_dx_network_proportions)
+ #UF_R_vol -> DiagnosisMS+Anxiety  1406.32     350.74   4.010 8.81e-05 ***
+disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
 summary(disease_UF_R_vol_lm)
 
- #UF_L_vol -> NS
-disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis, data = df_empi_dx_network_proportions)
+ #UF_L_vol -> DiagnosisMS+Anxiety   728.93     249.71   2.919  0.00395 ** 
+disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
 summary(disease_UF_L_vol_lm)
 
-## sex diff
+############## sex diff
+#df_anxiety_disorder_by_sex <-
 
 ## net by sex
+
 #simple lmer
-disease_within_vs_outside_anxiety_net_by_sex_diff_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject), data = df_empi_dx_network_proportions)
+#NetworkNonanxiety_network         -0.250361   0.011772  92.000001 -21.268  < 2e-16 ***
+  disease_within_vs_outside_anxiety_net_by_sex_diff_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
   summary(disease_within_vs_outside_anxiety_net_by_sex_diff_lmer)
@@
 ## diagnosis by sex 
- #simple lmer
-disease_diagnosis_by_sex_diff_lm <- lm(proportion_affected ~ Diagnosis*osex, data = df_empi_dx_network_proportions)
+ #simple lmer, DiagnosisMS+Anxiety         0.124327   0.040488   3.071  0.00246 **
+disease_diagnosis_by_sex_diff_lm <- lm(proportion_affected ~ Diagnosis*osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
 summary(disease_diagnosis_by_sex_diff_lm)
@@
 #network * diagnosis + sex
- #simple lmer
-disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer <- lmer(proportion_affected ~ Network*Diagnosis + osex + (1|subject), data = df_empi_dx_network_proportions)
+ #simple lmer: NetworkNonanxiety_network                      -0.254570   0.013575  92.000000 -18.753  < 2e-16 ***
+ ##DiagnosisMS+Anxiety                             0.107571   0.040361 101.820059   2.665  0.00895 ** 
+disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer <- lmer(proportion_affected ~ Network*Diagnosis + osex + (1|subject)+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
 summary(disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer)
@@
 confint(disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer)
+
+###### Sex differences - NONE. important because anxiety dx usually have differences
+
+## in anxiety diagnosis
+
+#####FIRST, SEX DIFF IN FREQUENCY OF ILLNESS - no diff between groups
+
+#first number is # with anxiety, second is number without anxiety
+anxiety_female_0 <-df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(anxiety_dose == 0 & osex == "Female") %>% count()
+anxiety_total_0 <-df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(anxiety_dose == 0) %>% count()
+anxiety_female_1 <-df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(anxiety_dose == 1 & osex == "Female") %>% count()
+anxiety_total_1 <-df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(anxiety_dose == 1) %>% count()
+anxiety_female_2 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(anxiety_dose == 2 & osex == "Female") %>% count()
+anxiety_total_2 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(anxiety_dose == 2) %>% count()
+
+#make table
+num_w_anxiety_female <- as.numeric(c(anxiety_female_0, anxiety_female_1, anxiety_female_2))
+num_total <-as.numeric(c(anxiety_total_0,anxiety_total_1, anxiety_total_2))
+df_2x3_anxiety_score_by_total_people_per_diagnosis <- data.frame(cbind(num_w_anxiety_female, num_total), row.names = c("MS+AnxietyandMed", "MS+AnxietyorMed", "MS-Anxiety"))
+
+#X-squared (Pearson's) X-squared = 0.19886, df = 2, p-value = 0.9054
+chisq_anxiety_dose <- chisq.test(df_2x3_anxiety_score_by_total_people_per_diagnosis)
+chisq_anxiety_dose
+
+#just healthy and super anxious/sick, X-squared = 0.056046, df = 1, p-value = 0.8129
+num_w_anxiety_female_just_healthy_and_sick <- as.numeric(c(anxiety_female_0, anxiety_female_2))
+num_total_just_healthy_and_sick <-as.numeric(c(anxiety_total_0,anxiety_total_2))
+df_2x2_anxiety_score_by_total_people_per_diagnosis_num_total_just_healthy_and_sick <- data.frame(cbind(num_w_anxiety_female_just_healthy_and_sick, num_total_just_healthy_and_sick), row.names = c("MS+AnxietyandMed", "MS-Anxiety"))
+
+chisq_healthy_vs_sick <- chisq.test(df_2x2_anxiety_score_by_total_people_per_diagnosis_num_total_just_healthy_and_sick)
+chisq_healthy_vs_sick
+
+#frequency_diff_between_sexes <- chisq.test(df_demo_and_fascicles$Has.Anxietydx.AND.Antianxietymed, df_demo_and_fascicles$osex)
+
+#simple lmer across whole network
+
+#overall - NS
+disease_between_sexes <- lm(proportion_volume_lost_per_total_network_size_sum ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(disease_between_sexes)
+
+### anxiety net NS
+disease_between_sexes_anxiety_net <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(disease_between_sexes_anxiety_net)
+
+### nonanxiety net - NS
+disease_between_sexes_nonanxiety_net <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(disease_between_sexes_nonanxiety_net)
+
+#uncinate R- NS
+disease_between_sexes_UF_R <- lm(UF_R_vol ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(disease_between_sexes_UF_R)
+
+#uncinate L - ns
+disease_between_sexes_UF_L <- lm(UF_L_vol ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(disease_between_sexes_UF_L)
+
+### diagnosis by age interaction?
+#overall - NS
+diagnosis_by_age <- lm(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose*PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age)
+
+#gam
+diagnosis_by_age_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_gam)
+summary(diagnosis_by_age_gam)$s.table
+plot(diagnosis_by_age_gam)
+
+####. within/outside anxiety network #######
+#dose
+diagnosis_by_age_anx_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_anx_net_gam)
+summary(diagnosis_by_age_anx_net_gam)$s.table
+plot(diagnosis_by_age_anx_net_gam)
+
+#factor
+diagnosis_by_age_anx_net_gam_factor <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ as.factor(anxiety_dose)+s(PAT_AGE_AT_EXAM, by = as.factor(anxiety_dose)), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_anx_net_gam_factor)
+summary(diagnosis_by_age_anx_net_gam_factor)$s.table
+plot(diagnosis_by_age_anx_net_gam_factor)
+
+##### #outside each network
+
+##dose
+diagnosis_by_age_nonanx_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_nonanx_net_gam)
+summary(diagnosis_by_age_nonanx_net_gam)$s.table
+plot(diagnosis_by_age_nonanx_net_gam)
+
+#factor
+
+diagnosis_by_age_nonanx_net_gam_factor <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ as.factor(anxiety_dose)+s(PAT_AGE_AT_EXAM, by = as.factor(anxiety_dose)), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_nonanx_net_gam_factor)
+summary(diagnosis_by_age_nonanx_net_gam_factor)$s.table
+plot(diagnosis_by_age_nonanx_net_gam_factor)
+
+### uncinate right
+
+#dose
+diagnosis_by_age_UF_R_gam <- gam(UF_R_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_UF_R_gam)
+summary(diagnosis_by_age_UF_R_gam)$s.table
+plot(diagnosis_by_age_UF_R_gam)
+
+#factor
+diagnosis_by_age_UF_R_gam_factor <- gam(UF_R_vol ~ as.factor(anxiety_dose)+s(PAT_AGE_AT_EXAM, by = as.factor(anxiety_dose)), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_UF_R_gam_factor)
+summary(diagnosis_by_age_UF_R_gam_factor)$s.table
+plot(diagnosis_by_age_UF_R_gam_factor)
+
+#uncinate left
+#dose
+diagnosis_by_age_UF_L_gam <- gam(UF_L_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_UF_L_gam)
+summary(diagnosis_by_age_UF_L_gam)$s.table
+plot(diagnosis_by_age_UF_L_gam)
+
+#factor
+diagnosis_by_age_UF_L_gam_factor <- gam(UF_L_vol ~ as.factor(anxiety_dose)+s(PAT_AGE_AT_EXAM, by = as.factor(anxiety_dose)), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_UF_L_gam_factor)
+summary(diagnosis_by_age_UF_L_gam_factor)$s.table
+plot(diagnosis_by_age_UF_L_gam_factor)
 

### 2024-07-16 scripts/clean_dac_pull_icd10_codes_and_make_clean_df.R

@@ -179,7 +179,8 @@ data_final_rds <-data_pull %>%
   mutate(anxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed = str_replace_all(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, c("Has.anxietydx" = "Has.Anxietydx.OR.Antianxiety.Meds","On.Anxiolytics" = "Has.Anxietydx.OR.Antianxiety.Meds"))) %>% ##combine people who have either anxiety or are on anxiety meds
   mutate(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed = ordered(anxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, levels = c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep", "unclassified"))) %>%
   
-  
+  # anxiety dose
+  mutate(anxiety_dose = (as.numeric(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) -1)) %>% #anxiety dose is 0 (no anxiety dx), 1 (anxietydx or anxiety meds), 2 (anxiety + anxiety meds), so take the factor and subtract 1
   ungroup() #n=3,737 unique people, n= 16,830 total
 
 saveRDS(data_final_rds, file = output_file)

### 2024-07-16 scripts/ms_functions.R

@@ -40,6 +40,7 @@ make_demographics_table_ms_anxiety<- function(data_frame) {
                 "Has.Anxietydx.AND.Antianxietymed",
                 "Has.Anxietydx.AND.AntianxietymedGroupVar",
                 "oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar",
+                "oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed",
                 "Has.depdx", 
                 "Has.anxietydx", 
                 "On.Antidepressants",
@@ -86,6 +87,7 @@ make_demographics_table_ms_anxiety<- function(data_frame) {
                       data_frame$Has.Anxietydx.AND.Antianxietymed,
                       data_frame$Has.Anxietydx.AND.AntianxietymedGroupVar,
                       data_frame$oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar,
+                      data_frame$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed,
                       data_frame$Has.depdx, 
                       data_frame$Has.anxietydx, 
                       data_frame$On.Antidepressants,
@@ -133,7 +135,7 @@ make_demographics_table_ms_anxiety<- function(data_frame) {
   
   
   #Define Categorical Variables
-  cat_variables <- c("Race", "Sex", "AnxietyGroupVar", "AnxietydxANDbenzoGroupVar", "Has.Anxietydx.AND.AntianxietymedGroupVar", "oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar", "Has.anxietydx","Anxiety.And.Dep.GroupVar", "Has.Anxietydx.Or.Antianxietymed", "On.Anxiolytics_no_beta_blocker","On.Benzos", "Has.depdx", "On.Antidepressants", "on_anti_cd20", "on_interferon", "on_steroids", "on_dmt", "on_bcp")
[…]

### 2024-07-17 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
All sorts of gams

@@
 library(ggpubr)
+library(tidymv)
 #functions
@@
 
-#n=867
+#n=867, individual scans
 df_people_with_good_mimosa <- data_2023_pull %>% 
@@
 #COLLAPSE anxiety dx and antianxiety meds with those plus depression, and anxiety dx OR on anxiety meds into 1 group -->> THIS IS THE MONEY
+### Overlap with depression group
+```{r overlap_with_dep_group}
+
+#read csv of empis from depression paper
+depression_empis <- read.table(file="/Users/eballer/BBL/msanxiety/data/empis_of_people_in_BP_depression_paper.csv")
+names(depression_empis) <- "EMPI"
+
+#get final anxiety dataset and make column if the empi is in the prev list
+df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
+  mutate(EMPI = as.numeric(EMPI)) %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  mutate(EMPI_in_dep_group = EMPI %in% depression_empis$EMPI)
+
+ tibble_overall_counts <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
+  group_by(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  summarize(n(),
+            num_in_dep_group = sum(EMPI_in_dep_group),
+            percent_overlap = num_in_dep_group/n())
+ tibble_overall_counts
+
+```
+### Overall Disease by Anxiety Dose *acnp
 ```{r group_anxietydx_meds_and_dep_comorbidity}
@@
 
-  #mean disease by anxiety dose: anxiety_dose  0.03606    0.01493   2.416   0.0162 *
+  #mean disease by anxiety dose: anxiety_dose    0.0347504  0.0149813   2.320  0.02091 *  
   anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  ### gam instead
+  ### gam instead, anxiety_dose  0.03606    0.01493   2.416   0.0162 *
     anxietyGrouping_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
       summary(anxietyGrouping_by_sex_mean_disease_gam)
+```
+
+### Anxiety network by anxiety dose
+```{r}
+
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter (anxiety_dose != 3)
 
@@
 
-  #gam
+  #gam, anxiety_dose  0.03735    0.01760   2.122   0.0345 * 
    anxietyGrouping_anxiety_net_gam<- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.053407   0.021365   2.500   0.0129 *  
+  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.053407   0.021365   2.500   0.0129 *  , no intx
   anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #gam
+  #gam, anxiety_dose         0.05395    0.02133   2.529   0.0119 *  
   anxietyGrouping_by_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #gam
+  #gam, anxiety_dose  0.03810    0.01765   2.159   0.0315 * 
    anxietyGrouping_cov_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-########UF R - just looking at uncinate by anxiety dose; anxiety_dose      369.72     187.93   1.967   0.0499 *  ***********
+```
+
+### NonAnxiety network by anxiety dose
+```{r}
+
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter (anxiety_dose != 3)
+
+  #anxiety network
+
+  ###  anxiety_dose: anxiety_dose    0.0334038  0.0135143   2.472   0.0139 * 
+  anxietyGrouping_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_nonanxiety_net_lm)
+
+  #gam, anxiety_dose  , anxiety_dose  0.03505    0.01340   2.616  0.00927 ** 
+   anxietyGrouping_nonanxiety_net_gam<- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_nonanxiety_net_gam)
+
+  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.0459425  0.0164036   2.801  0.00537 ** 
+  anxietyGrouping_by_sex_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose*osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_by_sex_nonanxiety_net_lm)
+
+  #gam, anxiety_dose, anxiety_dose         0.047100   0.016230   2.902  0.00393 **          
+  anxietyGrouping_by_sex_nonanxiety_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose*osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_by_sex_nonanxiety_net_gam)
+
+  #volume lost in anxiety net by anxiety dose + sex + PAT_AGE_AT_EXAM: anxiety_dose     0.0344065  0.0135309   2.543   0.0114 *  
+  anxietyGrouping_cov_sex_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_cov_sex_nonanxiety_net_lm)
+
+  #gam, anxiety_dose - anxiety_dose  0.03600    0.01342   2.682  0.00764 ** 
+   anxietyGrouping_cov_sex_nonanxiety_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_cov_sex_nonanxiety_net_gam)
+
+```
+
+###Check for polynomial relationships 
+```{r polynomial_relationships}
+ #Not finding them w healthy, anxietydx OR meds, anxiety AND meds
+
+ #check for polynomial relationship
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose_factor <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter (anxiety_dose != 3) %>% 
+  mutate(anxiety_dose = as.factor(anxiety_dose))
+
+contrasts(df_demo_and_fascicles_no_unclass_anxiety_dose_factor$anxiety_dose) <- contr.poly(3)
+
+# Perform Anova across all regions, anxiety_dose      2  0.195  0.0975   2.508  0.0829 .  
+anova_result_contrasts_whole_brain <- aov(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
+summary(anova_result_contrasts_whole_brain)
+
+# Perform ANOVA again with contrasts anxiety net, anxiety_dose      2  0.216  0.1079   2.012 0.135161    
+anova_result_contrasts_anxiety_net <- aov(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
+summary(anova_result_contrasts_anxiety_net)
+
+# Nonanxiety Net - anxiety_dose      2  0.180  0.0898   2.842   0.0596 . 
+anova_result_contrasts_nonanxiety_net <- aov(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
+summary(anova_result_contrasts_nonanxiety_net)
+
+#UF_R_vol, anxiety_dose      2 2.219e+07  11094236   1.811    0.165
+
+anova_result_contrasts_UF_R_net <- aov(UF_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
+summary(anova_result_contrasts_UF_R_net)
+
+#UF_L_vol, anxiety_dose      2 6.053e+06  3026730   0.988    0.373  
+anova_result_contrasts_UF_L_net <- aov(UF_L_vol ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
+summary(anova_result_contrasts_UF_L_net)
+
+```
+
+### Uncinate by Anxiety Dose *acnp?
+```{r uncinateByAnxietyDose}
+
+#results: Anxiety dose related to UF_R when covarying for linear effects of age and sex, just barely
+
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter (anxiety_dose != 3)
+
+########UF R - just looking at uncinate by anxiety dose; anxiety_dose      369.72     187.93   1.967   0.0499 *  *********** (LINEAR AGE)
   anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
   summary(anxietyGrouping_UF_L_by_sex_gam)
+```
+
+##### Laterality in uncinate
+```{r laterality}
+  #laterality 
+  #overall - t = -11.597, df = 1322.2, p-value < 2.2e-16
+  right_vs_left_uncinate <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol, df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol)
+  print(right_vs_left_uncinate)
+
+  #healthy - t = -6.3298, df = 347.5, p-value = 7.577e-10
+   right_vs_left_uncinate_healthy <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0])
+  print(right_vs_left_uncinate_healthy)
+
+  #anxietydx or meds - t = -7.7742, df = 705.18, p-value = 2.694e-14
+  right_vs_left_uncinate_anxiety_or_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1])
+  print(right_vs_left_uncinate_anxiety_or_meds)
+
+  #anxious+meds, t = -5.9638, df = 266.42, p-value = 7.804e-09
+   right_vs_left_uncinate_anxiety_and_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2])
+  print(right_vs_left_uncinate_anxiety_and_meds)
+```
+
+### Fornix by Anxiety Dose
+```{r uncinateByAnxietyDose}
+
+#results: Anxiety dose NOT related to F_R when covarying for linear effects of age and sex, not in line with that one paper that found fornix differences
+
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter (anxiety_dose != 3)
+
+########UF R - just looking at fornix by anxiety dose -NS
+  anxietyGrouping_F_R_lm <- lm(F_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_F_R_lm)
+
+  #gam, anxiety_dose    - NS
+  anxietyGrouping_F_R_gam <- gam(F_R_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_F_R_gam)
+
+  #UF _ R anxiety_dose     - NS    
+  anxietyGrouping_F_R_by_sex_lm <- lm(F_R_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_F_R_by_sex_lm)
+
+  #gam, anxiety_dose  - NS 
+    anxietyGrouping_F_R_by_sex_gam <- gam(F_R_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_F_R_by_sex_gam)
+
+  #UF L - anxiety_dose    - NS 
+  anxietyGrouping_F_L_lm <- lm(F_L_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_F_L_lm)
+
+   #gam, anxiety_dose    - NS  
+  anxietyGrouping_F_L_gam <- gam(F_L_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_F_L_gam)
+
+  #F_L anxiety_dose:NS        
+  anxietyGrouping_F_L_by_sex_lm <- lm(F_L_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_F_L_by_sex_lm)
+
+   #gam, anxiety_dose - NS
+  anxietyGrouping_F_L_by_sex_gam <- gam(F_L_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_F_L_by_sex_gam)
+```
+
+### Network*Diagnosis
+```{r networkxdiagnosis_groups_collapse}
+
+## take home: comparing healthy to has anxiety AND meds, more disease within vs outside net, anxiety vs non, no interaction.
+## take home #2 : More disease in R & L uncinate in anxious versus nonanxious
 
@@
   mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
-  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol) %>% 
-  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
+  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol) %>% 
+  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol, -F_R_vol, -F_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
   mutate(Network = as.factor(Network)) %>%
@@
 #do lm UF*Diagnosis
- #UF_R_vol -> DiagnosisMS+Anxiety  1406.32     350.74   4.010 8.81e-05 ***
-disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+ #UF_R_vol -> DiagnosisMS+Anxiety  1418.26     352.04   4.029 8.20e-05 ***
+disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + osex + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
 summary(disease_UF_R_vol_lm)
 
- #UF_L_vol -> DiagnosisMS+Anxiety   728.93     249.71   2.919  0.00395 ** 
-disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+ #UF_L_vol -> DiagnosisMS+Anxiety   737.97     250.61   2.945  0.00365 ** 
+disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
 summary(disease_UF_L_vol_lm)
 
-############## sex diff
-#df_anxiety_disorder_by_sex <-
-
+#Fornix - Right side but not left
+ #F_R_vol -> DiagnosisMS+Anxiety   860.50     368.16   2.337   0.0205 * 
+disease_F_R_vol_lm <- lm(F_R_vol ~ Diagnosis + osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+summary(disease_F_R_vol_lm)
+
+ #F_L_vol -> DiagnosisMS+Anxiety  329.724    181.609   1.816   0.0711 . 
+disease_F_L_vol_lm <- lm(F_L_vol ~ Diagnosis + osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+summary(disease_F_L_vol_lm)
 ## net by sex
@@
 confint(disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer)
+
+```
+
+### Diag Effect Size * Fascicle anxiety net overlap (from depression analysis) - NOT SIG both vol and prop, only vol shown here
+```{r dxEffSizeOverlapwithAnxietyNet}
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  mutate(anxiousAndMeds_or_healthy = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  filter(anxiousAndMeds_or_healthy %in% c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>%
+  mutate(anxiousAndMeds_or_healthy = factor(anxiousAndMeds_or_healthy, levels=c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
+
+#Positive Ts are places where anxious people have more disease than controls
+fascicle_anxiety_vs_healthy_effsize <- sapply(fascicle_names_w_vol_suffix, function(fascicle) 
+{
+
+  text_for_eval <- paste0("rstatix::wilcox_effsize(df_demo_and_fascicles_no_unclass_anxiety_dose, formula = ", fascicle, " ~ anxiousAndMeds_or_healthy, paired = F, conf.level = 0.95, ci.type = \"perc\", nboot = 1000)$effsize")
+  eval(parse(text=text_for_eval))
+})
+names(fascicle_anxiety_vs_healthy_effsize) <- fascicle_names_w_vol_suffix
+
+#convert to data frame
+df_effsize_values <- as.data.frame(fascicle_anxiety_vs_healthy_effsize)
+
+#write.table(x = df_effsize_values, file = paste0(homedir, "results/fascicle_and_wilcox_effect_size_for_volxdx_analysis_n77.csv"), row.names = T, col.names = F, quote = F, sep = ",")
+
+```
+
+#### Plot effect size x Anxiety net overlap - N.S. (including if I drop all fascicles with no overlap)
+``` {r plot_scatter}
+#######################
+### plot differences ##
+#######################
+
+#combine data frames, column 1 has names of fascicles, column 2 has Volume of overlap with anxiety network, column 3 has t-test value of anxiety vs healthy unc, 4th anxiety vs healthy fdr corrected within that fascicle
+
+df_fascicle_anxiety_mask_volume_overlap_effsize_value <- data.frame(neurosynth_anxiety_network_fascicle_overlap$fascicle, neurosynth_anxiety_network_fascicle_overlap$non_zero_voxels_in_anxiety_map, df_effsize_values)
+names(df_fascicle_anxiety_mask_volume_overlap_effsize_value) <- c("fascicle", "volume_in_anxiety_mask", "anxiety_vs_healthy_effsize")
+
+#remove values that have no overlap
+#df_fascicle_anxiety_mask_volume_overlap_effsize_value <- df_fascicle_anxiety_mask_volume_overlap_effsize_value
+
+# plot fascicle overlap x Eff size value
+#statistic, 
+anxiety_overlap_x_anxiety_vs_healthy_vol_effsize <- lm(anxiety_vs_healthy_effsize ~ volume_in_anxiety_mask, data=df_fascicle_anxiety_mask_volume_overlap_effsize_value )
+summary(anxiety_overlap_x_anxiety_vs_healthy_vol_effsize)
+
+scatter_effsize_val_by_anxiety_net_overlap_log <- ggplot(data=df_fascicle_anxiety_mask_volume_overlap_effsize_value, aes(x=volume_in_anxiety_mask, y=anxiety_vs_healthy_effsize, color=anxiety_vs_healthy_effsize)) +
+  geom_point(size=2) + 
+  scale_color_gradient(low = "#FFFFFF", high = "#ff00ff") +
+  geom_smooth(formula = y ~ x, method=lm, color="black")+
+  scale_x_continuous(trans=scales::pseudo_log_trans(base = 10), breaks=c(0, 10, 100, 1000, 10000, 100000)) + 
+  xlab("Volume of Fascicle in Anxiety Network") + 
+  ylab("Effect Size (r)") + 
+  theme(plot.title=element_text(hjust=0.5),
+        axis.text = element_text(size=16, color = "black"),
+        axis.title = element_text(size=18, color = "black"),
+        axis.line = element_line(color="black", size=1.3),
+        panel.background = element_blank(),
+        legend.position = "none",
+        aspect.ratio = 4/4) + 
+  annotate("text", x=1.6, y=0.14, size = 5, 
+           label = paste0("P = ", round(summary(anxiety_overlap_x_anxiety_vs_healthy_vol_effsize)$coef[2,4],2)))
+
+print(scatter_effsize_val_by_anxiety_net_overlap_log)
+
+#save as pdf
+#pdf(file=paste0(homedir, "/results/Figures_for_msanxietyn_paper/scatter_effsize_val_by_anxiety_net_overlap_log.pdf"))
+ # scatter_effsize_val_by_anxiety_net_overlap_log
+#dev.off()
+
+#df_for_making_colors <- df_fascicle_anxiety_mask_volume_overlap_effsize_value %>% dplyr::select(fascicle, anxiety_vs_healthy_effsize)
+#write.table(x = df_for_making_colors, file = paste0(homedir, "results/fascicle_and_effect_size_for_volxdx_analysis_n77.csv"), row.names = F, col.names = F, quote = F, sep = ",")
+
+```
+
+### Sex Differences
+```{r diseaseXsexdiff}
+############## sex diff
+#df_anxiety_disorder_by_sex <-
+
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter (anxiety_dose != 3)
 
@@
 
+```
+
+### Age*Disease
+```{r diagnosisXage}
+
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != 3) %>%
+  mutate(anxiety_dose_factor = ordered(anxiety_dose))
+
 ### diagnosis by age interaction?
@@
 
-#gam
+#gam dose
 diagnosis_by_age_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 summary(diagnosis_by_age_gam)$s.table
-plot(diagnosis_by_age_gam)
+#plot(diagnosis_by_age_gam)
+
+#gam factor - there is a linear dose effect per network size sum, as well as a sig age by anxiety relationship, but only in sick people
+diagnosis_by_age_gam_factor <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_gam_factor)
+summary(diagnosis_by_age_gam_factor)$s.table
+#plot(diagnosis_by_age_gam_factor)
+
+#plot proportion_volume_lost_per_total_network_size_sum
+plot_smooths_proportion_volume_lost_per_total_network_size_sum <- plot_smooths(
+  model = diagnosis_by_age_gam_factor,
+  series = PAT_AGE_AT_EXAM,
+  comparison = anxiety_dose_factor
+) +
+  theme(legend.position = "top")
+plot_smooths_proportion_volume_lost_per_total_network_size_sum
 
@@
 summary(diagnosis_by_age_anx_net_gam)$s.table
-plot(diagnosis_by_age_anx_net_gam)
+#plot(diagnosis_by_age_anx_net_gam)
 
 #factor
-diagnosis_by_age_anx_net_gam_factor <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ as.factor(anxiety_dose)+s(PAT_AGE_AT_EXAM, by = as.factor(anxiety_dose)), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_anx_net_gam_factor <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_anx_net_gam_factor)
 summary(diagnosis_by_age_anx_net_gam_factor)$s.table
-plot(diagnosis_by_age_anx_net_gam_factor)
+#plot(diagnosis_by_age_anx_net_gam_factor)
+
+#gam plot diagnosis_by_age_anx_net_gam_factor
+
+plot_smooths_diagnosis_by_age_anx_net_gam_factor <- plot_smooths(
+  model = diagnosis_by_age_anx_net_gam_factor,
+  series = PAT_AGE_AT_EXAM,
+  comparison = anxiety_dose_factor
+) +
+  theme(legend.position = "top")
+plot_smooths_diagnosis_by_age_anx_net_gam_factor
 
@@
 summary(diagnosis_by_age_nonanx_net_gam)$s.table
-plot(diagnosis_by_age_nonanx_net_gam)
+#plot(diagnosis_by_age_nonanx_net_gam)
 
@@
 
-diagnosis_by_age_nonanx_net_gam_factor <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ as.factor(anxiety_dose)+s(PAT_AGE_AT_EXAM, by = as.factor(anxiety_dose)), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_nonanx_net_gam_factor <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_nonanx_net_gam_factor)
 summary(diagnosis_by_age_nonanx_net_gam_factor)$s.table
-plot(diagnosis_by_age_nonanx_net_gam_factor)
+#plot(diagnosis_by_age_nonanx_net_gam_factor)
+
+#gam plot diagnosis_by_age_nonanx_net_gam_factor
+
+plot_smooths_diagnosis_by_age_nonanx_net_gam_factor <- plot_smooths(
+  model = diagnosis_by_age_nonanx_net_gam_factor,
+  series = PAT_AGE_AT_EXAM,
+  comparison = anxiety_dose_factor
+) +
+  theme(legend.position = "top")
+plot_smooths_diagnosis_by_age_nonanx_net_gam_factor
 
@@
 summary(diagnosis_by_age_UF_R_gam)$s.table
-plot(diagnosis_by_age_UF_R_gam)
+#plot(diagnosis_by_age_UF_R_gam)
 
 #factor
-diagnosis_by_age_UF_R_gam_factor <- gam(UF_R_vol ~ as.factor(anxiety_dose)+s(PAT_AGE_AT_EXAM, by = as.factor(anxiety_dose)), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_UF_R_gam_factor <- gam(UF_R_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_UF_R_gam_factor)
 summary(diagnosis_by_age_UF_R_gam_factor)$s.table
-plot(diagnosis_by_age_UF_R_gam_factor)
+#plot(diagnosis_by_age_UF_R_gam_factor)
+
+#gam UF_R plot
+
+plot_smooths_anxiety_dose_by_age_UF_R <- plot_smooths(
+  model = diagnosis_by_age_UF_R_gam_factor,
+  series = PAT_AGE_AT_EXAM,
+  comparison = anxiety_dose_factor
+) +
+  theme(legend.position = "top")
+plot_smooths_anxiety_dose_by_age_UF_R
 
@@
 summary(diagnosis_by_age_UF_L_gam)$s.table
-plot(diagnosis_by_age_UF_L_gam)
+#plot(diagnosis_by_age_UF_L_gam)
 
 #factor
-diagnosis_by_age_UF_L_gam_factor <- gam(UF_L_vol ~ as.factor(anxiety_dose)+s(PAT_AGE_AT_EXAM, by = as.factor(anxiety_dose)), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_UF_L_gam_factor <- gam(UF_L_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_UF_L_gam_factor)
 summary(diagnosis_by_age_UF_L_gam_factor)$s.table
-plot(diagnosis_by_age_UF_L_gam_factor)
-
-```
-
-###plots
+#plot(diagnosis_by_age_UF_L_gam_factor)
+
+#gam UF_L plot
+
+plot_smooths_anxiety_dose_by_age_UF_L <- plot_smooths(
+  model = diagnosis_by_age_UF_L_gam_factor,
+  series = PAT_AGE_AT_EXAM,
+  comparison = anxiety_dose_factor
+) +
+  theme(legend.position = "top")
+plot_smooths_anxiety_dose_by_age_UF_L
+
+## Sex diff trajectories by age
+#overall - NS
+sex_by_age <- lm(proportion_volume_lost_per_total_network_size_sum ~ osex*PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(sex_by_age)
+
+```
+
+### Individual Fascicle disease
+
+#### healthy vs super sick - values that fdr correct, most not anxiety net
+```{r individual_fascicle_disease_healthy_vs_super_sick}
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  mutate(anxiousAndMeds_or_healthy = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  filter(anxiousAndMeds_or_healthy %in% c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>%
+  mutate(anxiousAndMeds_or_healthy = factor(anxiousAndMeds_or_healthy, levels=c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
+
+#lm
+fascicle_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
+{
+  lm(substitute(i ~ anxiousAndMeds_or_healthy + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+})
+names(fascicle_lm) <- fascicle_names_w_prop_suffix
+
+#anova
+fascicle_anova <- lapply(fascicle_lm, anova)
+
+#fdr corrected
+fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
+print(fascicle_anova_fdr)
+
+#fdr corrected only association cortex
+#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
+##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
+#print(fascicle_anova_fdr_association)
+
+#uncorrected
+fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
+fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
+print(fascicle_anova_p05_unc) 
+```
+
+#### Parametric all fascicles
+```{r individual_fascicle_disease_healthy_vs_super_sick}
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != 3) %>%
+  mutate(anxiety_dose_factor = ordered(anxiety_dose))
+
+#lm
+fascicle_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
+{
+  lm(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+})
+names(fascicle_lm) <- fascicle_names_w_prop_suffix
+
+#anova
+fascicle_anova <- lapply(fascicle_lm, anova)
+
+#fdr corrected
+fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
+print(fascicle_anova_fdr)
+
+#fdr corrected only association cortex
+#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
+##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
+#print(fascicle_anova_fdr_association)
+
+#uncorrected
+fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
+fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
+print(fascicle_anova_p05_unc) 
+```
+#### Parametric anxiety net fascicles
+```{r individual_fascicle_disease_healthy_vs_super_sick}
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != 3) %>%
+  mutate(anxiety_dose_factor = ordered(anxiety_dose))
+
+#lm
+fascicle_lm <- lapply(fascicle_names_top_25_prop_w_suff, function(x) 
+{
+  lm(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+})
+names(fascicle_lm) <- fascicle_names_top_25_prop_w_suff
+
+#anova
+fascicle_anova <- lapply(fascicle_lm, anova)
+
+#fdr corrected
+fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
+print(fascicle_anova_fdr)
+
+#fdr corrected only association cortex
+#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
+##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
+#print(fascicle_anova_fdr_association)
+
+#uncorrected
+fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
+fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
+print(fascicle_anova_p05_unc) 
+```
+
+#### Parametric nonanxiety net fascicles
+```{r individual_fascicle_disease_healthy_vs_super_sick}
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != 3) %>%
+  mutate(anxiety_dose_factor = ordered(anxiety_dose))
+
+#lm
+fascicle_lm <- lapply(fascicle_names_bottom_75_prop_w_suff, function(x) 
+{
+  lm(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+})
+names(fascicle_lm) <- fascicle_names_bottom_75_prop_w_suff
+
+#anova
+fascicle_anova <- lapply(fascicle_lm, anova)
+
+#fdr corrected
+fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
+print(fascicle_anova_fdr)
+
+#fdr corrected only association cortex
+#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
+##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
+#print(fascicle_anova_fdr_association)
+
+#uncorrected
+fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
+fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
+print(fascicle_anova_p05_unc) 
+```
+
+### Plots
+
+##### Overall disease, within and outside anxiety net
 ```{r}
-prop_injured_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x= oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed , y=proportion_volume_lost_per_total_network_size_sum, fill= oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed )) +
+prop_injured_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x= oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed , y=proportion_volume_lost_per_total_network_size_sum, fill= oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed )) +
   geom_violin() +  
@@
   #proportion injured over anxiety net
-prop_injured_anxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+prop_injured_anxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
   geom_violin() +  
@@
   #proportion injured over nonanxiety net
-prop_injured_nonanxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+prop_injured_nonanxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
   geom_violin() +  
@@
 prop_injured_nonanxiety_net_by_anxiety_burden_collapsed_vars_plot
-
+```
+
+##### Plots Uncinate R& L Prop
+```{r plots_uncinate}
   #proportion injured over R Uncinate prop
-prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_R_prop, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_R_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
   geom_violin() +  
@@
 
+ #proportion injured over R Uncinate prop - geom_bar
+means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
+
+df_UF_R_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
+
+names(df_UF_R_mean_by_anxiety_dose) <- c("mean_UF_R", "Anxiety_dose")
+
+df_UF_R_mean_by_anxiety_dose <- df_UF_R_mean_by_anxiety_dose %>%
+  mutate(mean_UF_R = as.numeric(mean_UF_R)) %>%
+  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
+
+prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_UF_R_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_R, fill=Anxiety_dose)) +
+  geom_bar(stat="identity") +  
+  ylim(0,0.5)+
+#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
+        panel.background = element_rect(colour = "white", fill = "white"))
+prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
+
   #proportion injured over L Uncinate prop
-prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_L_prop, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_L_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
   geom_violin() +  
@@
 prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot
+
+ #proportion injured over R Uncinate prop - geom_bar
+means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
+
+df_UF_L_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
+
+names(df_UF_L_mean_by_anxiety_dose) <- c("mean_UF_L", "Anxiety_dose")
+
+df_UF_R_mean_by_anxiety_dose <- df_UF_L_mean_by_anxiety_dose %>%
+  mutate(mean_UF_L = as.numeric(mean_UF_L)) %>%
+  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
+
+prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_UF_R_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_L, fill=Anxiety_dose)) +
+  geom_bar(stat="identity") +  
+  ylim(0,0.5)+
+#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
+        panel.background = element_rect(colour = "white", fill = "white"))
+prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
 ```
@@
 #isolate out only the depressed group and healthy group
-dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% 
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>% 
   filter(depGroupVar != 0)  %>% 
@@
 #### age histo ###
-hist(dep_and_healthy_groups_for_ICD_analysis$PAT_AGE_AT_EXAM,
-main = paste0("Age In Good Mimosa Group : n = ", dim(dep_and_healthy_groups_for_ICD_analysis)[1]), xlab = "Age", breaks = 10)
+hist(df_demo_and_fascicles_no_unclass_anxiety_dose$PAT_AGE_AT_EXAM,
+main = paste0("Age In Good Mimosa Group : n = ", dim(df_demo_and_fascicles_no_unclass_anxiety_dose)[1]), xlab = "Age", breaks = 10)
 

### 2024-07-18 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
Add files via upload

@@
 
+### testing mean UF in depression group  - NS!!!
+(previous script (~/BBL/msdepression/scripts/Biological_Psychiatry_Revision_Scripts/msdepression_n380_started_20230927_mm_BP_r1.Rmd)), lines 734 and  779-781
+  #bilat: depGroupVar        85.32     206.70   t=0.413    p=0.680    
+  disease_mean_UF_vol_lm <- lm(mean_UF_vol ~ depGroupVar + osex+PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)
+  summary(disease_mean_UF_vol_lm)
 #findings
@@
 
+### Define anxiety net by top 25 in both vol/prop
+```{r defineanxietynet_with_25_propx25vol}
+##### make an array of fascicles that have both substantial overlap with the anxiety network (top 25% vol), and where each fascicle is substantially impacted (top 25% proportion), n = 14
+fascicle_names_top_25_vol_x_top_25_prop <- fascicle_names_top_25_vol[fascicle_names_top_25_vol %in% fascicle_names_top_25_prop]
+
+#add vol/prop suffixes
+fascicle_names_top_25_vol_x_top_25_prop_PROP_suffix <-fascicle_names_top_25_vol_x_top_25_prop%>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
+fascicle_names_top_25_vol_x_top_25_prop_VOL_suffix <-fascicle_names_top_25_vol_x_top_25_prop%>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
+
+#create fascicle vectors that don't include these special fascicles, n = 63
+fascicle_names_NOT_top_25_vol_x_top_25_prop <- fascicle_names_no_cranial_nerves[!(fascicle_names_no_cranial_nerves %in% fascicle_names_top_25_vol_x_top_25_prop)]
+
+#add vol/prop suffixes
+fascicle_names_NOT_top_25_vol_x_top_25_prop_PROP_suffix <- fascicle_names_NOT_top_25_vol_x_top_25_prop%>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
+fascicle_names_NOT_top_25_vol_x_top_25_prop_VOL_suffix <- fascicle_names_NOT_top_25_vol_x_top_25_prop%>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
+
+#anxiety25_propxvol overlap total, sum of these two is 1545449 (and this is total_fascicle_volume)
+anxiety_top_25_vol_x_top_25_prop_vol <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% fascicle_names_top_25_vol_x_top_25_prop]) #vol = 181869
+
+#nonanxiety25_propxvol overlap total
+anxiety_NOT_top_25_vol_x_top_25_prop_vol <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% fascicle_names_NOT_top_25_vol_x_top_25_prop]) #vol = 1363580
+
+#check sums
+if ((anxiety_top_25_vol_x_top_25_prop_vol + anxiety_NOT_top_25_vol_x_top_25_prop_vol) == total_fascicle_volume) {
+  print("anxiety + nonanxiety net = total fascicle volume")
+} else{
+  print("something is wrong with counts")
+}
+
+```
+
 ###Add columns in the main data frame indicating overall injury in the whole network, in the top 25 network (vol and prop), and bottom 75%
@@
   mutate(proportion_fascicle_vol_lost_inanxietynet_no_depression_overlap = sum_fascicle_vol_lost_inanxietynet_no_depression_overlap/anxiety_only_net_vol) %>%
+
+    ##sum of total volume lost in anxiety 25 volxanxiety25prop groups, and proportion of volume lost in network (volume lost/network volume size)
+  mutate(sum_fascicle_names_top_25_vol_x_top_25_prop = 
+           rowSums(across(all_of(fascicle_names_top_25_vol_x_top_25_prop_VOL_suffix)))) %>%
+  mutate(proportion_fascicle_vol_lost_top_25_vol_x_top_25_prop = sum_fascicle_names_top_25_vol_x_top_25_prop/anxiety_top_25_vol_x_top_25_prop_vol) %>%
+
+    ##sum of total volume lost in remaining 63 fascicles NOT in anxiety 25 volxanxiety25prop groups, and proportion of volume lost in network (volume lost/network volume size)
+  mutate(sum_fascicle_names_NOT_top_25_vol_x_top_25_prop = 
+           rowSums(across(all_of(fascicle_names_NOT_top_25_vol_x_top_25_prop_VOL_suffix)))) %>%
+  mutate(proportion_fascicle_vol_lost_NOT_top_25_vol_x_top_25_prop = sum_fascicle_names_NOT_top_25_vol_x_top_25_prop/anxiety_NOT_top_25_vol_x_top_25_prop_vol) %>%
+
+   ##mean_uncinate)
+  mutate(mean_UF_vol = (UF_L_vol + UF_R_vol)/2) %>%
+  mutate(mean_UF_prop = (UF_L_prop + UF_R_prop)/2) %>%
 
@@
 ```{r overlap_with_dep_group}
+#### 53.4% overlap total
 
@@
   mutate(EMPI_in_dep_group = EMPI %in% depression_empis$EMPI)
+
+#"Percent overlap 53.4%"
+print(paste0("Percent overlap ", round(sum(df_disease_burden_unc_and_anx_net_collapsed_variables$EMPI_in_dep_group)/length(df_disease_burden_unc_and_anx_net_collapsed_variables$EMPI), 3) * 100, "%"))
 
@@
 ```
+
 ### Overall Disease by Anxiety Dose *acnp
@@
 
-### Uncinate by Anxiety Dose *acnp?
+### Lesion volumes 
+#### Diagnosis 
+  - sick > healthy in vol of lesions
+```{r lesion_volumes_dx}
+ df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, volume_of_mimosa_lesions) %>%
+  ungroup()
+
+##### healthy vs sick
+
+#lm lesion volumes; DiagnosisMS+Anxiety  6310.99    2143.87   2.944 0.003694 ** 
+volume_of_mimosa_lesions_lm <- lm(volume_of_mimosa_lesions ~ Diagnosis + osex + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+summary(volume_of_mimosa_lesions_lm)
+
+#gam lesion volumes; DiagnosisMS+Anxiety   6973.5     2014.7   3.461 0.000681 ***
+volume_of_mimosa_lesions_gam <- gam(volume_of_mimosa_lesions ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+summary(volume_of_mimosa_lesions_gam)
+```
+
+#### Anxiety dose
+  - anxiety dose correlates with disease burden (volume of lesions)
+```{r lesion_volumes_anxiety_dose}
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter (anxiety_dose != 3)
+
+#dose; anxiety_dose     3028.07    1014.45   2.985 0.003026 **
+
+  anxiety_dose_volume_of_mimosa_lesions_by_sex_lm <- lm(volume_of_mimosa_lesions ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxiety_dose_volume_of_mimosa_lesions_by_sex_lm)
+
+ #bilat anxiety dose + sex + age: anxiety_dose   3304.7      985.8   3.352 0.000886 ***
+
+  anxiety_dose_volume_of_mimosa_lesions_by_sex_gam <- gam(volume_of_mimosa_lesions ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxiety_dose_volume_of_mimosa_lesions_by_sex_gam)
+
+```
+
+### Uncinate **ACNP**
+
+#### Demographics
+```{r demo_uncinate}
+
+###### all groups, no unclassified
+make_demographics_table_ms_anxiety_simple(df_demo_and_fascicles %>% filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified"))
+
+###### just healthy and sick
+make_demographics_table_ms_anxiety_simple(df_demo_and_fascicles %>% filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds"))
+
+```
+#### Uncinate by diagnosis 
+```{r uncinate_by_dx}
+
+### Results: LM Mean UF_R & L, age, sex cov, DiagnosisMS+Anxiety   621.95     276.11   2.252   0.0256 * 
+#define group
+  df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol, mean_UF_vol) %>%
+  ungroup()
+
+#do lm UF*Diagnosis
+ #UF_R_vol -> DiagnosisMS+Anxiety   793.14     361.94   2.191   0.0298 *   
+disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + osex + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+summary(disease_UF_R_vol_lm)
+
+ #UF_L_vol ->DiagnosisMS+Anxiety   450.75     261.20   1.726   0.0862 .    
+disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+summary(disease_UF_L_vol_lm)
+
+#bilat: DiagnosisMS+Anxiety   621.95     276.11   2.252   0.0256 *  
+disease_mean_UF_vol_lm <- lm(mean_UF_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+summary(disease_mean_UF_vol_lm)
+
+#gam
+#UF_R_vol -> DiagnosisMS+Anxiety   795.60     366.58   2.170   0.0314 *   
+disease_UF_R_vol_gam <- gam(UF_R_vol ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+summary(disease_UF_R_vol_gam)
+
+ #UF_L_vol -> DiagnosisMS+Anxiety   420.24     262.19   1.603    0.111   
+disease_UF_L_vol_gam <- gam(UF_L_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+summary(disease_UF_L_vol_gam)
+
+#bilateral UF: DiagnosisMS+Anxiety   607.92     279.34   2.176   0.0309 *  
+disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+summary(disease_mean_UF_vol_gam)
+
+#Fornix - Right side but not left
+ #F_R_vol -> DiagnosisMS+Anxiety   860.50     368.16   2.337   0.0205 * 
+#disease_F_R_vol_lm <- lm(F_R_vol ~ Diagnosis + osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+#summary(disease_F_R_vol_lm)
+
+ #F_L_vol -> DiagnosisMS+Anxiety  329.724    181.609   1.816   0.0711 . 
+#disease_F_L_vol_lm <- lm(F_L_vol ~ Diagnosis + osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+#summary(disease_F_L_vol_lm)
+## net by sex 
+```
+
+#### Uncinate by Anxiety Dose 
 ```{r uncinateByAnxietyDose}
@@
 #results: Anxiety dose related to UF_R when covarying for linear effects of age and sex, just barely
+# Additionally - taking the mean of both UF and UR, LM for bilat anxiety dose + sex + age: anxiety_dose most sig P= 0.0367 *
 
@@
 
-########UF R - just looking at uncinate by anxiety dose; anxiety_dose      369.72     187.93   1.967   0.0499 *  *********** (LINEAR AGE)
+#lm
+
+  #R anxiety dose + age ; anxiety_dose      369.72     187.93   1.967   0.0499 *  ***********
   anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #gam, anxiety_dose    357.0      188.8   1.891   0.0594 .
+   #R *anxiety dose + osex + age anxiety_dose          anxiety_dose      377.35     188.43   2.003    0.046 *********   
+  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_UF_R_by_sex_lm)
+
+   #UF L - anxiety_dose + age    222.193    133.138   1.669    0.096 .  
+  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_UF_L_lm)
+
+   #UF_L anxiety_dose + sex + age:         anxiety_dose     232.210    133.294   1.742   0.0823 .  
+  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_UF_L_by_sex_lm)
+
+  #bilat anxiety dose + age: anxiety_dose     295.957    145.116   2.039   0.0421 *  
+  anxietyGrouping_mean_UF_lm <- lm(mean_UF_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_mean_UF_lm)
+
+  #bilat anxiety dose + sex + age: anxiety_dose      304.78     145.39   2.096   0.0367 *  
+  anxietyGrouping_mean_UF_by_sex_lm <- lm(mean_UF_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_mean_UF_by_sex_lm)
+
+#gam
+
+  #UF _ R  anxiety_dose + age   357.0      188.8   1.891   0.0594 .
   anxietyGrouping_UF_R_gam <- gam(UF_R_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #UF _ R anxiety_dose          anxiety_dose      377.35     188.43   2.003    0.046 *********   
-  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_UF_R_by_sex_lm)
-
-  #gam, anxiety_dose    364.2      189.3   1.924   0.0552 .  
+ #R anxiety dose + sex + age: anxiety_dose    364.2      189.3   1.924   0.0552 .
+
     anxietyGrouping_UF_R_by_sex_gam <- gam(UF_R_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #UF L - anxiety_dose     222.193    133.138   1.669    0.096 .  
-  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_UF_L_lm)
-
-   #gam, anxiety_dose    220.1      133.7   1.646    0.101    
+   #UF_L, anxiety_dose + age    220.1      133.7   1.646    0.101    
   anxietyGrouping_UF_L_gam <- gam(UF_L_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #UF_L anxiety_dose:         anxiety_dose     232.210    133.294   1.742   0.0823 .  
-  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_UF_L_by_sex_lm)
-
-   #gam, anxiety_dose    229.9      133.9   1.717   0.0868 .  
+   #UF_L anxiety_dose + sex + age    229.9      133.9   1.717   0.0868 .  
   anxietyGrouping_UF_L_by_sex_gam <- gam(UF_L_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_UF_L_by_sex_gam)
+
+  #bilat
+
+  #bilat  anxiety_dose + age: anxiety_dose    288.5      145.7    1.98   0.0484 *  
+  anxietyGrouping_mean_UF_gam <- gam(mean_UF_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_mean_UF_gam)
+
+ #bilat anxiety dose + sex + age: anxiety_dose    297.0      146.0   2.034   0.0426 *
+
+    anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_mean_UF_by_sex_gam)
 ```
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>% 
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
   mutate(subject = as.factor(EMPI)) %>%
@@
 
-## Means of separate groups:
-
-#t test, t, t = 37.378, df = 271, p-value < 2.2e-16, anxiety net: 0.4974984; nonanxiety net: 0.256347
-within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
-summary(within_vs_outside_anxiety_net_t)
-
-#t test
-between_dx_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])
-summary(between_dx_t)
-
-######means
-
-#mean = 0.5665159
-mean_anxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
-mean_anxiety_dx_anx_net
-
-#mean = 0.310777
-mean_anxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
-mean_anxiety_dx_nonanx_net
-
-#mean =  0.4652665
-mean_nonanxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
-mean_nonanxiety_dx_anx_net
-
-#mean = 0.2106967
-mean_nonanxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
-mean_nonanxiety_dx_nonanx_net
-
 #simple lmer
 
-##NetworkNonanxiety_network                      -0.254570   0.013575  92.000000 -18.753  < 2e-16 ***
-##DiagnosisMS+Anxiety                             0.108710   0.040130 103.092356   2.709  0.00791 ** 
+#NetworkNonanxiety_network                      -0.246157   0.009900 173.000001 -24.864  < 2e-16 ***
+#DiagnosisMS+Anxiety                             0.075874   0.030315 194.726132   2.503 0.013142 *
+
 disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
@@
 
-#Network confit:NetworkNonanxiety_network -0.2496593 -0.23419230
+#Network confit:
+#NetworkNonanxiety_network                     -0.265556308 -0.226758160
+#DiagnosisMS+Anxiety                            0.016671783  0.135076698
 confint(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
 
-###do anova instead
-##Network             1  3.059  3.0587  82.472  < 2e-16 ***
-##Diagnosis           1  0.473  0.4728  12.749 0.000455 ***
-
-disease_within_vs_outside_anxiety_net_by_dx_groups_anova <- aov(proportion_affected ~ Network+Diagnosis + Network:Diagnosis + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_dx_groups_anova)
-
-#do lm UF*Diagnosis
- #UF_R_vol -> DiagnosisMS+Anxiety  1418.26     352.04   4.029 8.20e-05 ***
-disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + osex + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_UF_R_vol_lm)
-
- #UF_L_vol -> DiagnosisMS+Anxiety   737.97     250.61   2.945  0.00365 ** 
-disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_UF_L_vol_lm)
-
-#Fornix - Right side but not left
- #F_R_vol -> DiagnosisMS+Anxiety   860.50     368.16   2.337   0.0205 * 
-disease_F_R_vol_lm <- lm(F_R_vol ~ Diagnosis + osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_F_R_vol_lm)
-
- #F_L_vol -> DiagnosisMS+Anxiety  329.724    181.609   1.816   0.0711 . 
-disease_F_L_vol_lm <- lm(F_L_vol ~ Diagnosis + osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_F_L_vol_lm)
-## net by sex
-
 #simple lmer
-#NetworkNonanxiety_network         -0.250361   0.011772  92.000001 -21.268  < 2e-16 ***
+#NetworkNonanxiety_network         -0.248004   0.008994 173.000001 -27.573  < 2e-16 ***
   disease_within_vs_outside_anxiety_net_by_sex_diff_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
@@
 ## diagnosis by sex 
- #simple lmer, DiagnosisMS+Anxiety         0.124327   0.040488   3.071  0.00246 **
+ #simple lmer, DiagnosisMS+Anxiety         0.102015   0.030998   3.291   0.0011 ** 
 disease_diagnosis_by_sex_diff_lm <- lm(proportion_affected ~ Diagnosis*osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
@@
 #network * diagnosis + sex
- #simple lmer: NetworkNonanxiety_network                      -0.254570   0.013575  92.000000 -18.753  < 2e-16 ***
- ##DiagnosisMS+Anxiety                             0.107571   0.040361 101.820059   2.665  0.00895 ** 
+#NetworkNonanxiety_network                      -0.246157   0.009900 173.000001 -24.864  < 2e-16 ***
+#DiagnosisMS+Anxiety                             0.076902   0.030464 193.366257   2.524 0.012394 * 
 disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer <- lmer(proportion_affected ~ Network*Diagnosis + osex + (1|subject)+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
@@
 violin_within_vs_outside_network_sum_proportion_scaled_by_network_size
+```
+
+## Anxiety net defined as (25 vol x 25 prop anxiety net) -> no better, don't use
+### Anxiety and Non anxiety net by dose 
+```{r anxiety_and_nonanxiety_net_by_dose}
+
+### Will be using gam + s(age) and osex because this was giving me most robust findings previously.
+### I know that we already have an effect in across whole brain. Now i want to check if it differs within new anxiety net vs outside
+
+df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>% 
+  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_fascicle_volume_lost_top_25_vol_x_top_25_prop, proportion_fascicle_vol_lost_NOT_top_25_vol_x_top_25_prop, UF_L_prop, UF_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex, anxiety_dose, PAT_AGE_AT_EXAM)
+
+## gam, check original finding still there, anxiety_dose  0.03692    0.01496   2.468    0.014 *  
+   anxietyGrouping_cov_sex_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_disease_burden_unc_and_anx_net_collapsed_variables)
+  summary(anxietyGrouping_cov_sex_gam)
+
+  #gam, anxiety_dose, anxiety net, anxiety_dose  0.027830   0.015810   1.760   0.0792 . 
+   anxietyGrouping_cov_sex_anxiety_net_gam <- gam(proportion_fascicle_volume_lost_top_25_vol_x_top_25_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_disease_burden_unc_and_anx_net_collapsed_variables)
+  summary(anxietyGrouping_cov_sex_anxiety_net_gam)
+
+    #gam, anxiety_dose, non anxiety net; anxiety_dose  0.03814    0.01500   2.543   0.0114 *  
+   anxietyGrouping_cov_sex_nonanxiety_net_gam <- gam(proportion_fascicle_vol_lost_NOT_top_25_vol_x_top_25_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_disease_burden_unc_and_anx_net_collapsed_variables)
+  summary(anxietyGrouping_cov_sex_nonanxiety_net_gam)
+
+```
+
+### Network*Diagnosis 
+```{r networkxdiagnosis_groups_collapse}
+
+## take home: comparing healthy to has anxiety AND meds, more disease within vs outside net, anxiety vs non, no interaction.
+## take home #2 : More disease in R & L uncinate in anxious versus nonanxious
+## take home #3 : About the same results as using the previously described anxiety net (rather than the vol 25 x 25 prop)
+
+  #burden of anxiety by network
+  #clean up data frame
+ df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+
+  #### only two lines that are changed from normal Network * Diagnosis analysis
+  mutate(Anxiety_network = proportion_fascicle_vol_lost_top_25_vol_x_top_25_prop) %>%
+  mutate(Nonanxiety_network = proportion_fascicle_vol_lost_NOT_top_25_vol_x_top_25_prop) %>%
+  #### End changes ###
+
+  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol) %>% 
+  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol, -F_R_vol, -F_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
+  mutate(Network = as.factor(Network)) %>%
+  ungroup()
+
+ #simple lmer
+#NetworkNonanxiety_network                      -0.138487   0.008276 173.000010 -16.733  < 2e-16 ***
+#DiagnosisMS+Anxiety                             0.058186   0.029606 188.395804   1.965 0.050843 .
+
+disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
+
+#Network confit
+confint(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
+
+#simple lmer
+#NetworkNonanxiety_network         -0.124175   0.007485 173.000000 -16.589  < 2e-16 ***
+#osex.L                             0.009908   0.025201 187.843641   0.393 0.694647
+
+  disease_within_vs_outside_anxiety_net_by_sex_diff_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+  summary(disease_within_vs_outside_anxiety_net_by_sex_diff_lmer)
+
+#Network confit:
+confint(disease_within_vs_outside_anxiety_net_by_sex_diff_lmer)
+
+## diagnosis by sex 
+ #simple lmer, DiagnosisMS+Anxiety         0.0989168  0.0269866   3.665 0.000286 ***
+disease_diagnosis_by_sex_diff_lm <- lm(proportion_affected ~ Diagnosis*osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+summary(disease_diagnosis_by_sex_diff_lm)
+
+#Network confit:
+confint(disease_diagnosis_by_sex_diff_lm)
+
+#network * diagnosis + sex
+ #simple lmer: 
+#NetworkNonanxiety_network                      -0.138487   0.008276 173.000010 -16.733  < 2e-16 ***
+#DiagnosisMS+Anxiety                             0.058522   0.029769 187.116974   1.966 0.050793 .   
+disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer <- lmer(proportion_affected ~ Network*Diagnosis + osex + (1|subject)+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+summary(disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer)
+
+#Network confit
+confint(disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer)
+
 ```

### 2024-07-18 scripts/ms_functions.R

@@ -27,6 +27,72 @@ require('circlize')
 #############################
 
 #### anxiety demographics
+
+make_demographics_table_ms_anxiety_simple<- function(data_frame) {
+  #subset demographics
+  
+  listVars <- c("Race", 
+                "Sex",
+                "Age",
+                "Has.anxietydx", 
+                "On.Anxiolytics",
+                "oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed",
+                "anxiety_dose",
+                "on_anti_cd20",
+                "on_interferon",
+                "on_steroids",
+                "on_dmt",
+                "PHQ2",
+                "PHQ9",
+                "volume_of_mimosa_lesions", 
+                "mean_UF_vol",
+                "proportion_volume_lost_per_total_network_size_sum") #Race 1 = caucasian, Sex 1 = M age = years
+  
+  
+  #for_parse <- paste0("data.frame(data_frame$race_binarized, data_frame$sex_binarized, data_frame$PAT_AGE_AT_EXAM, data_frame$depGroupVar, data_frame$PHQ.2, data_frame$PHQ.9)")
+  for_parse <- paste0("data.frame(data_frame$RACE, 
+ # for_parse <- paste0("data.frame(data_frame$race_binarized,
+                      data_frame$sex_binarized, 
+                      data_frame$PAT_AGE_AT_EXAM, 
+                      data_frame$Has.anxietydx, 
+                      data_frame$On.Anxiolytics,
+                      data_frame$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed,
+                      data_frame$anxiety_dose,
+                      data_frame$On.Anti_cd20,
+                      data_frame$On.Interferon,
+                      data_frame$On.Steroids,
+                      data_frame$On.Dmt,
+                      data_frame$PHQ.2, 
+                      data_frame$PHQ.9, 
+                      data_frame$volume_of_mimosa_lesions, 
+                      data_frame$mean_UF_vol,
+                      data_frame$proportion_volume_lost_per_total_network_size_sum)")
+  
+  
+  demo <- eval(parse(text = for_parse)) 
+  names(demo) <- c(listVars)
+  
+  #Change categorical values to have names
+  
[…]

### 2024-07-25 scripts/ACNP2024_MSAnxiety.Rmd
Add files via upload

--- 2024-07-18 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
@@
 ---
-title: "MS Prelim Data K23"
+title: "ACNP 2024 MS ANXIETY"
 author: "Erica Baller"
-date: "2/25/2022"
+date: "7/1/2024"
 output:
@@
 Inclusion criteria for Anxious Group
-  1) Have an ICD10 F3* code (in our sample, people have F41.1; 41.3; 41.8; 41.9)
+  1) Have an ICD10 F4* code (in our sample, people have F41.1; 41.3; 41.8; 41.9)
         (may use this later)- https://www.nami.org/About-Mental-Illness/Treatments/Mental-Health-Medications
@@
   2) At least 1 PHQ2 or PHQ9 with a documented 0
-  3) Free of psychiatric medications per NAMI website
+  3) Free of psychiatric medications per NAMI website (plus editions per Dr. Baller)
 
@@
   If you received the MS protocol or had a diagnosis of MS but never actually saw an MS provider, we cannot be sure that the diagnosis of MS is truly valid, as it is hard to diagnose anyway.
-  If you did not have a diagnosis of depression and never completed a PHQ2 or 9, and had no history of medications, we could not safely confirm nor deny the presence of depression.
+  If you did not have a diagnosis of depression and never completed a PHQ2 or 9, and had no history of medications, we could not safely confirm nor deny the presence of anxiety.
 These subjects were excluded from future analyses.
@@
 
-## Anxiety within/outside network interaction
-```{r anxiety_net_intx}
-
-## demographics
-
-### BEST SPLIT IS STRATIFYING ON ANXIETY MEDS!!!! Better than on variable that includes anxietyGroupVar(meds + anxiety diagnoses), or anxiety diagnosis alone
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietyGroupVar != 0,])
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$Has.Anxietydx.AND.AntianxietymedGroupVar != 0,])
-
-#clean up data frame
-df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
-  filter(anxietyGroupVar != 0) %>% #lose 93, n now 719
-  mutate(subject = as.factor(EMPI)) %>%
-  mutate(Diagnosis = ifelse(anxietyGroupVar==1, "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
-  mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
-  mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
-  mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
-  mutate(Benzo_status = as.factor(Benzo_status)) %>%
-  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
-  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
-  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, Anxiolytics_status, Has.anxietydx, Benzo_status, PAT_AGE_AT_EXAM) %>% 
-  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -Anxiolytics_status, -Has.anxietydx, -Benzo_status) %>% #this is like a melt.
-Keeps empi and depGroupVar out of the melt
-  mutate(Network = as.factor(Network)) %>%
-  ungroup()
-
-#simple t test, disease within versus outside anxiety network; mean within anxiety net: 0.5426694 affected, mean outside anxiety network = 0.3062429, T=57.44, p<2.2*10^-16, 95% CI 0.22-0.24
-#MS+Anxiety, MS-Anxiety, meds + anxiety dx, true normal = 0.3850697; MS+ anxiety: ; MS-anxiety: 0.3672053
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"])
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])
-
-#Anxiety dx vs no anxiety dx
-#anxiety dx: 0.3785979; no anxiety dx: 0.3723245
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.anxietydx==1])
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.anxietydx==0])
-
-#On.Anxiolytics vs Off.Anxiolytics
-#on anxiolytics: 0.415625; off anxiolytics:0.3664898
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Anxiolytics_status=="On.Anxiolytics"])
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Anxiolytics_status=="Off.Anxiolytics"])
-
-#On.Benzos vs Off.Benzos
-#on benzos: 0.4022933; off benzos:0.372135
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Benzo_status=="On.Benzos"])
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Benzo_status=="Off.Benzos"])
-
-#Has.Anxietydx.Or.Antianxietymed
-#on benzos: 0.4022933; off benzos:0.372135
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.Anxietydx.Or.Antianxietymed=="On.Benzos"])
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.Anxietydx.Or.Antianxietymed=="Off.Benzos"])
-
-#histos
-hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], main = "Anxiety Network Injury", xlab = "Proportion Affected")
-hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], main = "Nonanxiety Network Injury", xlab = "Proportion Affected")
-
-## Means of separate groups:
-
-#t test, t = 63.621, df = 718, p-value < 2.2e-16; 95 percent confidence interval:0.2349467 0.2499088, mean diff: 0.2424277 
-within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
-summary(within_vs_outside_anxiety_net_t)
-
- #simple lmer, confirms T; -63.62   <2e-16 ***
-disease_within_vs_outside_anxiety_net_lmer <- lmer(proportion_affected ~ Network + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_lmer)
-
- #Net by sex, confirms T; -63.62   <2e-16, but no sex differences (p=0.179)
-disease_within_vs_outside_anxiety_net_sex_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_sex_lmer)
-
- #simple lmer, confirms network: -63.621  < 2e-16 , Pat age: 6.338 4.12e-10
-disease_within_vs_outside_anxiety_net_age_lmer <- lmer(proportion_affected ~ Network + PAT_AGE_AT_EXAM + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_age_lmer)
-
-#Age * network interaction, don't know if this is valid at all. outside > w/in net: -12.718  < 2e-16 ***; pat age = 6.837  1.6e-11 ***, NetworkNonanxiety_network:PAT_AGE_AT_EXAM -2.852  0.00447 
-disease_within_vs_outside_anxiety_net_age_intx_lmer <- lmer(proportion_affected ~ Network*PAT_AGE_AT_EXAM + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_age_intx_lmer)
-
-#diagnosis: NS
-diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
-summary(diagnosis_by_network_interaction_lmer)
-
-#Diagnosis: NS
-confint(diagnosis_by_network_interaction_lmer)
-
-## Anxiety network x anxiolytics status
-#Network (nonanxiety <anxiety network) : T = -58.141   <2e-16 ***; Anxiolytic status: On.anxiolytics>off.anxiolytics; T= 2.473   0.0136 *  
-#Mean prop affected: on anxiolytics: 0.415625;  off anxioloytics: 0.3664898
-
-disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer <- lmer(proportion_affected ~ Network*Anxiolytics_status + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
-confint(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
-
-## Anxiety network x benzo status
-#Network (nonanxiety <anxiety network) : T = -54.535   <2e-16***; Anxiety status: T = 0.462    P = 0.645
-
-disease_within_vs_outside_anxiety_net_by_benzo_lmer <- lmer(proportion_affected ~ Network*Benzo_status + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
-confint(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
-
-## Anxiety network x anxiety diagnosis
-#Network (nonanxiety <anxiety network) : T = -54.535   <2e-16***; Anxiety status: T = 0.462    P = 0.645
-
-disease_within_vs_outside_anxiety_net_by_anxietydx_lmer <- lmer(proportion_affected ~ Network*Has.anxietydx + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
-confint(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
-```
-
-#Anxiety network interactions and uncinate alone
-```{r anxiety_net_intx}
-
-## demographics
-
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$Has.Anxietydx.AND.AntianxietymedGroupVar != 0,])
-
-#clean up data frame
-cleaned_df <- df_demo_and_fascicles %>%
-  filter(Has.Anxietydx.AND.AntianxietymedGroupVar != 0) %>% #lose 93, n now 719
-  mutate(subject = as.factor(EMPI)) %>%
-  mutate(Diagnosis = ifelse(Has.Anxietydx.AND.AntianxietymedGroupVar==1, "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
-  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
-  mutate(mean_uncinate_injury = (UF_L_prop + UF_R_prop)/2) %>%
-  mutate(mean_uncinate_and_fornix_injury = (UF_L_prop + UF_R_prop + F_R_prop + F_L_prop)/2) %>%
-  ungroup()
-
-df_empi_dx_network_proportions <- cleaned_df %>%
-  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
-  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
-  mutate(Network = as.factor(Network)) %>%
-  ungroup()
-
-#histos
-hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], main = "Anxiety Network Injury", xlab = "Proportion Affected")
-hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], main = "Nonanxiety Network Injury", xlab = "Proportion Affected")
-hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS+Anxiety"], main = "Uncinate Injury in Anxious Patients", xlab = "Proportion Affected")
-hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS-Anxiety"], main = "Uncinate Injury in Healthyish Patients", xlab = "Proportion Affected")
-
-## Means of separate groups:
-
-#t test, 
-within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
-within_vs_outside_anxiety_net_t
-
-#diagnosis: 
-diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
-summary(diagnosis_by_network_interaction_lmer)
-confint(diagnosis_by_network_interaction_lmer)
-
-#Net by sex, confirms T; -63.62   <2e-16, but no sex differences (p=0.179)
-disease_within_vs_outside_anxiety_net_sex_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_sex_lmer)
-
-#t test uncinate alone
-mean_uncinate_by_dx_t <- t.test(cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
-mean_uncinate_by_dx_t
-
-#diagnosisxmean_uncinate: 
-diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_injury ~ Diagnosis, data = cleaned_df)
-summary(diagnosis_by_network_interaction_lmer)
-confint(diagnosis_by_network_interaction_lmer)
-
-#diagnosisxmean_uncinate+fornix: 
-diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_and_fornix_injury ~ Diagnosis, data = cleaned_df)
-summary(diagnosis_by_network_interaction_lmer)
-confint(diagnosis_by_network_interaction_lmer)
-
-#### if I decide later I want to look at L and right uncinate alone
-
-#t test uncinate alone, Left,
-l_uncinate_by_dx_t <- t.test(cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
-l_uncinate_by_dx_t
-
-#t test uncinate alone, right, remember everybody is double counted!!!! so this needs to be fixed.
-r_uncinate_by_dx_t <- t.test(cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
-r_uncinate_by_dx_t
-
-```
-
-## Anxiety burden severity ranking
-
-I am wondering here if, as my brain wants to think, that things in the chart reflect severity of anxiety.
-For example, I'd expect people with dep and anxiety comorbidity and on meds would be the sickest, followed by anxiety + on meds, then on meds, then anxiety dx, then healthyish.
-I am going to do a t-test comparing proportion of disease over whole brain, over anxiety net, and over uncinate in each of those groups as compared to the healthy group, and rank the T to see if that pattern bears out.
-And if it does, do some sort of regression.
-```{r anxiety_burden_severity_ranking }
-#variables_to_evaluate <- c("Has.Anxietydx.AND.AntianxietymedGroupVar")
-df_disease_burden_unc_and_anx_net <- df_demo_and_fascicles %>%
-  filter(oAnxiety.And.Dep.And.AnxietyMedsGroupVar != "unclassified") %>%
-  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxiety.And.Dep.And.AnxietyMedsGroupVar, osex)
-
-tibble_n <- df_disease_burden_unc_and_anx_net %>% 
-  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>% 
-  summarise(n())
-
-tibble_overall_disease <- 
-  df_disease_burden_unc_and_anx_net %>% 
-  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
-  summarize(mean_size = mean(proportion_volume_lost_per_total_network_size_sum))
-
-tibble_overall_summaries <- 
-  df_disease_burden_unc_and_anx_net %>% 
-  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
-  summarize(n(),
-            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
-            mean_UF_L = mean(UF_L_prop),
-            mean_UF_R = mean(UF_R_prop))
-tibble_overall_summaries
-
-tibble_overall_summaries_by_sex <- 
-  df_disease_burden_unc_and_anx_net %>% 
-  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar, osex) %>%
-  summarize(n(),
-            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
-            mean_UF_L = mean(UF_L_prop),
-            mean_UF_R = mean(UF_R_prop))
-  tibble_overall_summaries_by_sex
-
-  tibble_overall_summaries_females <- 
-  df_disease_burden_unc_and_anx_net %>% 
-  filter(osex == "Female") %>%
-  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
-  summarize(n(),
-            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
-            mean_UF_L = mean(UF_L_prop),
-            mean_UF_R = mean(UF_R_prop))
-  tibble_overall_summaries_females
-
-    tibble_overall_summaries_males <- 
-  df_disease_burden_unc_and_anx_net %>% 
-  filter(osex == "Male") %>%
-  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
-  summarize(n(),
-            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
-            mean_UF_L = mean(UF_L_prop),
-            mean_UF_R = mean(UF_R_prop))
-  tibble_overall_summaries_males
-
-  ### analyses
-
-```
-
-#### plots
-```{r}
-  #proportion injured over whole brain
-prop_injured_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=proportion_volume_lost_per_total_network_size_sum, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_by_anxiety_burden_plot
-
-  #proportion injured over anxiety net
-prop_injured_anxiety_net_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_anxiety_net_by_anxiety_burden_plot
-
-  #proportion injured over nonanxiety net
-prop_injured_nonanxiety_net_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_nonanxiety_net_by_anxiety_burden_plot
-
-  #proportion injured over R Uncinate prop
-prop_injured_R_uncinate_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=UF_R_prop, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_R_uncinate_by_anxiety_burden_plot
-
-  #proportion injured over L Uncinate prop
-prop_injured_L_uncinate_by_anxiety_burden_plot <-  ggplot(df_disease_burden_unc_and_anx_net, aes(x=oAnxiety.And.Dep.And.AnxietyMedsGroupVar, y=UF_L_prop, fill=oAnxiety.And.Dep.And.AnxietyMedsGroupVar)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_L_uncinate_by_anxiety_burden_plot
-
-prop_injured_by_anxiety_burden_and_sex_plot <- ggboxplot(df_disease_burden_unc_and_anx_net, x = "oAnxiety.And.Dep.And.AnxietyMedsGroupVar", y = "proportion_volume_lost_per_total_network_size_sum", color = "osex",
-          palette = c("#00AFBB", "#E7B800")) +
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_by_anxiety_burden_and_sex_plot
-
-```
-
-#Anxiety network interactions and uncinate alone, TRUE HEALTHY
-```{r anxiety_net_intx}
-
-## demographics
-
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar != "unclassified",])
-
-#clean up data frame
-cleaned_df <- df_demo_and_fascicles %>%
-  filter(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar != "unclassified") %>% #lose 93, n now 719
-  mutate(subject = as.factor(EMPI)) %>%
-  mutate(Diagnosis = ifelse(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
-  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
-  mutate(mean_uncinate_injury = (UF_L_prop + UF_R_prop)/2) %>%
-  mutate(mean_uncinate_and_fornix_injury = (UF_L_prop + UF_R_prop + F_R_prop + F_L_prop)/2) %>%
-  ungroup()
-
-df_empi_dx_network_proportions <- cleaned_df %>%
-  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
-  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
-  mutate(Network = as.factor(Network)) %>%
-  ungroup()
-
-#histos
-hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], main = "Anxiety Network Injury", xlab = "Proportion Affected")
-hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], main = "Nonanxiety Network Injury", xlab = "Proportion Affected")
-hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS+Anxiety"], main = "Uncinate Injury in Anxious Patients", xlab = "Proportion Affected")
-hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS-Anxiety"], main = "Uncinate Injury in Healthyish Patients", xlab = "Proportion Affected")
-
-## Means of separate groups:
-
-#t test, 
-within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
-within_vs_outside_anxiety_net_t
-
-#diagnosis: 
-diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
-summary(diagnosis_by_network_interaction_lmer)
-confint(diagnosis_by_network_interaction_lmer)
-
-#Net by sex, confirms T; -63.62   <2e-16, but no sex differences (p=0.179)
-disease_within_vs_outside_anxiety_net_sex_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_sex_lmer)
-
-#t test uncinate alone
-mean_uncinate_by_dx_t <- t.test(cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
-mean_uncinate_by_dx_t
-
-#diagnosisxmean_uncinate: 
-diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_injury ~ Diagnosis, data = cleaned_df)
-summary(diagnosis_by_network_interaction_lmer)
-confint(diagnosis_by_network_interaction_lmer)
-
-#diagnosisxmean_uncinate+fornix: 
-diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_and_fornix_injury ~ Diagnosis, data = cleaned_df)
-summary(diagnosis_by_network_interaction_lmer)
-confint(diagnosis_by_network_interaction_lmer)
-
-#### if I decide later I want to look at L and right uncinate alone
-
-#t test uncinate alone, Left,
-l_uncinate_by_dx_t <- t.test(cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
-l_uncinate_by_dx_t
-
-#t test uncinate alone, right, remember everybody is double counted!!!! so this needs to be fixed.
-r_uncinate_by_dx_t <- t.test(cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
-r_uncinate_by_dx_t
-
-```
-
-## Anxiety burden severity ranking true healthy
-
-I am wondering here if, as my brain wants to think, that things in the chart reflect severity of anxiety.
-For example, I'd expect people with dep and anxiety comorbidity and on meds would be the sickest, followed by anxiety + on meds, then on meds, then anxiety dx, then healthyish.
-I am going to do a t-test comparing proportion of disease over whole brain, over anxiety net, and over uncinate in each of those groups as compared to the healthy group, and rank the T to see if that pattern bears out.
-And if it does, do some sort of regression.
-```{r anxiety_burden_severity_ranking }
-#variables_to_evaluate <- c("Has.Anxietydx.AND.AntianxietymedGroupVar")
-df_disease_burden_unc_and_anx_net_true_healthy <- df_demo_and_fascicles %>%
-  filter(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar != "unclassified") %>%
-  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, osex)
-
-tibble_n <- df_disease_burden_unc_and_anx_net_true_healthy %>% 
-  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>% 
-  summarise(n())
-
-tibble_overall_disease <- 
-  df_disease_burden_unc_and_anx_net_true_healthy %>% 
-  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
-  summarize(mean_size = mean(proportion_volume_lost_per_total_network_size_sum))
-
-tibble_overall_summaries <- 
-  df_disease_burden_unc_and_anx_net_true_healthy %>% 
-  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
-  summarize(n(),
-            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
-            mean_UF_L = mean(UF_L_prop),
-            mean_UF_R = mean(UF_R_prop))
-tibble_overall_summaries
-
-tibble_overall_summaries_by_sex <- 
-  df_disease_burden_unc_and_anx_net_true_healthy %>% 
-  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, osex) %>%
-  summarize(n(),
-            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
-            mean_UF_L = mean(UF_L_prop),
-            mean_UF_R = mean(UF_R_prop))
-  tibble_overall_summaries_by_sex
-
-  tibble_overall_summaries_females <- 
-  df_disease_burden_unc_and_anx_net_true_healthy %>% 
-  filter(osex == "Female") %>%
-  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
-  summarize(n(),
-            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
-            mean_UF_L = mean(UF_L_prop),
-            mean_UF_R = mean(UF_R_prop))
-  tibble_overall_summaries_females
-
-    tibble_overall_summaries_males <- 
-  df_disease_burden_unc_and_anx_net_true_healthy %>% 
-  filter(osex == "Male") %>%
-  group_by(oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar) %>%
-  summarize(n(),
-            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
-            mean_UF_L = mean(UF_L_prop),
-            mean_UF_R = mean(UF_R_prop))
-  tibble_overall_summaries_males
-
-  ### analyses
-
-```
-
-#### plots
-```{r}
-  #proportion injured over whole brain
-prop_injured_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=proportion_volume_lost_per_total_network_size_sum, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_by_anxiety_burden_true_healty_plot
-
-  #proportion injured over anxiety net
-prop_injured_anxiety_net_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_anxiety_net_by_anxiety_burden_true_healty_plot
-
-  #proportion injured over nonanxiety net
-prop_injured_nonanxiety_net_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_nonanxiety_net_by_anxiety_burden_true_healty_plot
-
-  #proportion injured over R Uncinate prop
-prop_injured_R_uncinate_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=UF_R_prop, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_R_uncinate_by_anxiety_burden_true_healty_plot
-
-  #proportion injured over L Uncinate prop
-prop_injured_L_uncinate_by_anxiety_burden_true_healty_plot <-  ggplot(df_disease_burden_unc_and_anx_net_true_healthy, aes(x=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar, y=UF_L_prop, fill=oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_L_uncinate_by_anxiety_burden_true_healty_plot
-
-prop_injured_by_anxiety_burden_and_sex_true_healty_plot <- ggboxplot(df_disease_burden_unc_and_anx_net_true_healthy, x = "oAnxiety.And.Dep.And.AnxietyMeds.TrueHealthy.GroupVar", y = "proportion_volume_lost_per_total_network_size_sum", color = "osex",
-          palette = c("#00AFBB", "#E7B800")) +
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_by_anxiety_burden_and_sex_true_healty_plot
-
-```
-
-##Collapse anxiety dx and antianxiety meds with those plus depression
-```{r group_anxietydx_meds_and_dep_comorbidity}
-
-#this collapses anxiety group + meds with those with anxiety group + meds + with/without depression
-
-df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
-  filter(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)
-
- tibble_overall_summaries <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
-  group_by(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  summarize(n(),
-            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
-            mean_UF_L = mean(UF_L_prop),
-            mean_UF_R = mean(UF_R_prop))
-tibble_overall_summaries
-
-tibble_overall_summaries_by_sex <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
-  group_by(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex) %>%
-  summarize(n(),
-            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
-            mean_UF_L = mean(UF_L_prop),
-            mean_UF_R = mean(UF_R_prop))
-  tibble_overall_summaries_by_sex
-
-  tibble_overall_summaries_females <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
-  filter(osex == "Female") %>%
-  group_by(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  summarize(n(),
-            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
-            mean_UF_L = mean(UF_L_prop),
-            mean_UF_R = mean(UF_R_prop))
-  tibble_overall_summaries_females
-
-    tibble_overall_summaries_males <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
-  filter(osex == "Male") %>%
-  group_by(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  summarize(n(),
-            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
-            mean_UF_L = mean(UF_L_prop),
-            mean_UF_R = mean(UF_R_prop))
-  tibble_overall_summaries_males
-
-  #mean disease
-  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
-  summary(anxietyGrouping_mean_disease_lm)
-
-  anxietyGrouping_by_sex_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
-  summary(anxietyGrouping_by_sex_mean_disease_lm)
-
-  #anxiety network
-  anxietyGrouping_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
-  summary(anxietyGrouping_anxiety_net_lm)
-
-  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
-  summary(anxietyGrouping_by_sex_anxiety_net_lm)
-
-  #UF R
-  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
-  summary(anxietyGrouping_UF_R_lm)
-
-  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
-  summary(anxietyGrouping_UF_R_by_sex_lm)
-
-  #UF L
-  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, data=df_demo_and_fascicles)
-  summary(anxietyGrouping_UF_L_lm)
-
-  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed*osex, data=df_demo_and_fascicles)
-  summary(anxietyGrouping_UF_L_by_sex_lm)
-
-  #burden of anxiety by network
-  #clean up data frame
-  df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
-  #filter(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed == c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>% 
-  #filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "Has.anxietydx")) %>%  #-> doesn't work
- # filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "On.Anxiolytics")) %>% #-> doesn't work
-  mutate(subject = as.factor(EMPI)) %>%
-#  mutate(Diagnosis = oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
-  mutate(Diagnosis = ifelse(oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  #mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
-  #mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
-  #mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
-  ##mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
-  #mutate(Benzo_status = as.factor(Benzo_status)) %>%
-  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
-  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
-  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol) %>% 
-  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
-  mutate(Network = as.factor(Network)) %>%
-  ungroup()
-
-## Means of separate groups:
-
-#t test, t, t = 37.378, df = 271, p-value < 2.2e-16, anxiety net: 0.4974984; nonanxiety net: 0.256347
-within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
-summary(within_vs_outside_anxiety_net_t)
-
-#t test, between diagnoses, NS, mean MS+ANXIETY = .40, MS-Anxiety = 0.37
-between_dx_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])
-summary(between_dx_t)
-
-#means
-
-#mean = 0.5381082
-mean_anxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
-mean_anxiety_dx_anx_net
-
-#mean = 0.2681277
-mean_anxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
-mean_anxiety_dx_nonanx_net
-
-#mean = 0.4762486
-mean_nonanxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
-mean_nonanxiety_dx_anx_net
-
-#mean = 0.2444919
-mean_nonanxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
-mean_nonanxiety_dx_nonanx_net
-
- #simple lmer, NetworkNonanxiety_network   -0.23176    0.01462 85.00000 -15.855   <2e-16 ***; NetworkNonanxiety_network:DiagnosisMS+Anxiety -0.03822    0.02241 85.00000  -1.705   0.0918 .
-disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
-
-#Network confit:NetworkNonanxiety_network -0.2496593 -0.23419230
-confint(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
-
-#do anova instead
-
-disease_within_vs_outside_anxiety_net_by_dx_groups_anova <- aov(proportion_affected ~ Network+Diagnosis + Network:Diagnosis, data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_dx_groups_anova)
-
-#do lm UF*Diagnosis
- #UF_R_vol -> NS
-disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis, data = df_empi_dx_network_proportions)
-summary(disease_UF_R_vol_lm)
-
- #UF_L_vol -> NS
-disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis, data = df_empi_dx_network_proportions)
-summary(disease_UF_L_vol_lm)
-
-```
-
-###plots
-```{r}
-prop_injured_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x= oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed , y=proportion_volume_lost_per_total_network_size_sum, fill= oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed )) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_by_anxiety_burden_collapsed_vars_plot
-
-  #proportion injured over anxiety net
-prop_injured_anxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_anxiety_net_by_anxiety_burden_collapsed_vars_plot
-
-  #proportion injured over nonanxiety net
-prop_injured_nonanxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_nonanxiety_net_by_anxiety_burden_collapsed_vars_plot
-
-  #proportion injured over R Uncinate prop
-prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_R_prop, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot
-
-  #proportion injured over L Uncinate prop
-prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_L_prop, fill=oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot
-
-prop_injured_by_anxiety_burden_and_sex_true_healty_collapsed_plot <- ggboxplot(df_disease_burden_unc_and_anx_net_collapsed_variables, x = "oAnxietydx.Meds.And.Dep.True.Healthy.Collapsed", y = "proportion_volume_lost_per_total_network_size_sum", color = "osex",
-          palette = c("#00AFBB", "#E7B800")) +
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_by_anxiety_burden_and_sex_true_healty_collapsed_plot
-```
-
 #COLLAPSE anxiety dx and antianxiety meds with those plus depression, and anxiety dx OR on anxiety meds into 1 group -->> THIS IS THE MONEY
+
+### Double check that people in each group are correct
+```{r gut_check}
+
+#want to make sure that people in healthy are NOT on anxiolytics or have dx, that people in the second group have one OR the other, and that people in the third group have BOTH
+
+#make data frame
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+   filter (anxiety_dose != 3)
+
+###true healthy
+num_people_in_healthy_with_0_for_Has.Anxiety_and_On.Anxiolytics <- length(which(df_demo_and_fascicles_no_unclass_anxiety_dose$On.Anxiolytics ==0 & df_demo_and_fascicles_no_unclass_anxiety_dose$Has.anxietydx ==0))
+print(paste0("num_people_in_healthy_with_0_for_Has.Anxiety_and_On.Anxiolytics-> ", num_people_in_healthy_with_0_for_Has.Anxiety_and_On.Anxiolytics, " and num in this group from groupVar -> ", sum(df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0)))
+
+### Anxiety dose = 1
+num_people_in_Anxiety_OR_On.Anxiolytics <- length(which((df_demo_and_fascicles_no_unclass_anxiety_dose$On.Anxiolytics ==1 | df_demo_and_fascicles_no_unclass_anxiety_dose$Has.anxietydx ==1) &
+(df_demo_and_fascicles_no_unclass_anxiety_dose$On.Anxiolytics != df_demo_and_fascicles_no_unclass_anxiety_dose$Has.anxietydx)))
+
+print(paste0("num_people_in_Anxiety_OR_On.Anxiolytics-> ", num_people_in_Anxiety_OR_On.Anxiolytics, " and num in this group from groupVar -> ", sum(df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1)))
+
+#severe anxiety
+num_people_in_Anxiety_AND_Anxiolytics <- length(which(df_demo_and_fascicles_no_unclass_anxiety_dose$On.Anxiolytics ==1 & df_demo_and_fascicles_no_unclass_anxiety_dose$Has.anxietydx ==1))
+print(paste0("num_people_in_Anxiety_AND_Anxiolytics-> ", num_people_in_Anxiety_AND_Anxiolytics, " and num in this group from groupVar -> ", sum(df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2)))
+
+print(paste0("total n -> ",num_people_in_healthy_with_0_for_Has.Anxiety_and_On.Anxiolytics + num_people_in_Anxiety_OR_On.Anxiolytics + num_people_in_Anxiety_AND_Anxiolytics, " and row # in data frame -> ", dim(df_demo_and_fascicles_no_unclass_anxiety_dose)[1]))
+
+```
 ### Overlap with depression group
@@
 
+print(paste0("Percent overlap with depression group -> ", round(sum(tibble_overall_counts$num_in_dep_group)/sum(tibble_overall_counts$`n()`),2)))
 ```
@@
 #demo
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
-
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[((df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
+make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
+
+make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[((df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
 
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>% 
-  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex, anxiety_dose)
+  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)
 
@@
 
-  df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>% filter (anxiety_dose != 3) #3 is unclassified, 0 is no anxiety, 1 is diagnosis or on meds, 2 is diagnosis AND on meds
-
-  #mean disease by anxiety dose: anxiety_dose    0.0347504  0.0149813   2.320  0.02091 *  
+  df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>% filter (anxiety_dose != -1) #-1 is unclassified, 0 is no anxiety, 1 is diagnosis or on meds, 2 is diagnosis AND on meds, -> n = 371
+
+  #mean disease by anxiety dose: anxiety_dose    0.047452   0.019130   2.480  0.01357 *  
   anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  ### gam instead, anxiety_dose  0.03606    0.01493   2.416   0.0162 *
-    anxietyGrouping_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  ### gam instead, anxiety_dose  0.04846    0.01901   2.549   0.0112 * 
+    anxietyGrouping_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_mean_disease_gam)
 
-  #mean disease with sex in model : anxiety_dose         anxiety_dose     0.0356677  0.0150093   2.376  0.01800 *  
+  #mean disease with sex in model : anxiety_dose     0.0486229  0.0191648   2.537  0.01159 *  
   anxietyGrouping_by_sex_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #gam: anxiety_dose  0.03692    0.01496   2.468    0.014 *  
-      anxietyGrouping_by_sex_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + osex+ s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  #gam: anxiety_dose  0.04955    0.01905   2.601  0.00966 **  
+      anxietyGrouping_by_sex_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + osex+ s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
       summary(anxietyGrouping_by_sex_mean_disease_gam)
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter (anxiety_dose != 3)
+  filter (anxiety_dose != -1)
 
@@
 
-  ###  anxiety_dose    0.036474   0.017586   2.074 0.038768 *  ; PAT_AGE_AT_EXAM 0.004132   0.001058   3.905 0.000112 ***
+  ###  anxiety_dose   anxiety_dose    0.051190   0.022452   2.280   0.0232 *  
   anxietyGrouping_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #gam, anxiety_dose  0.03735    0.01760   2.122   0.0345 * 
+  #gam, anxiety_dose  0.05297    0.02248   2.357    0.019 *  
    anxietyGrouping_anxiety_net_gam<- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.053407   0.021365   2.500   0.0129 *  , no intx
+  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.066699   0.026574   2.510   0.0125 *  , no intx
   anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #gam, anxiety_dose         0.05395    0.02133   2.529   0.0119 *  
-  anxietyGrouping_by_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  #gam, anxiety_dose         0.06708    0.02648   2.533   0.0117 *   
+  anxietyGrouping_by_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_by_sex_anxiety_net_gam)
 
-  #volume lost in anxiety net by anxiety dose + sex + PAT_AGE_AT_EXAM: anxiety_dose     0.037282   0.017629   2.115   0.0351 *
+  #volume lost in anxiety net by anxiety dose + sex + PAT_AGE_AT_EXAM: anxiety_dose     0.052228   0.022506   2.321   0.0209 *  
   anxietyGrouping_cov_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #gam, anxiety_dose  0.03810    0.01765   2.159   0.0315 * 
-   anxietyGrouping_cov_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  #gam, anxiety_dose  0.05256    0.02244   2.342   0.0197 *  
+   anxietyGrouping_cov_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_cov_sex_anxiety_net_gam)
@@
 
-  ###  anxiety_dose: anxiety_dose    0.0334038  0.0135143   2.472   0.0139 * 
+  ###  anxiety_dose: anxiety_dose    0.0445315  0.0172621   2.580   0.0103 * 
   anxietyGrouping_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #gam, anxiety_dose  , anxiety_dose  0.03505    0.01340   2.616  0.00927 ** 
+  #gam, anxiety_dose  , anxiety_dose  0.04741    0.01712   2.769   0.0059 ** 
    anxietyGrouping_nonanxiety_net_gam<- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.0459425  0.0164036   2.801  0.00537 ** 
+  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.059732   0.020184   2.959  0.00328 ** 
   anxietyGrouping_by_sex_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose*osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #volume lost in anxiety net by anxiety dose + sex + PAT_AGE_AT_EXAM: anxiety_dose     0.0344065  0.0135309   2.543   0.0114 *  
+  #volume lost in anxiety net by anxiety dose + sex + PAT_AGE_AT_EXAM: anxiety_dose     0.0458062  0.0172824   2.650  0.00839 ** 
   anxietyGrouping_cov_sex_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #gam, anxiety_dose - anxiety_dose  0.03600    0.01342   2.682  0.00764 ** 
+  #gam, anxiety_dose - anxiety_dose  0.04861    0.01714   2.836  0.00483 ** 
    anxietyGrouping_cov_sex_nonanxiety_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_cov_sex_nonanxiety_net_gam)
-
-```
-
-###Check for polynomial relationships 
-```{r polynomial_relationships}
- #Not finding them w healthy, anxietydx OR meds, anxiety AND meds
-
- #check for polynomial relationship
-#define group
-df_demo_and_fascicles_no_unclass_anxiety_dose_factor <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter (anxiety_dose != 3) %>% 
-  mutate(anxiety_dose = as.factor(anxiety_dose))
-
-contrasts(df_demo_and_fascicles_no_unclass_anxiety_dose_factor$anxiety_dose) <- contr.poly(3)
-
-# Perform Anova across all regions, anxiety_dose      2  0.195  0.0975   2.508  0.0829 .  
-anova_result_contrasts_whole_brain <- aov(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
-summary(anova_result_contrasts_whole_brain)
-
-# Perform ANOVA again with contrasts anxiety net, anxiety_dose      2  0.216  0.1079   2.012 0.135161    
-anova_result_contrasts_anxiety_net <- aov(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
-summary(anova_result_contrasts_anxiety_net)
-
-# Nonanxiety Net - anxiety_dose      2  0.180  0.0898   2.842   0.0596 . 
-anova_result_contrasts_nonanxiety_net <- aov(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
-summary(anova_result_contrasts_nonanxiety_net)
-
-#UF_R_vol, anxiety_dose      2 2.219e+07  11094236   1.811    0.165
-
-anova_result_contrasts_UF_R_net <- aov(UF_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
-summary(anova_result_contrasts_UF_R_net)
-
-#UF_L_vol, anxiety_dose      2 6.053e+06  3026730   0.988    0.373  
-anova_result_contrasts_UF_L_net <- aov(UF_L_vol ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
-summary(anova_result_contrasts_UF_L_net)
 
@@
   dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, volume_of_mimosa_lesions) %>%
-  ungroup()
+  ungroup() #n=122
 
@@
 
-#lm lesion volumes; DiagnosisMS+Anxiety  6310.99    2143.87   2.944 0.003694 ** 
+#lm lesion volumes; DiagnosisMS+Anxiety  9210.15    2966.03   3.105 0.002381 ** 
 volume_of_mimosa_lesions_lm <- lm(volume_of_mimosa_lesions ~ Diagnosis + osex + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
@@
 
-#gam lesion volumes; DiagnosisMS+Anxiety   6973.5     2014.7   3.461 0.000681 ***
+#gam lesion volumes; DiagnosisMS+Anxiety   8765.2     2748.2   3.189  0.00183 ** 
 volume_of_mimosa_lesions_gam <- gam(volume_of_mimosa_lesions ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter (anxiety_dose != 3)
-
-#dose; anxiety_dose     3028.07    1014.45   2.985 0.003026 **
+  filter (anxiety_dose != -1) #n=371
+
+#dose; anxiety_dose     3562.72    1299.08   2.743 0.006396 *
 
@@
 
- #bilat anxiety dose + sex + age: anxiety_dose   3304.7      985.8   3.352 0.000886 ***
+ #bilat anxiety dose + sex + age: anxiety_dose     3995       1263   3.164  0.00169 **
 
@@
 
-### Results: LM Mean UF_R & L, age, sex cov, DiagnosisMS+Anxiety   621.95     276.11   2.252   0.0256 * 
+#### Fx = F gives better results than FX = T
+
+### Results:  
 #define group
@@
   dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol, mean_UF_vol) %>%
-  ungroup()
+  ungroup() #n=122
 
 #do lm UF*Diagnosis
- #UF_R_vol -> DiagnosisMS+Anxiety   793.14     361.94   2.191   0.0298 *   
+ #UF_R_vol -> DiagnosisMS+Anxiety  1019.03     535.20   1.904   0.0593 .  
 disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + osex + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
@@
 
- #UF_L_vol ->DiagnosisMS+Anxiety   450.75     261.20   1.726   0.0862 .    
+ #UF_L_vol ->DiagnosisMS+Anxiety   729.21     389.80   1.871  0.06386 .    
 disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
@@
 
-#bilat: DiagnosisMS+Anxiety   621.95     276.11   2.252   0.0256 *  
+#bilat: DiagnosisMS+Anxiety   874.12     412.30   2.120   0.0361 * 
 disease_mean_UF_vol_lm <- lm(mean_UF_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
@@
 
-#gam
-#UF_R_vol -> DiagnosisMS+Anxiety   795.60     366.58   2.170   0.0314 *   
-disease_UF_R_vol_gam <- gam(UF_R_vol ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+#gam, Fx= F
+#UF_R_vol -> DiagnosisMS+Anxiety  1019.03     535.20   1.904   0.0593 .   
+disease_UF_R_vol_gam <- gam(UF_R_vol ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = df_empi_dx_network_proportions)
 summary(disease_UF_R_vol_gam)
 
- #UF_L_vol -> DiagnosisMS+Anxiety   420.24     262.19   1.603    0.111   
-disease_UF_L_vol_gam <- gam(UF_L_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+ #UF_L_vol -> DiagnosisMS+Anxiety    675.7      381.3   1.772    0.079 .  
+disease_UF_L_vol_gam <- gam(UF_L_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = df_empi_dx_network_proportions)
 summary(disease_UF_L_vol_gam)
 
-#bilateral UF: DiagnosisMS+Anxiety   607.92     279.34   2.176   0.0309 *  
-disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+#bilateral UF: DiagnosisMS+Anxiety    866.7      411.9   2.104   0.0375 *  
+disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = df_empi_dx_network_proportions)
 summary(disease_mean_UF_vol_gam)
 
-#Fornix - Right side but not left
- #F_R_vol -> DiagnosisMS+Anxiety   860.50     368.16   2.337   0.0205 * 
-#disease_F_R_vol_lm <- lm(F_R_vol ~ Diagnosis + osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-#summary(disease_F_R_vol_lm)
-
- #F_L_vol -> DiagnosisMS+Anxiety  329.724    181.609   1.816   0.0711 . 
-#disease_F_L_vol_lm <- lm(F_L_vol ~ Diagnosis + osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-#summary(disease_F_L_vol_lm)
-## net by sex 
 ```
@@
 
+#### Fx = F gives better results than FX = T
 #results: Anxiety dose related to UF_R when covarying for linear effects of age and sex, just barely
-# Additionally - taking the mean of both UF and UR, LM for bilat anxiety dose + sex + age: anxiety_dose most sig P= 0.0367 *
+# Additionally - taking the mean of both UF and UR, LM for bilat anxiety dose + sex + age: anxiety_dose most sig P= 0.0367 *  (fx=T)
 
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter (anxiety_dose != 3)
+  filter (anxiety_dose != -1) #n=371
 
@@
 
-  #R anxiety dose + age ; anxiety_dose      369.72     187.93   1.967   0.0499 *  ***********
+  #R anxiety dose + age ; anxiety_dose      430.81     240.44   1.792    0.074 .   
   anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-   #R *anxiety dose + osex + age anxiety_dose          anxiety_dose      377.35     188.43   2.003    0.046 *********   
+   #R *anxiety dose + osex + age anxiety_dose:       anxiety_dose      440.30     241.07   1.826   0.0686 .  
   anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-   #UF L - anxiety_dose + age    222.193    133.138   1.669    0.096 .  
+   #UF L - anxiety_dose + age:    anxiety_dose     337.695    169.917   1.987   0.0476 *  
   anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-   #UF_L anxiety_dose + sex + age:         anxiety_dose     232.210    133.294   1.742   0.0823 .  
+   #UF_L anxiety_dose + sex + age:         anxiety_dose     350.563    170.099   2.061    0.040 *    
   anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #bilat anxiety dose + age: anxiety_dose     295.957    145.116   2.039   0.0421 *  
+  #bilat anxiety dose + age: anxiety_dose     anxiety_dose     384.254    185.461   2.072    0.039 *
   anxietyGrouping_mean_UF_lm <- lm(mean_UF_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #bilat anxiety dose + sex + age: anxiety_dose      304.78     145.39   2.096   0.0367 *  
+  #bilat anxiety dose + sex + age: anxiety_dose     395.432    185.804   2.128    0.034 *  
   anxietyGrouping_mean_UF_by_sex_lm <- lm(mean_UF_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-#gam
-
-  #UF _ R  anxiety_dose + age   357.0      188.8   1.891   0.0594 .
-  anxietyGrouping_UF_R_gam <- gam(UF_R_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+#gam, Fx=F - k = 4 and 5 give the same stats
+
+  #UF _ R  anxiety_dose    430.3      240.4    1.79   0.0742 .  
+  anxietyGrouping_UF_R_gam <- gam(UF_R_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_UF_R_gam)
 
- #R anxiety dose + sex + age: anxiety_dose    364.2      189.3   1.924   0.0552 .
-
-    anxietyGrouping_UF_R_by_sex_gam <- gam(UF_R_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+ #R anxiety dose + sex + age: anxiety_dose    439.8      241.0   1.825   0.0689 .
+
+    anxietyGrouping_UF_R_by_sex_gam <- gam(UF_R_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_UF_R_by_sex_gam)
 
-   #UF_L, anxiety_dose + age    220.1      133.7   1.646    0.101    
-  anxietyGrouping_UF_L_gam <- gam(UF_L_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+   #UF_L, anxiety_dose + age: anxiety_dose    337.8      169.8    1.99   0.0473 *  
+  anxietyGrouping_UF_L_gam <- gam(UF_L_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_UF_L_gam)
 
-   #UF_L anxiety_dose + sex + age    229.9      133.9   1.717   0.0868 .  
-  anxietyGrouping_UF_L_by_sex_gam <- gam(UF_L_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+   #UF_L anxiety_dose + sex + age: anxiety_dose    350.5      170.0   2.062   0.0399 *    
+  anxietyGrouping_UF_L_by_sex_gam <- gam(UF_L_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_UF_L_by_sex_gam)
@@
 
-  #bilat  anxiety_dose + age: anxiety_dose    288.5      145.7    1.98   0.0484 *  
-  anxietyGrouping_mean_UF_gam <- gam(mean_UF_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  #bilat  anxiety_dose + age: anxiety_dose    383.7      185.3   2.071   0.0391 *  
+  anxietyGrouping_mean_UF_gam <- gam(mean_UF_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_mean_UF_gam)
 
- #bilat anxiety dose + sex + age: anxiety_dose    297.0      146.0   2.034   0.0426 *
-
-    anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+ #bilat anxiety dose + sex + age: anxiety_dose    394.7      185.7   2.126   0.0342 *
+
+    anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_mean_UF_by_sex_gam)
@@
   #laterality 
-  #overall - t = -11.597, df = 1322.2, p-value < 2.2e-16
+  #overall - t = -8.1948, df = 660.22, p-value = 1.304e-15
   right_vs_left_uncinate <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol, df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol)
@@
 
-  #healthy - t = -6.3298, df = 347.5, p-value = 7.577e-10
+  #healthy - t = -4.4646, df = 172.88, p-value = 1.443e-05
    right_vs_left_uncinate_healthy <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0])
@@
 
-  #anxietydx or meds - t = -7.7742, df = 705.18, p-value = 2.694e-14
+  #anxietydx or meds -t = -6.517, df = 441.79, p-value = 1.96e-10
   right_vs_left_uncinate_anxiety_or_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1])
@@
 
-  #anxious+meds, t = -5.9638, df = 266.42, p-value = 7.804e-09
+  #anxious+meds,t = -2.2382, df = 40.97, p-value = 0.0307
    right_vs_left_uncinate_anxiety_and_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2])
@@
 ### Fornix by Anxiety Dose
-```{r uncinateByAnxietyDose}
+```{r fornixByAnxietyDose}
 
@@
   mutate(Network = as.factor(Network)) %>%
-  ungroup()
+  ungroup() #n=244 (122 x 2)
 
@@
 
-#NetworkNonanxiety_network                      -0.246157   0.009900 173.000001 -24.864  < 2e-16 ***
-#DiagnosisMS+Anxiety                             0.075874   0.030315 194.726132   2.503 0.013142 *
+#NetworkNonanxiety_network                      -0.245959   0.009028 120.000000 -27.245  < 2e-16 ***
+#DiagnosisMS+Anxiety                             0.143579   0.045316 132.184401   3.168  0.00190 **
 
@@
 #Network confit:
-#NetworkNonanxiety_network                     -0.265556308 -0.226758160
-#DiagnosisMS+Anxiety                            0.016671783  0.135076698
 confint(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
@@
 #simple lmer
-#NetworkNonanxiety_network         -0.248004   0.008994 173.000001 -27.573  < 2e-16 ***
+#NetworkNonanxiety_network         -0.247316   0.009473 120.000000 -26.107  < 2e-16 ***
   disease_within_vs_outside_anxiety_net_by_sex_diff_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
@@
 ## diagnosis by sex 
- #simple lmer, DiagnosisMS+Anxiety         0.102015   0.030998   3.291   0.0011 ** 
+ #simple lmer, DiagnosisMS+Anxiety         0.148038   0.045605   3.246 0.001337 ** 
 disease_diagnosis_by_sex_diff_lm <- lm(proportion_affected ~ Diagnosis*osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
@@
 #network * diagnosis + sex
-#NetworkNonanxiety_network                      -0.246157   0.009900 173.000001 -24.864  < 2e-16 ***
-#DiagnosisMS+Anxiety                             0.076902   0.030464 193.366257   2.524 0.012394 * 
+#NetworkNonanxiety_network                      -0.245959   0.009028 120.000001 -27.245  < 2e-16 ***
+#DiagnosisMS+Anxiety                             0.143161   0.045499 130.966650   3.146  0.00205 ** 
 disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer <- lmer(proportion_affected ~ Network*Diagnosis + osex + (1|subject)+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
@@
 
-#Network confit:NetworkNonanxiety_network -0.2496593 -0.23419230
+#Confit
 confint(disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer)
@@
 ```{r dxEffSizeOverlapwithAnxietyNet}
+
+#tried looking at prop instead of volume - opposite effects of depression. Higher effect sizes -> lower overlap with anxiety net
+
 #define group
@@
   filter(anxiousAndMeds_or_healthy %in% c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>%
-  mutate(anxiousAndMeds_or_healthy = factor(anxiousAndMeds_or_healthy, levels=c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
+    mutate(anxiousAndMeds_or_healthy = ordered(anxiousAndMeds_or_healthy)) #n=122
+
+#  mutate(anxiousAndMeds_or_healthy = factor(anxiousAndMeds_or_healthy, levels=c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
 
@@
 #remove values that have no overlap
-#df_fascicle_anxiety_mask_volume_overlap_effsize_value <- df_fascicle_anxiety_mask_volume_overlap_effsize_value
+df_fascicle_anxiety_mask_volume_overlap_effsize_value <- df_fascicle_anxiety_mask_volume_overlap_effsize_value %>% filter(volume_in_anxiety_mask > 0)
 
@@
 #statistic,
+
 anxiety_overlap_x_anxiety_vs_healthy_vol_effsize <- lm(anxiety_vs_healthy_effsize ~ volume_in_anxiety_mask, data=df_fascicle_anxiety_mask_volume_overlap_effsize_value )
@@
 
-#X-squared (Pearson's) X-squared = 0.19886, df = 2, p-value = 0.9054
+#X-squared (Pearson's) X-squared = 0.23427, df = 2, p-value = 0.8895
 chisq_anxiety_dose <- chisq.test(df_2x3_anxiety_score_by_total_people_per_diagnosis)
@@
 
-#just healthy and super anxious/sick, X-squared = 0.056046, df = 1, p-value = 0.8129
+#just healthy and super anxious/sick, X-squared = 0, df = 1, p-value = 1
 num_w_anxiety_female_just_healthy_and_sick <- as.numeric(c(anxiety_female_0, anxiety_female_2))
@@
 ### Age*Disease
-```{r diagnosisXage}
+
+#### Anxiety diagnosis
+```{r anxiety_dx_x_age}
+
+#purpose of this analysis is to evaluate the relationship between disease (cross sectional) by diagnosis as well as by anxiety dose
+#hypothesize that anxiety vs nonanxiety will have worse disease overall, and that this may be related to anxiety dose
+#start by defining new variables and a new data frame that contains anxiety dose (as factor and as ordinal), as well as diagnosis (no anxiety vs severe anxiety)
+
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) %>%
+  mutate(anxiety_dose_factor = ordered(anxiety_dose)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) #n=371
+
+### diagnosis by age interaction?
+#overall - NS for diagnosis
+diagnosis_by_age <- lm(proportion_volume_lost_per_total_network_size_sum ~ Diagnosis*PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age)
+
+#gam diagnosis - SPLINE SIGNIFICANT
+#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.579  1.927 5.027  0.0138 * 
+#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.988  2.379 5.205  0.0033 **
+diagnosis_by_age_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_gam)
+summary(diagnosis_by_age_gam)$s.table
+
+#plot proportion_volume_lost_per_total_network_size_sum
+plot_smooths_proportion_volume_lost_per_total_network_size_sum <- plot_smooths(
+  model = diagnosis_by_age_gam,
+  series = PAT_AGE_AT_EXAM,
+  comparison = Diagnosis
+) +
+  theme(legend.position = "top")
+plot_smooths_proportion_volume_lost_per_total_network_size_sum
+
+####. within/outside anxiety network #######
+#diagnosis
+#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.05  1.099 5.539 0.01921 * 
+#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.74  2.115 5.257 0.00473 **
+diagnosis_by_age_anx_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_anx_net_gam)
+summary(diagnosis_by_age_anx_net_gam)$s.table
+#plot(diagnosis_by_age_anx_net_gam)
+
+#gam plot diagnosis_by_age_anx_net_gam_factor
+
+plot_smooths_diagnosis_by_age_anx_net_gam_factor <- plot_smooths(
+  model = diagnosis_by_age_anx_net_gam,
+  series = PAT_AGE_AT_EXAM,
+  comparison = Diagnosis
+) +
+  theme(legend.position = "top")
+plot_smooths_diagnosis_by_age_anx_net_gam_factor
+
+##### #outside each network
+#diagnosis: MS+Anxiety p=0.0432
+#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.975  2.373 4.660 0.00556 **
+#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 2.157  2.543 5.059 0.00282 **
+diagnosis_by_age_nonanx_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_nonanx_net_gam)
+summary(diagnosis_by_age_nonanx_net_gam)$s.table
+#plot(diagnosis_by_age_nonanx_net_gam)
+
+#gam plot diagnosis_by_age_nonanx_net_gam_factor
+
+plot_smooths_diagnosis_by_age_nonanx_net_gam_factor <- plot_smooths(
+  model = diagnosis_by_age_nonanx_net_gam,
+  series = PAT_AGE_AT_EXAM,
+  comparison = Diagnosis
+) +
+  theme(legend.position = "top")
+plot_smooths_diagnosis_by_age_nonanx_net_gam_factor
+
+### uncinate right
+#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.001  1.003 24.11 2.01e-06 ***
+#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.059  1.116 15.01 0.000105 ***
+
+diagnosis_by_age_UF_R_gam <- gam(UF_R_vol ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_UF_R_gam)
+summary(diagnosis_by_age_UF_R_gam)$s.table
+#plot(diagnosis_by_age_UF_R_gam)
+
+#gam UF_R plot
+
+plot_smooths_anxiety_diagnosis_by_age_UF_R <- plot_smooths(
+  model = diagnosis_by_age_UF_R_gam,
+  series = PAT_AGE_AT_EXAM,
+  comparison = Diagnosis
+) +
+  theme(legend.position = "top")
+plot_smooths_anxiety_diagnosis_by_age_UF_R
+
+#uncinate left
+#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.930  2.328  7.546 0.00046 ***
+#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.001  1.002 10.868 0.00107 **
+
+diagnosis_by_age_UF_L_gam <- gam(UF_L_vol ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_UF_L_gam)
+summary(diagnosis_by_age_UF_L_gam)$s.table
+#plot(diagnosis_by_age_UF_L_gam)
+
+#gam UF_L plot
+
+plot_smooths_anxiety_diagnosis_by_age_UF_L <- plot_smooths(
+  model = diagnosis_by_age_UF_L_gam,
+  series = PAT_AGE_AT_EXAM,
+  comparison = Diagnosis
+) +
+  theme(legend.position = "top")
+plot_smooths_anxiety_diagnosis_by_age_UF_L
+
+#uncinate mean
+#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.006  1.013 23.95 2.10e-06 ***
+#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.000  1.000 17.02 4.59e-05 ***
+
+diagnosis_by_age_mean_UF_gam <- gam(mean_UF_vol ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_mean_UF_gam)
+summary(diagnosis_by_age_mean_UF_gam)$s.table
+#plot(diagnosis_by_age_UF_L_gam)
+
+#gam UF mean plot
+
+plot_smooths_anxiety_diagnosis_by_age_mean_UF_vol <- plot_smooths(
+  model = diagnosis_by_age_mean_UF_gam,
+  series = PAT_AGE_AT_EXAM,
+  comparison = Diagnosis
+) +
+  theme(legend.position = "top")
+plot_smooths_anxiety_diagnosis_by_age_mean_UF_vol
+
+## Sex diff trajectories by age
+#overall - NS
+sex_by_age <- lm(proportion_volume_lost_per_total_network_size_sum ~ osex*PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(sex_by_age)
+
+```
+
+#### Anxiety DOSE -> NEED TO UPDATE stats in text
+```{r anxietydosexage}
+
+#purpose of this analysis is to evaluate the relationship between disease (cross sectional) by diagnosis as well as by anxiety dose
+#hypothesize that anxiety vs nonanxiety will have worse disease overall, and that this may be related to anxiety dose
+#start by defining new variables and a new data frame that contains anxiety dose (as factor and as ordinal), as well as diagnosis (no anxiety vs severe anxiety)
 
@@
   filter(anxiety_dose != 3) %>%
-  mutate(anxiety_dose_factor = ordered(anxiety_dose))
+  mutate(anxiety_dose_factor = ordered(anxiety_dose)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis))
 
@@
 #gam dose
-diagnosis_by_age_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_gam)
@@
 #gam factor - there is a linear dose effect per network size sum, as well as a sig age by anxiety relationship, but only in sick people
-diagnosis_by_age_gam_factor <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_gam_factor <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_gam_factor)
@@
 #dose
-diagnosis_by_age_anx_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_anx_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_anx_net_gam)
@@
 #factor
-diagnosis_by_age_anx_net_gam_factor <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_anx_net_gam_factor <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_anx_net_gam_factor)
@@
 ##dose
-diagnosis_by_age_nonanx_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_nonanx_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_nonanx_net_gam)
@@
 
-diagnosis_by_age_nonanx_net_gam_factor <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_nonanx_net_gam_factor <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_nonanx_net_gam_factor)
@@
 #dose
-diagnosis_by_age_UF_R_gam <- gam(UF_R_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_UF_R_gam <- gam(UF_R_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_UF_R_gam)
@@
 #factor
-diagnosis_by_age_UF_R_gam_factor <- gam(UF_R_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_UF_R_gam_factor <- gam(UF_R_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_UF_R_gam_factor)
@@
 #dose
-diagnosis_by_age_UF_L_gam <- gam(UF_L_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_UF_L_gam <- gam(UF_L_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_UF_L_gam)
@@
 #factor
-diagnosis_by_age_UF_L_gam_factor <- gam(UF_L_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+diagnosis_by_age_UF_L_gam_factor <- gam(UF_L_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
 summary(diagnosis_by_age_UF_L_gam_factor)
@@
 
+#uncinate mean
+#dose
+
+diagnosis_by_age_mean_UF_gam <- gam(mean_UF_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_mean_UF_gam)
+summary(diagnosis_by_age_mean_UF_gam)$s.table
+
+#factor
+diagnosis_by_age_mean_UF_gam_factor <- gam(mean_UF_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
+summary(diagnosis_by_age_mean_UF_gam_factor)
+summary(diagnosis_by_age_mean_UF_gam_factor)$s.table
+#plot(diagnosis_by_age_UF_L_gam_factor)
+
+#gam mean
+
+plot_smooths_anxiety_dose_by_age_mean_UF_factor <- plot_smooths(
+  model = diagnosis_by_age_mean_UF_gam_factor,
+  series = PAT_AGE_AT_EXAM,
+  comparison = anxiety_dose_factor
+) +
+  theme(legend.position = "top")
+plot_smooths_anxiety_dose_by_age_mean_UF_factor
+
 ## Sex diff trajectories by age
@@
 #### Parametric all fascicles
-```{r individual_fascicle_disease_healthy_vs_super_sick}
+```{r individual_fascicle_disease_anxiety_dose}
+
+### 3 meet FDR - C_FPH_R_prop	0.037			C_FP_R_prop	0.042			DRTT_R_prop	0.042
 df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
@@
 #### Parametric anxiety net fascicles
-```{r individual_fascicle_disease_healthy_vs_super_sick}
+```{r indiv_fascicle_anxiety_net_anxiety_dose}
+
+## 3 meet FDR - EMC_L_prop	0.0320914948			C_PHP_R_prop	0.0265819790			C_FPH_R_prop	0.0004861282	
 df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != 3) %>%
+  filter(anxiety_dose != -1) %>%
   mutate(anxiety_dose_factor = ordered(anxiety_dose))
@@
 #### Parametric nonanxiety net fascicles
-```{r individual_fascicle_disease_healthy_vs_super_sick}
+```{r nonanxiety_net_anxiety_dose}
+
+# 2 FDR corr sig: C_FP_R_prop	0.048			DRTT_R_prop	0.048
+
 df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != 3) %>%
+  filter(anxiety_dose != -1) %>%
   mutate(anxiety_dose_factor = ordered(anxiety_dose))
@@
 ```{r}
+#n = 371
 prop_injured_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x= oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed , y=proportion_volume_lost_per_total_network_size_sum, fill= oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed )) +
@@
   #proportion injured over R Uncinate prop
+#n=371
 prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_R_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
@@
 prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
+```
+
+##### Plots C_FPH_R_prop	0.037			C_FP_R_prop	0.042			DRTT_R_prop	0.042
+
+```{r plots_areas_that_FDR_correct}
+
+#n=371
+
+df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>% 
+  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, C_FPH_R_prop, C_FP_R_prop,DRTT_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)
+
+ #proportion injured over C_FPH_R_prop
+prop_injured_C_FPH_R_prop_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=C_FPH_R_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_C_FPH_R_prop_by_anxiety_burden_collapsed_vars_plot
+
+ #proportion injured over C_FPH_R_prop - geom_bar
+means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$C_FPH_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$C_FPH_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$C_FPH_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
+
+df_C_FPH_R_prop_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
+
+names(df_C_FPH_R_prop_mean_by_anxiety_dose) <- c("C_FPH_R_prop", "Anxiety_dose")
+
+df_C_FPH_R_prop_mean_by_anxiety_dose <- df_C_FPH_R_prop_mean_by_anxiety_dose %>%
+  mutate(mean_C_FPH_R_prop = as.numeric(C_FPH_R_prop)) %>%
+  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
+
+prop_injured_C_FPH_R_prop_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_C_FPH_R_prop_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_C_FPH_R_prop, fill=Anxiety_dose)) +
+  geom_bar(stat="identity") +  
+  ylim(0,1)+
+#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
+        panel.background = element_rect(colour = "white", fill = "white"))
+prop_injured_C_FPH_R_prop_by_anxiety_burden_collapsed_vars_plot_bar
+
+ #proportion injured over C_FP_R_prop
+prop_injured_C_FP_R_prop_prop_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=C_FP_R_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_C_FP_R_prop_prop_by_anxiety_burden_collapsed_vars_plot
+
+ #proportion injured over C_FP_R_prop - geom_bar
+means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$C_FP_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$C_FP_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$C_FP_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
+
+df_C_FP_R_prop_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
+
+names(df_C_FP_R_prop_mean_by_anxiety_dose) <- c("C_FP_R_prop", "Anxiety_dose")
+
+df_C_FP_R_prop_mean_by_anxiety_dose <- df_C_FP_R_prop_mean_by_anxiety_dose %>%
+  mutate(mean_C_FP_R_prop = as.numeric(C_FP_R_prop)) %>%
+  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
+
+prop_injured_C_FP_R_prop_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_C_FP_R_prop_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_C_FP_R_prop, fill=Anxiety_dose)) +
+  geom_bar(stat="identity") +  
+  ylim(0,1)+
+#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
+        panel.background = element_rect(colour = "white", fill = "white"))
+prop_injured_C_FP_R_prop_by_anxiety_burden_collapsed_vars_plot_bar
+
+ #proportion injured over DRTT_R_prop
+prop_injured_DRTT_R_prop_prop_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=DRTT_R_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_DRTT_R_prop_prop_by_anxiety_burden_collapsed_vars_plot
+
+ #proportion injured over DRTT_R_prop - geom_bar
+means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$DRTT_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$DRTT_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$DRTT_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
+
+df_DRTT_R_prop_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
+
+names(df_DRTT_R_prop_mean_by_anxiety_dose) <- c("DRTT_R_prop", "Anxiety_dose")
+
+df_DRTT_R_prop_mean_by_anxiety_dose <- df_DRTT_R_prop_mean_by_anxiety_dose %>%
+  mutate(mean_DRTT_R_prop = as.numeric(DRTT_R_prop)) %>%
+  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
+
+prop_injured_DRTT_R_prop_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_DRTT_R_prop_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_DRTT_R_prop, fill=Anxiety_dose)) +
+  geom_bar(stat="identity") +  
+  ylim(0,1)+
+#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
+        panel.background = element_rect(colour = "white", fill = "white"))
+prop_injured_C_FP_R_prop_by_anxiety_burden_collapsed_vars_plot_bar
+
 ```
@@
 ```
-
-## Anxiety net defined as (25 vol x 25 prop anxiety net) -> no better, don't use
-### Anxiety and Non anxiety net by dose 
-```{r anxiety_and_nonanxiety_net_by_dose}
-
-### Will be using gam + s(age) and osex because this was giving me most robust findings previously.
-### I know that we already have an effect in across whole brain. Now i want to check if it differs within new anxiety net vs outside
-
-df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>% 
-  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_fascicle_volume_lost_top_25_vol_x_top_25_prop, proportion_fascicle_vol_lost_NOT_top_25_vol_x_top_25_prop, UF_L_prop, UF_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex, anxiety_dose, PAT_AGE_AT_EXAM)
-
-## gam, check original finding still there, anxiety_dose  0.03692    0.01496   2.468    0.014 *  
-   anxietyGrouping_cov_sex_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_disease_burden_unc_and_anx_net_collapsed_variables)
-  summary(anxietyGrouping_cov_sex_gam)
-
-  #gam, anxiety_dose, anxiety net, anxiety_dose  0.027830   0.015810   1.760   0.0792 . 
-   anxietyGrouping_cov_sex_anxiety_net_gam <- gam(proportion_fascicle_volume_lost_top_25_vol_x_top_25_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_disease_burden_unc_and_anx_net_collapsed_variables)
-  summary(anxietyGrouping_cov_sex_anxiety_net_gam)
-
-    #gam, anxiety_dose, non anxiety net; anxiety_dose  0.03814    0.01500   2.543   0.0114 *  
-   anxietyGrouping_cov_sex_nonanxiety_net_gam <- gam(proportion_fascicle_vol_lost_NOT_top_25_vol_x_top_25_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_disease_burden_unc_and_anx_net_collapsed_variables)
-  summary(anxietyGrouping_cov_sex_nonanxiety_net_gam)
-
-```
-
-### Network*Diagnosis 
-```{r networkxdiagnosis_groups_collapse}
-
-## take home: comparing healthy to has anxiety AND meds, more disease within vs outside net, anxiety vs non, no interaction.
-## take home #2 : More disease in R & L uncinate in anxious versus nonanxious
-## take home #3 : About the same results as using the previously described anxiety net (rather than the vol 25 x 25 prop)
-
-  #burden of anxiety by network
-  #clean up data frame
- df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
-  mutate(subject = as.factor(EMPI)) %>%
-  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(Diagnosis = as.factor(Diagnosis)) %>%
-
-  #### only two lines that are changed from normal Network * Diagnosis analysis
-  mutate(Anxiety_network = proportion_fascicle_vol_lost_top_25_vol_x_top_25_prop) %>%
-  mutate(Nonanxiety_network = proportion_fascicle_vol_lost_NOT_top_25_vol_x_top_25_prop) %>%
-  #### End changes ###
-
-  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol) %>% 
-  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol, -F_R_vol, -F_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
-  mutate(Network = as.factor(Network)) %>%
-  ungroup()
-
- #simple lmer
-#NetworkNonanxiety_network                      -0.138487   0.008276 173.000010 -16.733  < 2e-16 ***
-#DiagnosisMS+Anxiety                             0.058186   0.029606 188.395804   1.965 0.050843 .
-
-disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
-
-#Network confit
-confint(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
-
-#simple lmer
-#NetworkNonanxiety_network         -0.124175   0.007485 173.000000 -16.589  < 2e-16 ***
-#osex.L                             0.009908   0.025201 187.843641   0.393 0.694647
-
-  disease_within_vs_outside_anxiety_net_by_sex_diff_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-  summary(disease_within_vs_outside_anxiety_net_by_sex_diff_lmer)
-
-#Network confit:
-confint(disease_within_vs_outside_anxiety_net_by_sex_diff_lmer)
-
-## diagnosis by sex 
- #simple lmer, DiagnosisMS+Anxiety         0.0989168  0.0269866   3.665 0.000286 ***
-disease_diagnosis_by_sex_diff_lm <- lm(proportion_affected ~ Diagnosis*osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_diagnosis_by_sex_diff_lm)
-
-#Network confit:
-confint(disease_diagnosis_by_sex_diff_lm)
-
-#network * diagnosis + sex
- #simple lmer: 
-#NetworkNonanxiety_network                      -0.138487   0.008276 173.000010 -16.733  < 2e-16 ***
-#DiagnosisMS+Anxiety                             0.058522   0.029769 187.116974   1.966 0.050793 .   
-disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer <- lmer(proportion_affected ~ Network*Diagnosis + osex + (1|subject)+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer)
-
-#Network confit
-confint(disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer)
-
-```
-
-## AnxietydxANDbenzoGroupVar within/outside network
-```{r anxiety_net_intx}
-
-## demographics
-
-### demographics
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietydxANDbenzoGroupVar != 0,])
-
-#clean up data frame
-df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
-  filter(anxietydxANDbenzoGroupVar != 0) %>% #lose 150, n now 662
-  mutate(subject = as.factor(EMPI)) %>%
-  mutate(Diagnosis = ifelse(anxietydxANDbenzoGroupVar==1, "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
-  mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
-  mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
-  mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
-  mutate(Benzo_status = as.factor(Benzo_status)) %>%
-  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
-  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
-  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, Anxiolytics_status, Has.anxietydx, Benzo_status, PAT_AGE_AT_EXAM) %>% 
-  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -Anxiolytics_status, -Has.anxietydx, -Benzo_status) %>% #this is like a melt.
-Keeps empi and depGroupVar out of the melt
-  mutate(Network = as.factor(Network)) %>%
-  ungroup()
-
-#MS+Anxiety, MS-Anxiety, benzos + anxiety dx, true normal = 0.3782694; MS+ anxiety: ; MS-anxiety: 0.3672053
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"])
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])
-t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
-
-#histos
-hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], main = "Anxiety Network Injury", xlab = "Proportion Affected")
-hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], main = "Nonanxiety Network Injury", xlab = "Proportion Affected")
-
-## Means of separate groups:
-
-#t test, t; t = 61.356, df = 661, p-value < 2.2e-16; 95 percent confidence interval:0.2341835 0.2496681
-within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
-summary(within_vs_outside_anxiety_net_t)
-
- #simple lmer, NetworkNonanxiety_network  -0.241926   0.003943 661.000022  -61.36   <2e-16 ***
-disease_within_vs_outside_anxiety_net_lmer <- lmer(proportion_affected ~ Network + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_lmer)
-
-#Network confit:NetworkNonanxiety_network -0.2496593 -0.23419230
-confint(disease_within_vs_outside_anxiety_net_lmer)
-
-#diagnosis: NS; DiagnosisMS+Anxiety T=  0.811, p=    0.418    ; NetworkNonanxiety_network T= -49.984   p<2e-16 ***
-diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
-summary(diagnosis_by_network_interaction_lmer)
-
-#Diagnosis: NS
-confint(diagnosis_by_network_interaction_lmer)
-
-## Anxiety network x anxiolytics status
-#Network (nonanxiety <anxiety network) : 
-# anxiolytic status: Anxiolytics_statusOn.Anxiolytics 0.064088   0.031256 736.439692    2.05   0.0407 *  
-#Mean prop affected:
-
-disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer <- lmer(proportion_affected ~ Network*Anxiolytics_status + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
-confint(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
-
-## Anxiety network x benzo status
-#Network (nonanxiety <anxiety network) -59.082   <2e-16; Anxiety status: T = 1.210    P = 0.227
-
-disease_within_vs_outside_anxiety_net_by_benzo_lmer <- lmer(proportion_affected ~ Network*Benzo_status + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
-confint(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
-
-## Anxiety network x anxiety diagnosis
-#Network (nonanxiety <anxiety network) :  -51.733   <2e-16 *** ; Anxiety status:  0.721    0.471
-
-disease_within_vs_outside_anxiety_net_by_anxietydx_lmer <- lmer(proportion_affected ~ Network*Has.anxietydx + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
-confint(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
-```
-
-## Anxiety network interaction, matching groups 
-```{r anxiety_net_intx}
-
-## demographics
-
-### BEST SPLIT IS STRATIFYING ON ANXIETY MEDS!!!! Better than on variable that includes anxietyGroupVar(meds + anxiety diagnoses), or anxiety diagnosis alone
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietyGroupVar != 0,])
-
-#clean up data frame
-df_prematched <- df_demo_and_fascicles %>%
-  filter(anxietyGroupVar != 0) %>% #lose 93, n now 719
-  mutate(anxietyGroupVar = as.factor(anxietyGroupVar)) %>%
-  mutate(subject = as.factor(EMPI)) %>%
-  mutate(Diagnosis = ifelse(anxietyGroupVar==1, "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
-  mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
-  mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
-  mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
-  mutate(Benzo_status = as.factor(Benzo_status)) %>%
-  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
-  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
-  ungroup()
-
-#Do the match
-### first, check the prematched data, can play with which variable I want to match on, Has.anxietydx, anxietyGroupVar, Anxiolytics_status
-m.out.prematched <- matchit(anxietyGroupVar ~ sex_binarized + PAT_AGE_AT_EXAM , data = df_prematched,
-                 method = NULL, distance = "glm")
-summary(m.out.prematched)
-
-#then, do the match with the "nearest" method
-m.out.matched <-  matchit(anxietyGroupVar ~ sex_binarized + PAT_AGE_AT_EXAM , data = df_prematched,
-                 method = "nearest", distance = "glm")
-
-#display output
-summary(m.out.matched, un = FALSE)
-
-#add column for keeping to the prematched data frame
-df_prematched$keep <- m.out.matched$weights
-
-#drop values to not keep
-
-df_matched <- df_prematched %>% filter(keep == 1)
-
-### check demographics
-make_demographics_table_ms_anxiety(data_frame = df_matched)
-
-df_empi_dx_network_proportions <-  df_matched %>%
-  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, Anxiolytics_status, Has.anxietydx, Benzo_status, PAT_AGE_AT_EXAM) %>% 
-  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -Anxiolytics_status, -Has.anxietydx, -Benzo_status) %>% #this is like a melt.
-Keeps empi and depGroupVar out of the melt
-  mutate(Network = as.factor(Network)) %>%
-  ungroup()
-
-#simple t test, disease within versus outside anxiety network; mean within anxiety net: 0.5426694 affected, mean outside anxiety network = 0.3062429, T=57.44, p<2.2*10^-16, 95% CI 0.22-0.24
-#MS+Anxiety, MS-Anxiety, meds + anxiety dx, true normal = 0.3850697; MS+ anxiety: ; MS-anxiety: 0.3672053
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"])
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])
-
-#Anxiety dx vs no anxiety dx
-#anxiety dx: 0.3785979; no anxiety dx: 0.3723245
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.anxietydx==1])
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.anxietydx==0])
-
-#On.Anxiolytics vs Off.Anxiolytics
-#on anxiolytics: 0.415625; off anxiolytics:0.3664898
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Anxiolytics_status=="On.Anxiolytics"])
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Anxiolytics_status=="Off.Anxiolytics"])
-
-#On.Benzos vs Off.Benzos
-#on benzos: 0.4022933; off benzos:0.372135
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Benzo_status=="On.Benzos"])
-mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Benzo_status=="Off.Benzos"])
-
-#histos
-hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"])
-hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"])
-
-## Means of separate groups:
-
-#t test, t = 63.621, df = 718, p-value < 2.2e-16; 95 percent confidence interval:0.2349467 0.2499088, mean diff: 0.2424277 
-within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
-summary(within_vs_outside_anxiety_net_t)
-
- #simple lmer, confirms T; -63.62   <2e-16 ***
-disease_within_vs_outside_anxiety_net_lmer <- lmer(proportion_affected ~ Network + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_lmer)
-
- #Net by sex, confirms T; -63.62   <2e-16, but no sex differences (p=0.179)
-disease_within_vs_outside_anxiety_net_sex_lmer <- lmer(proportion_affected ~ Network +osex + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_sex_lmer)
-
- #simple lmer, confirms network: -63.621  < 2e-16 , Pat age: 6.338 4.12e-10
-disease_within_vs_outside_anxiety_net_age_lmer <- lmer(proportion_affected ~ Network + PAT_AGE_AT_EXAM + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_age_lmer)
-
-#Age * network interaction, don't know if this is valid at all. outside > w/in net: -12.718  < 2e-16 ***; pat age = 6.837  1.6e-11 ***, NetworkNonanxiety_network:PAT_AGE_AT_EXAM -2.852  0.00447 
-disease_within_vs_outside_anxiety_net_age_intx_lmer <- lmer(proportion_affected ~ Network*PAT_AGE_AT_EXAM + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_age_intx_lmer)
-
-#diagnosis: NS
-diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
-summary(diagnosis_by_network_interaction_lmer)
-
-#Diagnosis: NS
-confint(diagnosis_by_network_interaction_lmer)
-
-## Anxiety network x anxiolytics status
-#Network (nonanxiety <anxiety network) : T = -58.141   <2e-16 ***; Anxiolytic status: On.anxiolytics>off.anxiolytics; T= 2.473   0.0136 *  
-#Mean prop affected: on anxiolytics: 0.415625;  off anxioloytics: 0.3664898
-
-disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer <- lmer(proportion_affected ~ Network*Anxiolytics_status + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
-confint(disease_within_vs_outside_anxiety_net_by_anxiolytic_status_lmer)
-
-## Anxiety network x benzo status
-#Network (nonanxiety <anxiety network) : T = -54.535   <2e-16***; Anxiety status: T = 0.462    P = 0.645
-
-disease_within_vs_outside_anxiety_net_by_benzo_lmer <- lmer(proportion_affected ~ Network*Benzo_status + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
-confint(disease_within_vs_outside_anxiety_net_by_benzo_lmer)
-
-## Anxiety network x anxiety diagnosis
-#Network (nonanxiety <anxiety network) : T = -54.535   <2e-16***; Anxiety status: T = 0.462    P = 0.645
-
-disease_within_vs_outside_anxiety_net_by_anxietydx_lmer <- lmer(proportion_affected ~ Network*Has.anxietydx + (1|subject), data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
-confint(disease_within_vs_outside_anxiety_net_by_anxietydx_lmer)
-```
-
-### Plot within vs outside network, matched groups
-```{r plottting_bar_graph_matched}
-
-#Within vs outside network
-anxiety_net_group <- c(rep("Anxiety Network", times = dim(df_matched)[1]), rep("Nonanxiety Network",times =dim(df_matched)[1]))
-net_values <- c(df_matched$proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, df_matched$proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75)
-
-newdf <- data.frame(anxiety_net_group, net_values)
-
-newdf <- newdf %>%
-  mutate( anxiety_net_group=factor(anxiety_net_group,levels=c( "Nonanxiety Network", "Anxiety Network")))
-
-violin_within_vs_outside_network_sum_proportion_scaled_by_network_size_matched <- ggplot(newdf, aes(x=anxiety_net_group, y=net_values, fill=anxiety_net_group)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  ggtitle(paste0("Volume of Fascicle Disease Burden")) +
-  ylab("Proportion of network affected") +
-  ylim(0,1) + 
-  scale_fill_manual(values=c("#D3D3D3", "#841DE2")) +
-  theme(plot.title = element_text(size=16, hjust = 0.55),
-        axis.text = element_text(size = 16, colour = "black"), axis.title.y  = element_blank(), 
-        axis.title.x = element_text(size=16),
-        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
-        legend.position = "none",
-        aspect.ratio=4/7,
-        panel.background = element_rect(colour = "white", fill = "white")) + 
-  coord_flip()
-
-#display
-violin_within_vs_outside_network_sum_proportion_scaled_by_network_size_matched
-```
-
-## Compare disease burden by anxiety comorbidity by fascicle
-```{r compare_disease_burden_by_anxiety_comorbidity}
-
-#### in each fascicle
+### Yeo networks
+#### healthy vs super sick 
+```{r individual_fascicle_disease_healthy_vs_super_sick_yeo}
+
+## all correct
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  mutate(anxiousAndMeds_or_healthy = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  filter(anxiousAndMeds_or_healthy %in% c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>%
+  mutate(anxiousAndMeds_or_healthy = factor(anxiousAndMeds_or_healthy, levels=c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"))) #n=122
+
 #lm
-fascicle_number_of_anxiety_dx_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
+fascicle_lm <- lapply(yeo_network_names_prop, function(x) 
 {
-  lm(substitute(i ~ number_of_anxiety_comorbidities_extended, list(i = as.name(x))), data = df_demo_and_fascicles)
+  lm(substitute(i ~ anxiousAndMeds_or_healthy + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
 })
-names(fascicle_number_of_anxiety_dx_lm) <- fascicle_names_w_prop_suffix
-fascicle_number_of_anxiety_dx_anova <- lapply(fascicle_number_of_anxiety_dx_lm, anova)
-
-##uncorrected
-p_anova <- as.data.frame(sapply(fascicle_number_of_anxiety_dx_anova, function(v) v$"Pr(>F)"[1]) )
-
-#extract values that are significant
-p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
-
-#print BEFORE FDR correction 
-print(p_anova_unc)
-
-#fdr corrected
-fascicle_number_of_anxiety_dx_anova_fdr <- fdr_anova_generic(fascicle_number_of_anxiety_dx_anova, 1)
-print(fascicle_number_of_anxiety_dx_anova_fdr)
-
-## limbic area disease by anxiety diagnosis
-
-yeo_lim_no_anxiety <- lm(LIM~number_of_anxiety_comorbidities_extended, data = df_demo_and_fascicles) #nothing
-
-```
-
-## Has depression AND anxiety diagnoses
-```{r compare_disease_burden_by_dep_AND_anxiety_comorbidity}
-
-#lm
-fascicle_depANDanx_dx_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
-{
-  lm(substitute(i ~ Has.depANDanx.dx, list(i = as.name(x))), data = df_demo_and_fascicles)
-})
-names(fascicle_depANDanx_dx_lm) <- fascicle_names_w_prop_suffix
-fascicle_depANDanx_dx_anova <- lapply(fascicle_depANDanx_dx_lm, anova)
-
-##uncorrected
-p_anova <- as.data.frame(sapply(fascicle_depANDanx_dx_anova, function(v) v$"Pr(>F)"[1]) )
-
-#extract values that are significant
-p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
-
-#print BEFORE FDR correction 
-print(p_anova_unc)
-
-#fdr corrected
-fascicle_depANDanx_dx_anova_fdr <- fdr_anova_generic(fascicle_depANDanx_dx_anova, 1)
-print(fascicle_depANDanx_dx_anova_fdr)
-
-```
-
-#compare disease burden by psychiatric comorbidity
-```{r compare_disease_burden_between_anxiety_and_no_psych_dx}
-
-#lm
-fascicle_number_of_psychiatric_dx_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
-{
-  lm(substitute(i ~ number_of_psychiatric_comorbidities_extended, list(i = as.name(x))), data = df_demo_and_fascicles)
-})
-names(fascicle_number_of_psychiatric_dx_lm) <- fascicle_names_w_prop_suffix
-
-fascicle_number_of_psychiatric_dx_anova <- lapply(fascicle_number_of_psychiatric_dx_lm, anova)
-
-#Pull p-values
-p_anova <- as.data.frame(sapply(fascicle_number_of_psychiatric_dx_anova, function(v) v$"Pr(>F)"[1]) )
-
-#extract values that are significant
-p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
-
-#print BEFORE FDR correction 
-print(p_anova_unc)
-
-#fdr corrected
-fascicle_number_of_psychiatric_dx_anova_fdr <- fdr_anova_generic(fascicle_number_of_psychiatric_dx_anova, 1)
-print(fascicle_number_of_psychiatric_dx_anova_fdr)
-
-## yeo
-#lm
-psych_comorbidity_lm_yeo <- lapply(yeo_network_names, function(x) 
-{
-  lm(substitute(i ~ number_of_psychiatric_comorbidities_extended, list(i = as.name(x))), data = df_demo_and_fascicles)
-})
-names(psych_comorbidity_lm_yeo) <- yeo_network_names
-
-psych_comorbidity_yeo_anova <- lapply(psych_comorbidity_lm_yeo, anova)
-
-#uncorrected
-#Pull p-values
-p_anova <- as.data.frame(sapply(psych_comorbidity_yeo_anova, function(v) v$"Pr(>F)"[1]) )
-
-#extract values that are significant
-p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
-
-#print BEFORE FDR correction 
-print(p_anova_unc)
-
-#fdr corrected
-psych_comorbidity_yeo_anova_fdr <- fdr_anova_generic(psych_comorbidity_yeo_anova, 1)
-print(psych_comorbidity_yeo_anova_fdr)
-
-```
-
-##compare disease in anxiety versus patients with no psychiatric comorbidity
-```{r anxiety_vs_healthy_ish}
-
-anxiety_vs_no_psych <- df_demo_and_fascicles %>%
-  mutate(anxietyGroupVar = ifelse(Has.anxietydx, 2, ifelse(healthy_ish, 1, 0))) %>% #complicated, if they have an anxiety disorder, they get a 2, if they are health-ish, no psych dx or meds, 1, otherwise, exclude
-  filter(anxietyGroupVar != 0) %>% #get rid of the people who are not anxious and not healthy_ish, n =643, lost n=169
-  filter(is.na(depGroupVar)) %>% #exclude people with depression (87 have both depression and anxiety), n = 557, anxiety = 101, nonanxious = 456)
-  group_by(EMPI) %>%
-  arrange(EXAM_DATE) %>%
-  slice(1) %>%
-  ungroup
-
-#lm
-anxiety_vs_no_psych_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
-{
-  lm(substitute(i ~ anxietyGroupVar, list(i = as.name(x))), data = anxiety_vs_no_psych)
-})
-names(anxiety_vs_no_psych_lm) <- fascicle_names_w_prop_suffix
-
-anxiety_vs_no_psych_lm_anova <- lapply(anxiety_vs_no_psych_lm, anova)
-
-#uncorrected
-#Pull p-values
-p_anova <- as.data.frame(sapply(anxiety_vs_no_psych_lm_anova, function(v) v$"Pr(>F)"[1]) )
-
-#extract values that are significant
-p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
-
-#print BEFORE FDR correction 
-print(p_anova_unc)
-
-#fdr corrected
-anxiety_vs_no_psych_lm_anova_fdr <- fdr_anova_generic(anxiety_vs_no_psych_lm_anova, 1)
-print(anxiety_vs_no_psych_lm_anova_fdr)
-
-## yeo
-#lm
-anxiety_vs_no_psych_lm_yeo <- lapply(yeo_network_names, function(x) 
-{
-  lm(substitute(i ~ anxietyGroupVar, list(i = as.name(x))), data = anxiety_vs_no_psych)
-})
-names(anxiety_vs_no_psych_lm_yeo) <- yeo_network_names
-
-anxiety_vs_no_psych_yeo_anova <- lapply(anxiety_vs_no_psych_lm_yeo, anova)
-
-#uncorrected
-#Pull p-values
-p_anova <- as.data.frame(sapply(anxiety_vs_no_psych_yeo_anova, function(v) v$"Pr(>F)"[1]) )
-
-#extract values that are significant
-p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
-
-#print BEFORE FDR correction 
-print(p_anova_unc)
-
-#fdr corrected
-anxiety_vs_no_psych_yeo_anova_fdr <- fdr_anova_generic(anxiety_vs_no_psych_yeo_anova, 1)
-print(anxiety_vs_no_psych_yeo_anova_fdr)
-
-### total lesion burden
-
-### lesion volume
-
-```
-### Run analysis again but include in anxiety group people on anti-anxiety meds
-```{r anxiety_oranxiety_meds_vs_healthy_ish}
-
-anxiety_vs_no_psych <- df_demo_and_fascicles %>%
-  mutate(anxietyGroupVar = ifelse((Has.anxietydx | On.Anxiolytics_no_beta_blocker), 2, ifelse(healthy_ish, 1, 0))) %>% #complicated, if they have an anxiety disorder, they get a 2, if they are health-ish, no psych dx or meds, 1, otherwise, exclude; n anxiety = 271, healthyish = 448, unclassified = 93
-  mutate(anxietyGroupVar_ordered = ordered(anxietyGroupVar,levels = c(0,1,2), labels = c("unclassified", "healthyish", "anxiety"))) %>%
-  filter(anxietyGroupVar_ordered != "unclassified") %>% #get rid of the people who are not anxious and not healthy_ish, n =541, lost n=93
-  filter(is.na(depGroupVar)) %>% #exclude people with depression (87 have both depression and anxiety), n = 557, anxiety = 101, nonanxious = 456)
-  group_by(EMPI) %>%
-  arrange(EXAM_DATE) %>%
-  slice(1) %>%
-  ungroup
-
-#lm
-anxiety_vs_no_psych_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
-{
-  lm(substitute(i ~ anxietyGroupVar, list(i = as.name(x))), data = anxiety_vs_no_psych)
-})
-names(anxiety_vs_no_psych_lm) <- fascicle_names_w_prop_suffix
-
-anxiety_vs_no_psych_lm_anova <- lapply(anxiety_vs_no_psych_lm, anova)
-
-#uncorrected
-#Pull p-values
-p_anova <- as.data.frame(sapply(anxiety_vs_no_psych_lm_anova, function(v) v$"Pr(>F)"[1]) )
-
-#extract values that are significant
-p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
-
-#print BEFORE FDR correction 
-print(p_anova_unc)
-
-#fdr corrected
-anxiety_vs_no_psych_lm_anova_fdr <- fdr_anova_generic(anxiety_vs_no_psych_lm_anova, 1)
-print(anxiety_vs_no_psych_lm_anova_fdr)
-
-## yeo
-#lm
-anxiety_vs_no_psych_lm_yeo <- lapply(yeo_network_names, function(x) 
-{
-  lm(substitute(i ~ anxietyGroupVar, list(i = as.name(x))), data = anxiety_vs_no_psych)
-})
-names(anxiety_vs_no_psych_lm_yeo) <- yeo_network_names
-
-anxiety_vs_no_psych_yeo_anova <- lapply(anxiety_vs_no_psych_lm_yeo, anova)
-
-#uncorrected
-#Pull p-values
-p_anova <- as.data.frame(sapply(anxiety_vs_no_psych_yeo_anova, function(v) v$"Pr(>F)"[1]) )
-
-#extract values that are significant
-p_anova_unc <- as.data.frame(cbind(row.names(p_anova)[p_anova < 0.05], p_anova[p_anova <0.05]))
-
-#print BEFORE FDR correction 
-print(p_anova_unc)
-
-#fdr corrected
-anxiety_vs_no_psych_yeo_anova_fdr <- fdr_anova_generic(anxiety_vs_no_psych_yeo_anova, 1)
-print(anxiety_vs_no_psych_yeo_anova_fdr)
-
-```
-
-## Compare total disease burden and lesion volume by anxiety comorbidity
-```{r total_burden_and_lesion_volume_by_anxiety_comorbdity}
-
-total_burden_by_anxietydx_lm <- lm(anxietyGroupVar~total_fascicle_volume_lost_no_cranial_nerves, data = anxiety_vs_no_psych)
-print(summary(total_burden_by_anxietydx_lm))
-
-total_burden_by_anxiety_lm <- lm(number_of_anxiety_comorbidities_extended~total_fascicle_volume_lost_no_cranial_nerves, data = anxiety_vs_no_psych)
-print(summary(total_burden_by_anxiety_lm))
-
-total_lesion_volume_by_anxietydx_lm <- lm(anxietyGroupVar ~volume_of_mimosa_lesions, data = anxiety_vs_no_psych)
-print(summary(total_lesion_volume_by_anxietydx_lm))
-
-total_lesion_volume_by_anxiety_lm <- lm(number_of_anxiety_comorbidities_extended ~volume_of_mimosa_lesions, data = anxiety_vs_no_psych)
-print(summary(total_lesion_volume_by_anxiety_lm))
-
-```
-
-### Send anxiety groups to HYDRA (diagnosis only, no on meds)
-```{r anxiety_group_prep_for_hydra}
-### remake data frame from above
-
-anxiety_vs_no_psych <- df_demo_and_fascicles %>%
-  mutate(anxietyGroupVar = ifelse(Has.anxietydx, 2, ifelse(healthy_ish, 1, 0))) %>% #complicated, if they have an anxiety disorder, they get a 2, if they are health-ish, no psych dx or meds, 1, otherwise, exclude
-  filter(anxietyGroupVar != 0) %>% #get rid of the people who are not anxious and not healthy_ish, n =643, lost n=169
-  filter(is.na(depGroupVar)) %>% #exclude people with depression (87 have both depression and anxiety), n = 557, anxiety = 101, nonanxious = 456)
-  mutate(anxietyHydraVar = ifelse(anxietyGroupVar == 2, 1, -1)) %>%
-  group_by(EMPI) %>%
-  arrange(EXAM_DATE) %>%
-  slice(1) %>%
-  ungroup
-
-#pull out EMPI, proportion, and anxiety group var
-anxiety_vs_no_psych_features_for_hydra <- anxiety_vs_no_psych %>%
-  dplyr::select(EMPI, fascicle_names_w_prop_suffix, anxietyHydraVar)
-
-write.csv(file=paste0(homedir, "/hydra/data/Features_ms_fascicle_dysconnectome_anxiety_prop.csv"),x=anxiety_vs_no_psych_features_for_hydra, quote = F, row.names = F)
-
-#pull out age, age + sex covariates
-anxiety_age <- anxiety_vs_no_psych %>%
-  dplyr::select(EMPI, PAT_AGE_AT_EXAM)
-
-write.csv(file=paste0(homedir, "/hydra/data/Covariates_age.csv"),x=anxiety_age, quote = F, row.names = F)
-
-anxiety_age_and_sex <- anxiety_vs_no_psych %>%
-  dplyr::select(EMPI, PAT_AGE_AT_EXAM, sex_binarized)
-
-write.csv(file=paste0(homedir, "/hydra/data/Covariates_age_and_sex.csv"),x=anxiety_age_and_sex, quote = F, row.names = F)
-
-#pull out yeo proportions
-anxiety_vs_no_psych_yeo_features_for_hydra <- anxiety_vs_no_psych %>%
-  dplyr::select(EMPI, yeo_network_names_prop, anxietyHydraVar)
-
-write.csv(file=paste0(homedir, "/hydra/data/Features_ms_fascicle_dysconnectome_anxiety_yeo_prop.csv"),x=anxiety_vs_no_psych_yeo_features_for_hydra, quote = F, row.names = F)
-
-```
-
-### Send anxiety groups to HYDRA ((diagnosis only + benzos)
-```{r anxiety_group_prep_for_hydra}
-### remake data frame from above
-
-anxiety_vs_no_psych <- df_demo_and_fascicles %>%
-  filter(anxietydxANDbenzoGroupVar != 0) %>% #get rid of the people who are not anxious and not healthy_ish, n =662, lost n=150
-  filter(depGroupVar!=2) %>% #exclude people with depression , n =568, lost 104
-  mutate(anxietyHydraVar = ifelse(anxietyGroupVar == 2, 1, -1)) %>%
-  group_by(EMPI) %>%
-  arrange(EXAM_DATE) %>%
-  slice(1) %>%
-  ungroup
-
-#pull out EMPI, proportion, and anxiety group var
-anxiety_vs_no_psych_features_for_hydra <- anxiety_vs_no_psych %>%
-  dplyr::select(EMPI, fascicle_names_w_prop_suffix, anxietyHydraVar)
-
-write.csv(file=paste0(homedir, "/hydra/data/Features_anxietydxANDbenzo_prop.csv"),x=anxiety_vs_no_psych_features_for_hydra, quote = F, row.names = F)
-
-#pull out age, age + sex covariates
-anxiety_age <- anxiety_vs_no_psych %>%
-  dplyr::select(EMPI, PAT_AGE_AT_EXAM)
-
-write.csv(file=paste0(homedir, "/hydra/data/Covariates_anxietydxANDbenzo_age.csv"),x=anxiety_age, quote = F, row.names = F)
-
-anxiety_age_and_sex <- anxiety_vs_no_psych %>%
-  dplyr::select(EMPI, PAT_AGE_AT_EXAM, sex_binarized)
-
-write.csv(file=paste0(homedir, "/hydra/data/Covariates_anxietydxANDbenzo_age_and_sex.csv"),x=anxiety_age_and_sex, quote = F, row.names = F)
-
-#pull out yeo proportions
-anxiety_vs_no_psych_yeo_features_for_hydra <- anxiety_vs_no_psych %>%
-  dplyr::select(EMPI, yeo_network_names_prop, anxietyHydraVar)
-
-write.csv(file=paste0(homedir, "/hydra/data/Features_anxietydxANDbenzo_yeo_prop.csv"),x=anxiety_vs_no_psych_yeo_features_for_hydra, quote = F, row.names = F)
-
-```
-
-## Depression versus healthy analysis
-
-```{r demographics}
-
-#this will display a demographics table comparing age, race, sex between healthy and depressed groups, using the first presentation to treatment
-
-make_demographics_table_ms(data_frame = data_2023_pull)
-
-df_unique_empi <- data_empi_acc_f_phq %>% 
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  ungroup()
-
-make_demographics_table_ms(data_frame = df_unique_empi)
-
-df_just_healthy_and_depressed <- df_unique_empi %>% filter(depGroupVar != 0)
-
-make_demographics_table_ms(data_frame = df_just_healthy_and_depressed)
-
-#just people with good mimosa
-df_good_mimosa <- df_demo_and_fascicles %>% filter(depGroupVar != 0)
-make_demographics_table_ms(data_frame = df_good_mimosa)
-
-df_good_mimosa_unique <- df_demo_and_fascicles %>% 
-  filter(depGroupVar != 0) %>%
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  ungroup() 
-make_demographics_table_ms(data_frame = df_good_mimosa_unique)
-```
-
-```{r proof_of_concept}
-
-#this section creates histograms looking at the proportion of volume lost in each fascicle across subjects
-#we recapitulate earlier work and show that higher volume loss with our method reflects regions previously known to have higher volume loss
-#These findings suggest that the streamline filtering approach could be a reasonable approach for this analysis
-
-#have to pull out just the pieces I'm interested in
-just_dep_and_empi <- subset(data_empi_acc_f_phq, select = c("EMPI", "depGroupVar"))
-added_dep_to_fascicles <- merge(just_dep_and_empi, fascicle_proportions, by = c("EMPI"))
-melted_df <- melt(added_dep_to_fascicles, id.vars = c("EMPI", "EXAM_DATE", "depGroupVar"))
-
-#exclude regions where there was no lesion at all
-lesioned <- subset(melted_df, value > 0)
-
-#only include people in healthy or depressed group
-lesioned_dx <- subset(lesioned, depGroupVar != 0)
-
-#separate out healthy and depressed
-healthy <- subset(lesioned, depGroupVar == 1)
-depressed <- subset(lesioned, depGroupVar == 2)
-
-q<-ggplot(lesioned, aes(x=value, fill=depGroupVar)) + geom_histogram() + facet_wrap(~variable)
-r<-ggplot(lesioned_dx, aes(x=value, fill=depGroupVar)) + geom_histogram() + facet_wrap(~variable)
-r_color<-ggplot(lesioned_dx, aes(x=value, color=factor(depGroupVar))) + geom_histogram() + facet_wrap(~variable)
-x<-ggplot(lesioned, aes(x=value)) + geom_histogram() + facet_wrap(~variable)
-y<-ggplot(healthy, aes(x=value)) + geom_histogram() + facet_wrap(~variable)
-z<-ggplot(depressed, aes(x=value)) + geom_histogram() + facet_wrap(~variable)
-
-#print(q)
-#print(r)
-print(r_color)
-#print(x)
-#print(y)
-#print(z)
-```
-
-```{r age_effects_fascicles_unique}
-########### age effect whole group
-
-#isolate out only the depressed group and healthy group
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>% 
-  filter(depGroupVar != 0)  %>% 
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  ungroup()
-
-#### age histo ###
-hist(df_demo_and_fascicles_no_unclass_anxiety_dose$PAT_AGE_AT_EXAM,
-main = paste0("Age In Good Mimosa Group : n = ", dim(df_demo_and_fascicles_no_unclass_anxiety_dose)[1]), xlab = "Age", breaks = 10)
-
-#lm
-fascicle_age_lm <- lapply(fascicle_names, function(x) 
-{
-  lm(substitute(i ~ PAT_AGE_AT_EXAM, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
-})
-names(fascicle_age_lm) <- fascicle_names
-
-#anova
-fascicle_age_anova <- lapply(fascicle_age_lm, anova)
-
-#fdr corrected
-fascicle_age_anova_fdr <- fdr_anova_generic(fascicle_age_anova, 1)
-print(fascicle_age_anova_fdr)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_age_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#visreg
-#sapply(fascicle_age_lm,visreg)
-visreg(fascicle_age_lm$AF_R,ylab = "Proportion of Affected Streamlines", xlab = "Age in Years",
-       line=list(col="red"),
-       points=list(col="black"))
-
-```
-
-```{r sex_effects_fascicles_unique}
-
-### really not interesting at all. 3 areas that are uncorrected: SCP, CPT_O_R, OR_R
-
-#isolate out only the depressed group and healthy group
-dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% filter(depGroupVar != 0)  %>% 
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  ungroup()
-
-#### sex histo ###
-hist(dep_and_healthy_groups_for_ICD_analysis$sex_binarized,
-main = paste0("Sex In Good Mimosa Group : n (M/F)= ", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1), "/", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)),  xlab = "Sex", breaks = 2)
-
-#lm
-fascicle_sex_lm <- lapply(fascicle_names, function(x) 
-{
-  lm(substitute(i ~ osex, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
-})
-names(fascicle_sex_lm) <- fascicle_names
-
-#anova
-fascicle_sex_anova <- lapply(fascicle_sex_lm, anova)
-
-#fdr corrected
-fascicle_sex_anova_fdr <- fdr_anova_generic(fascicle_sex_anova, 1)
-print(fascicle_sex_anova_fdr)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_sex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_sex_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_sex_anova_p <- sapply(fascicle_sex_anova, function(v) v$"Pr(>F)"[1])
-fascicle_sex_anova_p05_unc <- as.data.frame(fascicle_sex_anova_p[fascicle_sex_anova_p < 0.05])
-print(fascicle_sex_anova_p05_unc)
-
-```
-
-```{r depression_unique_all_fascicles_together_in_dep_networks}
-
-#isolate out only the depressed group and healthy group, make a column that sums up the total prop lost)
-dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% 
-  filter(depGroupVar != 0)  %>% 
-  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
-  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
-  mutate(total_fascicle_prop_lost_indepnet_10_percent =
-           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
-   mutate(total_fascicle_prop_lost_indepnet_5_percent =
-           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
-  mutate(total_fascicle_prop_lost_nondep_network =
-           rowMeans(across(fascicle_names_nondep_network))) %>%
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  ungroup()
-
-dep_vs_healthy <- lm(total_fascicle_prop_lost ~ depGroupVar, data = dep_and_healthy_groups_for_ICD_analysis)
-summary(dep_vs_healthy) #p=0.494, cohen d = 0.2
-
-#power analysis to predict sample required for K, u = num df, v = denom df, f2=0.01 (cohen d = 0.02/2) 
-#prop in each fascicle predicting dep (87), number of predictors (age, sex, ef, ess?) = 4, u = 87-4 = 83
-pwr.f2.test(u=83, f2 = 0.02, sig.level = 0.5, power = 0.8)
-
-#test whether proportion lost overall different between depressed and healthy- yes, p = 0.049
-total_volume_lost_dep_vs_healthy_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 27%, mean non_dep = 24%, p = 0.049
-
-df_for_visreg <- as.data.frame(cbind(c(dep_and_healthy_groups_for_ICD_analysis$EMPI, dep_and_healthy_groups_for_ICD_analysis$EMPI), c(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]), c(rep(1,298), rep(2,298))))
-names(df_for_visreg) <- c("EMPI", "prop_lost", "Diagnosis")
-df_for_visreg$Diagnosis <- as.factor(df_for_visreg$Diagnosis)
-
-plot <- ggplot(df_for_visreg, aes(x=Diagnosis, y = prop_lost, col=Diagnosis)) +
-  geom_violin() + 
-  geom_jitter(shape=16, position=position_jitter(0.05)) + 
-  geom_boxplot(width=0.1) + theme_minimal() + 
-  stat_summary(fun.y=median, geom="point", size=2, color="black") + 
-  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed"))
-
-print(plot)
-
-#bar plot
-Diagnosis <- c("MS w/Depression", "MS No Depression")
-value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
-           mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]))
-
-sem <- c((sd(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==2))),
-           (sd(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==1))))
-
-data <- data.frame(Diagnosis,value, sem)
-#data$Fascicle <- pretty_names
-
-# Grouped
-barplot <- ggplot(data, aes(x=Diagnosis,fill=Diagnosis, y=value)) + 
-  geom_bar(stat="identity", position=position_dodge(0.9)) + 
-    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
-  ylab("Proportion of Fascicles Affected") +
-  ylim(0,0.5) +
-  theme(axis.text = element_text(size = 12, colour = "black"))
-
-print(barplot)
-
-# Grouped
-barplot <- ggplot(data, aes(x=reorder(Diagnosis, -value),fill=Diagnosis, y=value)) + 
-  geom_bar(stat="identity", colour="black", width=0.8, size=1.5) + 
-    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9), size=1.5) +
-  scale_fill_manual(values = c("#cdcdcd", "#FFFFFF")) + #comment out if you want colored graph
-  ylab("Proportion of Fascicles Affected") +
-  theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
-        axis.title.y = element_text(size=20),
-        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
-        panel.background = element_rect(colour = "white", fill = "white")) + #comment out if you want pretty 
-  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.52)) #comment out if you want colored graph
-
-print(barplot)
-
-#look at within depression network specifically - trend, p = 0.059
-total_volume_lost_dep_vs_healthy_unique_in_dep_network <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 36%, mean non_dep = 32%, p = 0.071
-
-#look at within depression network in fascicles where at least 10% of the volume of the fascicle was in dep network
-#yes, p = 0.048
-total_volume_lost_dep_vs_healthy_unique_in_dep_network_10percent <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_10_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_10_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 33%, mean non_dep = 27%, p = 0.048
-
-#look at within depression network in fascicles where at least 5% of the volume of the fascicle was in dep network
-#yes, 
-total_volume_lost_dep_vs_healthy_unique_in_dep_network_5percent <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_5_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_5_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 32%, mean non_dep = 27%, p = 0.056
-
-#look at outside depression network, yes p = 0.037
-total_volume_lost_dep_vs_healthy_unique_in_nondep_network <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 18%, mean non_dep = 16%, p = 0.037
-
-### Age actually makes things worse
-#dep_vs_healthy_w_age <- lm(total_fascicle_prop_lost ~ depGroupVar + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)
-#summary(dep_vs_healthy_w_age)
-
-#df for visreg - actually not using visreg. Just a nice way to see that there is significantly more loss in depression network versus outside depression network
-
-```
-
-```{r depressed_versus_healthy_unique_subjs_indiv_fascicle}
-##### repeat above analysis but use only the first instance of each EMPI, sorted by date
-df_unique_empi <- df_demo_and_fascicles %>% 
-  filter(depGroupVar != 0) %>%
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  ungroup()
-
-#lm
-fascicle_lm_unique <- lapply(fascicle_names, function(x) 
-{
-  lm(substitute(i ~ depGroupVar + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_unique_empi)
-})
-names(fascicle_lm_unique) <- fascicle_names
-
-#anova
-fascicle_anova_unique <- lapply(fascicle_lm_unique, anova)
-
-#fdr corrected
-fascicle_anova_unique_fdr <- fdr_anova_generic(fascicle_anova_unique, 1)
-print(fascicle_anova_unique_fdr)#anova values < 0.05, uncorrected
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_anova_unique[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only dep network
-fascicle_anova_w_fiber_mapping <- fascicle_anova_unique[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr)
-
-#fdr corrected only dep 10% mask
-fascicle_anova_w_fiber_mapping <- fascicle_anova_unique[which(fascicle_bundle_mapping$inDepNetwork_vector ==2)]
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr)
-
-#fdr corrected only dep 5% mask
-fascicle_anova_w_fiber_mapping <- fascicle_anova_unique[which(fascicle_volumes_dep_network$prop_in_mask >= 0.05)]
-fascicle_anova_fdr<- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr)
-
-#uncorrected
-fascicle_anova_unique_p <- sapply(fascicle_anova_unique, function(v) v$"Pr(>F)"[1])
-fascicle_anova_unique_p05_unc <- as.data.frame(fascicle_anova_unique_p[fascicle_anova_unique_p < 0.05])
-print(fascicle_anova_unique_p05_unc)
-
-### plot AF_R
-
-df_for_visreg <- as.data.frame(cbind(c(dep_and_healthy_groups_for_ICD_analysis$EMPI, dep_and_healthy_groups_for_ICD_analysis$EMPI), c(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]), c(rep(1,298), rep(2,298))))
-names(df_for_visreg) <- c("EMPI", "prop_lost", "Diagnosis")
-df_for_visreg$Diagnosis <- as.factor(df_for_visreg$Diagnosis)
-
-plot <- ggplot(df_for_visreg, aes(x=Diagnosis, y = prop_lost, col=Diagnosis)) +
-  ggtitle("Arcuate Fasciculus R") + 
- # geom_violin() + 
-  geom_jitter(shape=16, position=position_jitter(0.05)) + 
-  geom_boxplot(width=0.1) + theme_minimal() + 
-  stat_summary(fun.y=median, geom="point", size=2, color="black") + 
-  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed"))
-
-print(plot)
-
-### Plot OR_R	0.69024050
-df_for_visreg <- as.data.frame(cbind(c(dep_and_healthy_groups_for_ICD_analysis$EMPI, dep_and_healthy_groups_for_ICD_analysis$EMPI), c(dep_and_healthy_groups_for_ICD_analysis$OR_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$OR_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]), c(rep(1,298), rep(2,298))))
-names(df_for_visreg) <- c("EMPI", "prop_lost", "Diagnosis")
-df_for_visreg$Diagnosis <- as.factor(df_for_visreg$Diagnosis)
-
-plot <- ggplot(df_for_visreg, aes(x=Diagnosis, y = prop_lost, col=Diagnosis)) +
-  ggtitle("Optic Radiation R") + 
- # geom_violin() + 
-  geom_jitter(shape=16, position=position_jitter(0.05)) + 
-  geom_boxplot(width=0.1) + theme_minimal() + 
-  stat_summary(fun.y=median, geom="point", size=2, color="black") + 
-  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed")) 
-print(plot)
-
-### grouped bar plot
-
-Diagnosis <- c(rep("Depressed" , 2) , rep("Non-Depressed" , 2))
-Fascicle <- rep(c("Depression Network (AF)" , "Region Outside Depression Network (C_PH)"), 2)
-value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
-           mean(dep_and_healthy_groups_for_ICD_analysis$C_PH_L[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
-           mean(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]),
-           mean(dep_and_healthy_groups_for_ICD_analysis$C_PH_L[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]))
-
-sem <- c((sd(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==2))),
-           (sd(dep_and_healthy_groups_for_ICD_analysis$C_PH_L[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==2))),
-           (sd(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==1 ))),
-          (sd(dep_and_healthy_groups_for_ICD_analysis$C_PH_L[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==1 ))))
-
-data <- data.frame(Diagnosis,Fascicle,value, sem)
-#data$Fascicle <- pretty_names
-
-# Grouped
-barplot <- ggplot(data, aes(fill=Diagnosis, y=value, x=Fascicle)) + 
-    geom_bar(position="dodge", stat="identity") + 
-    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
-  ylab("Proportion of Fascicles Affected") +
-  theme(axis.text = element_text(size = 12, colour = "black"), axis.title.x = element_blank())
-
-print(barplot)
-
-# Grouped
-barplot <- ggplot(data, aes(fill=Diagnosis, y=value, x=Fascicle)) + 
-    geom_bar(position="dodge", stat="identity") + 
-    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
-  ylab("Proportion of Fascicles Affected") +
-  theme(axis.text = element_text(size = 12, colour = "black"), axis.title.x = element_blank())
-
-print(barplot)
-
-barplot2 <- ggplot(data, aes(fill=Diagnosis, y=value, x=Fascicle)) + 
-    geom_bar(position="dodge", stat="identity", colour = "black", width=0.9,size=1.5) + 
-    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9), size=1) + 
-    scale_fill_manual(values = c("#cdcdcd", "#FFFFFF", "#cdcdcd", "#FFFFFF")) + #comment out if you want colored graph
-
-    ylab("Proportion of Fascicles Affected") +
-    theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
-          axis.title.y = element_text(size=20),
-          axis.line = element_line(size = 1.5, colour = "black", linetype=1),
-          panel.background = element_rect(colour = "white", fill = "white")) + #comment out if you want pretty graph
-    scale_y_continuous(expand = c(0, 0), limits = c(0, 0.52)) #comment out if you want colored graph
-
-print(barplot2)
-
-```
-
-```{r testing_whether_ms_disease_more_likely_in_depression_mask_unique}
-### tests whether there is higher proportion of vertices lost in depression network versus not
-
-dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% 
-  filter(depGroupVar != 0)  %>% 
-  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
-  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
-  mutate(total_fascicle_prop_lost_indepnet_10_percent =
-           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
-  mutate(total_fascicle_prop_lost_indepnet_5_percent =
-           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
-  mutate(total_fascicle_prop_lost_nondep_network =
-           rowMeans(across(fascicle_names_nondep_network))) %>%
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  ### when I filter and remove fascicles where there was no loss at all, the depression vs healthy findings go away
-#  filter(total_fascicle_prop_lost > 0) %>%
-  ungroup()
-
-#test whether there is differentially more volume loss in depression versus nondepression network
-volume_lost_dep_vs_nondep_network_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network, var.equal = F) #mean dep_net = 35%, mean non_dep_net =  17%, p 2.2 x 10^-16
-
-volume_lost_dep10_vs_nondep_network_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_10_percent,
-dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network, var.equal = F) #mean dep net = 31%, mean non_dep_net = 17%, p 2.2 * 10^-16
-
-volume_lost_dep5_vs_nondep_network_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_5_percent,
-dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network, var.equal = F) #mean dep net = 30%, mean non_dep_net = 17%, p 2.2 * 10^-16
-
-#df for visreg - actually not using visreg. Just a nice way to see that there is significantly more loss in depression network versus outside depression network
-df_for_visreg <- as.data.frame(cbind(c(dep_and_healthy_groups_for_ICD_analysis$EMPI, dep_and_healthy_groups_for_ICD_analysis$EMPI), c(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network), c(rep(1,298), rep(2,298))))
-names(df_for_visreg) <- c("EMPI", "prop_lost", "network")
-df_for_visreg$network <- as.factor(df_for_visreg$network)
-
-plot <- ggplot(df_for_visreg, aes(x=network, y = prop_lost, col=network)) +
-  geom_violin() + 
-  geom_jitter(shape=16, position=position_jitter(0.05)) + 
-  geom_boxplot(width=0.1) + theme_minimal() + 
-  stat_summary(fun.y=median, geom="point", size=2, color="red") + 
-  scale_x_discrete(labels=c("1" = "Depression Network", "2" = "Non-Depression Network")) + 
-  ylab("Proportion of Fascicles Affected") + 
-  theme(axis.text =element_text(size=14), axis.title.x = element_blank())
-
-print(plot)
-
-########## Bar plot
-Network <- c("Depression Network","Non-Depression Network")
-value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet),
-           mean(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network))
-
-sem <- c((sd(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet)/sqrt(dim(dep_and_healthy_groups_for_ICD_analysis)[1])),
-           (sd(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network)/sqrt(dim(dep_and_healthy_groups_for_ICD_analysis)[1])))
-
-data <- data.frame(Network,value,sem)
-#data$Fascicle <- pretty_names
-
-# Grouped
-barplot <- ggplot(data, aes(x=Network,fill=Network, y=value)) + 
-  geom_bar(stat="identity", position=position_dodge(0.9)) + 
-  geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
-  ylab("Proportion of Fascicles Affected") +
-  ylim(0,0.5) +
-  theme(axis.text = element_text(size = 12, colour = "black"))
-
-print(barplot)
-# Black and white
-barplot <- ggplot(data, aes(x=Network,fill=Network, y=value)) + 
-  geom_bar(stat="identity", colour="black", width=0.8, size=1.5) + 
-  geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9), size=1.5) +
-  scale_fill_manual(values = c("#cdcdcd", "#FFFFFF")) + #comment out if you want colored graph
-  ylab("Proportion of Fascicles Affected") +
-  theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
-        axis.title.y = element_text(size=20),
-        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
-        panel.background = element_rect(colour = "white", fill = "white")) + #comment out if you want pretty 
-  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.52)) #comment out if you want colored graph
-
-print(barplot)
-
-###### Depression network x depression group interaction - It is there, depression always worse. 
-#these lms largely match up with the t.tests above. Sig differences between depressed (more disease) within and outside of mask
-
-loss_in_dep_network <- lm(total_fascicle_prop_lost_indepnet~depGroupVar, data = dep_and_healthy_groups_for_ICD_analysis) #non sig, p = 0.061
-loss_in_dep_network_10_percent <- lm(total_fascicle_prop_lost_indepnet_10_percent~depGroupVar, data = dep_and_healthy_groups_for_ICD_analysis) #p = 0.0492
-loss_in_nondep_network <- lm(total_fascicle_prop_lost_nondep_network~depGroupVar, data = dep_and_healthy_groups_for_ICD_analysis) #p=0.037
-```
-
-```{r phq9_correlation_fascicles}
-
-####### NOTHING SIGNIFICANT!!!! ########3
-#isolate out only the depressed group and healthy group
-with_phq9 <- df_demo_and_fascicles %>%
-  filter(depGroupVar != 0) %>%
-  filter(!is.na(PHQ.9)) %>%
-  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
-  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
-  mutate(total_fascicle_prop_lost_indepnet_10_percent =
-           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
-  mutate(total_fascicle_prop_lost_indepnet_5_percent =
-           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
-  mutate(total_fascicle_prop_lost_nondep_network =
-           rowMeans(across(fascicle_names_nondep_network))) %>%
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  ungroup()
-
-#lm
-fascicle_lm <- lapply(fascicle_names, function(x) 
-{
-  lm(substitute(i ~ PHQ.9, list(i = as.name(x))), data = with_phq9)
-})
-names(fascicle_lm) <- fascicle_names
+names(fascicle_lm) <- yeo_network_names_prop
 
@@
 #fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only dep network
-fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
-fascicle_anova_fdr<- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr)
-
-#fdr corrected only dep 10% mask
-fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$inDepNetwork_vector == 2)]
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr)
+#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
+##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
+#print(fascicle_anova_fdr_association)
 
@@
 fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_p05_unc <- fascicle_anova_p[!is.na(fascicle_anova_p) & fascicle_anova_p < 0.05]
+fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
 print(fascicle_anova_p05_unc) 
-
-######### overall fascicle proportion affected - nothing is significant
-overall_prop_affected <- lm(total_fascicle_prop_lost~PHQ.9, data=with_phq9)
-overall_prop_affected_depnet <- lm(total_fascicle_prop_lost_indepnet~PHQ.9, data=with_phq9)
-overall_prop_affected_depnet_10percent <- lm(total_fascicle_prop_lost_indepnet_10_percent~PHQ.9, data=with_phq9)
-overall_prop_affected_depnet_5percent <- lm(total_fascicle_prop_lost_indepnet_5_percent~PHQ.9, data=with_phq9)
-overall_prop_affected_nondep <- lm(total_fascicle_prop_lost_nondep_network~PHQ.9, data=with_phq9)
-```
-
-```{r phq9_regressions_just_dep_group}
-##### NOTHING SIGNIFICANT ########
-##################################
-## Just within depression group ##
-##################################
-#isolate out only the depressed group and healthy group
-with_phq9 <- df_demo_and_fascicles %>%
-  filter(depGroupVar == 2) %>%
-  filter(!is.na(PHQ.9)) %>%
-  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
-  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
-  mutate(total_fascicle_prop_lost_indepnet_10_percent =
-           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
-  mutate(total_fascicle_prop_lost_indepnet_5_percent =
-           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
-  mutate(total_fascicle_prop_lost_nondep_network =
-           rowMeans(across(fascicle_names_nondep_network))) %>%
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  ungroup()
+```
+
+#### Parametric yeo networks
+```{r individual_fascicle_disease_anxiety_dose_yeo}
+#n=371, all correct
+
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) %>%
+  mutate(anxiety_dose_factor = ordered(anxiety_dose))
+
 #lm
-fascicle_lm <- lapply(fascicle_names, function(x) 
+fascicle_lm <- lapply(yeo_network_names_prop, function(x) 
 {
-  lm(substitute(i ~ PHQ.9, list(i = as.name(x))), data = with_phq9)
+  lm(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
 })
-names(fascicle_lm) <- fascicle_names
+names(fascicle_lm) <- yeo_network_names_prop
 
@@
 
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only dep network
-fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
-fascicle_anova_fdr<- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr)
-
-#fdr corrected only dep 10% mask
-fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$inDepNetwork_vector == 2)]
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr)
-
 #uncorrected
 fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_p05_unc <- fascicle_anova_p[!is.na(fascicle_anova_p) & fascicle_anova_p < 0.05]
-print(fascicle_anova_p05_unc)
-
-######### overall fascicle proportion affected - nothing is significant
-overall_prop_affected <- lm(total_fascicle_prop_lost~PHQ.9, data=with_phq9)
-overall_prop_affected_depnet <- lm(total_fascicle_prop_lost_indepnet~PHQ.9, data=with_phq9)
-overall_prop_affected_depnet_10percent <- lm(total_fascicle_prop_lost_indepnet_10_percent~PHQ.9, data=with_phq9)
-overall_prop_affected_depnet_5percent <- lm(total_fascicle_prop_lost_indepnet_5_percent~PHQ.9, data=with_phq9)
-overall_prop_affected_nondep <- lm(total_fascicle_prop_lost_nondep_network~PHQ.9, data=with_phq9)
-
-#visreg
-#sapply(fascicle_lm, visreg)
-```
-All the mixed models are below
-```{r age_effects_indiv_fascicles_mm}
-
-### This subscript compares proportion of fascicles lost across age for each fascicle of the 80+.
-Looks lonly at the people in the depressed versus healthy group.
-Importantly, I ran this looking at everyone, at the results are the same.
-### Separately considers findings just within the association cortex
-
-#isolate out only the depressed group and healthy group
-df_mm <- df_demo_and_fascicles %>% filter(depGroupVar != 0)
-#n depressed = 859, healthy = 604, total n = 1463
-
-#lm
-fascicle_lm_mm <- lapply(fascicle_names, function(x) 
-{
-  lmerTest::lmer(substitute(i ~ PAT_AGE_AT_EXAM + (1 | EMPI), list(i = as.name(x))), data = df_mm)
-})
-names(fascicle_lm_mm) <- fascicle_names
-
-#anova
-fascicle_anova_mm <- lapply(fascicle_lm_mm, anova)
-
-#fdr corrected
-fascicle_anova_mm_fdr <- fdr_anova_generic(fascicle_anova_mm, 1)
-print(fascicle_anova_mm_fdr)#anova values < 0.05, uncorrected
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only dep network
-fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only dep network 10%
-fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$inDepNetwork_vector == 2)]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_anova_mm_p <- sapply(fascicle_anova_mm, function(v) v$"Pr(>F)"[1])
-fascicle_anova_mm_p05_unc <- as.data.frame(fascicle_anova_mm_p[fascicle_anova_mm_p < 0.05])
-print(fascicle_anova_mm_p05_unc)
-
-```
-
-```{r sex_effects_fascicles_mm}
-########### sex effect whole group
-
-#isolate out only the depressed group and healthy group
-dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% filter(depGroupVar != 0) 
-#healthhy = 713, total n = 1106
-
-#### sex histo ###
-hist(dep_and_healthy_groups_for_ICD_analysis$sex_binarized,
-main = paste0("Sex In Good Mimosa Group : n (M/F)= ", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1), "/", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)),  xlab = "Sex", breaks = 2)
-
-#lm
-fascicle_sex_lm <- lapply(fascicle_names, function(x) 
-{
-  lmerTest::lmer(substitute(i ~ osex + (1|EMPI), list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
-})
-names(fascicle_sex_lm) <- fascicle_names
-
-#anova
-fascicle_sex_anova <- lapply(fascicle_sex_lm, anova)
-
-#fdr corrected
-fascicle_sex_anova_fdr <- fdr_anova_generic(fascicle_sex_anova, 1)
-print(fascicle_sex_anova_fdr)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_sex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#visreg
-#sapply(fascicle_sex_lm,visreg)
-```
-
-```{r depressed_versus_healthy_indiv_fascicles_mm}
-
-### This subscript compares proportion of fascicles lost for each fascicle of the 80+ between those in the depressed and the clean healthy group.
-Done as both a mixed model as well as using unique individuals alone.
-
-#Of note, adding age into this model makes things WORSE
-
-### Separately considers findings just within the association cortex
-#isolate out only the depressed group and healthy group
-df_mm <- df_demo_and_fascicles %>% filter(depGroupVar != 0)
-#n depressed = 859, healthy = 604, total n = 1463
-
-#lm
-fascicle_lm_mm <- lapply(fascicle_names, function(x) 
-{
-  lmerTest::lmer(substitute(i ~ depGroupVar + (1 | EMPI), list(i = as.name(x))), data = df_mm)
-})
-names(fascicle_lm_mm) <- fascicle_names
-
-#anova
-fascicle_anova_mm <- lapply(fascicle_lm_mm, anova)
-
-#fdr corrected
-fascicle_anova_mm_fdr <- fdr_anova_generic(fascicle_anova_mm, 1)
-print(fascicle_anova_mm_fdr)#anova values < 0.05, uncorrected
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only dep network
-fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only dep network 10%
-fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$inDepNetwork_vector == 2)]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_anova_mm_p <- sapply(fascicle_anova_mm, function(v) v$"Pr(>F)"[1])
-fascicle_anova_mm_p05_unc <- as.data.frame(fascicle_anova_mm_p[fascicle_anova_mm_p < 0.05])
-print(fascicle_anova_mm_p05_unc)
-
-```
-
-Lastly, this section will explore interactions (age * dep), (sex * dep)
-
-```{r age_by_depression_unique}
-
-#isolate out only the depressed group and healthy group
-dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>%
-  filter(depGroupVar != 0)  %>% 
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  ungroup()
-
-#lm
-fascicle_agedep_lm <- lapply(fascicle_names, function(x) 
-{
-   lm(substitute(i ~ PAT_AGE_AT_EXAM*depGroupVar, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
-# lm(substitute(i ~ depGroupVar + PAT_AGE_AT_EXAM + osex, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
-})
-names(fascicle_agedep_lm) <- fascicle_names
-
-#anova
-fascicle_agedep_anova <- lapply(fascicle_agedep_lm, anova)
-
-#fdr corrected - depression alone
-fascicle_agedep_anova_fdr <- fdr_anova_generic(fascicle_agedep_anova, 2)
-print(fascicle_agedep_anova_fdr)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_agedep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,2)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected - interaction
-fascicle_agedep_anova_fdr <- fdr_anova_generic(fascicle_agedep_anova, 3)
-print(fascicle_agedep_anova_fdr)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_agedep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only dep network
-fascicle_anova_w_fiber_mapping <- fascicle_agedep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only dep network 10%
-fascicle_anova_w_fiber_mapping <- fascicle_agedep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector == 2)]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
-print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_anova_p <- sapply(fascicle_agedep_anova, function(v) v$"Pr(>F)"[3])
 fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
@@
 ```
-
-```{r sex_by_depression_unique}
-
-#isolate out only the depressed group and healthy group
-dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>%
-  filter(depGroupVar != 0)  %>% 
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  ungroup()
-
-#lm
-fascicle_sexdep_lm <- lapply(fascicle_names, function(x) 
-{
-   lm(substitute(i ~ osex*depGroupVar, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
-
-})
-names(fascicle_sexdep_lm) <- fascicle_names
-
-#anova
-fascicle_sexdep_anova <- lapply(fascicle_sexdep_lm, anova)
-
-#fdr corrected - depression alone
-fascicle_sexdep_anova_fdr <- fdr_anova_generic(fascicle_sexdep_anova, 2)
-print(fascicle_sexdep_anova_fdr)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,2)
-print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_anova_p <- sapply(fascicle_sexdep_anova, function(v) v$"Pr(>F)"[2])
-fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
-print(fascicle_anova_p05_unc)
-
-#fdr corrected - interaction
-fascicle_sexdep_anova_fdr <- fdr_anova_generic(fascicle_sexdep_anova, 3)
-print(fascicle_sexdep_anova_fdr)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only dep network
-fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only dep network 10%
-fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector == 2)]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
-print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_anova_p <- sapply(fascicle_sexdep_anova, function(v) v$"Pr(>F)"[3])
-fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
-print(fascicle_anova_p05_unc)
-```
-Interaction models below
-
-```{r sexdep_effects_fascicles_unique}
-
-### Trying to figure out if there are any sex * depression effects, covarying for age given that men tend to get worse over time. dep*sex uncorrected in SLF1_L and CNVIII_R p< 0.05)
-
-#isolate out only the depressed group and healthy group
-dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% filter(depGroupVar != 0)  %>% 
-  group_by(EMPI) %>% 
-  arrange(EXAM_DATE) %>% 
-  slice(1) %>% 
-  ungroup()
-
-#### sex histo ###
-hist(dep_and_healthy_groups_for_ICD_analysis$sex_binarized,
-main = paste0("Sex In Good Mimosa Group : n (M/F)= ", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1), "/", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)),  xlab = "Sex", breaks = 2)
-
-#lm
-fascicle_sexdep_lm <- lapply(fascicle_names, function(x) 
-{
-  lm(substitute(i ~ depGroupVar*osex + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
-})
-names(fascicle_sexdep_lm) <- fascicle_names
-
-#anova
-fascicle_sexdep_anova <- lapply(fascicle_sexdep_lm, anova)
-
-##### depGroupVar ####
-### 12 areas, nearly identical to reg model
-
-#fdr corrected
-fascicle_sexdep_anova_fdr <- fdr_anova_generic(fascicle_sexdep_anova, 1)
-print(fascicle_sexdep_anova_fdr)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_sexdep_anova_p <- sapply(fascicle_sexdep_anova, function(v) v$"Pr(>F)"[1])
-fascicle_sexdep_anova_p05_unc <- as.data.frame(fascicle_sexdep_anova_p[fascicle_sexdep_anova_p < 0.05])
-print(fascicle_sexdep_anova_p05_unc) ### CNVIII p < 0.05
-
-##### sex differences ####
-## same as above, just add in CNVIII_R
-
-#fdr corrected
-fascicle_sexdep_anova_fdr <- fdr_anova_generic(fascicle_sexdep_anova, 2)
-print(fascicle_sexdep_anova_fdr)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,2)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,2)
-print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_sexdep_anova_p <- sapply(fascicle_sexdep_anova, function(v) v$"Pr(>F)"[2])
-fascicle_sexdep_anova_p05_unc <- as.data.frame(fascicle_sexdep_anova_p[fascicle_sexdep_anova_p < 0.05])
-print(fascicle_sexdep_anova_p05_unc) ### CNVIII p < 0.05
-
-#######interaction ####
-
-### SLF1_L and CNVIII_R
-
-#fdr corrected interaction
-fascicle_sexdep_anova_fdr <- fdr_anova_generic(fascicle_sexdep_anova, 4)
-print(fascicle_sexdep_anova_fdr)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,4)
-print(fascicle_anova_fdr_association)
-
-#fdr corrected only association cortex
-fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
-fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,4)
-print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_sexdep_anova_p <- sapply(fascicle_sexdep_anova, function(v) v$"Pr(>F)"[4])
-fascicle_sexdep_anova_p05_unc <- as.data.frame(fascicle_sexdep_anova_p[fascicle_sexdep_anova_p < 0.05])
-print(fascicle_sexdep_anova_p05_unc) #p uncorrected slf1_L p = 0.0488, CNVIII_R 0.01)
-
-### grouped bar and line plot
-
-Diagnosis <- c(rep("Depressed" , 2) , rep("Non-Depressed" , 2))
-Sex <- rep(c("Male" , "Female"), 2)
-value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)]),
-           mean(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)]),
-           mean(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)]),
-           mean(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)]))
-
-sem <- c((sd(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)])/sqrt(sum((dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)))),
-         (sd(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)])/sqrt(sum((dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)))),
-         (sd(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)])/sqrt(sum((dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1)))),
-         (sd(dep_and_healthy_groups_for_ICD_analysis$SLF1_L[(dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)])/sqrt(sum((dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1) & (dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)))))
-
-data <- data.frame(Diagnosis,Sex,value, sem)
-#data$Fascicle <- pretty_names
-
-# Grouped
-barplot <- ggplot(data, aes(fill=Sex, y=value, x=Diagnosis)) + 
-    geom_bar(position="dodge", stat="identity") + 
-    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9)) + 
-  ylab("Proportion of SLF Affected") +
-  theme(axis.text = element_text(size = 12, colour = "black"), axis.title.x = element_blank())
-
-print(barplot)
-
-lineplot <- ggplot(data=data, aes(fill=Sex, y=value, x=Diagnosis, group = Sex)) +
-
-    geom_line(aes(color=Sex, size=0.9)) +
-    geom_point(aes(color=Sex, size=0.9)) +
-    ylim(0.05,0.30)+
-    ylab("Proportion of SLF Affected") +
-    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1) + 
-    theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank())
-
-print(lineplot)
-
-```

### 2024-07-25 scripts/Anxiety_longitudinal_started_20240717.Rmd
Add files via upload

--- 2024-07-17 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
@@
 ---
-title: "MS Prelim Data K23"
+title: "MS Anxiety Longitudinal"
 author: "Erica Baller"
-date: "2/25/2022"
+date: "7/25/2024"
 output:
@@
 
-#get list of unique patients, n = 890
-mimosa_qc_unique <- mimosa_qc_df %>%
-  group_by(EMPI) %>%
-  arrange(EXAM_DATE) %>%
-  slice(1) %>%
-  ungroup #n=890
-
-#get list of unique patients with good QC, n = 867
-mimosa_unique_score_gre_75 <- mimosa_qc_unique %>%
+#get list of scans with good Mimosa, n = 2263
+mimosa_qc_gr_75 <- mimosa_qc_df %>%
   filter(score >= 75) %>%
-  group_by(EMPI) %>%
-  arrange(EXAM_DATE) %>%
   mutate(EXAM_DATA = as.character(EXAM_DATE)) %>%
@@
   dplyr::select(EMPI, EXAM_DATE, score) %>%
-  slice(1) %>%
+  distinct(EMPI, EXAM_DATE, .keep_all = TRUE) %>%
   ungroup 
@@
 
-#n=867, individual scans
+#n=770, 1078 scans total
 df_people_with_good_mimosa <- data_2023_pull %>% 
-  group_by(EMPI, EXAM_DATE) %>%
-  slice(1) %>%
-  left_join(mimosa_unique_score_gre_75, by = c("EMPI", "EXAM_DATE")) %>%
+  distinct(EMPI, EXAM_DATE, .keep_all = TRUE) %>%
+  group_by(EMPI) %>%
+  arrange(EMPI, EXAM_DATE) %>%
+  filter(row_number() <= 2) %>%
+  left_join(mimosa_qc_gr_75, by = c("EMPI", "EXAM_DATE")) %>%
   filter(!is.na(score))
+
+# Check the number of rows per EMPI and keep people with only 2, n scans=616, with n=308 subjects
+df_people_with_2_rows <- df_people_with_good_mimosa %>%
+  group_by(EMPI) %>%
+  filter(n() == 2) %>%
+  ungroup()
+
+# View the result, n = 308, with 616 total scans
+print(df_people_with_2_rows)
+print(length(df_people_with_2_rows$EMPI))
+print(length(unique(df_people_with_2_rows$EMPI)))
 ```
@@
 
- #n = 812
+ #n = 
 df_demo_and_fascicles <- df_people_with_good_mimosa %>% 
@@
   filter(!is.na(Has.MS.Provider)) %>% #remove people who don't have MS provider
-  filter(!is.na(CNII_L)) #this is a sample fascicle that should have a value. if it does not, it means something is usually wrong with whole person. Remove rows with NAs
+  filter(!is.na(CNII_L)) %>%#this is a sample fascicle that should have a value. if it does not, it means something is usually wrong with whole person. Remove rows with NAs
+  group_by(EMPI) %>% # again verify that this only includes people with two days
+  filter(n() == 2) %>%
+  mutate(exam_timepoint = ifelse(row_number() == 1, "t1", "t2"))
+
+#check num unique EMPIs, n = 281
+print(length(unique(df_demo_and_fascicles$EMPI)))
+
+#check total n = 562
+print(length(df_demo_and_fascicles$EMPI))
+
+```
+
+## Check to see the consistency within anxiety dose between t1 and t2
+```{r consistency_of_anxiety}
+# Create a summary to check for consistency, 127 people have two different anxiety doses
+anxiety_dose_check <- df_demo_and_fascicles %>%
+  group_by(EMPI) %>%
+  summarize(
+    unique_doses = n_distinct(anxiety_dose),
+    doses = paste(unique(anxiety_dose), collapse = ", ")
+  ) %>%
+  ungroup()
+
+# Filter to find EMPIs with more than one unique anxiety dose
+inconsistent_doses <- anxiety_dose_check %>%
+  filter(unique_doses > 1)
+
+# Display the result
+inconsistent_doses
+
+#there are some, will take the higher value because if at some point you had disease, it should count as a lifetime history
+df_demo_and_fascicles <- df_demo_and_fascicles %>%
+  group_by(EMPI) %>%
+  mutate(lifetime_max_anxiety_dose = max(anxiety_dose))
+
+#now check inconsistent doses
+# Create a summary to check for consistency, 127 people have two different anxiety doses
+anxiety_dose_check <- df_demo_and_fascicles %>%
+  group_by(EMPI) %>%
+  summarize(
+    unique_doses = n_distinct(lifetime_max_anxiety_dose),
+    doses = paste(unique(anxiety_dose), collapse = ", ")
+  ) %>%
+  ungroup()
+
+# Filter to find EMPIs with more than one unique anxiety dose
+inconsistent_doses <- anxiety_dose_check %>%
+  filter(unique_doses > 1)
+
+# Display the result - nothing there! It worked! Also checked this with my eyeballs
+inconsistent_doses
 
@@
 ##########################################################
-#merge whole data set with fascicle proportions, n = 812
+#merge whole data set with fascicle proportions, n = 809
 df_demo_and_fascicles <- df_demo_and_fascicles %>%
   left_join(lesion_volumes, by = c("EMPI", "EXAM_DATE"))
+
+#check num unique EMPIs, n = 809
+print(length(unique(df_demo_and_fascicles$EMPI)))
+
+#check total n = 1618
+print(length(df_demo_and_fascicles$EMPI))
 
@@
   # mutate(total_fascicle_vol_lost = rowMeans(across(all_of(fascicle_names_w_vol_suffix)))) %>%
-  dplyr::select(EMPI, ends_with("_vol")) %>%
+  dplyr::select(EMPI, EXAM_DATE, ends_with("_vol")) %>%
   ungroup()
@@
 
+# Longitudinal Age*Disease
+
+## Anxiety Diagnosis
+```{r diagnosisXage}
+
+#n healthy = 155 total, 122 unique, +minA = 131
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  mutate(mean_UF_vol = (UF_L_vol + UF_R_vol)/2) %>%
+  mutate(mean_UF_prop = (UF_L_prop + UF_R_prop)/2) %>%
+#  dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol, mean_UF_vol) %>%
+  ungroup()
+
+### diagnosis by age interaction?
+#overall - NS
+diagnosis_by_age <- lmer(proportion_volume_lost_per_total_network_size_sum ~ Diagnosis*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age)
+
+### anxiety net
+diagnosis_by_age_anx_net <- lmer(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ Diagnosis*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age_anx_net)
+
+###nonanxiety net
+diagnosis_by_age_nonanx_net <- lmer(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ Diagnosis*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age_nonanx_net)
+
+### UF_R
+diagnosis_by_age_UF_R <- lmer(UF_R_vol ~ Diagnosis*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age_UF_R)
+
+### UF_L
+diagnosis_by_age_UF_L <- lmer(UF_L_vol ~ Diagnosis*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age_UF_L)
+
+### mean UF
+diagnosis_by_age_mean_UF <- lmer(mean_UF_vol ~ Diagnosis*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age_mean_UF)
+```
+
+## Anxiety Dose
+```{r diagnosisXage}
+#n healthy = 135, +minA = 131, severeA = 60
+
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  mutate(EMPI = as.factor(EMPI)) %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(lifetime_max_anxiety_dose != -1) %>%
+  mutate(anxiety_dose = as.numeric(lifetime_max_anxiety_dose)) %>%
+  mutate(anxiety_dose_factor = ordered(anxiety_dose)) %>%
+  #mean UF
+  mutate(mean_UF_vol = (UF_L_vol + UF_R_vol)/2) %>%
+  mutate(mean_UF_prop = (UF_L_prop + UF_R_prop)/2)
+
+### diagnosis by age interaction?
+#overall - NS
+diagnosis_by_age <- lmer(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age)
+
+diagnosis_by_age_factor <- lmer(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose_factor*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age_factor)
+
+### anxiety net
+diagnosis_by_age_anx_net <- lmer(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age_anx_net)
+
+###nonanxiety net
+diagnosis_by_age_nonanx_net <- lmer(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age_nonanx_net)
+
+### UF_R
+diagnosis_by_age_UF_R <- lmer(UF_R_vol ~ anxiety_dose*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age_UF_R)
+
+### UF_L
+diagnosis_by_age_UF_L <- lmer(UF_L_vol ~ anxiety_dose*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age_UF_L)
+
+### mean UF
+diagnosis_by_age_mean_UF <- lmer(mean_UF_vol ~ anxiety_dose*PAT_AGE_AT_EXAM + (1|EMPI), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(diagnosis_by_age_mean_UF)
+```
+
 ## Anxiety within/outside network interaction
@@
 ### BEST SPLIT IS STRATIFYING ON ANXIETY MEDS!!!! Better than on variable that includes anxietyGroupVar(meds + anxiety diagnoses), or anxiety diagnosis alone
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietyGroupVar != 0,])
-make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$Has.Anxietydx.AND.AntianxietymedGroupVar != 0,])
+#make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
+#make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietyGroupVar != 0,])
+#make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$Has.Anxietydx.AND.AntianxietymedGroupVar != 0,])
 
@@
 #COLLAPSE anxiety dx and antianxiety meds with those plus depression, and anxiety dx OR on anxiety meds into 1 group -->> THIS IS THE MONEY
-### Overlap with depression group
-```{r overlap_with_dep_group}
-
-#read csv of empis from depression paper
-depression_empis <- read.table(file="/Users/eballer/BBL/msanxiety/data/empis_of_people_in_BP_depression_paper.csv")
-names(depression_empis) <- "EMPI"
-
-#get final anxiety dataset and make column if the empi is in the prev list
-df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
-  mutate(EMPI = as.numeric(EMPI)) %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  mutate(EMPI_in_dep_group = EMPI %in% depression_empis$EMPI)
-
- tibble_overall_counts <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
-  group_by(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  summarize(n(),
-            num_in_dep_group = sum(EMPI_in_dep_group),
-            percent_overlap = num_in_dep_group/n())
- tibble_overall_counts
-
-```
-### Overall Disease by Anxiety Dose *acnp
+### Overall Disease by Anxiety Dose
 ```{r group_anxietydx_meds_and_dep_comorbidity}
@@
 
-  #gam, anxiety_dose  , anxiety_dose  0.03505    0.01340   2.616  0.00927 ** 
+  #gam, anxiety_dose  
    anxietyGrouping_nonanxiety_net_gam<- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.0459425  0.0164036   2.801  0.00537 ** 
+  #volume lost in anxiety net by anxiety dose*sex: 
   anxietyGrouping_by_sex_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose*osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #gam, anxiety_dose, anxiety_dose         0.047100   0.016230   2.902  0.00393 **          
+  #gam, anxiety_dose         
   anxietyGrouping_by_sex_nonanxiety_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose*osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #volume lost in anxiety net by anxiety dose + sex + PAT_AGE_AT_EXAM: anxiety_dose     0.0344065  0.0135309   2.543   0.0114 *  
+  #volume lost in anxiety net by anxiety dose + sex + PAT_AGE_AT_EXAM: 
   anxietyGrouping_cov_sex_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #gam, anxiety_dose - anxiety_dose  0.03600    0.01342   2.682  0.00764 ** 
+  #gam, anxiety_dose 
    anxietyGrouping_cov_sex_nonanxiety_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-###Check for polynomial relationships 
+###Check for polynomial relationships - Not finding them w healthy, anxietydx OR meds, anxiety AND meds
 ```{r polynomial_relationships}
- #Not finding them w healthy, anxietydx OR meds, anxiety AND meds
-
   #check for polynomial relationship
@@
 
-### Uncinate by Anxiety Dose *acnp?
+### Uncinate by Anxiety Dose
 ```{r uncinateByAnxietyDose}
@@
   summary(anxietyGrouping_UF_L_by_sex_gam)
-```
-
-##### Laterality in uncinate
-```{r laterality}
-  #laterality 
-  #overall - t = -11.597, df = 1322.2, p-value < 2.2e-16
-  right_vs_left_uncinate <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol, df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol)
-  print(right_vs_left_uncinate)
-
-  #healthy - t = -6.3298, df = 347.5, p-value = 7.577e-10
-   right_vs_left_uncinate_healthy <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0])
-  print(right_vs_left_uncinate_healthy)
-
-  #anxietydx or meds - t = -7.7742, df = 705.18, p-value = 2.694e-14
-  right_vs_left_uncinate_anxiety_or_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1])
-  print(right_vs_left_uncinate_anxiety_or_meds)
-
-  #anxious+meds, t = -5.9638, df = 266.42, p-value = 7.804e-09
-   right_vs_left_uncinate_anxiety_and_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2])
-  print(right_vs_left_uncinate_anxiety_and_meds)
-```
-
-### Fornix by Anxiety Dose
-```{r uncinateByAnxietyDose}
-
-#results: Anxiety dose NOT related to F_R when covarying for linear effects of age and sex, not in line with that one paper that found fornix differences
-
-#define group
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter (anxiety_dose != 3)
-
-########UF R - just looking at fornix by anxiety dose -NS
-  anxietyGrouping_F_R_lm <- lm(F_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_R_lm)
-
-  #gam, anxiety_dose    - NS
-  anxietyGrouping_F_R_gam <- gam(F_R_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_R_gam)
-
-  #UF _ R anxiety_dose     - NS    
-  anxietyGrouping_F_R_by_sex_lm <- lm(F_R_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_R_by_sex_lm)
-
-  #gam, anxiety_dose  - NS 
-    anxietyGrouping_F_R_by_sex_gam <- gam(F_R_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_R_by_sex_gam)
-
-  #UF L - anxiety_dose    - NS 
-  anxietyGrouping_F_L_lm <- lm(F_L_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_L_lm)
-
-   #gam, anxiety_dose    - NS  
-  anxietyGrouping_F_L_gam <- gam(F_L_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_L_gam)
-
-  #F_L anxiety_dose:NS        
-  anxietyGrouping_F_L_by_sex_lm <- lm(F_L_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_L_by_sex_lm)
-
-   #gam, anxiety_dose - NS
-  anxietyGrouping_F_L_by_sex_gam <- gam(F_L_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_L_by_sex_gam)
 ```
@@
   mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
-  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol) %>% 
-  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol, -F_R_vol, -F_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
+  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol) %>% 
+  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
   mutate(Network = as.factor(Network)) %>%
@@
 #do lm UF*Diagnosis
- #UF_R_vol -> DiagnosisMS+Anxiety  1418.26     352.04   4.029 8.20e-05 ***
-disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + osex + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+ #UF_R_vol -> DiagnosisMS+Anxiety  1406.32     350.74   4.010 8.81e-05 ***
+disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
 summary(disease_UF_R_vol_lm)
 
- #UF_L_vol -> DiagnosisMS+Anxiety   737.97     250.61   2.945  0.00365 ** 
-disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+ #UF_L_vol -> DiagnosisMS+Anxiety   728.93     249.71   2.919  0.00395 ** 
+disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
 summary(disease_UF_L_vol_lm)
 
-#Fornix - Right side but not left
- #F_R_vol -> DiagnosisMS+Anxiety   860.50     368.16   2.337   0.0205 * 
-disease_F_R_vol_lm <- lm(F_R_vol ~ Diagnosis + osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_F_R_vol_lm)
-
- #F_L_vol -> DiagnosisMS+Anxiety  329.724    181.609   1.816   0.0711 . 
-disease_F_L_vol_lm <- lm(F_L_vol ~ Diagnosis + osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_F_L_vol_lm)
 ## net by sex
@@
 
-```
-
-### Individual Fascicle disease
-
-#### healthy vs super sick - values that fdr correct, most not anxiety net
-```{r individual_fascicle_disease_healthy_vs_super_sick}
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  mutate(anxiousAndMeds_or_healthy = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  filter(anxiousAndMeds_or_healthy %in% c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>%
-  mutate(anxiousAndMeds_or_healthy = factor(anxiousAndMeds_or_healthy, levels=c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
-
-#lm
-fascicle_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
-{
-  lm(substitute(i ~ anxiousAndMeds_or_healthy + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-})
-names(fascicle_lm) <- fascicle_names_w_prop_suffix
-
-#anova
-fascicle_anova <- lapply(fascicle_lm, anova)
-
-#fdr corrected
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
-print(fascicle_anova_fdr)
-
-#fdr corrected only association cortex
-#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-#print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
-print(fascicle_anova_p05_unc) 
-```
-
-#### Parametric all fascicles
-```{r individual_fascicle_disease_healthy_vs_super_sick}
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != 3) %>%
-  mutate(anxiety_dose_factor = ordered(anxiety_dose))
-
-#lm
-fascicle_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
-{
-  lm(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-})
-names(fascicle_lm) <- fascicle_names_w_prop_suffix
-
-#anova
-fascicle_anova <- lapply(fascicle_lm, anova)
-
-#fdr corrected
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
-print(fascicle_anova_fdr)
-
-#fdr corrected only association cortex
-#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-#print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
-print(fascicle_anova_p05_unc) 
-```
-#### Parametric anxiety net fascicles
-```{r individual_fascicle_disease_healthy_vs_super_sick}
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != 3) %>%
-  mutate(anxiety_dose_factor = ordered(anxiety_dose))
-
-#lm
-fascicle_lm <- lapply(fascicle_names_top_25_prop_w_suff, function(x) 
-{
-  lm(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-})
-names(fascicle_lm) <- fascicle_names_top_25_prop_w_suff
-
-#anova
-fascicle_anova <- lapply(fascicle_lm, anova)
-
-#fdr corrected
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
-print(fascicle_anova_fdr)
-
-#fdr corrected only association cortex
-#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-#print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
-print(fascicle_anova_p05_unc) 
-```
-
-#### Parametric nonanxiety net fascicles
-```{r individual_fascicle_disease_healthy_vs_super_sick}
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != 3) %>%
-  mutate(anxiety_dose_factor = ordered(anxiety_dose))
-
-#lm
-fascicle_lm <- lapply(fascicle_names_bottom_75_prop_w_suff, function(x) 
-{
-  lm(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-})
-names(fascicle_lm) <- fascicle_names_bottom_75_prop_w_suff
-
-#anova
-fascicle_anova <- lapply(fascicle_lm, anova)
-
-#fdr corrected
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
-print(fascicle_anova_fdr)
-
-#fdr corrected only association cortex
-#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-#print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
-print(fascicle_anova_p05_unc) 
 ```

### 2024-07-25 scripts/clean_dac_pull_icd10_codes_and_make_clean_df.R

@@ -88,7 +88,10 @@ psych_meds <- read.csv("/Users/eballer/BBL/medication_data/nami_psych_meds_antid
 psych_meds$Medication.Name <- toupper(psych_meds$Medication.Name)
 
 #depression/psych meds from NAMI website + neurontin, gabapentin, elavil, amitriptyline
-psych_meds_extended <- read.csv("/Users/eballer/BBL/medication_data/nami_psych_meds_antidepressants_plus_gabapentin_and_amitriptyline.csv", sep = ",", header = TRUE)
+#psych_meds_extended <- read.csv("/Users/eballer/BBL/medication_data/nami_psych_meds_antidepressants_plus_gabapentin_and_amitriptyline.csv", sep = ",", header = TRUE)
+
+#psych meds from NAMI + medications used for anxiety (neurontin/gabapentin, elavil/amitriptyline, propranolol, nortriptyline/pamelor)
+psych_meds_extended <- read.csv("/Users/eballer/BBL/medication_data/nami_psych_meds_antidepressants_plus_gabapentin_and_amitriptyline_benzos_beta_blockers.csv", sep = ",", header = TRUE)
 psych_meds_extended$Medication.Name <- toupper(psych_meds_extended$Medication.Name)
 
 
@@ -169,19 +172,24 @@ data_final_rds <-data_pull %>%
   mutate(oAnxietydx.Meds.Inc.Dep.Collapsed = ordered(Anxietydx.Meds.And.Dep.Collapsed, levels = c("healthy_ish", "Has.anxietydx", "On.Anxiolytics", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep", "unclassified"))) %>%
   
   #make groups with true healthy to try to pull out the best patients
[…]

### 2024-07-25 scripts/ms_functions.R

@@ -50,8 +50,8 @@ make_demographics_table_ms_anxiety_simple<- function(data_frame) {
   
   
   #for_parse <- paste0("data.frame(data_frame$race_binarized, data_frame$sex_binarized, data_frame$PAT_AGE_AT_EXAM, data_frame$depGroupVar, data_frame$PHQ.2, data_frame$PHQ.9)")
+  # for_parse <- paste0(data.frame(data_frame$race_binarized,
   for_parse <- paste0("data.frame(data_frame$RACE, 
- # for_parse <- paste0("data.frame(data_frame$race_binarized,
                       data_frame$sex_binarized, 
                       data_frame$PAT_AGE_AT_EXAM, 
                       data_frame$Has.anxietydx, 

### 2024-07-26 scripts/ACNP2024_MSAnxiety.Rmd
fixed indiv fascicle analyses

@@
   summary(anxietyGrouping_mean_UF_by_sex_gam)
+
 ```
@@
 #anova
-fascicle_anova <- lapply(fascicle_lm, anova)
+fascicle_lm_anova <- lapply(fascicle_lm, anova)
+
+#uncorrected
+fascicle_anova_lm_p <- sapply(fascicle_lm_anova, function(v) v$"Pr(>F)"[1])
+fascicle_anova_lm_p05_unc <- as.data.frame(fascicle_anova_lm_p[fascicle_anova_lm_p < 0.05])
+print(fascicle_anova_lm_p05_unc)
 
 #fdr corrected
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
-print(fascicle_anova_fdr)
-
-#fdr corrected only association cortex
-#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-#print(fascicle_anova_fdr_association)
+fascicle_anova_lm_fdr <- fdr_anova_generic(fascicle_lm_anova, 1, print_unc_df = TRUE)
+print(fascicle_anova_lm_fdr)
+
+#gam
+fascicle_gam <- lapply(fascicle_names_w_prop_suffix, function(x) 
+{
+  gam(substitute(i ~ anxiousAndMeds_or_healthy + +osex+ s(PAT_AGE_AT_EXAM, k=4, fx=F), list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+})
+names(fascicle_gam) <- fascicle_names_w_prop_suffix
+
+#anova
+fascicle_anova_gam <- lapply(fascicle_gam, anova)
 
 #uncorrected
-fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
-print(fascicle_anova_p05_unc) 
+fascicle_anova_gam_p <- sapply(fascicle_anova_gam, function(v) v$p.pv[2])
+print(as.data.frame(fascicle_anova_gam_p))
+fascicle_anova_gam_p05_unc <- as.data.frame(fascicle_anova_gam_p[fascicle_anova_gam_p < 0.05])
+print(fascicle_anova_gam_p05_unc)
+
+#fdr corrected
+fascicle_anova_gam_fdr <- round(p.adjust(fascicle_anova_gam_p, method = "fdr"),3)
+fascicle_anova_gam_fdr_p05 <- as.data.frame(fascicle_anova_gam_fdr[fascicle_anova_gam_fdr < 0.05])
+print(fascicle_anova_gam_fdr_p05) 
 ```
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != 3) %>%
+  filter(anxiety_dose != -1) %>%
   mutate(anxiety_dose_factor = ordered(anxiety_dose))
@@
 {
-  lm(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+  lm(substitute(i ~ anxiety_dose + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
 })
@@
 #anova
-fascicle_anova <- lapply(fascicle_lm, anova)
+fascicle_anova_lm <- lapply(fascicle_lm, anova)
 
 #fdr corrected
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
-print(fascicle_anova_fdr)
-
-#fdr corrected only association cortex
-#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-#print(fascicle_anova_fdr_association)
+fascicle_anova_lm_fdr <- fdr_anova_generic(fascicle_lm_anova, 1, print_unc_df = TRUE)
+print(fascicle_anova_lm_fdr)
 
 #uncorrected
-fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
-print(fascicle_anova_p05_unc) 
-```
-#### Parametric anxiety net fascicles
+fascicle_anova_lm_p <- sapply(fascicle_anova_lm, function(v) v$"Pr(>F)"[1])
+fascicle_anova_lm_p05_unc <- as.data.frame(fascicle_anova_lm_p[fascicle_anova_lm_p < 0.05])
+print(fascicle_anova_lm_p05_unc)
+
+#gam
+fascicle_gam <- lapply(fascicle_names_w_prop_suffix, function(x) 
+{
+  print(x)
+  gam(substitute(i ~ anxiety_dose + osex+s(PAT_AGE_AT_EXAM, k=4, fx=F), list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+})
+names(fascicle_gam) <- fascicle_names_w_prop_suffix
+
+#anova
+fascicle_anova_gam <- lapply(fascicle_gam, anova)
+
+#uncorrected
+fascicle_anova_gam_p <- sapply(fascicle_anova_gam, function(v) v$p.pv[2])
+print(as.data.frame(fascicle_anova_gam_p))
+fascicle_anova_gam_p05_unc <- as.data.frame(fascicle_anova_gam_p[fascicle_anova_gam_p < 0.05])
+print(fascicle_anova_gam_p05_unc)
+
+#fdr corrected
+fascicle_anova_gam_fdr <- round(p.adjust(fascicle_anova_gam_p, method = "fdr"),3)
+fascicle_anova_gam_fdr_p05 <- as.data.frame(fascicle_anova_gam_fdr[fascicle_anova_gam_fdr < 0.05])
+print(fascicle_anova_gam_fdr_p05) 
+```
+#### Parametric anxiety net fascicles -> needs GAM
 ```{r indiv_fascicle_anxiety_net_anxiety_dose}
@@
 
-#fdr corrected only association cortex
-#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-#print(fascicle_anova_fdr_association)
-
 #uncorrected
@@
 
-#### Parametric nonanxiety net fascicles
+#### Parametric nonanxiety net fascicles --> Needs gam
 ```{r nonanxiety_net_anxiety_dose}

### 2024-07-26 scripts/ms_functions.R

@@ -1125,7 +1125,7 @@ cohen_d_allpairs <- function(data_frame, measure, hydra_cluster) {
 }
 
 
-fdr_anova <- function(data_frame) {
+fdr_anova <- function(data_frame, print_unc_df = FALSE) {
   models_anova <- lapply(data_frame, summary)
   
   #Pull p-values
@@ -1136,7 +1136,9 @@ fdr_anova <- function(data_frame) {
   
   #print BEFORE FDR correction 
   #print("Anova scores, BEFORE FDR correction: i.e., uncorrected")
-  print(p_anova)
+  if (print_unc_df == TRUE){
+    print(p_anova)
+  }
   
   #Print original p-values to three decimal places
   p_round_anova <- round(p_anova,3)
@@ -1166,7 +1168,7 @@ fdr_anova <- function(data_frame) {
   
 }
 
-fdr_anova_generic <- function(data_frame, item_index ) {
+fdr_anova_generic <- function(data_frame, item_index, print_unc_df = FALSE) {
   models_anova <- lapply(data_frame, summary)
   
   #Pull p-values
@@ -1177,7 +1179,9 @@ fdr_anova_generic <- function(data_frame, item_index ) {
   
   #print BEFORE FDR correction 
   #print("Anova scores, BEFORE FDR correction: i.e., uncorrected")
-  print(p_anova)
+  if(print_unc_df == TRUE) {
+    print(p_anova)
+  }
   
   #Print original p-values to three decimal places
   p_round_anova <- round(p_anova,3)

### 2024-07-26 scripts/ACNP2024_MSAnxiety.Rmd
Add files via upload

@@
 
-  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.059732   0.020184   2.959  0.00328 ** 
+  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.057403   0.020404   2.813  0.00517 ** 
   anxietyGrouping_by_sex_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose*osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #gam, anxiety_dose, anxiety_dose         0.047100   0.016230   2.902  0.00393 **          
+  #gam, anxiety_dose, anxiety_dose      anxiety_dose         0.059732   0.020184   2.959  0.00328 **        
   anxietyGrouping_by_sex_nonanxiety_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose*osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 ```
-#### Uncinate by diagnosis 
+
+#### Uncinate by anxiety diagnosis 
 ```{r uncinate_by_dx}
@@
 #define group
-  df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
+  uncinate_by_dx_df <- df_demo_and_fascicles %>%
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
@@
   mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol, mean_UF_vol) %>%
+ # dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol, mean_UF_vol) %>%
   ungroup() #n=122
@@
  #UF_R_vol -> DiagnosisMS+Anxiety  1019.03     535.20   1.904   0.0593 .  
-disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + osex + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + osex + PAT_AGE_AT_EXAM, data = uncinate_by_dx_df)
 summary(disease_UF_R_vol_lm)
@@
  #UF_L_vol ->DiagnosisMS+Anxiety   729.21     389.80   1.871  0.06386 .    
-disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = uncinate_by_dx_df)
 summary(disease_UF_L_vol_lm)
@@
 #bilat: DiagnosisMS+Anxiety   874.12     412.30   2.120   0.0361 * 
-disease_mean_UF_vol_lm <- lm(mean_UF_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
+disease_mean_UF_vol_lm <- lm(mean_UF_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = uncinate_by_dx_df)
 summary(disease_mean_UF_vol_lm)
@@
 #UF_R_vol -> DiagnosisMS+Anxiety  1019.03     535.20   1.904   0.0593 .   
-disease_UF_R_vol_gam <- gam(UF_R_vol ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = df_empi_dx_network_proportions)
+disease_UF_R_vol_gam <- gam(UF_R_vol ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
 summary(disease_UF_R_vol_gam)
@@
  #UF_L_vol -> DiagnosisMS+Anxiety    675.7      381.3   1.772    0.079 .  
-disease_UF_L_vol_gam <- gam(UF_L_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = df_empi_dx_network_proportions)
+disease_UF_L_vol_gam <- gam(UF_L_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
 summary(disease_UF_L_vol_gam)
@@
 #bilateral UF: DiagnosisMS+Anxiety    866.7      411.9   2.104   0.0375 *  
-disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = df_empi_dx_network_proportions)
+disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
 summary(disease_mean_UF_vol_gam)
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter (anxiety_dose != -1) #n=371
+  filter(anxiety_dose != -1) #n=371
 
@@
 
+  ## UF_R ##
+
   #UF _ R  anxiety_dose    430.3      240.4    1.79   0.0742 .  
@@
   #R anxiety dose + sex + age: anxiety_dose    439.8      241.0   1.825   0.0689 .  
-
   anxietyGrouping_UF_R_by_sex_gam <- gam(UF_R_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_UF_R_by_sex_gam)
+
+  ## UF_L ##
 
@@
 
-  #bilat
+  ## bilat ##
 
@@
   #bilat anxiety dose + sex + age: anxiety_dose    394.7      185.7   2.126   0.0342 * 
-
   anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-##### Laterality in uncinate
+###### Laterality in uncinate
 ```{r laterality}
@@
 
-  #anxietydx or meds -t = -6.517, df = 441.79, p-value = 1.96e-10
+  #anxietydx or meds -t = -6.5586, df = 443.4, p-value = 1.516e-10
   right_vs_left_uncinate_anxiety_or_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1])
@@
 
-### Fornix by Anxiety Dose
+#### Sensitivity
+###### UF by depGroupVar (N.S)
+```{r UF_by_depGroupVar}
+# Specificity - want to make sure the UF findings are specific to anxiety, so check to see if same findings exist in depression
+### Reviewed previous pull from BP paper, finding was also consistent there -> no diff in uncinate in depressed vs non depressed
+
+df_dep <- df_demo_and_fascicles %>%
+  filter(depGroupVar != 0) %>%
+  mutate(depDiagnosis = as.factor(ifelse(depGroupVar ==2, "MS+Depression", "MS+noDepression")))
+
+table(df_dep$depDiagnosis) #MS+Dep n = 199; MS+noDep n = 99
+
+# UF_L, P = NS
+dep_UF_L_gam <- gam(UF_L_vol ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
+summary(dep_UF_L_gam)
+
+#UF_R, P = NS
+dep_UF_R_gam <- gam(UF_R_vol ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
+summary(dep_UF_R_gam)
+
+#mean UF, P = NS
+dep_mean_UF_gam <- gam(mean_UF_vol ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
+summary(dep_mean_UF_gam)
+
+```
+
+###### Fornix by Anxiety Dose (N.S)
 ```{r fornixByAnxietyDose}
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter (anxiety_dose != 3)
-
-########UF R - just looking at fornix by anxiety dose -NS
-  anxietyGrouping_F_R_lm <- lm(F_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_R_lm)
-
-  #gam, anxiety_dose    - NS
-  anxietyGrouping_F_R_gam <- gam(F_R_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_R_gam)
-
-  #UF _ R anxiety_dose     - NS    
-  anxietyGrouping_F_R_by_sex_lm <- lm(F_R_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_R_by_sex_lm)
-
-  #gam, anxiety_dose  - NS 
+  filter(anxiety_dose != -1) %>%
+  mutate(mean_fornix_volume = (F_R_vol+F_L_vol)/2)
+
+  #gam, Fornix R anxiety_dose  - NS 
   anxietyGrouping_F_R_by_sex_gam <- gam(F_R_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #UF L - anxiety_dose    - NS 
-  anxietyGrouping_F_L_lm <- lm(F_L_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_L_lm)
-
-   #gam, anxiety_dose    - NS  
-  anxietyGrouping_F_L_gam <- gam(F_L_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_L_gam)
-
-  #F_L anxiety_dose:NS        
-  anxietyGrouping_F_L_by_sex_lm <- lm(F_L_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_L_by_sex_lm)
-
-   #gam, anxiety_dose - NS
+  #gam, Fornix L anxiety_dose - NS
   anxietyGrouping_F_L_by_sex_gam <- gam(F_L_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_F_L_by_sex_gam)
+
+  #gam, Fornix mean anxiety_dose - NS
+  anxietyGrouping_mean_F_by_sex_gam <- gam(mean_fornix_volume ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_mean_F_by_sex_gam)
+```
+
+#### Plots Uncinate R,L,mean Prop
+```{r plots_uncinate}
+  #proportion injured over R Uncinate prop
+  # Of note, PROP AND VOL ARE LINEARLY RELATED -> USE PROP FOR ANALYSIS OTHERWISE THE GRAPHS BECOME CONFUSING TO LOOK AT. PROP is proportion of total fascicle injury
+
+#n=371
+df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1)
+
+prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_R_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot
+
+ #proportion injured over R Uncinate prop - geom_bar
+means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
+
+df_UF_R_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
+
+names(df_UF_R_mean_by_anxiety_dose) <- c("mean_UF_R", "Anxiety_dose")
+
+df_UF_R_mean_by_anxiety_dose <- df_UF_R_mean_by_anxiety_dose %>%
+  mutate(mean_UF_R = as.numeric(mean_UF_R)) %>%
+  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
+
+prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_UF_R_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_R, fill=Anxiety_dose)) +
+  geom_bar(stat="identity") +  
+  ylim(0,0.5)+
+#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
+        panel.background = element_rect(colour = "white", fill = "white"))
+prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
+
+  #proportion injured over L Uncinate prop
+prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_L_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot
+
+ #proportion injured over L Uncinate prop - geom_bar
+means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
+
+df_UF_L_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
+
+names(df_UF_L_mean_by_anxiety_dose) <- c("mean_UF_L", "Anxiety_dose")
+
+df_UF_L_mean_by_anxiety_dose <- df_UF_L_mean_by_anxiety_dose %>%
+  mutate(mean_UF_L = as.numeric(mean_UF_L)) %>%
+  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
+
+prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_UF_L_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_L, fill=Anxiety_dose)) +
+  geom_bar(stat="identity") +  
+  ylim(0,0.5)+
+#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
+        panel.background = element_rect(colour = "white", fill = "white"))
+prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
+
+#mean UF
+
+  #proportion injured over mean Uncinate prop
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=mean_UF_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
+  geom_violin() +  
+  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
+
+ #proportion injured over mean Uncinate prop - geom_bar
+means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$mean_UF_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$mean_UF_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
+                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$mean_UF_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
+
+df_mean_UF_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
+
+names(df_mean_UF_mean_by_anxiety_dose) <- c("mean_UF_mean", "Anxiety_dose")
+
+df_mean_UF_mean_by_anxiety_dose <- df_mean_UF_mean_by_anxiety_dose %>%
+  mutate(mean_UF_mean = as.numeric(mean_UF_mean)) %>%
+  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
+
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_mean_UF_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_mean, fill=Anxiety_dose)) +
+  geom_bar(stat="identity") +  
+  ylim(0,0.5)+
+#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
+        panel.background = element_rect(colour = "white", fill = "white"))
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
 ```
@@
 
-### Diag Effect Size * Fascicle anxiety net overlap (from depression analysis) - NOT SIG both vol and prop, only vol shown here
+### Diag Effect Size * Fascicle anxiety net overlap (from depression analysis) 
+#### Make data frame 
 ```{r dxEffSizeOverlapwithAnxietyNet}
@@
 
-#### Plot effect size x Anxiety net overlap - N.S. (including if I drop all fascicles with no overlap)
+#### Plot EfSize x Anxiety net overlap - N.S. 
 ``` {r plot_scatter}
@@
 
+#N.S., (including if I drop all fascicles with no overlap)
 #combine data frames, column 1 has names of fascicles, column 2 has Volume of overlap with anxiety network, column 3 has t-test value of anxiety vs healthy unc, 4th anxiety vs healthy fdr corrected within that fascicle
@@
 #remove values that have no overlap
-df_fascicle_anxiety_mask_volume_overlap_effsize_value <- df_fascicle_anxiety_mask_volume_overlap_effsize_value %>% filter(volume_in_anxiety_mask > 0)
+#df_fascicle_anxiety_mask_volume_overlap_effsize_value <- df_fascicle_anxiety_mask_volume_overlap_effsize_value %>% filter(volume_in_anxiety_mask > 0)
 
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != 3) %>%
+  filter(anxiety_dose != -1) %>%
   mutate(anxiety_dose_factor = ordered(anxiety_dose)) %>%
@@
 
-#gam dose
+#gam dose; s(PAT_AGE_AT_EXAM):anxiety_dose 3.046783 3.441174 5.334908 0.001092626
 diagnosis_by_age_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 #gam factor - there is a linear dose effect per network size sum, as well as a sig age by anxiety relationship, but only in sick people
+#anxiety_dose_factor.L  0.08111    0.03267   2.482   0.0135 * 
+#(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.457  1.762 5.730  0.0139 *
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.927  2.326 1.924  0.1394  
 diagnosis_by_age_gam_factor <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 ####. within/outside anxiety network #######
-#dose
+#dose, s(PAT_AGE_AT_EXAM):anxiety_dose 2.842  3.231 4.792 0.00242 **
 diagnosis_by_age_anx_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 #factor
+#anxiety_dose_factor.L  0.09073    0.03830   2.369   0.0184 * 
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.000  1.000 8.158 0.00453 **
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.816  2.208 1.651 0.19973  
 diagnosis_by_age_anx_net_gam_factor <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 ##dose
+#s(PAT_AGE_AT_EXAM):anxiety_dose 3.19  3.577 5.659 0.000746 ***
 diagnosis_by_age_nonanx_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 #factor
-
+#anxiety_dose_factor.L  0.07359    0.02950   2.495    0.013 * 
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.703  2.071 4.247  0.0136 *
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 2.003  2.403 2.034  0.1110  
 diagnosis_by_age_nonanx_net_gam_factor <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 #dose
+#s(PAT_AGE_AT_EXAM):anxiety_dose 2.006  2.013 7.36 0.00071 ***
 diagnosis_by_age_UF_R_gam <- gam(UF_R_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 
-#factor
+#factor, only sig is smooth
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.127  1.242 12.824 0.000293 ***
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.002  1.003  0.538 0.463889    
 diagnosis_by_age_UF_R_gam_factor <- gam(UF_R_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 #dose
+#s(PAT_AGE_AT_EXAM):anxiety_dose   2      2 4.635  0.0103 *
 diagnosis_by_age_UF_L_gam <- gam(UF_L_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 #factor
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.001  1.002 13.507 0.000271 ***
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.007  1.014  0.611 0.432612    
 diagnosis_by_age_UF_L_gam_factor <- gam(UF_L_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 #dose
-
+#s(PAT_AGE_AT_EXAM):anxiety_dose   2  2.001 7.423 0.00069 ***
 diagnosis_by_age_mean_UF_gam <- gam(mean_UF_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 #factor
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.002  1.004 17.439 3.73e-05 ***
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.002  1.004  0.014    0.913   
 diagnosis_by_age_mean_UF_gam_factor <- gam(mean_UF_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 #lm
-fascicle_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
+fascicle_lm <- lapply(fascicle_names_w_vol_suffix, function(x) 
 {
@@
 })
-names(fascicle_lm) <- fascicle_names_w_prop_suffix
+names(fascicle_lm) <- fascicle_names_w_vol_suffix
 
@@
 #gam
-fascicle_gam <- lapply(fascicle_names_w_prop_suffix, function(x) 
+fascicle_gam <- lapply(fascicle_names_w_vol_suffix, function(x) 
 {
@@
 })
-names(fascicle_gam) <- fascicle_names_w_prop_suffix
+names(fascicle_gam) <- fascicle_names_w_vol_suffix
 
@@
 #fdr corrected
-fascicle_anova_lm_fdr <- fdr_anova_generic(fascicle_lm_anova, 1, print_unc_df = TRUE)
+fascicle_anova_lm_fdr <- fdr_anova_generic(fascicle_anova_lm, 1, print_unc_df = TRUE)
 print(fascicle_anova_lm_fdr)
@@
 #gam
-fascicle_gam <- lapply(fascicle_names_w_prop_suffix, function(x) 
+fascicle_gam <- lapply(fascicle_names_w_vol_suffix, function(x) 
 {
-  print(x)
   gam(substitute(i ~ anxiety_dose + osex+s(PAT_AGE_AT_EXAM, k=4, fx=F), list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
 })
-names(fascicle_gam) <- fascicle_names_w_prop_suffix
+names(fascicle_gam) <- fascicle_names_w_vol_suffix
 
@@
 ```
-#### Parametric anxiety net fascicles -> needs GAM
+#### Parametric anxiety net fascicles 
 ```{r indiv_fascicle_anxiety_net_anxiety_dose}
@@
 
-#lm
-fascicle_lm <- lapply(fascicle_names_top_25_prop_w_suff, function(x) 
+#gam
+fascicle_gam <- lapply(fascicle_names_top_25_vol_w_suff, function(x) 
 {
-  lm(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+  gam(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + osex+s(PAT_AGE_AT_EXAM, k=4, fx=F), list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
 })
-names(fascicle_lm) <- fascicle_names_top_25_prop_w_suff
+names(fascicle_gam) <- fascicle_names_top_25_vol_w_suff
 
 #anova
-fascicle_anova <- lapply(fascicle_lm, anova)
+fascicle_anova_gam <- lapply(fascicle_gam, anova)
+
+#uncorrected
+fascicle_anova_gam_p <- sapply(fascicle_anova_gam, function(v) v$p.pv[2])
+print(as.data.frame(fascicle_anova_gam_p))
+fascicle_anova_gam_p05_unc <- as.data.frame(fascicle_anova_gam_p[fascicle_anova_gam_p < 0.05])
+print(fascicle_anova_gam_p05_unc)
 
 #fdr corrected
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
-print(fascicle_anova_fdr)
-
-#uncorrected
-fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
-print(fascicle_anova_p05_unc) 
-```
-
-#### Parametric nonanxiety net fascicles --> Needs gam
+fascicle_anova_gam_fdr <- round(p.adjust(fascicle_anova_gam_p, method = "fdr"),3)
+fascicle_anova_gam_fdr_p05 <- as.data.frame(fascicle_anova_gam_fdr[fascicle_anova_gam_fdr < 0.05])
+print(fascicle_anova_gam_fdr_p05)
+
+```
+
+#### Parametric nonanxiety net fascicles 
 ```{r nonanxiety_net_anxiety_dose}
 
-# 2 FDR corr sig: C_FP_R_prop	0.048			DRTT_R_prop	0.048
+# 23  sig things
 
@@
 
-#lm
-fascicle_lm <- lapply(fascicle_names_bottom_75_prop_w_suff, function(x) 
+#gam
+fascicle_gam <- lapply(fascicle_names_bottom_75_prop_w_suff, function(x) 
 {
-  lm(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+  gam(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + osex+s(PAT_AGE_AT_EXAM, k=4, fx=F), list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
 })
-names(fascicle_lm) <- fascicle_names_bottom_75_prop_w_suff
+names(fascicle_gam) <- fascicle_names_bottom_75_prop_w_suff
 
 #anova
-fascicle_anova <- lapply(fascicle_lm, anova)
+fascicle_anova_gam <- lapply(fascicle_gam, anova)
+
+#uncorrected
+fascicle_anova_gam_p <- sapply(fascicle_anova_gam, function(v) v$p.pv[2])
+print(as.data.frame(fascicle_anova_gam_p))
+fascicle_anova_gam_p05_unc <- as.data.frame(fascicle_anova_gam_p[fascicle_anova_gam_p < 0.05])
+print(fascicle_anova_gam_p05_unc)
 
 #fdr corrected
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
-print(fascicle_anova_fdr)
-
-#fdr corrected only association cortex
-#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-#print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
-print(fascicle_anova_p05_unc) 
+fascicle_anova_gam_fdr <- round(p.adjust(fascicle_anova_gam_p, method = "fdr"),3)
+fascicle_anova_gam_fdr_p05 <- as.data.frame(fascicle_anova_gam_fdr[fascicle_anova_gam_fdr < 0.05])
+print(fascicle_anova_gam_fdr_p05) 
 ```
@@
 #n = 371
+
+df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>% 
+  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, C_FPH_R_prop, C_FP_R_prop,DRTT_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)
+
 prop_injured_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x= oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed , y=proportion_volume_lost_per_total_network_size_sum, fill= oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed )) +
@@
 prop_injured_nonanxiety_net_by_anxiety_burden_collapsed_vars_plot
-```
-
-##### Plots Uncinate R& L Prop
-```{r plots_uncinate}
-  #proportion injured over R Uncinate prop
-#n=371
-prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_R_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot
-
- #proportion injured over R Uncinate prop - geom_bar
-means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
-
-df_UF_R_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
-
-names(df_UF_R_mean_by_anxiety_dose) <- c("mean_UF_R", "Anxiety_dose")
-
-df_UF_R_mean_by_anxiety_dose <- df_UF_R_mean_by_anxiety_dose %>%
-  mutate(mean_UF_R = as.numeric(mean_UF_R)) %>%
-  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
-
-prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_UF_R_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_R, fill=Anxiety_dose)) +
-  geom_bar(stat="identity") +  
-  ylim(0,0.5)+
-#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
-        panel.background = element_rect(colour = "white", fill = "white"))
-prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
-
-  #proportion injured over L Uncinate prop
-prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_L_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot
-
- #proportion injured over R Uncinate prop - geom_bar
-means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
-
-df_UF_L_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
-
-names(df_UF_L_mean_by_anxiety_dose) <- c("mean_UF_L", "Anxiety_dose")
-
-df_UF_R_mean_by_anxiety_dose <- df_UF_L_mean_by_anxiety_dose %>%
-  mutate(mean_UF_L = as.numeric(mean_UF_L)) %>%
-  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
-
-prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_UF_R_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_L, fill=Anxiety_dose)) +
-  geom_bar(stat="identity") +  
-  ylim(0,0.5)+
-#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
-        panel.background = element_rect(colour = "white", fill = "white"))
-prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
 ```

### 2024-08-09 scripts/clean_dac_pull_icd10_codes_and_make_clean_df.R
Add files via upload

@@ -47,8 +47,8 @@ output_file <- paste0(homedir, "/data/data_2023_pull_with_curated_icd10_codes.rd
 data_pt1 <- read.csv(paste0(homedir, "/data/dac/investigatingpatientsms2010to2023_full_psych_codes_pt1.csv"), sep = ",", header = TRUE) 
 data_pt2 <- read.csv(paste0(homedir, "/data/dac/investigatingpatientsms2010to2023_full_psych_codes_pt2.csv"), sep = ",", header = TRUE) 
 
-#dac pull with ms providers, will need to have victoria update this.
-dac_pull_2021_with_ms_providers <- read.csv("/Users/eballer/BBL/msdepression/data/dac/investigatingdepressioninmspatients_dates_right_format.csv", sep = ",", header = TRUE)
+#dac pull with ms providers
+dac_pull_2021_with_ms_providers <- read.csv(paste0(homedir, "/data/dac/investigatingdepressioninmspatients_dates_right_format.csv"), sep = ",", header = TRUE)
 empi_and_provider <- dac_pull_2021_with_ms_providers %>% dplyr::select(EMPI, Provider) %>% mutate(EMPI = as.character(EMPI))
 
 #msproviders

### 2024-08-09 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
Add files via upload

--- 2024-07-26 scripts/ACNP2024_MSAnxiety.Rmd
@@
 
-Final N demographics
-
-(unique, with good MIMoSA):
+Groups:
+1. Total unique individuals who also have MS - 1026
+2. Total unique who had good MIMoSA - 867 (lost 159)
+3. Remove people without MS provider, n=823 (lost 44)
+4. Remove people with bad streamline filtering, n=854 (lost 13)
+5. Remove people without MS provider, n=812 (lost 42)
 
@@
   summary(disease_mean_UF_vol_lm)
-#findings
 
@@
 
-#open Rds
+#open Rds, n=51238
 data_2023_pull <- readRDS(paste0(homedir, "/data/data_2023_pull_with_curated_icd10_codes.rds"))
@@
 
-#1 Total unique individuals who also have MS - 890
-#2 Total unique who had good MIMoSA - 786
-#3 Total unique with bad MIMoSA - 890-786 = 104
-#4 Total lost in streamline filtering - 3
-#5 Final N going into inclusion/exclusion - 783
-
 #read in mimosa data
-mimosa_qc <- read.csv("/Users/eballer/BBL/msdepression/data/melissa_martin_files/csv/mimosa_dataframe", sep = ",", header = FALSE) #n=2840
-
-#preprocess data frame to extract dates, empis, and score
+mimosa_qc <- read.csv("/Users/eballer/BBL/msdepression/data/melissa_martin_files/csv/mimosa_dataframe", sep = ",", header = FALSE) #n=2841
+
+#preprocess data frame to extract dates, empis, and score, n=2841
 empis_with_qc <- mimosa_qc %>% 
@@
 #merge with whole data frame to make sure we exclude people w/out MS
-mimosa_qc_df <- merge(data_2023_pull, empis_with_qc, by = c("EMPI", "EXAM_DATE")) #n = 3592
-
-#get list of unique patients, n = 890
+mimosa_qc_df <- merge(data_2023_pull, empis_with_qc, by = c("EMPI", "EXAM_DATE")) #n = 11252
+
+#get list of unique patients, n = 1026
 mimosa_qc_unique <- mimosa_qc_df %>%
@@
   slice(1) %>%
-  ungroup #n=890
+  ungroup
 
@@
   left_join(fascicle_proportions, by = c("EMPI", "EXAM_DATE")) %>%
-  filter(!is.na(Has.MS.Provider)) %>% #remove people who don't have MS provider
-  filter(!is.na(CNII_L)) #this is a sample fascicle that should have a value. if it does not, it means something is usually wrong with whole person. Remove rows with NAs
+  filter(!is.na(CNII_L)) %>% #this is a sample fascicle that should have a value. if it does not, it means something is usually wrong with whole person. Remove rows with NAs, n=854, lost 13
+  filter(!is.na(Has.MS.Provider))  #remove people who don't have MS provider, n=823 (lost 42)
 
@@
 
-lesion_volumes <- read.csv("/Users/eballer/BBL/msdepression/results/mimosa_binary_masks_hcp_space_20211026_n2336_volumes", sep = ",", header = TRUE) #n=958 unique, identical to fascicle unique
+lesion_volumes <- read.csv("/Users/eballer/BBL/msdepression/results/mimosa_binary_masks_hcp_space_20211026_n2336_volumes", sep = ",", header = TRUE) #n=2336, 958 unique, identical to fascicle unique
 lesion_volumes <- lesion_volumes %>%
@@
 
-##YEO Networks
-###Read in fascicle info
-```{r read_in_yeo_fascicle_info}
-##########################################################
-#             Read in Fascicle info             #
-##########################################################
-########
-#fascicle volumes in yeo networks
-########
-
-#read in file with proportions
-#fascicle_volumes_yeo_7 <- read.csv(paste0(homedir, "results/yeo_7_network_overlap_proportions.txt"), header = T, sep = ",", na.strings="0")
-
-#make titles nice
-#names(fascicle_volumes_yeo_7) <-gsub("prop_in_mask_", "prop_", names(fascicle_volumes_yeo_7))
-
-#make Nas into 0
-#fascicle_volumes_yeo_7[is.na(fascicle_volumes_yeo_7)]=0
-
-#read in file with binarized yes/no 
-fascicle_volumes_yeo_7_binarized <- read.csv("/Users/eballer/BBL/msdepression/results/yeo_7_network_overlap_proportions_binarized.txt", header = T, sep = ",")
-
-#drop cranial nerves
-fascicle_volumes_yeo_7_binarized_no_cranial_nerves <- fascicle_volumes_yeo_7_binarized %>% filter(!grepl('CN', fascicle))
-
-#check that order of df is same as yeo networks
-new_df <- gsub(pattern = "_vol", replacement = "", x = names(df_demo_and_fascicles[grep(pattern = "_vol", x = names(df_demo_and_fascicles))]))
-
-combined_df <- data.frame(cbind(new_df, fascicle_volumes_yeo_7_binarized_no_cranial_nerves$fascicle))
-names(combined_df) <- c("df", "yeo")
-
-#they match
-combined_df$match <- combined_df$df == combined_df$yeo
-```
-
-### Calc healthy volume of yeo networks
-```{r calc_healthy_volume_of_yeo_networks}
-#multiply with the binary yeo maps to get absolute volumes of healthy
-fascicle_volumes_yeo_7_full_volumes <- fascicle_volumes_yeo_7_binarized_no_cranial_nerves %>% 
-  tibble::remove_rownames() %>%
-  tibble::column_to_rownames(var = 'fascicle') %>%
-  mutate(across(everything()) * fiber_volume_values_no_cranial_nerves$volume_full) %>%
-  rename_with(~ str_c(.x, "_vol"), everything())
-
-#sum the volumes of each network to get total. 
-sums_of_volume_of_healthy_fascicles_by_network <- fascicle_volumes_yeo_7_full_volumes %>%
-  summarise(across(everything(), ~ sum(., na.rm = TRUE)))
-
-```
-
-###Calculate injury to yeo networks for each subject
-```{r calculate_injury_to_network}
-
-#grab names of networks, get rid of first element which is "fasiscle"
-yeo_network_names <- names(fascicle_volumes_yeo_7_binarized_no_cranial_nerves)[-1]
-
-#make names with _prop_net for use later to grap columns of proportions and not volumes
-yeo_network_names_prop <- paste(yeo_network_names, 'prop_net', sep = '_')
-
-df_w_yeo_volume_info <- df_demo_and_fascicles %>%
-  # mutate(total_fascicle_vol_lost = rowMeans(across(all_of(fascicle_names_w_vol_suffix)))) %>%
-  dplyr::select(EMPI, ends_with("_vol")) %>%
-  ungroup()
-
-#add columns to data frame for each network
-df_w_yeo_volume_info[,yeo_network_names] = 0
-
-#this has been checked with eyeballs and works. You CAN trust the df_w_yeo_volume_info
-for (network in yeo_network_names) {
-
-  for (subj in 1:dim(df_w_yeo_volume_info)[1]) {
-      # multiply the binary vector of the network with the fascicle volumes of injury, sum, and store in data frame
-      text_to_eval <- paste0("df_w_yeo_volume_info$", network,"[", subj,"]=sum(fascicle_volumes_yeo_7_binarized_no_cranial_nerves$", network,
-      "*df_w_yeo_volume_info[",subj,",3:(dim(df_w_yeo_volume_info)[2] - 7)])")
-     # print(text_to_eval)
-      eval(parse(text=text_to_eval))
-  }
-}
-
-### going to add 7 more columns to the data frame that contain the volume of injury/total healthy volume
-df_w_yeo_volume_info_with_prop_of_network <- tibble(df_w_yeo_volume_info) %>% 
-  mutate(across(all_of(yeo_network_names), 
-    .names = "{.col}_prop_net"
-
-  ))
-
-#go through each subject, and divide their total volume of injury within each network by the overall volume of the network
-for (subj in 1:dim(df_w_yeo_volume_info_with_prop_of_network)[1]){
-  df_w_yeo_volume_info_with_prop_of_network[subj, grepl(x = names(df_w_yeo_volume_info_with_prop_of_network), pattern = "_prop_net")] = df_w_yeo_volume_info_with_prop_of_network[subj, grepl(x = names(df_w_yeo_volume_info_with_prop_of_network), pattern = "_prop_net")]/sums_of_volume_of_healthy_fascicles_by_network
-}
-
-### rename the whole new data frame df_demo_and_fascicles
-df_demo_and_fascicles <- df_w_yeo_volume_info_with_prop_of_network %>% 
-  dplyr::select(-contains('_vol')) %>% #removes all columns with volume, leaving only the exam date, empi, and yeo values
-  right_join(df_demo_and_fascicles, by = c("EXAM_DATE", "EMPI")) #combine with demo_and_fascicles
-
-```
 ##Anxiety Network from neurosynth (association, not uniformity)
@@
 
-fascicles_with_any_anxiety_overlap <- neurosynth_anxiety_network_fascicle_overlap %>%
-  filter(prop_in_mask > 0)  #n = 43
-
-#top 25% 
-#number_of_brain_regions_in_top_25 <- round((dim(fascicles_with_any_anxiety_overlap)[1]/4)) #n=11
-number_of_brain_regions_in_top_25 <- round((dim(neurosynth_anxiety_network_fascicle_overlap)[1]/4)) #n=19
-
-fascicles_with_vol_top_25_percent_anxiety_overlap <- neurosynth_anxiety_network_fascicle_overlap %>%
-  filter(!is.na(prop_in_mask)) %>%
-  arrange(desc(non_zero_voxels_in_anxiety_map)) %>%
-  slice(1:number_of_brain_regions_in_top_25)
-
-fascicles_with_prop_top_25_percent_anxiety_overlap <- neurosynth_anxiety_network_fascicle_overlap %>%
-  filter(!is.na(prop_in_mask)) %>%
-  arrange(desc(prop_in_mask)) %>%
-  slice(1:number_of_brain_regions_in_top_25)
-
-#name vectors to use later
-fascicle_names_any_anxiety_overlap_vol <- fascicles_with_any_anxiety_overlap$fascicle 
-fascicle_names_top_25_vol <- fascicles_with_vol_top_25_percent_anxiety_overlap$fascicle 
-fascicle_names_bottom_75_vol <- neurosynth_anxiety_network_fascicle_overlap %>% filter(!(fascicle %in% fascicle_names_top_25_vol)) %>% pull(fascicle)
-
-fascicle_names_any_anxiety_overlap_prop <- fascicles_with_any_anxiety_overlap$fascicle
-fascicle_names_top_25_prop <-fascicles_with_prop_top_25_percent_anxiety_overlap$fascicle 
-fascicle_names_bottom_75_prop <- neurosynth_anxiety_network_fascicle_overlap %>% filter(!(fascicle %in% fascicle_names_top_25_prop)) %>% pull(fascicle)
-
-##add vol/prop
-fascicle_names_any_anxiety_overlap_vol_w_suff <- fascicle_names_any_anxiety_overlap_vol %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
-fascicle_names_top_25_vol_w_suff <- fascicle_names_top_25_vol %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
-fascicle_names_bottom_75_vol_w_suff <- fascicle_names_bottom_75_vol  %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in
-
-fascicle_names_any_anxiety_overlap_prop_w_suff <- fascicle_names_any_anxiety_overlap_prop %>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
-fascicle_names_top_25_prop_w_suff <- fascicle_names_top_25_prop %>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
-fascicle_names_bottom_75_prop_w_suff <- fascicle_names_bottom_75_prop %>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
-
-# Total volume of injury within each anxiety network, double checked that : top_25_total_volume + bottom_75_total_volume
+# Total volume of healthy fascicles within brain
 total_fascicle_volume <- sum(neurosynth_anxiety_network_fascicle_overlap$num_voxels_total)
-any_anxiety_overlap_total_volume <- sum(fascicles_with_any_anxiety_overlap$num_voxels_total) # vol = 1093606
-top_25_total_volume <-sum(fascicles_with_vol_top_25_percent_anxiety_overlap$num_voxels_total) # vol = 548305
-bottom_75_total_volume <- sum(neurosynth_anxiety_network_fascicle_overlap$num_voxels_total[neurosynth_anxiety_network_fascicle_overlap$fascicle %in% fascicle_names_bottom_75_vol]) #vol = 548305
-
-### Sort all the fascicles by %overlap, in decreasing order (so highest overlap at the top), and then take names of the top quartile, save for making binary maps later
-anxiety_network_names_top_quartile_no_cranial_nerves<- (neurosynth_anxiety_network_fascicle_overlap[order(neurosynth_anxiety_network_fascicle_overlap$non_zero_voxels_in_anxiety_map, decreasing = TRUE),])$fascicle[1:number_of_brain_regions_in_top_25]
-
-write.table(anxiety_network_names_top_quartile_no_cranial_nerves, paste0(homedir, "/results/anxiety_network_names_top_quartile_no_cranial_nerves_by_vol.txt"), row.names = F, col.names = F, quote = F)
-
-df_for_making_binary_color_maps_vol <- neurosynth_anxiety_network_fascicle_overlap %>% dplyr::select(fascicle, non_zero_voxels_in_anxiety_map)
-
-write.table(df_for_making_binary_color_maps_vol, paste0(homedir, "/results/volume_of_overlap_w_anxiety_net_n77.csv"), row.names = F, col.names = F, quote = F, sep = ",")
-
-df_for_making_binary_color_maps_prop <- neurosynth_anxiety_network_fascicle_overlap %>% dplyr::select(fascicle, prop_in_mask)
-
-write.table(df_for_making_binary_color_maps_prop, paste0(homedir, "/results/proportion_of_overlap_w_anxiety_net_n77.csv"), row.names = F, col.names = F, quote = F, sep = ",")
-
-```
-
-### Get dep network data
-```{r depression_network_injury}
-#take depression network from the BP paper, and find names of fascicles in each group
-
-#read in depression network overlap by volume data frame
-dep_net_overlap_from_bp_paper <- read.csv("/Users/eballer/BBL/msdepression/results/df_fascicles_sorted_by_volume_in_mask_for_eTable3.csv", sep = ",", header = TRUE)
-
-dep_net_top_25_percent <- dep_net_overlap_from_bp_paper$fascicle[1:round((dim(dep_net_overlap_from_bp_paper)[1]/4),0)]
-dep_net_top_25_percent_w_suff <- dep_net_top_25_percent %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
-
-top_25_total_volume_dep <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[1:round((dim(dep_net_overlap_from_bp_paper)[1]/4),0)])
-
-nondep_net_bottom_75_percent <- dep_net_overlap_from_bp_paper$fascicle[(round(dim(dep_net_overlap_from_bp_paper)[1]/4,0) +1):dim(dep_net_overlap_from_bp_paper)[1]]
-nondep_net_bottom_75_percent_w_suff <- nondep_net_bottom_75_percent %>%gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
-
-bottom_75_total_volume_nondep <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[(round(dim(dep_net_overlap_from_bp_paper)[1]/4,0) +1):dim(dep_net_overlap_from_bp_paper)[1]])
-
-```
-
-### find names of fascicles in anxiety + dep network, unique to dep net, and unique to anxiety net
-```{r find_names_and_overlaps_of_dep_and_anxiety_networks}
-
-#I want to figure out what the volume is in all voxels within the overlap of depression and anxiety network, as well as within the nonoverlapping networks
-#the depression net overlap from bp paper contains a colum (num_voxels_total) that has the full voxel sizes of all of the fascicles. Will use this to help find the "total volume size"
-
-#total volume = 1545449
-#checked to make sure that dep_only_net_vol + anxiety_only_net_vol + dep_and_anxiety_net_overlap_net_volume = dep_and_anxiety_net_unique_net_volume
-
-dep_and_anxiety_combined <- c(fascicle_names_top_25_vol, dep_net_top_25_percent) #n = 38
-
-dep_and_anxiety_net_unique_names <- dep_and_anxiety_combined %>% unique() #n=34
-dep_and_anxiety_net_unique_net_volume <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_and_anxiety_net_unique_names]) #vol = 1048643
-
-dep_and_anxiety_net_overlap_names <- dep_and_anxiety_combined[dep_and_anxiety_combined %>% duplicated()] #n=4
-dep_and_anxiety_net_overlap_net_volume <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_and_anxiety_net_overlap_names]) #vol = 486260
-
-dep_and_anxiety_net_overlap_names_no_CC <- dep_and_anxiety_net_overlap_names[dep_and_anxiety_net_overlap_names != "CC"]
-dep_and_anxiety_net_overlap_net_volume_no_CC <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_and_anxiety_net_overlap_names_no_CC]) #vol = 95659
-
-dep_only_names <- dep_and_anxiety_net_unique_names[!(dep_and_anxiety_net_unique_names %in% fascicle_names_top_25_vol)] #n=15
-dep_only_net_vol <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_only_names]) #vol = 370747
-
-anxiety_only_names <-dep_and_anxiety_net_unique_names[!(dep_and_anxiety_net_unique_names %in% dep_net_top_25_percent)] #n=15
-anxiety_only_net_vol <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% anxiety_only_names]) #vol = 191636
-
-### add suffix
-dep_and_anxiety_net_unique_names_w_suff <- dep_and_anxiety_net_unique_names  %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in
-
-dep_and_anxiety_net_overlap_names_w_suff <- dep_and_anxiety_net_overlap_names %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in
-
-dep_and_anxiety_net_overlap_names_w_suff_no_CC <- dep_and_anxiety_net_overlap_names_no_CC %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in
-
-dep_only_names_w_suff <- dep_only_names %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in
-
-anxiety_only_names_w_suff <- anxiety_only_names %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in 
-```
-
-### Define anxiety net by top 25 in both vol/prop
-```{r defineanxietynet_with_25_propx25vol}
-##### make an array of fascicles that have both substantial overlap with the anxiety network (top 25% vol), and where each fascicle is substantially impacted (top 25% proportion), n = 14
-fascicle_names_top_25_vol_x_top_25_prop <- fascicle_names_top_25_vol[fascicle_names_top_25_vol %in% fascicle_names_top_25_prop]
-
-#add vol/prop suffixes
-fascicle_names_top_25_vol_x_top_25_prop_PROP_suffix <-fascicle_names_top_25_vol_x_top_25_prop%>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
-fascicle_names_top_25_vol_x_top_25_prop_VOL_suffix <-fascicle_names_top_25_vol_x_top_25_prop%>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
-
-#create fascicle vectors that don't include these special fascicles, n = 63
-fascicle_names_NOT_top_25_vol_x_top_25_prop <- fascicle_names_no_cranial_nerves[!(fascicle_names_no_cranial_nerves %in% fascicle_names_top_25_vol_x_top_25_prop)]
-
-#add vol/prop suffixes
-fascicle_names_NOT_top_25_vol_x_top_25_prop_PROP_suffix <- fascicle_names_NOT_top_25_vol_x_top_25_prop%>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
-fascicle_names_NOT_top_25_vol_x_top_25_prop_VOL_suffix <- fascicle_names_NOT_top_25_vol_x_top_25_prop%>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
-
-#anxiety25_propxvol overlap total, sum of these two is 1545449 (and this is total_fascicle_volume)
-anxiety_top_25_vol_x_top_25_prop_vol <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% fascicle_names_top_25_vol_x_top_25_prop]) #vol = 181869
-
-#nonanxiety25_propxvol overlap total
-anxiety_NOT_top_25_vol_x_top_25_prop_vol <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% fascicle_names_NOT_top_25_vol_x_top_25_prop]) #vol = 1363580
-
-#check sums
-if ((anxiety_top_25_vol_x_top_25_prop_vol + anxiety_NOT_top_25_vol_x_top_25_prop_vol) == total_fascicle_volume) {
-  print("anxiety + nonanxiety net = total fascicle volume")
-} else{
-  print("something is wrong with counts")
-}
 
@@
 
-  #sum of total volume lost in anxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) 
-  mutate(sum_fascicle_vol_lost_inanxietynet_all = 
-           rowSums(across(all_of(fascicle_names_any_anxiety_overlap_vol_w_suff)))) %>%
-  mutate(proportion_volume_lost_anxiety_net_by_network_size_sum = sum_fascicle_vol_lost_inanxietynet_all/any_anxiety_overlap_total_volume) %>%
-
-  #sum of total volume lost in anxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) top quartile
-  mutate(sum_fascicle_vol_lost_inanxietynet_top_quartile = 
-           rowSums(across(all_of(fascicle_names_top_25_vol_w_suff)))) %>%
-  mutate(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 = sum_fascicle_vol_lost_inanxietynet_top_quartile/top_25_total_volume) %>%
-
-  #sum of total volume lost in nonanxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) bottom 3 quartiles
-  mutate(sum_fascicle_vol_lost_nonanxiety_net_bottom_3_quartiles = 
-           rowSums(across(all_of(fascicle_names_bottom_75_vol_w_suff)))) %>%
-  mutate(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 = sum_fascicle_vol_lost_nonanxiety_net_bottom_3_quartiles/bottom_75_total_volume) %>%
-
-  ##sum of total volume lost in depression network and proportion of volume lost in depression network (volume lost/network volume size) top quartile
-  mutate(sum_fascicle_vol_lost_indepressionnet_top_quartile = 
-           rowSums(across(all_of(dep_net_top_25_percent_w_suff)))) %>%
-  mutate(proportion_volume_lost_depression_net_by_network_size_sum_top_25 = sum_fascicle_vol_lost_indepressionnet_top_quartile/top_25_total_volume_dep) %>%
-
-  #sum of total volume lost in nondepression network and proportion of volume lost in depression network (volume lost/network volume size) bottom 3 quartiles
-  mutate(sum_fascicle_vol_lost_nondepression_net_bottom_3_quartiles = 
-           rowSums(across(all_of(nondep_net_bottom_75_percent_w_suff)))) %>%
-  mutate(proportion_volume_lost_nondepression_net_by_network_size_sum_bottom_75 = sum_fascicle_vol_lost_nondepression_net_bottom_3_quartiles/bottom_75_total_volume_nondep) %>%
-
-  ##sum of total volume lost in depression + anxiety network and proportion of volume lost in network (volume lost/network volume size) top quartile
-  mutate(sum_fascicle_vol_lost_indep_and_anxiety_net_combined = 
-           rowSums(across(all_of(dep_and_anxiety_net_unique_names_w_suff)))) %>%
-  mutate(proportion_fascicle_vol_lost_indep_and_anxiety_net_combined = sum_fascicle_vol_lost_indep_and_anxiety_net_combined/dep_and_anxiety_net_unique_net_volume) %>%
-
-  ##sum of total volume lost in areas of overlap between depression + anxiety network and proportion of volume lost in network (volume lost/network volume size) top quartile
-  mutate(sum_fascicle_vol_lost_indep_and_anxiety_net_overlap = 
-           rowSums(across(all_of(dep_and_anxiety_net_overlap_names_w_suff)))) %>%
-  mutate(proportion_fascicle_vol_lost_indep_and_anxiety_net_overlap = sum_fascicle_vol_lost_indep_and_anxiety_net_overlap/dep_and_anxiety_net_overlap_net_volume) %>%
-
-  ##sum of total volume lost in areas of overlap between depression + anxiety network and proportion of volume lost in network (volume lost/network volume size), no CC
-  mutate(sum_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC = 
-           rowSums(across(all_of(dep_and_anxiety_net_overlap_names_w_suff_no_CC)))) %>%
-  mutate(proportion_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC = sum_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC/dep_and_anxiety_net_overlap_net_volume_no_CC) %>%
-
-  ##sum of total volume lost in depression, no overlap with anxiety network and proportion of volume lost in network (volume lost/network volume size) top quartile
-  mutate(sum_fascicle_vol_lost_indepressionnet_no_anxiety_overlap = 
-           rowSums(across(all_of(dep_only_names_w_suff)))) %>%
-  mutate(proportion_fascicle_vol_lost_indepressionnet_no_anxiety_overlap = sum_fascicle_vol_lost_indepressionnet_no_anxiety_overlap/dep_only_net_vol) %>%
-
-    ##sum of total volume lost in anxiety, no depression overlap network and proportion of volume lost in network (volume lost/network volume size) top quartile
-  mutate(sum_fascicle_vol_lost_inanxietynet_no_depression_overlap = 
-           rowSums(across(all_of(anxiety_only_names_w_suff)))) %>%
-  mutate(proportion_fascicle_vol_lost_inanxietynet_no_depression_overlap = sum_fascicle_vol_lost_inanxietynet_no_depression_overlap/anxiety_only_net_vol) %>%
-
-    ##sum of total volume lost in anxiety 25 volxanxiety25prop groups, and proportion of volume lost in network (volume lost/network volume size)
-  mutate(sum_fascicle_names_top_25_vol_x_top_25_prop = 
-           rowSums(across(all_of(fascicle_names_top_25_vol_x_top_25_prop_VOL_suffix)))) %>%
-  mutate(proportion_fascicle_vol_lost_top_25_vol_x_top_25_prop = sum_fascicle_names_top_25_vol_x_top_25_prop/anxiety_top_25_vol_x_top_25_prop_vol) %>%
-
-    ##sum of total volume lost in remaining 63 fascicles NOT in anxiety 25 volxanxiety25prop groups, and proportion of volume lost in network (volume lost/network volume size)
-  mutate(sum_fascicle_names_NOT_top_25_vol_x_top_25_prop = 
-           rowSums(across(all_of(fascicle_names_NOT_top_25_vol_x_top_25_prop_VOL_suffix)))) %>%
-  mutate(proportion_fascicle_vol_lost_NOT_top_25_vol_x_top_25_prop = sum_fascicle_names_NOT_top_25_vol_x_top_25_prop/anxiety_NOT_top_25_vol_x_top_25_prop_vol) %>%
-
-   ##mean_uncinate)
+  ##mean_uncinate
   mutate(mean_UF_vol = (UF_L_vol + UF_R_vol)/2) %>%
   mutate(mean_UF_prop = (UF_L_prop + UF_R_prop)/2) %>%
+
+  ##mean_fornix
+  mutate(mean_fornix_volume = (F_L_vol + F_R_vol)/2) %>%
+  mutate(mean_fornix_prop = (F_L_prop + F_R_prop)/2) %>%
 
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>% 
-  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)
+  dplyr::select(proportion_volume_lost_per_total_network_size_sum, UF_L_prop, UF_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)
 
@@
             mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
-            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
-            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
             mean_UF_L = mean(UF_L_prop),
@@
 
-  #mean disease by anxiety dose: anxiety_dose    0.047452   0.019130   2.480  0.01357 *  
-  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_mean_disease_lm)
-
-  ### gam instead, anxiety_dose  0.04846    0.01901   2.549   0.0112 * 
-    anxietyGrouping_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_mean_disease_gam)
-
-  #mean disease with sex in model : anxiety_dose     0.0486229  0.0191648   2.537  0.01159 *  
-  anxietyGrouping_by_sex_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_by_sex_mean_disease_lm)
-
-  #gam: anxiety_dose  0.04955    0.01905   2.601  0.00966 **  
+  #anxiety_dose  0.04955    0.01905   2.601  0.00966 ** 
   anxietyGrouping_by_sex_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + osex+ s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_by_sex_mean_disease_gam)
-```
-
-### Anxiety network by anxiety dose
-```{r}
-
-#define group
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter (anxiety_dose != -1)
-
-  #anxiety network
-
-  ###  anxiety_dose   anxiety_dose    0.051190   0.022452   2.280   0.0232 *  
-  anxietyGrouping_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_anxiety_net_lm)
-
-  #gam, anxiety_dose  0.05297    0.02248   2.357    0.019 *  
-   anxietyGrouping_anxiety_net_gam<- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_anxiety_net_gam)
-
-  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.066699   0.026574   2.510   0.0125 *  , no intx
-  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_by_sex_anxiety_net_lm)
-
-  #gam, anxiety_dose         0.06708    0.02648   2.533   0.0117 *   
-  anxietyGrouping_by_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_by_sex_anxiety_net_gam)
-
-  #volume lost in anxiety net by anxiety dose + sex + PAT_AGE_AT_EXAM: anxiety_dose     0.052228   0.022506   2.321   0.0209 *  
-  anxietyGrouping_cov_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_cov_sex_anxiety_net_lm)
-
-  #gam, anxiety_dose  0.05256    0.02244   2.342   0.0197 *  
-   anxietyGrouping_cov_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_cov_sex_anxiety_net_gam)
-
-```
-
-### NonAnxiety network by anxiety dose
-```{r}
-
-#define group
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter (anxiety_dose != -1)
-
-  #anxiety network
-
-  ###  anxiety_dose: anxiety_dose    0.0445315  0.0172621   2.580   0.0103 * 
-  anxietyGrouping_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_nonanxiety_net_lm)
-
-  #gam, anxiety_dose  , anxiety_dose  0.04741    0.01712   2.769   0.0059 ** 
-   anxietyGrouping_nonanxiety_net_gam<- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_nonanxiety_net_gam)
-
-  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.057403   0.020404   2.813  0.00517 ** 
-  anxietyGrouping_by_sex_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose*osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_by_sex_nonanxiety_net_lm)
-
-  #gam, anxiety_dose, anxiety_dose      anxiety_dose         0.059732   0.020184   2.959  0.00328 **        
-  anxietyGrouping_by_sex_nonanxiety_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose*osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_by_sex_nonanxiety_net_gam)
-
-  #volume lost in anxiety net by anxiety dose + sex + PAT_AGE_AT_EXAM: anxiety_dose     0.0458062  0.0172824   2.650  0.00839 ** 
-  anxietyGrouping_cov_sex_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_cov_sex_nonanxiety_net_lm)
-
-  #gam, anxiety_dose - anxiety_dose  0.04861    0.01714   2.836  0.00483 ** 
-   anxietyGrouping_cov_sex_nonanxiety_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-   summary(anxietyGrouping_cov_sex_nonanxiety_net_gam)
-
 ```
@@
 
-#lm lesion volumes; DiagnosisMS+Anxiety  9210.15    2966.03   3.105 0.002381 ** 
-volume_of_mimosa_lesions_lm <- lm(volume_of_mimosa_lesions ~ Diagnosis + osex + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(volume_of_mimosa_lesions_lm)
-
 #gam lesion volumes; DiagnosisMS+Anxiety   8765.2     2748.2   3.189  0.00183 ** 
@@
   filter (anxiety_dose != -1) #n=371
-
-#dose; anxiety_dose     3562.72    1299.08   2.743 0.006396 *
-
-  anxiety_dose_volume_of_mimosa_lesions_by_sex_lm <- lm(volume_of_mimosa_lesions ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxiety_dose_volume_of_mimosa_lesions_by_sex_lm)
 
@@
 
-#do lm UF*Diagnosis
- #UF_R_vol -> DiagnosisMS+Anxiety  1019.03     535.20   1.904   0.0593 .  
-disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + osex + PAT_AGE_AT_EXAM, data = uncinate_by_dx_df)
-summary(disease_UF_R_vol_lm)
-
- #UF_L_vol ->DiagnosisMS+Anxiety   729.21     389.80   1.871  0.06386 .    
-disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = uncinate_by_dx_df)
-summary(disease_UF_L_vol_lm)
-
-#bilat: DiagnosisMS+Anxiety   874.12     412.30   2.120   0.0361 * 
-disease_mean_UF_vol_lm <- lm(mean_UF_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = uncinate_by_dx_df)
-summary(disease_mean_UF_vol_lm)
-
-#gam, Fx= F
-#UF_R_vol -> DiagnosisMS+Anxiety  1019.03     535.20   1.904   0.0593 .   
-disease_UF_R_vol_gam <- gam(UF_R_vol ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
-summary(disease_UF_R_vol_gam)
-
- #UF_L_vol -> DiagnosisMS+Anxiety    675.7      381.3   1.772    0.079 .  
-disease_UF_L_vol_gam <- gam(UF_L_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
-summary(disease_UF_L_vol_gam)
-
-#bilateral UF: DiagnosisMS+Anxiety    866.7      411.9   2.104   0.0375 *  
+#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety    866.7      411.9   2.104   0.0375 *  
 disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
@@
   filter(anxiety_dose != -1) #n=371
-
-#lm
-
-  #R anxiety dose + age ; anxiety_dose      430.81     240.44   1.792    0.074 .   
-  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_UF_R_lm)
-
-   #R *anxiety dose + osex + age anxiety_dose:       anxiety_dose      440.30     241.07   1.826   0.0686 .  
-  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_UF_R_by_sex_lm)
-
-   #UF L - anxiety_dose + age:    anxiety_dose     337.695    169.917   1.987   0.0476 *  
-  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_UF_L_lm)
-
-   #UF_L anxiety_dose + sex + age:         anxiety_dose     350.563    170.099   2.061    0.040 *    
-  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_UF_L_by_sex_lm)
-
-  #bilat anxiety dose + age: anxiety_dose     anxiety_dose     384.254    185.461   2.072    0.039 *
-  anxietyGrouping_mean_UF_lm <- lm(mean_UF_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_mean_UF_lm)
-
-  #bilat anxiety dose + sex + age: anxiety_dose     395.432    185.804   2.128    0.034 *  
-  anxietyGrouping_mean_UF_by_sex_lm <- lm(mean_UF_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_mean_UF_by_sex_lm)
-
-#gam, Fx=F - k = 4 and 5 give the same stats
-
-  ## UF_R ##
-
-  #UF _ R  anxiety_dose    430.3      240.4    1.79   0.0742 .  
-  anxietyGrouping_UF_R_gam <- gam(UF_R_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_UF_R_gam)
-
-  #R anxiety dose + sex + age: anxiety_dose    439.8      241.0   1.825   0.0689 .  
-  anxietyGrouping_UF_R_by_sex_gam <- gam(UF_R_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_UF_R_by_sex_gam)
-
-  ## UF_L ##
-
-  #UF_L, anxiety_dose + age: anxiety_dose    337.8      169.8    1.99   0.0473 *  
-  anxietyGrouping_UF_L_gam <- gam(UF_L_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_UF_L_gam)
-
-  #UF_L anxiety_dose + sex + age: anxiety_dose    350.5      170.0   2.062   0.0399 *    
-  anxietyGrouping_UF_L_by_sex_gam <- gam(UF_L_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_UF_L_by_sex_gam)
-
-  ## bilat ##
-
-  #bilat  anxiety_dose + age: anxiety_dose    383.7      185.3   2.071   0.0391 *  
-  anxietyGrouping_mean_UF_gam <- gam(mean_UF_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_mean_UF_gam)
 
@@
 
-# UF_L, P = NS
-dep_UF_L_gam <- gam(UF_L_vol ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
-summary(dep_UF_L_gam)
-
-#UF_R, P = NS
-dep_UF_R_gam <- gam(UF_R_vol ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
-summary(dep_UF_R_gam)
-
 #mean UF, P = NS
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) %>%
-  mutate(mean_fornix_volume = (F_R_vol+F_L_vol)/2)
-
-  #gam, Fornix R anxiety_dose  - NS 
-  anxietyGrouping_F_R_by_sex_gam <- gam(F_R_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_R_by_sex_gam)
-
-  #gam, Fornix L anxiety_dose - NS
-  anxietyGrouping_F_L_by_sex_gam <- gam(F_L_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_F_L_by_sex_gam)
+  filter(anxiety_dose != -1)
 
@@
 
-### Network*Diagnosis
-```{r networkxdiagnosis_groups_collapse}
-
-## take home: comparing healthy to has anxiety AND meds, more disease within vs outside net, anxiety vs non, no interaction.
-## take home #2 : More disease in R & L uncinate in anxious versus nonanxious
-
-  #burden of anxiety by network
-  #clean up data frame
-  df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
-  mutate(subject = as.factor(EMPI)) %>%
-  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
-  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
-  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol) %>% 
-  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol, -F_R_vol, -F_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
-  mutate(Network = as.factor(Network)) %>%
-  ungroup() #n=244 (122 x 2)
-
-#simple lmer
-
-#NetworkNonanxiety_network                      -0.245959   0.009028 120.000000 -27.245  < 2e-16 ***
-#DiagnosisMS+Anxiety                             0.143579   0.045316 132.184401   3.168  0.00190 **
-
-disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
-
-#Network confit:
-confint(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
-
-#simple lmer
-#NetworkNonanxiety_network         -0.247316   0.009473 120.000000 -26.107  < 2e-16 ***
-  disease_within_vs_outside_anxiety_net_by_sex_diff_lmer <- lmer(proportion_affected ~ Network*osex + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-  summary(disease_within_vs_outside_anxiety_net_by_sex_diff_lmer)
-
-#Network confit:
-confint(disease_within_vs_outside_anxiety_net_by_sex_diff_lmer)
-
-## diagnosis by sex 
- #simple lmer, DiagnosisMS+Anxiety         0.148038   0.045605   3.246 0.001337 ** 
-disease_diagnosis_by_sex_diff_lm <- lm(proportion_affected ~ Diagnosis*osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_diagnosis_by_sex_diff_lm)
-
-#Network confit:
-confint(disease_diagnosis_by_sex_diff_lm)
-
-#network * diagnosis + sex
-#NetworkNonanxiety_network                      -0.245959   0.009028 120.000001 -27.245  < 2e-16 ***
-#DiagnosisMS+Anxiety                             0.143161   0.045499 130.966650   3.146  0.00205 ** 
-disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer <- lmer(proportion_affected ~ Network*Diagnosis + osex + (1|subject)+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
-summary(disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer)
-
-#Confit
-confint(disease_within_vs_outside_anxiety_net_by_dx_groups_sex_diff_lmer)
-
-```
-
-### Diag Effect Size * Fascicle anxiety net overlap (from depression analysis) 
-#### Make data frame 
-```{r dxEffSizeOverlapwithAnxietyNet}
-
-#tried looking at prop instead of volume - opposite effects of depression. Higher effect sizes -> lower overlap with anxiety net
-
-#define group
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  mutate(anxiousAndMeds_or_healthy = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  filter(anxiousAndMeds_or_healthy %in% c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>%
-    mutate(anxiousAndMeds_or_healthy = ordered(anxiousAndMeds_or_healthy)) #n=122
-
-#  mutate(anxiousAndMeds_or_healthy = factor(anxiousAndMeds_or_healthy, levels=c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
-
-#Positive Ts are places where anxious people have more disease than controls
-fascicle_anxiety_vs_healthy_effsize <- sapply(fascicle_names_w_vol_suffix, function(fascicle) 
-{
-
-  text_for_eval <- paste0("rstatix::wilcox_effsize(df_demo_and_fascicles_no_unclass_anxiety_dose, formula = ", fascicle, " ~ anxiousAndMeds_or_healthy, paired = F, conf.level = 0.95, ci.type = \"perc\", nboot = 1000)$effsize")
-  eval(parse(text=text_for_eval))
-})
-names(fascicle_anxiety_vs_healthy_effsize) <- fascicle_names_w_vol_suffix
-
-#convert to data frame
-df_effsize_values <- as.data.frame(fascicle_anxiety_vs_healthy_effsize)
-
-#write.table(x = df_effsize_values, file = paste0(homedir, "results/fascicle_and_wilcox_effect_size_for_volxdx_analysis_n77.csv"), row.names = T, col.names = F, quote = F, sep = ",")
-
-```
-
-#### Plot EfSize x Anxiety net overlap - N.S. 
-``` {r plot_scatter}
-#######################
-### plot differences ##
-#######################
-
-#N.S., (including if I drop all fascicles with no overlap)
-#combine data frames, column 1 has names of fascicles, column 2 has Volume of overlap with anxiety network, column 3 has t-test value of anxiety vs healthy unc, 4th anxiety vs healthy fdr corrected within that fascicle
-
-df_fascicle_anxiety_mask_volume_overlap_effsize_value <- data.frame(neurosynth_anxiety_network_fascicle_overlap$fascicle, neurosynth_anxiety_network_fascicle_overlap$non_zero_voxels_in_anxiety_map, df_effsize_values)
-names(df_fascicle_anxiety_mask_volume_overlap_effsize_value) <- c("fascicle", "volume_in_anxiety_mask", "anxiety_vs_healthy_effsize")
-
-#remove values that have no overlap
-#df_fascicle_anxiety_mask_volume_overlap_effsize_value <- df_fascicle_anxiety_mask_volume_overlap_effsize_value %>% filter(volume_in_anxiety_mask > 0)
-
-# plot fascicle overlap x Eff size value
-#statistic,
-
-anxiety_overlap_x_anxiety_vs_healthy_vol_effsize <- lm(anxiety_vs_healthy_effsize ~ volume_in_anxiety_mask, data=df_fascicle_anxiety_mask_volume_overlap_effsize_value )
-summary(anxiety_overlap_x_anxiety_vs_healthy_vol_effsize)
-
-scatter_effsize_val_by_anxiety_net_overlap_log <- ggplot(data=df_fascicle_anxiety_mask_volume_overlap_effsize_value, aes(x=volume_in_anxiety_mask, y=anxiety_vs_healthy_effsize, color=anxiety_vs_healthy_effsize)) +
-  geom_point(size=2) + 
-  scale_color_gradient(low = "#FFFFFF", high = "#ff00ff") +
-  geom_smooth(formula = y ~ x, method=lm, color="black")+
-  scale_x_continuous(trans=scales::pseudo_log_trans(base = 10), breaks=c(0, 10, 100, 1000, 10000, 100000)) + 
-  xlab("Volume of Fascicle in Anxiety Network") + 
-  ylab("Effect Size (r)") + 
-  theme(plot.title=element_text(hjust=0.5),
-        axis.text = element_text(size=16, color = "black"),
-        axis.title = element_text(size=18, color = "black"),
-        axis.line = element_line(color="black", size=1.3),
-        panel.background = element_blank(),
-        legend.position = "none",
-        aspect.ratio = 4/4) + 
-  annotate("text", x=1.6, y=0.14, size = 5, 
-           label = paste0("P = ", round(summary(anxiety_overlap_x_anxiety_vs_healthy_vol_effsize)$coef[2,4],2)))
-
-print(scatter_effsize_val_by_anxiety_net_overlap_log)
-
-#save as pdf
-#pdf(file=paste0(homedir, "/results/Figures_for_msanxietyn_paper/scatter_effsize_val_by_anxiety_net_overlap_log.pdf"))
- # scatter_effsize_val_by_anxiety_net_overlap_log
-#dev.off()
-
-#df_for_making_colors <- df_fascicle_anxiety_mask_volume_overlap_effsize_value %>% dplyr::select(fascicle, anxiety_vs_healthy_effsize)
-#write.table(x = df_for_making_colors, file = paste0(homedir, "results/fascicle_and_effect_size_for_volxdx_analysis_n77.csv"), row.names = F, col.names = F, quote = F, sep = ",")
-
-```
-
 ### Sex Differences
@@
 
-### anxiety net NS
-disease_between_sexes_anxiety_net <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-summary(disease_between_sexes_anxiety_net)
-
-### nonanxiety net - NS
-disease_between_sexes_nonanxiety_net <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-summary(disease_between_sexes_nonanxiety_net)
-
-#uncinate R- NS
-disease_between_sexes_UF_R <- lm(UF_R_vol ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-summary(disease_between_sexes_UF_R)
-
-#uncinate L - ns
-disease_between_sexes_UF_L <- lm(UF_L_vol ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-summary(disease_between_sexes_UF_L)
+# mean uncinate L - ns
+disease_between_sexes_UF_mean <- lm(mean_UF_vol ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(disease_between_sexes_UF_mean)
 
@@
 
-####. within/outside anxiety network #######
-#diagnosis
-#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.05  1.099 5.539 0.01921 * 
-#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.74  2.115 5.257 0.00473 **
-diagnosis_by_age_anx_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_anx_net_gam)
-summary(diagnosis_by_age_anx_net_gam)$s.table
-#plot(diagnosis_by_age_anx_net_gam)
-
-#gam plot diagnosis_by_age_anx_net_gam_factor
-
-plot_smooths_diagnosis_by_age_anx_net_gam_factor <- plot_smooths(
-  model = diagnosis_by_age_anx_net_gam,
-  series = PAT_AGE_AT_EXAM,
-  comparison = Diagnosis
-) +
-  theme(legend.position = "top")
-plot_smooths_diagnosis_by_age_anx_net_gam_factor
-
-##### #outside each network
-#diagnosis: MS+Anxiety p=0.0432
-#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.975  2.373 4.660 0.00556 **
-#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 2.157  2.543 5.059 0.00282 **
-diagnosis_by_age_nonanx_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_nonanx_net_gam)
-summary(diagnosis_by_age_nonanx_net_gam)$s.table
-#plot(diagnosis_by_age_nonanx_net_gam)
-
-#gam plot diagnosis_by_age_nonanx_net_gam_factor
-
-plot_smooths_diagnosis_by_age_nonanx_net_gam_factor <- plot_smooths(
-  model = diagnosis_by_age_nonanx_net_gam,
-  series = PAT_AGE_AT_EXAM,
-  comparison = Diagnosis
-) +
-  theme(legend.position = "top")
-plot_smooths_diagnosis_by_age_nonanx_net_gam_factor
-
-### uncinate right
-#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.001  1.003 24.11 2.01e-06 ***
-#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.059  1.116 15.01 0.000105 ***
-
-diagnosis_by_age_UF_R_gam <- gam(UF_R_vol ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_UF_R_gam)
-summary(diagnosis_by_age_UF_R_gam)$s.table
-#plot(diagnosis_by_age_UF_R_gam)
-
-#gam UF_R plot
-
-plot_smooths_anxiety_diagnosis_by_age_UF_R <- plot_smooths(
-  model = diagnosis_by_age_UF_R_gam,
-  series = PAT_AGE_AT_EXAM,
-  comparison = Diagnosis
-) +
-  theme(legend.position = "top")
-plot_smooths_anxiety_diagnosis_by_age_UF_R
-
-#uncinate left
-#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.930  2.328  7.546 0.00046 ***
-#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.001  1.002 10.868 0.00107 **
-
-diagnosis_by_age_UF_L_gam <- gam(UF_L_vol ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_UF_L_gam)
-summary(diagnosis_by_age_UF_L_gam)$s.table
-#plot(diagnosis_by_age_UF_L_gam)
-
-#gam UF_L plot
-
-plot_smooths_anxiety_diagnosis_by_age_UF_L <- plot_smooths(
-  model = diagnosis_by_age_UF_L_gam,
-  series = PAT_AGE_AT_EXAM,
-  comparison = Diagnosis
-) +
-  theme(legend.position = "top")
-plot_smooths_anxiety_diagnosis_by_age_UF_L
-
 #uncinate mean
@@
 
-####. within/outside anxiety network #######
-#dose, s(PAT_AGE_AT_EXAM):anxiety_dose 2.842  3.231 4.792 0.00242 **
-diagnosis_by_age_anx_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_anx_net_gam)
-summary(diagnosis_by_age_anx_net_gam)$s.table
-#plot(diagnosis_by_age_anx_net_gam)
-
-#factor
-#anxiety_dose_factor.L  0.09073    0.03830   2.369   0.0184 * 
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.000  1.000 8.158 0.00453 **
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.816  2.208 1.651 0.19973  
-diagnosis_by_age_anx_net_gam_factor <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_anx_net_gam_factor)
-summary(diagnosis_by_age_anx_net_gam_factor)$s.table
-#plot(diagnosis_by_age_anx_net_gam_factor)
-
-#gam plot diagnosis_by_age_anx_net_gam_factor
-
-plot_smooths_diagnosis_by_age_anx_net_gam_factor <- plot_smooths(
-  model = diagnosis_by_age_anx_net_gam_factor,
-  series = PAT_AGE_AT_EXAM,
-  comparison = anxiety_dose_factor
-) +
-  theme(legend.position = "top")
-plot_smooths_diagnosis_by_age_anx_net_gam_factor
-
-##### #outside each network
-
-##dose
-#s(PAT_AGE_AT_EXAM):anxiety_dose 3.19  3.577 5.659 0.000746 ***
-diagnosis_by_age_nonanx_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_nonanx_net_gam)
-summary(diagnosis_by_age_nonanx_net_gam)$s.table
-#plot(diagnosis_by_age_nonanx_net_gam)
-
-#factor
-#anxiety_dose_factor.L  0.07359    0.02950   2.495    0.013 * 
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.703  2.071 4.247  0.0136 *
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 2.003  2.403 2.034  0.1110  
-diagnosis_by_age_nonanx_net_gam_factor <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_nonanx_net_gam_factor)
-summary(diagnosis_by_age_nonanx_net_gam_factor)$s.table
-#plot(diagnosis_by_age_nonanx_net_gam_factor)
-
-#gam plot diagnosis_by_age_nonanx_net_gam_factor
-
-plot_smooths_diagnosis_by_age_nonanx_net_gam_factor <- plot_smooths(
-  model = diagnosis_by_age_nonanx_net_gam_factor,
-  series = PAT_AGE_AT_EXAM,
-  comparison = anxiety_dose_factor
-) +
-  theme(legend.position = "top")
-plot_smooths_diagnosis_by_age_nonanx_net_gam_factor
-
-### uncinate right
-
-#dose
-#s(PAT_AGE_AT_EXAM):anxiety_dose 2.006  2.013 7.36 0.00071 ***
-diagnosis_by_age_UF_R_gam <- gam(UF_R_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_UF_R_gam)
-summary(diagnosis_by_age_UF_R_gam)$s.table
-#plot(diagnosis_by_age_UF_R_gam)
-
-#factor, only sig is smooth
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.127  1.242 12.824 0.000293 ***
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.002  1.003  0.538 0.463889    
-diagnosis_by_age_UF_R_gam_factor <- gam(UF_R_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_UF_R_gam_factor)
-summary(diagnosis_by_age_UF_R_gam_factor)$s.table
-#plot(diagnosis_by_age_UF_R_gam_factor)
-
-#gam UF_R plot
-
-plot_smooths_anxiety_dose_by_age_UF_R <- plot_smooths(
-  model = diagnosis_by_age_UF_R_gam_factor,
-  series = PAT_AGE_AT_EXAM,
-  comparison = anxiety_dose_factor
-) +
-  theme(legend.position = "top")
-plot_smooths_anxiety_dose_by_age_UF_R
-
-#uncinate left
-#dose
-#s(PAT_AGE_AT_EXAM):anxiety_dose   2      2 4.635  0.0103 *
-diagnosis_by_age_UF_L_gam <- gam(UF_L_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_UF_L_gam)
-summary(diagnosis_by_age_UF_L_gam)$s.table
-#plot(diagnosis_by_age_UF_L_gam)
-
-#factor
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.001  1.002 13.507 0.000271 ***
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.007  1.014  0.611 0.432612    
-diagnosis_by_age_UF_L_gam_factor <- gam(UF_L_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_UF_L_gam_factor)
-summary(diagnosis_by_age_UF_L_gam_factor)$s.table
-#plot(diagnosis_by_age_UF_L_gam_factor)
-
-#gam UF_L plot
-
-plot_smooths_anxiety_dose_by_age_UF_L <- plot_smooths(
-  model = diagnosis_by_age_UF_L_gam_factor,
-  series = PAT_AGE_AT_EXAM,
-  comparison = anxiety_dose_factor
-) +
-  theme(legend.position = "top")
-plot_smooths_anxiety_dose_by_age_UF_L
-
 #uncinate mean
@@
 ```
-#### Parametric anxiety net fascicles 
-```{r indiv_fascicle_anxiety_net_anxiety_dose}
-
-## 3 meet FDR - EMC_L_prop	0.0320914948			C_PHP_R_prop	0.0265819790			C_FPH_R_prop	0.0004861282	
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) %>%
-  mutate(anxiety_dose_factor = ordered(anxiety_dose))
-
-#gam
-fascicle_gam <- lapply(fascicle_names_top_25_vol_w_suff, function(x) 
-{
-  gam(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + osex+s(PAT_AGE_AT_EXAM, k=4, fx=F), list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-})
-names(fascicle_gam) <- fascicle_names_top_25_vol_w_suff
-
-#anova
-fascicle_anova_gam <- lapply(fascicle_gam, anova)
-
-#uncorrected
-fascicle_anova_gam_p <- sapply(fascicle_anova_gam, function(v) v$p.pv[2])
-print(as.data.frame(fascicle_anova_gam_p))
-fascicle_anova_gam_p05_unc <- as.data.frame(fascicle_anova_gam_p[fascicle_anova_gam_p < 0.05])
-print(fascicle_anova_gam_p05_unc)
-
-#fdr corrected
-fascicle_anova_gam_fdr <- round(p.adjust(fascicle_anova_gam_p, method = "fdr"),3)
-fascicle_anova_gam_fdr_p05 <- as.data.frame(fascicle_anova_gam_fdr[fascicle_anova_gam_fdr < 0.05])
-print(fascicle_anova_gam_fdr_p05)
-
-```
-
-#### Parametric nonanxiety net fascicles 
-```{r nonanxiety_net_anxiety_dose}
-
-# 23  sig things
-
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) %>%
-  mutate(anxiety_dose_factor = ordered(anxiety_dose))
-
-#gam
-fascicle_gam <- lapply(fascicle_names_bottom_75_prop_w_suff, function(x) 
-{
-  gam(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + osex+s(PAT_AGE_AT_EXAM, k=4, fx=F), list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-})
-names(fascicle_gam) <- fascicle_names_bottom_75_prop_w_suff
-
-#anova
-fascicle_anova_gam <- lapply(fascicle_gam, anova)
-
-#uncorrected
-fascicle_anova_gam_p <- sapply(fascicle_anova_gam, function(v) v$p.pv[2])
-print(as.data.frame(fascicle_anova_gam_p))
-fascicle_anova_gam_p05_unc <- as.data.frame(fascicle_anova_gam_p[fascicle_anova_gam_p < 0.05])
-print(fascicle_anova_gam_p05_unc)
-
-#fdr corrected
-fascicle_anova_gam_fdr <- round(p.adjust(fascicle_anova_gam_p, method = "fdr"),3)
-fascicle_anova_gam_fdr_p05 <- as.data.frame(fascicle_anova_gam_fdr[fascicle_anova_gam_fdr < 0.05])
-print(fascicle_anova_gam_fdr_p05) 
-```
-
 ### Plots
@@
 df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>% 
-  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, C_FPH_R_prop, C_FP_R_prop,DRTT_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified")
 
@@
 prop_injured_by_anxiety_burden_collapsed_vars_plot
-
-  #proportion injured over anxiety net
-prop_injured_anxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_anxiety_net_by_anxiety_burden_collapsed_vars_plot
-
-  #proportion injured over nonanxiety net
-prop_injured_nonanxiety_net_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_nonanxiety_net_by_anxiety_burden_collapsed_vars_plot
 ```
@@
 ```
-
-##Plot within vs outside network
-```{r plottting_bar_graph}
-
-#Within vs outside network
-anxiety_net_group <- c(rep("Anxiety Network", times = dim(df_demo_and_fascicles)[1]), rep("Nonanxiety Network",times =dim(df_demo_and_fascicles)[1]))
-net_values <- c(df_demo_and_fascicles$proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, df_demo_and_fascicles$proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75)
-
-newdf <- data.frame(anxiety_net_group, net_values)
-
-newdf <- newdf %>%
-  mutate( anxiety_net_group=factor(anxiety_net_group,levels=c( "Nonanxiety Network", "Anxiety Network")))
-
-violin_within_vs_outside_network_sum_proportion_scaled_by_network_size <- ggplot(newdf, aes(x=anxiety_net_group, y=net_values, fill=anxiety_net_group)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  ggtitle(paste0("Volume of Fascicle Disease Burden")) +
-  ylab("Proportion of network affected") +
-  ylim(0,1) + 
-  scale_fill_manual(values=c("#D3D3D3", "#841DE2")) +
-  theme(plot.title = element_text(size=16, hjust = 0.55),
-        axis.text = element_text(size = 16, colour = "black"), axis.title.y  = element_blank(), 
-        axis.title.x = element_text(size=16),
-        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
-        legend.position = "none",
-        aspect.ratio=4/7,
-        panel.background = element_rect(colour = "white", fill = "white")) + 
-  coord_flip()
-
-#display
-violin_within_vs_outside_network_sum_proportion_scaled_by_network_size
-```
-### Yeo networks
-#### healthy vs super sick 
-```{r individual_fascicle_disease_healthy_vs_super_sick_yeo}
-
-## all correct
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  mutate(anxiousAndMeds_or_healthy = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  filter(anxiousAndMeds_or_healthy %in% c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>%
-  mutate(anxiousAndMeds_or_healthy = factor(anxiousAndMeds_or_healthy, levels=c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"))) #n=122
-
-#lm
-fascicle_lm <- lapply(yeo_network_names_prop, function(x) 
-{
-  lm(substitute(i ~ anxiousAndMeds_or_healthy + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-})
-names(fascicle_lm) <- yeo_network_names_prop
-
-#anova
-fascicle_anova <- lapply(fascicle_lm, anova)
-
-#fdr corrected
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
-print(fascicle_anova_fdr)
-
-#fdr corrected only association cortex
-#fascicle_anova_w_fiber_mapping <- fascicle_agesex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
-##fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
-#print(fascicle_anova_fdr_association)
-
-#uncorrected
-fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
-print(fascicle_anova_p05_unc) 
-```
-
-#### Parametric yeo networks
-```{r individual_fascicle_disease_anxiety_dose_yeo}
-#n=371, all correct
-
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) %>%
-  mutate(anxiety_dose_factor = ordered(anxiety_dose))
-
-#lm
-fascicle_lm <- lapply(yeo_network_names_prop, function(x) 
-{
-  lm(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-})
-names(fascicle_lm) <- yeo_network_names_prop
-
-#anova
-fascicle_anova <- lapply(fascicle_lm, anova)
-
-#fdr corrected
-fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
-print(fascicle_anova_fdr)
-
-#uncorrected
-fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
-print(fascicle_anova_p05_unc) 
-```

### 2024-08-09 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
Add files via upload

@@
 
+#figure brainstorming
+1. Flowchart of inclusion/exclusion
+2. Demographics (age, sex, race, +/- PHQ2, PHQ9, has anxiety dx, on anxiety meds, both, on dmt) 
+3. Some sort of schematic of pipeline - 
+  a. amygdala - mpfc blobs
+  b. uncinate connecting the two
+  c. white matter lesion dropped in uncinates
+  d. streamline filtering
+  e. mean of both side
+4. Mean UF Anxiety diagnosis either violin or bar
+5. Mean Anxiety dose either violin or bar
+6. Supplement: 
+ - More detailed streamline filtering
+ - Depression group uncinate burden
+ - Fornix diagnosis and dose; depression group
+
 ```{r read_in_df}

### 2024-08-09 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
Add files via upload

@@
  - Fornix diagnosis and dose; depression group 
+ - Corr mean_UF with social problems?
 
@@
 
+## Add PROMIS
+```{r promis_data_handling}
+##########################################################
+#            Read in PROMIS Data              #
+##########################################################
+promis_data <- readRDS(paste0(homedir, "/data/dac/promis_data_20220824_fixed_physical_health_cleaned_n1813_unique_indiv_n532_2015-2022.rds"))
+promis_score_names <- names(promis_data[7:16])
+
+df_people_with_promis_data <- df_demo_and_fascicles %>%
+  filter(EMPI %in% promis_data$EMPI) #n=129
+
+unique_empis_in_promis_group <- unique(df_people_with_promis_data$EMPI) #n=129
+
+#go through each person w/promis data and append the columns to their row that reflects the closest collected PROMIS
+
+#function, take an empi and date, returns the row of data w/promis scores
+get_closest_promis_to_ms_exam_date <- function(subj_empi, subj_exam_date) {
+  df_closest_promis <- promis_data %>%
+    filter(EMPI == subj_empi) %>%
+    mutate(distance_from_scan = abs(RECORDED_TIME-subj_exam_date)) %>%
+    filter(abs(RECORDED_TIME-subj_exam_date)==min(abs(RECORDED_TIME-subj_exam_date))) %>%
+    slice(1)
+  return(df_closest_promis)
+}
+
+#make dataframe to store promis info
+promis_info_closest_proximity <- data.frame(matrix(NA, nrow=dim(df_people_with_promis_data)[1], ncol=(dim(promis_data)[2] + 1)))
+names(promis_info_closest_proximity) <- c(names(promis_data), "distance_from_scan")
+
+for (line in 1:dim(df_people_with_promis_data)[1]) {
+  #pull out subject empi and exam date
+  subj_empi <- df_people_with_promis_data$EMPI[line]
+  subj_exam_date <- df_people_with_promis_data$BEGIN_EXAM_DTTM[line]
+
+  #returns whole line, promis scores, id, empi, everything
+  closest_promis_data <- get_closest_promis_to_ms_exam_date(subj_empi = subj_empi, subj_exam_date = subj_exam_date)
+
+  #store as new line
+  promis_info_closest_proximity[line,] = closest_promis_data
+}
+
+#drop unnecessary columns c("DE_PAT_ID", "EMPI", "HUP_MRN", "SEX", "RACE")
+promis_info_closest_proximity_just_scores <- promis_info_closest_proximity[,6:dim(promis_info_closest_proximity)[2]]
+
+#combine with df_people_with_promis_data
+df_people_with_promis_data_scores_added = cbind(df_people_with_promis_data, promis_info_closest_proximity_just_scores)
+
+#summarize the distance from scans
+summary(df_people_with_promis_data_scores_added$distance_from_scan/364) #mean 3.1 ys, median 2.8 years, range 0.39 y to 7.16
+
+hist(df_people_with_promis_data_scores_added$distance_from_scan/364, 
+     main = "Hisogram of years between Promis and Scan",
+     xlab = "Years from Scan") #convert to years
+
+```
+
+### Demographics
+```{r demographics}
+
+#this will display a demographics table comparing age, race, sex between healthy and depressed groups, using the first presentation to treatment
+#demo
+make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
+
+make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[((df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
+
+#just good mimosa w/promis
+df_people_with_promis_data_scores_added_unique <- df_people_with_promis_data_scores_added %>%
+  filter(anxiety_dose != -1)  %>%
+  group_by(EMPI) %>% 
+  arrange(EXAM_DATE) %>% 
+  slice(1) %>% 
+  ungroup() 
+make_demographics_table_ms_w_promis_anxiety(data_frame = df_people_with_promis_data_scores_added_unique)
+make_demographics_table_ms_w_promis_anxiety(data_frame = df_people_with_promis_data_scores_added_unique[df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
+
+make_demographics_table_ms_w_promis_anxiety(data_frame = df_people_with_promis_data_scores_added_unique[((df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
+
+#testing whether PROMIS sub sample is equally representative with respect to prevalence of depression/non-depression.
+I.e.
+do more people with depression get PROMIS scores?
+or are we equally drawing from both groups?
+
+#first number is # with depression, second is number without depression
+num_w_promis <- c(sum(df_people_with_promis_data_scores_added_unique$depGroupVar == 2), sum(df_people_with_promis_data_scores_added_unique$depGroupVar == 1))
+
+#first number is # with depression, second is number without depression
+num_total <- c(sum(df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"), sum(df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy"))
+
+df_2x2_promis_score_by_total_people_per_diagnosis <- data.frame(cbind(num_w_promis, num_total), row.names = c("MS+NoA", "MS+severeA"))
+
+#X-squared = 0.21, p = 0.65, not significant)
+chisq <- chisq.test(df_2x2_promis_score_by_total_people_per_diagnosis)
+print(chisq)
+```
+
 ##Anxiety Network from neurosynth (association, not uniformity)
@@
    filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-   filter (anxiety_dose != 3)
+   filter(anxiety_dose != 3)
 
@@
 #this collapses anxiety group + meds with those with anxiety group + meds + with/without depression
-
-#demo
-make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
-
-make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[((df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
 
@@
 ```
+
+###Promis data in UF - groups too small
+#### Uncinate by anxiety diagnosis (N.S) 
+```{r uncinate_by_dx}
+
+### Results:  
+#define group
+  uncinate_by_dx_df <- df_people_with_promis_data_scores_added_unique %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  ungroup() #n=22
+
+#bilateral UF ~ Diagnosis: N.S.
+disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
+summary(disease_mean_UF_vol_gam)
+
+```
+
+#### Uncinate by Anxiety Dose (N.S.)
+```{r uncinateByAnxietyDose}
+
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_people_with_promis_data_scores_added_unique %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) #n=79
+
+  #bilat anxiety dose - NS
+  anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_mean_UF_by_sex_gam)
+
+```

### 2024-08-09 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
Add files via upload

@@
 5. Mean Anxiety dose either violin or bar
-6. Supplement: 
+6. PROMIS scores (each type of measure is a line, y axis is score, x axis is anxiety dose)
+7. Supplement: 
  - More detailed streamline filtering
@@
 
+## Make final data frame for analysis
+### read in emr data
 ```{r read_in_df}
@@
 
+### read in Mimosa data
 ```{r read_in_mimosa_qc}
@@
 
+### merge with Mimosa data
 ```{r merge_df_with_mimosa}
@@
 
-### Read in fascicle info, use this to determine proportion and volume of injury within each fascicle, and save it in the df_demo_and_fascicles_df
+### read in fascicle info, use this to determine proportion and volume of injury within each fascicle, and save it in the df_demo_and_fascicles_df
 ```{r read_in_fascicle_info}
@@
 
-## Merge data with good mimosa
+### merge data with good mimosa
 ```{r merge_with_good_mimosa}
@@
 
-## Read in lesion volume size
+### read in lesion volume size
 ```{r read_in_lesion_volumes}
@@
 
-## Merge with data frame with good mimosas
+### merge with data frame with good mimosas
 ```{r merge_lesion_volume_w_mimosa_df}
@@
 
-## Make separate columns for proportional injury (prop), total volume injury (vol)
+### make separate columns for proportional injury (prop), total volume injury (vol)
 ```{r add_suffix_to_each_measure}
@@
 
-## Add PROMIS
+### add PROMIS
 ```{r promis_data_handling}
@@
 
-### Demographics
+## Demographics
+### simple demographics
 ```{r demographics}
@@
 make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[((df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
-
+```
+
+### demographics with PROMIS
+```{r demo_with_promis}
 #just good mimosa w/promis
@@
 make_demographics_table_ms_w_promis_anxiety(data_frame = df_people_with_promis_data_scores_added_unique)
-make_demographics_table_ms_w_promis_anxiety(data_frame = df_people_with_promis_data_scores_added_unique[df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
-
-make_demographics_table_ms_w_promis_anxiety(data_frame = df_people_with_promis_data_scores_added_unique[((df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
+
+make_demographics_table_ms_w_promis_anxiety(data_frame = df_people_with_promis_data_scores_added_unique[(df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds"),])
 
@@
 
-#### Demographics
-```{r demo_uncinate}
-
-###### all groups, no unclassified
-make_demographics_table_ms_anxiety_simple(df_demo_and_fascicles %>% filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified"))
-
-###### just healthy and sick
-make_demographics_table_ms_anxiety_simple(df_demo_and_fascicles %>% filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds"))
-
-```
-
 #### Uncinate by anxiety diagnosis 

### 2024-08-09 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
Add files via upload

@@
 ```
+#### Plot promis x anxiety dose
+```{r plot_Promis_x_anxiety}
+
+# Reshape the data from wide to long format
+df_for_promis_plot <- df_people_with_promis_data_scores_added_unique %>%
+  dplyr::select(EMPI,
+                anxiety_dose, 
+                Quality_of_Life, 
+                Physical_Health, 
+                Mental_Health_and_Mood,
+                Social_Activities_Satisfaction,
+                Carrying_Out_Social_Activities,
+                Carrying_Out_Physical_Activities,
+                Emotional_Problems, 
+                Fatique_Average,
+                PostOp.PROMIS.Physical.Score,
+                PostOp.PROMIS.Mental.Score) %>%
+  group_by(anxiety_dose) %>%
+
+  # summarize by score
+  summarise(across(c(Quality_of_Life, 
+                     Physical_Health, 
+                     Mental_Health_and_Mood,
+                     Social_Activities_Satisfaction,
+                     Carrying_Out_Social_Activities,
+                     Carrying_Out_Physical_Activities,
+                     Emotional_Problems, 
+                     Fatique_Average,
+                     PostOp.PROMIS.Physical.Score, #this has a much bigger range
+                     PostOp.PROMIS.Mental.Score), #bigger range
+                   list(mean = ~mean(. , na.rm = TRUE)))) %>% #                   ,     sd = ~sd(. , na.rm = TRUE))))
+
+  # Reshape to long format for plotting
+    pivot_longer(cols = -anxiety_dose, 
+               names_to = "PROMIS_Score", 
+               values_to = "Score")
+
+custom_colors <- c(
+  "Quality_of_Life" = "#66c2a5",  # Green
+  "Physical_Health" = "#8da0cb",  # Purple
+  "Mental_Health_and_Mood" = "#99d8c9",  # Green
+  "Social_Activities_Satisfaction" = "#238b45",  # Green
+  "Carrying_Out_Social_Activities" = "#41ae76",  # Green
+  "Carrying_Out_Physical_Activities" = "#8856a7",  # Purple
+  "Emotional_Problems" = "#006d2c",  # Dark Green
+  "Fatique_Average" = "#4B0082",  # Light Purple
+  "PostOp.PROMIS.Mental.Score" = "#9ACD32",  # Green
+  "PostOp.PROMIS.Physical.Score" = "#810f7c"  # Dark Purple
+)
+
+custom_colors_simple <- c("#8856a7","#41ae76", "#006d2c", "#4B0082", "#99d8c9", "#8da0cb",  "#9ACD32", "#810f7c", "#66c2a5", "#238b45") #done in alphabetical order.
+
+# Create the ggplot
+promis_with_post_op <- ggplot(df_for_promis_plot, aes(x = anxiety_dose, y = Score, color = PROMIS_Score)) +
+  geom_line(size = 1.2) +
+  scale_x_continuous(breaks = c(0, 1, 2)) +
+  scale_y_continuous(limits = c(0, 20)) +
+  theme_minimal() +
+  labs(x = "Anxiety Dose", y = "Mean PROMIS Score", 
+       title = "PROMIS Scores by Anxiety Dose") +
+#  scale_color_brewer(palette = "Set3") 
+  scale_color_manual(values = custom_colors_simple)
+promis_with_post_op
+
+#remove postop scores
+
+promis_without_postop<- ggplot(df_for_promis_plot, aes(x = anxiety_dose, y = Score, color = PROMIS_Score)) +
+  geom_line(size = 1.2) +
+  scale_x_continuous(breaks = c(0, 1, 2)) +
+  scale_y_continuous(limits = c(0, 5)) +
+  theme_minimal() +
+  labs(x = "Anxiety Dose", y = "Mean PROMIS Score", 
+       title = "PROMIS Scores by Anxiety Dose") +
+  #scale_color_brewer(palette = "Set3") 
+  scale_color_manual(values = custom_colors_simple)
+
+promis_without_postop
+
+```
 

### 2024-08-13 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
promis graphs

@@
   group_by(EMPI) %>% 
+  mutate(num_na = sum(is.na(across(promis_score_names)))) %>%
+  filter(num_na == 0) %>%
   arrange(EXAM_DATE) %>% 
@@
 ```{r plot_Promis_x_anxiety}
+#set mood versus physical domains
+mood_domains <- c("Quality_of_Life", 
+                "Mental_Health_and_Mood",
+                "Social_Activities_Satisfaction",
+                "Carrying_Out_Social_Activities",
+                "Emotional_Problems", 
+                "PostOp.PROMIS.Mental.Score")
+
+physical_domains <- c("Physical_Health", 
+                      "Carrying_Out_Physical_Activities",
+                      "Fatique_Average",
+                      "PostOp.PROMIS.Physical.Score")
 
@@
 
+#### Plot promis x anxiety dose, group by mental vs physical health
+```{r plot_Promis_x_anxiety}
+#set mood versus physical domains
+mood_domains <- c("Quality_of_Life", 
+                "Mental_Health_and_Mood",
+                "Social_Activities_Satisfaction",
+                "Carrying_Out_Social_Activities",
+                "Emotional_Problems", 
+                "PostOp.PROMIS.Mental.Score")
+
+physical_domains <- c("Physical_Health", 
+                      "Carrying_Out_Physical_Activities",
+                      "Fatique_Average",
+                      "PostOp.PROMIS.Physical.Score")
+
+# Reshape the data from wide to long format
+df_for_promis_plot_mental_vs_physical_healthy <- df_people_with_promis_data_scores_added_unique %>%
+  group_by(EMPI) %>%
+  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
+  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
+  dplyr::select(EMPI,
+                anxiety_dose,
+                physical_health_score,
+                mental_health_score) %>%
+  gather(health_variable, PROMIS_Score, -anxiety_dose, -EMPI) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
+  group_by(anxiety_dose, health_variable) %>%
+  summarise(mean_promis_score = mean(PROMIS_Score , na.rm = TRUE)) %>%
+  ungroup()
+
+custom_colors <- c("physical_health_score" = "#9ACD32","mental_health_score" =  "#4B0082")
+
+custom_colors_simple <- c("#9ACD32", "#4B0082") #done in alphabetical order.
+
+# Create the ggplot
+promis_with_post_op_mental_vs_physical <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, color = health_variable)) +
+  geom_line(size = 1.2) +
+  scale_x_continuous(breaks = c(0, 1, 2)) +
+  scale_y_continuous(limits = c(0, 7)) +
+  theme(
+       # plot.title = element_text(size=16, hjust = 0.55),
+      #  axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
+      #  axis.title.y = element_text(size=16),
+        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
+      #  legend.position = "none",
+        aspect.ratio=7/5,
+        panel.background = element_rect(colour = "white", fill = "white")) +
+  labs(x = "Anxiety Dose", y = "Mean PROMIS Score", 
+       title = "PROMIS Scores by Anxiety Dose") +
+#  scale_color_brewer(palette = "Set3") 
+  scale_color_manual(values = custom_colors_simple)
+promis_with_post_op_mental_vs_physical
+
+# Create the ggplot -> bar
+promis_with_post_op_mental_vs_physical_bar <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, fill = health_variable)) +
+  geom_bar(stat = "identity", position = position_dodge()) +  
+  scale_x_continuous(breaks = c(0, 1, 2)) +
+  scale_y_continuous(limits = c(0, 7)) +
+
+  theme_minimal() +
+  labs(x = "Anxiety Dose", y = "Mean PROMIS Score", 
+       title = "PROMIS Scores by Anxiety Dose") +
+  scale_fill_manual(values = custom_colors)
+
+promis_with_post_op_mental_vs_physical_bar
+
+```
+
 ##Anxiety Network from neurosynth (association, not uniformity)
@@
 ```
+
 ### Overlap with depression group
@@
 
-#### Anxiety DOSE -> NEED TO UPDATE stats in text
+#### Anxiety DOSE 
 ```{r anxietydosexage}

### 2024-08-13 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
playing with promis graphs

@@
   group_by(anxiety_dose, health_variable) %>%
-  summarise(mean_promis_score = mean(PROMIS_Score , na.rm = TRUE)) %>%
+  summarise(mean_promis_score = mean(PROMIS_Score , na.rm = TRUE),
+            sd_promis_score = sd(PROMIS_Score, na.rm = TRUE),
+            sem_promis_score = sd(PROMIS_Score, na.rm = TRUE) / sqrt(n())) %>%
   ungroup()
@@
   scale_y_continuous(limits = c(0, 7)) +
+  geom_errorbar(aes(ymin = mean_promis_score - sem_promis_score, ymax = mean_promis_score + sem_promis_score), width = 0.2, size = 0.8)  +
   theme(
@@
 promis_with_post_op_mental_vs_physical_bar <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, fill = health_variable)) +
-  geom_bar(stat = "identity", position = position_dodge()) +  
+  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +  
+  geom_errorbar(aes(ymin = mean_promis_score - sem_promis_score, ymax = mean_promis_score + sem_promis_score), 
+                width = 0.2, size = 0.8, color = "black", position = position_dodge(width = 0.9)) +
   scale_x_continuous(breaks = c(0, 1, 2)) +
   scale_y_continuous(limits = c(0, 7)) +
-
   theme_minimal() +

### 2024-08-13 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
promis_analyses

@@
 
+####Test promis*anxiety dose  stats
+#####Physical and Mental Health together
+```{r phsy_and_mental_step_x_anxiety_dose}
+###
+df_for_promis_plot_mental_vs_physical_healthy_test <- df_people_with_promis_data_scores_added_unique %>%
+  group_by(EMPI) %>%
+  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
+  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
+  mutate(phys_mental_diff_score = physical_health_score-mental_health_score) %>%
+  dplyr::select(EMPI,
+                anxiety_dose,
+                physical_health_score,
+                mental_health_score,
+                phys_mental_diff_score)
+
+#anxiety_dose  -0.7345     0.2946  -2.493   0.0153 *  
+anxiety_dose_x_phys_score <- lm(physical_health_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
+summary(anxiety_dose_x_phys_score)
+
+#anxiety_dose  -1.1181     0.2681  -4.171 9.59e-05 ***
+anxiety_dose_x_mental_score <- lm(mental_health_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
+summary(anxiety_dose_x_mental_score)
+
+#anxiety_dose   0.3836     0.2391   1.605    0.114
+anxiety_dose_x_diff_score <- lm(phys_mental_diff_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
+summary(anxiety_dose_x_diff_score)
+```
+
+##### Physical and Mental Health x anxiety dose intx
+```{r phys_and_mental_x_anxiety_dose}
+###
+df_for_promis_plot_mental_vs_physical_healthy_no_summarize <- df_people_with_promis_data_scores_added_unique %>%
+  group_by(EMPI) %>%
+  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
+  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
+  mutate(anxiety_dose = as.numeric(anxiety_dose)) %>%
+  dplyr::select(EMPI,
+                anxiety_dose,
+                physical_health_score,
+                mental_health_score) %>%
+  gather(health_variable, PROMIS_Score, -anxiety_dose, -EMPI)
+
+#anxiety_dose                                       -1.1181     0.2816 88.0000  -3.970 0.000146 ***, others NS
+anxiety_dose_by_health_var_score <- lmer(PROMIS_Score ~anxiety_dose*health_variable + (1|EMPI), df_for_promis_plot_mental_vs_physical_healthy_no_summarize)
+summary(anxiety_dose_by_health_var_score)
+
+```
+
 ##Anxiety Network from neurosynth (association, not uniformity)

### 2024-08-13 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
stats for promis - group too small

@@
 summary(anxiety_dose_x_diff_score)
+
+#looking at anxiety_dose = 2 only, 0.22 -> sample size too small
+
+mental_vs_physical_health_t <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
+mental_vs_physical_health_t
 ```

### 2024-08-13 MSAnxiety_manuscript_audrey_replication.Rmd
Add files via upload

--- 2024-08-13 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
@@
 #set mood versus physical domains
-mood_domains <- c("Quality_of_Life", 
-                "Mental_Health_and_Mood",
+mood_domains <- c("Mental_Health_and_Mood",
                 "Social_Activities_Satisfaction",
@@
                 "Emotional_Problems", 
+                "Quality_of_Life",
                 "PostOp.PROMIS.Mental.Score")

### 2024-08-13 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
Add files via upload

@@
 mental_vs_physical_health_t
+
+#looking at physical health and mental health in sick vs healthy
+
+#physical health, sick vs healthy - t = 2.0048, df = 8.6555, p-value = 0.07722
+physical_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
+physical_health_t_sick_vs_healthy
+
+#mental health, sick vs healthy - t = 3.6838, df = 8.1324, p-value = 0.006011
+mental_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
+mental_health_t_sick_vs_healthy
 ```
@@
 
+### do just with super sick and healthy
+df_for_promis_plot_mental_vs_physical_healthy_no_summarize_just_sick_and_healthy <- df_people_with_promis_data_scores_added_unique %>%
+  group_by(EMPI) %>%
+  filter(anxiety_dose != 1) %>%
+  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
+  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
+  mutate(anxiety_dose = as.numeric(anxiety_dose)) %>%
+  dplyr::select(EMPI,
+                anxiety_dose,
+                physical_health_score,
+                mental_health_score) %>%
+  gather(health_variable, PROMIS_Score, -anxiety_dose, -EMPI)
+
+#aanxiety_dose                                       -1.0417     0.2611 24.3607  -3.989  0.00053 ***
+##health_variablephysical_health_score                0.1875     0.2731 17.0000   0.687  0.50155    
+#anxiety_dose:health_variablephysical_health_score   0.4063     0.2249 17.0000   1.806  0.08864 .  
+anxiety_dose_by_health_var_score_just_sick_and_healthy <- lmer(PROMIS_Score ~anxiety_dose*health_variable + (1|EMPI), df_for_promis_plot_mental_vs_physical_healthy_no_summarize_just_sick_and_healthy)
+summary(anxiety_dose_by_health_var_score_just_sick_and_healthy)
 ```

### 2024-08-21 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
fixed order of some things

@@
 df_demo_and_fascicles <- cbind(df_everything_else, df_fascicles_prop, df_fascicles_volumes)
+```
+
+##Anxiety Network from neurosynth (association, not uniformity)
+###read in file with fasciclexanxiety overlap, and define anxiety network
+```{r read_in_neurosynth_anxiety_network}
+neurosynth_anxiety_network_fascicle_overlap <- read.csv("/Users/eballer/BBL/msanxiety/results/streamline_volume_within_anxiety_network_association_neuro_maps_FDR_01.csv", header = T, sep = ",") %>% 
+  filter(fascicle %in% fascicle_names_no_cranial_nerves) %>%
+  slice(order(factor(fascicle, levels = fascicle_names_no_cranial_nerves))) %>% #get rid of cranial nerves up front 
+  replace(is.na(.), 0)
+
+# Total volume of healthy fascicles within brain
+total_fascicle_volume <- sum(neurosynth_anxiety_network_fascicle_overlap$num_voxels_total)
+
+```
+
+###Add columns in the main data frame indicating overall injury in the whole network, in the top 25 network (vol and prop), and bottom 75%
+```{r add_anxiety_and_dep_network_details_to_data_frame}
+
+#all of this has been checked - making sure prop * vol network = sum of damage
+
+df_demo_and_fascicles <- df_demo_and_fascicles %>%
+
+  mutate(mean_fascicle_prop_lost_no_cranial_nerves = rowMeans(across(all_of(fascicle_names_w_prop_suffix)))) %>%
+  mutate(mean_fascicle_volume_lost_no_cranial_nerves = rowMeans(across(all_of(fascicle_names_w_vol_suffix)))) %>%
+
+  #sum of total volume lost and proportion of volume lost 
+  mutate(sum_fascicle_vol_lost = rowSums(across(all_of(fascicle_names_w_vol_suffix)))) %>%
+  mutate(proportion_volume_lost_per_total_network_size_sum = sum_fascicle_vol_lost/total_fascicle_volume) %>%
+
+  ##mean_uncinate
+  mutate(mean_UF_vol = (UF_L_vol + UF_R_vol)/2) %>%
+  mutate(mean_UF_prop = (UF_L_prop + UF_R_prop)/2) %>%
+
+  ##mean_fornix
+  mutate(mean_fornix_volume = (F_L_vol + F_R_vol)/2) %>%
+  mutate(mean_fornix_prop = (F_L_prop + F_R_prop)/2) %>%
+
+  ungroup()
+
+#neurosynth_anxiety_network_fascicle_overlap
 ```
@@
 
-##Anxiety Network from neurosynth (association, not uniformity)
-###read in file with fasciclexanxiety overlap, and define anxiety network
-```{r read_in_neurosynth_anxiety_network}
-neurosynth_anxiety_network_fascicle_overlap <- read.csv("/Users/eballer/BBL/msanxiety/results/streamline_volume_within_anxiety_network_association_neuro_maps_FDR_01.csv", header = T, sep = ",") %>% 
-  filter(fascicle %in% fascicle_names_no_cranial_nerves) %>%
-  slice(order(factor(fascicle, levels = fascicle_names_no_cranial_nerves))) %>% #get rid of cranial nerves up front 
-  replace(is.na(.), 0)
-
-# Total volume of healthy fascicles within brain
-total_fascicle_volume <- sum(neurosynth_anxiety_network_fascicle_overlap$num_voxels_total)
-
-```
-
-###Add columns in the main data frame indicating overall injury in the whole network, in the top 25 network (vol and prop), and bottom 75%
-```{r add_anxiety_and_dep_network_details_to_data_frame}
-
-#all of this has been checked - making sure prop * vol network = sum of damage
-
-df_demo_and_fascicles <- df_demo_and_fascicles %>%
-
-  mutate(mean_fascicle_prop_lost_no_cranial_nerves = rowMeans(across(all_of(fascicle_names_w_prop_suffix)))) %>%
-  mutate(mean_fascicle_volume_lost_no_cranial_nerves = rowMeans(across(all_of(fascicle_names_w_vol_suffix)))) %>%
-
-  #sum of total volume lost and proportion of volume lost 
-  mutate(sum_fascicle_vol_lost = rowSums(across(all_of(fascicle_names_w_vol_suffix)))) %>%
-  mutate(proportion_volume_lost_per_total_network_size_sum = sum_fascicle_vol_lost/total_fascicle_volume) %>%
-
-  ##mean_uncinate
-  mutate(mean_UF_vol = (UF_L_vol + UF_R_vol)/2) %>%
-  mutate(mean_UF_prop = (UF_L_prop + UF_R_prop)/2) %>%
-
-  ##mean_fornix
-  mutate(mean_fornix_volume = (F_L_vol + F_R_vol)/2) %>%
-  mutate(mean_fornix_prop = (F_L_prop + F_R_prop)/2) %>%
-
-  ungroup()
-
-#neurosynth_anxiety_network_fascicle_overlap
-```
-
 #COLLAPSE anxiety dx and antianxiety meds with those plus depression, and anxiety dx OR on anxiety meds into 1 group -->> THIS IS THE MONEY
@@
 ### Uncinate **ACNP**
+#### Presence of Uncinate Lesions chisq - N.S.
+```{r uncinate_presence_of_lesions}
+### Basically, I'd like to answer the question - is it just a presence or absence of uncinate lesions, or is it the burden of uncinate lesions/
+### To do this, I perform a chisq to see if there is a statistically significant difference in the number of people with uncinate lesions within each of the diagnostic groups
+### I found that there are no statistically significant differences in the frequency of uncinate lesions between groups - meaning that it is not just the presence of lesions, but the impact
+
+#define group and make column for people who do have uncinate lesions and those who don't
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) %>% #n=371
+  mutate(has.uncinate.lesion = ifelse(mean_UF_vol >0, 1, 0)) #anywhere where there is *some* overlap counts as a 1 - they have an uncinate lesion, otherwise 0
+
+#define number of people within each group that have uncinate lesions
+uncinate_lesions_dose_0 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(has.uncinate.lesion == 1 & anxiety_dose == 0) %>% count() #n=76
+uncinate_lesions_dose_1 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(has.uncinate.lesion == 1 & anxiety_dose == 1) %>% count() #n=190
+uncinate_lesions_dose_2 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(has.uncinate.lesion == 1 & anxiety_dose == 2) %>% count() #n=19
+
+#define total number of people in each group
+anxiety_total_dose_0 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(anxiety_dose == 0) %>% count() #n=99
+anxiety_total_dose_1 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(anxiety_dose == 1) %>% count() #n=249
+anxiety_total_dose_2 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(anxiety_dose == 2) %>% count() #n=23
+
+#make table
+num_w_uncinate_lesions <- as.numeric(c(uncinate_lesions_dose_0, uncinate_lesions_dose_1, uncinate_lesions_dose_2))
+num_total <-as.numeric(c(anxiety_total_dose_0,anxiety_total_dose_1, anxiety_total_dose_2))
+df_2x3_presence_of_UF_lesions_by_total_people_per_dose <- data.frame(cbind(num_w_uncinate_lesions, num_total), row.names = c("MS+noAnxiety","MS+AnxietyorMed", "MS+AnxietyandMed"))
+
+#X-squared (Pearson's) X-squared(2,371) = 0.059833, p = 0.9705
+chisq_anxiety_dose <- chisq.test(x=df_2x3_presence_of_UF_lesions_by_total_people_per_dose)
+chisq_anxiety_dose
+
+#just healthy and super anxious/sick
+num_w_UF_just_healthy_and_sick <- as.numeric(c(uncinate_lesions_dose_0, uncinate_lesions_dose_2))
+num_total_just_healthy_and_sick <-as.numeric(c(anxiety_total_dose_0,anxiety_total_dose_2))
+df_2x2_UF_lesions_by_total_people_per_diagnosis_num_total_just_healthy_and_sick <- data.frame(cbind(num_w_UF_just_healthy_and_sick, num_total_just_healthy_and_sick), row.names = c("MS+noAnxiety", "MS+AnxietyandMed"))
+
+#X-squared(1,122) = 0.001529, p = 0.9688
+chisq_healthy_vs_sick <- chisq.test(x = df_2x2_UF_lesions_by_total_people_per_diagnosis_num_total_just_healthy_and_sick)
+chisq_healthy_vs_sick
+
+```
 
@@
 ```{r uncinate_by_dx}
+### Having found that there is no association between the number of uncinate lesions and the anxiety dose, I next explored whether the *burden* of uncinate lesions differs by diagnosis/group
 
@@
 
-#mean UF, P = NS
+#mean UF, T=-1.7, P = NS
 dep_mean_UF_gam <- gam(mean_UF_vol ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
@@
 
-###### Fornix by Anxiety Dose (N.S)
+###### Fornix by Anxiety Diagnosis and Dose (N.S)
 ```{r fornixByAnxietyDose}
@@
 #results: Anxiety dose NOT related to F_R when covarying for linear effects of age and sex, not in line with that one paper that found fornix differences
-
 #define group
+
+#anxiety diagnosis
+ df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  ungroup() #n=122
+
+##### healthy vs sick
+#Fornix gam Diagnosis; DiagnosisMS+Anxiety    342.5      382.7   0.895   0.3726   = NS
+anxietyDiagnosis_mean_F_by_sex_gam <- gam(mean_fornix_volume ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+summary(anxietyDiagnosis_mean_F_by_sex_gam)
+
+#define group for dose
 df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
@@
 
-  #gam, Fornix mean anxiety_dose - NS
+  #gam, Fornix anxiety_dose    186.5      168.0   1.110    0.268  =NS
   anxietyGrouping_mean_F_by_sex_gam <- gam(mean_fornix_volume ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-### Sex Differences
+### Sex Differences lm and chisq
 ```{r diseaseXsexdiff}
@@
 num_total <-as.numeric(c(anxiety_total_0,anxiety_total_1, anxiety_total_2))
-df_2x3_anxiety_score_by_total_people_per_diagnosis <- data.frame(cbind(num_w_anxiety_female, num_total), row.names = c("MS+AnxietyandMed", "MS+AnxietyorMed", "MS-Anxiety"))
+df_2x3_anxiety_score_by_total_people_per_diagnosis <- data.frame(cbind(num_w_anxiety_female, num_total), row.names = c("MS+noAnxiety","MS+AnxietyorMed", "MS+AnxietyandMed"))
 
@@
 num_total_just_healthy_and_sick <-as.numeric(c(anxiety_total_0,anxiety_total_2))
-df_2x2_anxiety_score_by_total_people_per_diagnosis_num_total_just_healthy_and_sick <- data.frame(cbind(num_w_anxiety_female_just_healthy_and_sick, num_total_just_healthy_and_sick), row.names = c("MS+AnxietyandMed", "MS-Anxiety"))
+df_2x2_anxiety_score_by_total_people_per_diagnosis_num_total_just_healthy_and_sick <- data.frame(cbind(num_w_anxiety_female_just_healthy_and_sick, num_total_just_healthy_and_sick), row.names = c("MS+noAnxiety", "MS+AnxietyandMed"))
 

### 2024-08-22 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
added IF/Steroids sensitivity analysis

@@
 
-##### Physical and Mental Health x anxiety dose intx
+##### Physical and Mental Health x anxiety dose intx -N.S.
 ```{r phys_and_mental_x_anxiety_dose}
@@
 
+##### No steroids/IF -N.S. but low n's
+```{r no_steroids_or_if}
+#### Steroids and interferon are known to have psychiatric side effects
+### we repeated our analyses but removed these groups
+### Nothing sig but trend, probably because we lose N (2 people in MS+noA, 1 in MS+mildA, 2 in MS+severeA)
+
+### remove people on IF or steroids
+df_demo_and_fascicles_no_steroids_or_ifn <- df_demo_and_fascicles %>%
+  filter((On.Steroids == 0) & (On.Interferon == 0))
+
+### print demographics, MS+noA = 96, MS+mildA = 248, MS+severeA=21
+make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles_no_steroids_or_ifn[df_demo_and_fascicles_no_steroids_or_ifn$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
+
+make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles_no_steroids_or_ifn[((df_demo_and_fascicles_no_steroids_or_ifn$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_demo_and_fascicles_no_steroids_or_ifn$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
+
+## Make df for Anxiety Diagnosis
+#define group
+  uncinate_by_dx_df <- df_demo_and_fascicles_no_steroids_or_ifn %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+ # dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol, mean_UF_vol) %>%
+  ungroup()
+
+#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety    768.2      422.2   1.820   0.0715 .  trend, likely due to sample size
+disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
+summary(disease_mean_UF_vol_gam)
+
+##test Anxiety Severity Model
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles_no_steroids_or_ifn %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) #n=371
+
+  #bilat anxiety dose + sex + age: anxiety_dose: anxiety_dose    369.9      189.7   1.949    0.052 . (trend, likely due to sample size)   
+  anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_mean_UF_by_sex_gam)
+
+```
+
 #### Plots Uncinate R,L,mean Prop
@@
 
-### Sex Differences lm and chisq
+### Sex Differences lm and chisq - N.S.
 ```{r diseaseXsexdiff}
@@
 ```{r individual_fascicle_disease_healthy_vs_super_sick}
+
 df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%

### 2024-08-27 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
cleaned after recs from audrey

@@
 2. Total unique who had good MIMoSA - 867 (lost 159)
-3. Remove people without MS provider, n=823 (lost 44)
-4. Remove people with bad streamline filtering, n=854 (lost 13)
-5. Remove people without MS provider, n=812 (lost 42)
-
-### testing mean UF in depression group  - NS!!!
-(previous script (~/BBL/msdepression/scripts/Biological_Psychiatry_Revision_Scripts/msdepression_n380_started_20230927_mm_BP_r1.Rmd)), lines 734 and  779-781
-  #bilat: depGroupVar        85.32     206.70   t=0.413    p=0.680    
-  disease_mean_UF_vol_lm <- lm(mean_UF_vol ~ depGroupVar + osex+PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)
-  summary(disease_mean_UF_vol_lm)
+3. Remove people without MS provider, n=814 (lost 53)
 
@@
 
- #n = 812
+ #n = 814
 df_demo_and_fascicles <- df_people_with_good_mimosa %>% 
@@
   filter(!is.na(CNII_L)) %>% #this is a sample fascicle that should have a value. if it does not, it means something is usually wrong with whole person. Remove rows with NAs, n=854, lost 13
-  filter(!is.na(Has.MS.Provider))  #remove people who don't have MS provider, n=823 (lost 42)
+  filter(!is.na(Has.MS.Provider))  #remove people who don't have MS provider, n=814 (lost 53)
 
@@
 ##########################################################
-#merge whole data set with fascicle proportions, n = 812
+#merge whole data set with fascicle proportions, n = 814
 df_demo_and_fascicles <- df_demo_and_fascicles %>%
@@
 #df_demo_and_fascicle_volumes_full <- cbind(df_everything_else, df_fascicle_volumes)
-df_demo_and_fascicles <- cbind(df_everything_else, df_fascicles_prop, df_fascicles_volumes)
+df_demo_and_fascicles <- cbind(df_everything_else, df_fascicles_prop, df_fascicles_volumes) #n=814
 ```
@@
 
-  #anxiety_dose  0.04955    0.01905   2.601  0.00966 ** 
+  #anxiety_dose  0.04849    0.01890   2.566   0.0107 *  
   anxietyGrouping_by_sex_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + osex+ s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-#gam lesion volumes; DiagnosisMS+Anxiety   8765.2     2748.2   3.189  0.00183 ** 
+#gam lesion volumes; DiagnosisMS+Anxiety   8215.7     2702.7   3.040  0.00292 ** 
 volume_of_mimosa_lesions_gam <- gam(volume_of_mimosa_lesions ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
@@
 
- #bilat anxiety dose + sex + age: anxiety_dose     3995       1263   3.164  0.00169 **
+ #bilat anxiety dose + sex + age: anxiety_dose     3866       1254   3.084   0.0022 **
 
@@
 
-#X-squared (Pearson's) X-squared(2,371) = 0.059833, p = 0.9705
+#X-squared (Pearson's) X-squared(2,372) = 0.077073, p = 0.9622
 chisq_anxiety_dose <- chisq.test(x=df_2x3_presence_of_UF_lesions_by_total_people_per_dose)
@@
 
-#X-squared(1,122) = 0.001529, p = 0.9688
+#X-squared(1,123) = 0.0052081, p = 0.9425
 chisq_healthy_vs_sick <- chisq.test(x = df_2x2_UF_lesions_by_total_people_per_diagnosis_num_total_just_healthy_and_sick)
@@
 
-#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety    866.7      411.9   2.104   0.0375 *  
+#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety   816.97     404.08   2.022   0.0454 * 
 disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
@@
 
-  #bilat anxiety dose + sex + age: anxiety_dose    394.7      185.7   2.126   0.0342 * 
+  #bilat anxiety dose + sex + age: anxiety_dose    383.3      184.3   2.080   0.0383 *  
   anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
   #laterality 
-  #overall - t = -8.1948, df = 660.22, p-value = 1.304e-15
+  #overall - t = -8.2035, df = 661.94, p-value = 1.217e-15
   right_vs_left_uncinate <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol, df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol)
@@
 
-  #healthy - t = -4.4646, df = 172.88, p-value = 1.443e-05
+  #healthy - t = -4.3999, df = 171.31, p-value = 1.898e-05
    right_vs_left_uncinate_healthy <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0])
@@
 
-  #anxietydx or meds -t = -6.5586, df = 443.4, p-value = 1.516e-10
+  #anxietydx or meds, t = -6.5586, df = 443.4, p-value = 1.516e-10
   right_vs_left_uncinate_anxiety_or_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1])
@@
 
-  #anxious+meds,t = -2.2382, df = 40.97, p-value = 0.0307
+  #anxious+meds,t = -2.261, df = 42.723, p-value = 0.02891
    right_vs_left_uncinate_anxiety_and_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2])
@@
 
-#mean UF, T=-1.7, P = NS
+#mean UF, T=-1.678, P = NS
 dep_mean_UF_gam <- gam(mean_UF_vol ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
@@
 ##### healthy vs sick
-#Fornix gam Diagnosis; DiagnosisMS+Anxiety    342.5      382.7   0.895   0.3726   = NS
+#Fornix gam Diagnosis; DiagnosisMS+Anxiety    283.0      375.6   0.753   0.4528   - NS
 anxietyDiagnosis_mean_F_by_sex_gam <- gam(mean_fornix_volume ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
@@
 
-  #gam, Fornix anxiety_dose    186.5      168.0   1.110    0.268  =NS
+  #gam, Fornix anxiety_dose    173.1      166.7   1.038    0.300   - NS
   anxietyGrouping_mean_F_by_sex_gam <- gam(mean_fornix_volume ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 ### Nothing sig but trend, probably because we lose N (2 people in MS+noA, 1 in MS+mildA, 2 in MS+severeA)
+### Will not report these analyses, but just note number of people in the table who are on these things
 
@@
 
-### print demographics, MS+noA = 96, MS+mildA = 248, MS+severeA=21
+### print demographics, MS+noA = 96, MS+mildA = 248, MS+severeA=22
 make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles_no_steroids_or_ifn[df_demo_and_fascicles_no_steroids_or_ifn$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
@@
 
-#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety    768.2      422.2   1.820   0.0715 .  trend, likely due to sample size
+#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety    718.8      413.2    1.74   0.0846 .   trend, likely due to sample size
 disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
@@
 
-  #bilat anxiety dose + sex + age: anxiety_dose: anxiety_dose    369.9      189.7   1.949    0.052 . (trend, likely due to sample size)   
+  #bilat anxiety dose + sex + age: anxiety_dose: anxiety_dose    358.3      188.3   1.903   0.0578 .   (trend, likely due to sample size)   
   anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-#X-squared (Pearson's) X-squared = 0.23427, df = 2, p-value = 0.8895
+#X-squared (Pearson's) X-squared = 0.23182, df = 2, p-value = 0.8906
 chisq_anxiety_dose <- chisq.test(df_2x3_anxiety_score_by_total_people_per_diagnosis)
@@
 
-#just healthy and super anxious/sick, X-squared = 0, df = 1, p-value = 1
+#just healthy and super anxious/sick, X-squared = 2.9757e-31, df = 1, p-value = 1
 num_w_anxiety_female_just_healthy_and_sick <- as.numeric(c(anxiety_female_0, anxiety_female_2))
@@
 
-#overall - NS
+#overall - osex.L          -0.0154963  0.0180285  -0.860    0.391 - NS
 disease_between_sexes <- lm(proportion_volume_lost_per_total_network_size_sum ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-# mean uncinate L - ns
+# mean uncinate L - osex.L          -152.317    174.353  -0.874    0.383 ns
 disease_between_sexes_UF_mean <- lm(mean_UF_vol ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 ### diagnosis by age interaction?
-#overall - NS for diagnosis
+#overall - DiagnosisMS+Anxiety  0.03966    0.02329   1.703   0.0893 .  NS for diagnosis
 diagnosis_by_age <- lm(proportion_volume_lost_per_total_network_size_sum ~ Diagnosis*PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 #gam diagnosis - SPLINE SIGNIFICANT
-#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.579  1.927 5.027  0.0138 * 
-#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.988  2.379 5.205  0.0033 **
+#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.581  1.930 5.026 0.01362 * 
+#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.994  2.385 5.249 0.00313 **
 diagnosis_by_age_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 
-#uncinate mean
-#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.006  1.013 23.95 2.10e-06 ***
-#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.000  1.000 17.02 4.59e-05 ***
+#uncinate mean, DiagnosisMS+Anxiety    420.3      224.9   1.869   0.0624 . NS
+#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.007  1.014 23.98 2.07e-06 ***
+#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.000  1.000 17.15 4.36e-05 ***
 
@@
 ## Sex diff trajectories by age
-#overall - NS
+#overall - osex.L                  0.066402   0.075006   0.885  0.37658  NS
 sex_by_age <- lm(proportion_volume_lost_per_total_network_size_sum ~ osex*PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-#gam dose; s(PAT_AGE_AT_EXAM):anxiety_dose 3.046783 3.441174 5.334908 0.001092626
+#gam dose; s(PAT_AGE_AT_EXAM):anxiety_dose 2.058  2.452 4.972 0.00315 **
 diagnosis_by_age_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 #gam factor - there is a linear dose effect per network size sum, as well as a sig age by anxiety relationship, but only in sick people
-#anxiety_dose_factor.L  0.08111    0.03267   2.482   0.0135 * 
-#(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.457  1.762 5.730  0.0139 *
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.927  2.326 1.924  0.1394  
+#anxiety_dose_factor.L  0.07788    0.03209   2.427   0.0157 * 
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.459  1.765 5.736  0.0138 *
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.972  2.372 2.128  0.1123  
 diagnosis_by_age_gam_factor <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 #dose
-#s(PAT_AGE_AT_EXAM):anxiety_dose   2  2.001 7.423 0.00069 ***
+#s(PAT_AGE_AT_EXAM):anxiety_dose 1.003  1.005 12.59 0.000427 ***
 diagnosis_by_age_mean_UF_gam <- gam(mean_UF_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 #factor
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.002  1.004 17.439 3.73e-05 ***
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.002  1.004  0.014    0.913   
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.002  1.004 17.462 3.69e-05 ***
+#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.002  1.005  0.029    0.872 
 diagnosis_by_age_mean_UF_gam_factor <- gam(mean_UF_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
@@
 ## Sex diff trajectories by age
-#overall - NS
+#overall -osex.L                  0.066402   0.075006   0.885  0.37658  NS
 sex_by_age <- lm(proportion_volume_lost_per_total_network_size_sum ~ osex*PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-#uncorrected
+#uncorrected, n=33
 fascicle_anova_lm_p <- sapply(fascicle_lm_anova, function(v) v$"Pr(>F)"[1])
@@
 
-#fdr corrected
+#fdr corrected, n = 11
 fascicle_anova_lm_fdr <- fdr_anova_generic(fascicle_lm_anova, 1, print_unc_df = TRUE)
@@
 
-#uncorrected
+#uncorrected (38 items)
 fascicle_anova_gam_p <- sapply(fascicle_anova_gam, function(v) v$p.pv[2])
@@
 
-#fdr corrected
+#fdr corrected (18 items correct)
 fascicle_anova_gam_fdr <- round(p.adjust(fascicle_anova_gam_p, method = "fdr"),3)
@@
 
-### 3 meet FDR - C_FPH_R_prop	0.037			C_FP_R_prop	0.042			DRTT_R_prop	0.042
+### 
 df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
@@
 
-#fdr corrected
+#fdr corrected, n = 1
 fascicle_anova_lm_fdr <- fdr_anova_generic(fascicle_anova_lm, 1, print_unc_df = TRUE)
@@
 
-#uncorrected
+#uncorrected, n = 19
 fascicle_anova_lm_p <- sapply(fascicle_anova_lm, function(v) v$"Pr(>F)"[1])
@@
 
-#uncorrected
+#uncorrected, n = 30
 fascicle_anova_gam_p <- sapply(fascicle_anova_gam, function(v) v$p.pv[2])
@@
 
-#fdr corrected
+#fdr corrected, n = 11
 fascicle_anova_gam_fdr <- round(p.adjust(fascicle_anova_gam_p, method = "fdr"),3)
@@
 ```{r}
-#n = 371
+#n = 372
 
@@
 prop_injured_by_anxiety_burden_collapsed_vars_plot
-```
-
-##### Plots C_FPH_R_prop	0.037			C_FP_R_prop	0.042			DRTT_R_prop	0.042
-
-```{r plots_areas_that_FDR_correct}
-
-#n=371
-
-df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified")
-
- #proportion injured over C_FPH_R_prop
-prop_injured_C_FPH_R_prop_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=C_FPH_R_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_C_FPH_R_prop_by_anxiety_burden_collapsed_vars_plot
-
- #proportion injured over C_FPH_R_prop - geom_bar
-means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$C_FPH_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$C_FPH_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$C_FPH_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
-
-df_C_FPH_R_prop_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
-
-names(df_C_FPH_R_prop_mean_by_anxiety_dose) <- c("C_FPH_R_prop", "Anxiety_dose")
-
-df_C_FPH_R_prop_mean_by_anxiety_dose <- df_C_FPH_R_prop_mean_by_anxiety_dose %>%
-  mutate(mean_C_FPH_R_prop = as.numeric(C_FPH_R_prop)) %>%
-  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
-
-prop_injured_C_FPH_R_prop_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_C_FPH_R_prop_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_C_FPH_R_prop, fill=Anxiety_dose)) +
-  geom_bar(stat="identity") +  
-  ylim(0,1)+
-#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
-        panel.background = element_rect(colour = "white", fill = "white"))
-prop_injured_C_FPH_R_prop_by_anxiety_burden_collapsed_vars_plot_bar
-
- #proportion injured over C_FP_R_prop
-prop_injured_C_FP_R_prop_prop_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=C_FP_R_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_C_FP_R_prop_prop_by_anxiety_burden_collapsed_vars_plot
-
- #proportion injured over C_FP_R_prop - geom_bar
-means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$C_FP_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$C_FP_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$C_FP_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
-
-df_C_FP_R_prop_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
-
-names(df_C_FP_R_prop_mean_by_anxiety_dose) <- c("C_FP_R_prop", "Anxiety_dose")
-
-df_C_FP_R_prop_mean_by_anxiety_dose <- df_C_FP_R_prop_mean_by_anxiety_dose %>%
-  mutate(mean_C_FP_R_prop = as.numeric(C_FP_R_prop)) %>%
-  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
-
-prop_injured_C_FP_R_prop_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_C_FP_R_prop_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_C_FP_R_prop, fill=Anxiety_dose)) +
-  geom_bar(stat="identity") +  
-  ylim(0,1)+
-#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
-        panel.background = element_rect(colour = "white", fill = "white"))
-prop_injured_C_FP_R_prop_by_anxiety_burden_collapsed_vars_plot_bar
-
- #proportion injured over DRTT_R_prop
-prop_injured_DRTT_R_prop_prop_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=DRTT_R_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_DRTT_R_prop_prop_by_anxiety_burden_collapsed_vars_plot
-
- #proportion injured over DRTT_R_prop - geom_bar
-means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$DRTT_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$DRTT_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$DRTT_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
-
-df_DRTT_R_prop_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
-
-names(df_DRTT_R_prop_mean_by_anxiety_dose) <- c("DRTT_R_prop", "Anxiety_dose")
-
-df_DRTT_R_prop_mean_by_anxiety_dose <- df_DRTT_R_prop_mean_by_anxiety_dose %>%
-  mutate(mean_DRTT_R_prop = as.numeric(DRTT_R_prop)) %>%
-  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
-
-prop_injured_DRTT_R_prop_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_DRTT_R_prop_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_DRTT_R_prop, fill=Anxiety_dose)) +
-  geom_bar(stat="identity") +  
-  ylim(0,1)+
-#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
-        panel.background = element_rect(colour = "white", fill = "white"))
-prop_injured_C_FP_R_prop_by_anxiety_burden_collapsed_vars_plot_bar
-
 ```
@@
 
-#bilateral UF ~ Diagnosis: N.S.
+#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety   -187.4      885.1  -0.212    0.835 N.S.
 disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
@@
 
-  #bilat anxiety dose - NS
+  #bilat anxiety dose -anxiety_dose   -46.71     423.41  -0.110 0.912524   NS
   anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)

### 2024-08-27 scripts/clean_dac_pull_icd10_codes_and_make_clean_df_post_replication.R

@@ -1,0 +1,190 @@
+### Clean data frame up
+
+##pre: dac pulls from 2023 with full psychiatric ICD10 codes
+##post: rds that contains beautifully curated all_icd10_dx column. 
+## uses: Takes the dac pull, combines csvs, adds column with beautifully curated icd10 codes
+## dependencies: dplyr
+
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(purrr)
+
+
+######################
+## FUNCTIONS #########
+######################
+####Extract unique ICD10 codes
+### takes an empi, returns all the unique diagnostic codes.
+### steps: 1) filter data frame by EMPI; 2) separate into 1 column per diagnosis; 3) remove doubles; 4) combine/paste into 1 column separated by semicolons; 5) return
+get_all_unique_ICD10_diagnoses <- function(indiv_empi) {
+  data_frame<-data_pull
+  all_unique_diagnoses <- data_frame %>% 
+    filter(str_detect(EMPI, indiv_empi)) %>% 
+    dplyr::select(ICD10) %>%
+    separate_rows(ICD10, sep = ";") %>%
+    summarize(all_icd_codes = paste(unique(ICD10), collapse = ";"))
+  #print(all_unique_diagnoses$all_icd_codes)
+  return(all_unique_diagnoses$all_icd_codes)
+}
+
+
+
+######################
+## CODE ##############
+######################
+
+#this goes through dac pulls, combines them, cleans them, and saves them as rds that can be loaded in other analyses. To clean up. 
+
+#############################################################################################################################
+### ***** MUST CHANGE THE HOMEDIR  AND THE PATHS TO DATA AND OUTPUT IN ORDER FOR THIS TO WORK ON A NEW PULL> THIS IS REALLY IMPORTANT ###
+#############################################################################################################################
+
+homedir <- "/Users/eballer/BBL/msanxiety/"
+
+## output directory
[…]

### 2024-08-27 scripts/clean_dac_pull_icd10_codes_and_make_clean_df_post_replication.R
Went back to loop

@@ -70,10 +70,10 @@ data_pull <- rbind(data_pt1, data_pt2) %>%
   mutate(all_icd10_dx = "NA")
 
 #assemble new data frame and change names of ICD9/10 columns to reflect that they contain multiple dx
-data_pull$all_icd10_dx <- map(data_pull$EMPI, get_all_unique_ICD10_diagnoses)
-#for(row in 1:dim(data_pull)[1]) {
-#  data_pull$all_icd10_dx[row] <- get_all_unique_ICD10_diagnoses(data_pull$EMPI[row])
-#}
+
+for(row in 1:dim(data_pull)[1]) {
+  data_pull$all_icd10_dx[row] <- get_all_unique_ICD10_diagnoses(data_pull$EMPI[row])
+}
 
 columns_to_make_integer <- c("ACCESSION_NUM", "PAT_AGE_AT_EXAM","MRI_ENC_AGE","CURRENT_AGE","hemoglobin", "WBC","RBC","B12","FOLATE", "TSH", "RPR","CSFAPPEAR1","CSFAPPEAR4","CSFCOLOR1", "CSFCOLOR4","CSFTUBE","CSFTUBE4","PHQ.2","PHQ.9") #removed "VitD", not in new pull for some reason
 

### 2024-08-28 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
adding line to display output

@@
 library(tidymv)
+
 #functions
@@
   summary(anxietyGrouping_by_sex_mean_disease_gam)
+
+  #print summary stats
+  gam_summary_stats(anxietyGrouping_by_sex_mean_disease_gam)
 ```
@@
 summary(volume_of_mimosa_lesions_gam)
+
+ #print summary stats
+ gam_summary_stats(volume_of_mimosa_lesions_gam)
 ```
@@
   summary(anxiety_dose_volume_of_mimosa_lesions_by_sex_gam)
+
+   #print summary stats
+ gam_summary_stats(anxiety_dose_volume_of_mimosa_lesions_by_sex_gam)
 
@@
 uncinate_lesions_dose_1 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(has.uncinate.lesion == 1 & anxiety_dose == 1) %>% count() #n=190
-uncinate_lesions_dose_2 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(has.uncinate.lesion == 1 & anxiety_dose == 2) %>% count() #n=19
+uncinate_lesions_dose_2 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(has.uncinate.lesion == 1 & anxiety_dose == 2) %>% count() #n=20
 
@@
 anxiety_total_dose_1 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(anxiety_dose == 1) %>% count() #n=249
-anxiety_total_dose_2 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(anxiety_dose == 2) %>% count() #n=23
+anxiety_total_dose_2 <- df_demo_and_fascicles_no_unclass_anxiety_dose %>% filter(anxiety_dose == 2) %>% count() #n=24
 
@@
 
+#print summary stats
+ gam_summary_stats(disease_mean_UF_vol_gam)
 ```
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) #n=371
+  filter(anxiety_dose != -1) #n=372
 
@@
   summary(anxietyGrouping_mean_UF_by_sex_gam)
+
+  #print summary stats
+ gam_summary_stats(anxietyGrouping_mean_UF_by_sex_gam)
 
@@
 
-table(df_dep$depDiagnosis) #MS+Dep n = 199; MS+noDep n = 99
-
-#mean UF, T=-1.678, P = NS
+table(df_dep$depDiagnosis) #MS+Dep n = 207; MS+noDep n = 99
+
+#mean UF, depDiagnosisMS+noDepression   -386.4      232.8  -1.660    0.098 .
 dep_mean_UF_gam <- gam(mean_UF_vol ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
@@
 
+  #print summary stats
+ gam_summary_stats(dep_mean_UF_gam)
 ```
@@
 
+ #print summary stats
+ gam_summary_stats(anxietyDiagnosis_mean_F_by_sex_gam)
+
 #define group for dose
@@
   summary(anxietyGrouping_mean_F_by_sex_gam)
+
+ #print summary stats
+ gam_summary_stats(anxietyGrouping_mean_F_by_sex_gam)
 ```
@@
 
+ #print summary stats
+ gam_summary_stats(disease_mean_UF_vol_gam)
+
 ##test Anxiety Severity Model
@@
 
+   #print summary stats
+ gam_summary_stats(anxietyGrouping_mean_UF_by_sex_gam)
 ```
@@
 summary(diagnosis_by_age_gam)$s.table
+
+  #print summary stats
+ gam_summary_stats(diagnosis_by_age_gam)
 
@@
 
+  #print summary stats
+ gam_summary_stats(diagnosis_by_age_mean_UF_gam)
+
 #gam UF mean plot
@@
 #plot(diagnosis_by_age_gam)
+
+  #print summary stats
+ gam_summary_stats(diagnosis_by_age_gam)
 
@@
 
+  #print summary stats
+ gam_summary_stats(diagnosis_by_age_gam_factor)
+
 #plot proportion_volume_lost_per_total_network_size_sum
@@
 
+  #print summary stats
+ gam_summary_stats(diagnosis_by_age_mean_UF_gam_factor)
+
 #gam mean
@@
 
+    #print summary stats
+ gam_summary_stats(disease_mean_UF_vol_gam)
+
 ```
@@
 
-```
+    #print summary stats
+ gam_summary_stats(anxietyGrouping_mean_UF_by_sex_gam)
+
+```

### 2024-08-28 scripts/clean_dac_pull_icd10_codes_and_make_clean_df_post_replication.R

@@ -158,7 +158,7 @@ data_final_rds <-data_pull %>%
   mutate(PHQ.9_zero = ifelse((Has.PHQ9==1) & PHQ.9 == 0, 1, 0)) %>%
   
   #Create variables based on psychiatric diagnoses
-  mutate(Has.depdx = ifelse(grepl("F3[2:4]", all_icd10_dx), 1, 0)) %>%
+  mutate(Has.depdx = ifelse(grepl("F3[2-4](\\.|\\d)*", all_icd10_dx), 1, 0)) %>%
   mutate(Has.anxietydx = ifelse(grepl("F4", all_icd10_dx), 1, 0)) %>%
   mutate(Has.CannabisUsedx = ifelse(grepl("F12", all_icd10_dx), 1, 0)) %>%
   mutate(Has.Anxietydx.Or.Antianxietymed = ifelse((Has.anxietydx==1) | (On.Anxiolytics==1),1,0)) %>%

### 2024-08-28 scripts/ms_functions.R

@@ -93,6 +93,91 @@ make_demographics_table_ms_anxiety_simple<- function(data_frame) {
   
 }
 
+make_demographics_table_ms_w_promis_anxiety<- function(data_frame) {
+  #subset demographics
+  
+  #subset demographics
+  
+  listVars <- c("Race", 
+                "Sex",
+                "Age",
+                "Has.anxietydx", 
+                "On.Anxiolytics",
+                "oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed",
+                "anxiety_dose",
+                "on_anti_cd20",
+                "on_interferon",
+                "on_steroids",
+                "on_dmt",
+                "PHQ2",
+                "PHQ9",
+                "volume_of_mimosa_lesions", 
+                "mean_UF_vol",
+                "proportion_volume_lost_per_total_network_size_sum",
+                "Quality_of_Life", 
+                "Physical_Health", 
+                "Mental_Health_and_Mood",
+                "Social_Activities_Satisfaction",
+                "Carrying_Out_Social_Activities",
+                "Carrying_Out_Physical_Activities",
+                "Emotional_Problems", 
+                "Fatique_Average",
+                "PostOp.PROMIS.Physical.Score",
+                "PostOp.PROMIS.Mental.Score") #Race 1 = caucasian, Sex 1 = M age = years
+  
+  
+  #for_parse <- paste0("data.frame(data_frame$race_binarized, data_frame$sex_binarized, data_frame$PAT_AGE_AT_EXAM, data_frame$depGroupVar, data_frame$PHQ.2, data_frame$PHQ.9)")
+  # for_parse <- paste0(data.frame(data_frame$race_binarized,
+  for_parse <- paste0("data.frame(data_frame$RACE, 
+                      data_frame$sex_binarized, 
+                      data_frame$PAT_AGE_AT_EXAM, 
+                      data_frame$Has.anxietydx, 
+                      data_frame$On.Anxiolytics,
+                      data_frame$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed,
+                      data_frame$anxiety_dose,
+                      data_frame$On.Anti_cd20,
[…]

### 2024-08-29 scripts/MSAnxiety_manuscript_audrey_replication_prop.Rmd
changed vol to prop - more approp for uf

--- 2024-08-28 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
@@
   filter(anxiety_dose != -1) %>% #n=371
-  mutate(has.uncinate.lesion = ifelse(mean_UF_vol >0, 1, 0)) #anywhere where there is *some* overlap counts as a 1 - they have an uncinate lesion, otherwise 0
+  mutate(has.uncinate.lesion = ifelse(mean_UF_prop >0, 1, 0)) #anywhere where there is *some* overlap counts as a 1 - they have an uncinate lesion, otherwise 0
 
@@
 
-#### Uncinate by anxiety diagnosis 
+#### Uncinate by anxiety diagnosis (vol and prop)
 ```{r uncinate_by_dx}
@@
   mutate(Diagnosis = as.factor(Diagnosis)) %>%
- # dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol, mean_UF_vol) %>%
-  ungroup() #n=122
-
-#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety   816.97     404.08   2.022   0.0454 * 
-disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
-summary(disease_mean_UF_vol_gam)
+  ungroup() #n=123
+
+#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety   0.10624    0.05255   2.022   0.0455  * 
+disease_mean_UF_prop_gam <- gam(mean_UF_prop ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
+summary(disease_mean_UF_prop_gam)
 
  #print summary stats
- gam_summary_stats(disease_mean_UF_vol_gam)
-```
-
-#### Uncinate by Anxiety Dose 
+  gam_summary_stats(disease_mean_UF_prop_gam)
+```
+
+#### Uncinate by Anxiety Dose (vol and prop)
 ```{r uncinateByAnxietyDose}
@@
 
-  #bilat anxiety dose + sex + age: anxiety_dose    383.3      184.3   2.080   0.0383 *  
-  anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_mean_UF_by_sex_gam)
+    #bilat anxiety dose + sex + age: anxiety_dose    0.04989    0.02397   2.082   0.0381 * 
+ anxietyGrouping_mean_UF_by_sex_gam_prop <- gam(mean_UF_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_mean_UF_by_sex_gam_prop)
 
   #print summary stats
- gam_summary_stats(anxietyGrouping_mean_UF_by_sex_gam)
-
-```
-
-###### Laterality in uncinate
+  gam_summary_stats(anxietyGrouping_mean_UF_by_sex_gam_prop)
+
+```
+
+###### Laterality in uncinate (prop)
 ```{r laterality}
   #laterality 
-  #overall - t = -8.2035, df = 661.94, p-value = 1.217e-15
-  right_vs_left_uncinate <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol, df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol)
+  #overall - t = -7.9761, df = 668.34, p-value = 6.564e-15
+  right_vs_left_uncinate <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_prop, df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_prop)
   print(right_vs_left_uncinate)
 
-  #healthy - t = -4.3999, df = 171.31, p-value = 1.898e-05
-   right_vs_left_uncinate_healthy <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0])
+  #healthy - t = -4.2898, df = 173.04, p-value = 2.969e-05
+   right_vs_left_uncinate_healthy <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_prop[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_prop[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0])
   print(right_vs_left_uncinate_healthy)
 
-  #anxietydx or meds, t = -6.5586, df = 443.4, p-value = 1.516e-10
-  right_vs_left_uncinate_anxiety_or_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1])
+  #anxietydx or meds, t = -6.3724, df = 447.66, p-value = 4.629e-10
+  right_vs_left_uncinate_anxiety_or_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_prop[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_prop[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1])
   print(right_vs_left_uncinate_anxiety_or_meds)
 
-  #anxious+meds,t = -2.261, df = 42.723, p-value = 0.02891
-   right_vs_left_uncinate_anxiety_and_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2])
+  #anxious+meds,t = -2.19, df = 43.079, p-value = 0.03398
+   right_vs_left_uncinate_anxiety_and_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_prop[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_prop[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2])
   print(right_vs_left_uncinate_anxiety_and_meds)
@@
 #### Sensitivity
-###### UF by depGroupVar (N.S)
+###### UF by depGroupVar (vol and prop, N.S)
 ```{r UF_by_depGroupVar}
@@
 
-#mean UF, depDiagnosisMS+noDepression   -386.4      232.8  -1.660    0.098 .
-dep_mean_UF_gam <- gam(mean_UF_vol ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
-summary(dep_mean_UF_gam)
+ #mean UF, depDiagnosisMS+noDepression   -0.05029    0.03028  -1.661   0.0978 . 
+dep_mean_UF_gam_prop <- gam(mean_UF_prop ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
+summary(dep_mean_UF_gam_prop)
 
   #print summary stats
- gam_summary_stats(dep_mean_UF_gam)
-```
-
-###### Fornix by Anxiety Diagnosis and Dose (N.S)
+ gam_summary_stats(dep_mean_UF_gam_prop)
+```
+
+###### Fornix by Anxiety Diagnosis and Dose (vol and prop, N.S)
 ```{r fornixByAnxietyDose}
@@
 
-##### healthy vs sick
-#Fornix gam Diagnosis; DiagnosisMS+Anxiety    283.0      375.6   0.753   0.4528   - NS
-anxietyDiagnosis_mean_F_by_sex_gam <- gam(mean_fornix_volume ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
-summary(anxietyDiagnosis_mean_F_by_sex_gam)
-
- #print summary stats
- gam_summary_stats(anxietyDiagnosis_mean_F_by_sex_gam)
+ ##### healthy vs sick - prop
+#Fornix gam Diagnosis; DiagnosisMS+Anxiety    0.03690    0.05405   0.683   0.4961    - NS
+anxietyDiagnosis_mean_F_by_sex_gam_prop <- gam(mean_fornix_prop ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+summary(anxietyDiagnosis_mean_F_by_sex_gam_prop)
 
@@
 
-  #gam, Fornix anxiety_dose    173.1      166.7   1.038    0.300   - NS
-  anxietyGrouping_mean_F_by_sex_gam <- gam(mean_fornix_volume ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_mean_F_by_sex_gam)
+  #gam, Fornix anxiety_dose   0.02303    0.02401   0.959    0.338    - NS
+  anxietyGrouping_mean_F_by_sex_gam_prop <- gam(mean_fornix_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_mean_F_by_sex_gam_prop)
 
  #print summary stats
- gam_summary_stats(anxietyGrouping_mean_F_by_sex_gam)
+ gam_summary_stats(anxietyDiagnosis_mean_F_by_sex_gam_prop)
+ gam_summary_stats(anxietyGrouping_mean_F_by_sex_gam_prop)
 ```
@@
   mutate(Diagnosis = as.factor(Diagnosis)) %>%
- # dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol, mean_UF_vol) %>%
   ungroup()
 
-#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety    718.8      413.2    1.74   0.0846 .   trend, likely due to sample size
-disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
-summary(disease_mean_UF_vol_gam)
-
- #print summary stats
- gam_summary_stats(disease_mean_UF_vol_gam)
+ #bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety    0.09339    0.05373   1.738   0.0849 .    trend, likely due to sample size
+disease_mean_UF_gam_prop <- gam(mean_UF_prop ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
+summary(disease_mean_UF_gam_prop)
 
@@
 
-  #bilat anxiety dose + sex + age: anxiety_dose: anxiety_dose    358.3      188.3   1.903   0.0578 .   (trend, likely due to sample size)   
-  anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_mean_UF_by_sex_gam)
+  #bilat anxiety dose + sex + age: anxiety_dose: anxiety_dose    0.04662    0.02448   1.904   0.0577 .    (trend, likely due to sample size)   
+  anxietyGrouping_mean_UF_by_sex_gam_prop <- gam(mean_UF_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_mean_UF_by_sex_gam_prop)
 
    #print summary stats
- gam_summary_stats(anxietyGrouping_mean_UF_by_sex_gam)
+   gam_summary_stats(disease_mean_UF_gam_prop)
+   gam_summary_stats(anxietyGrouping_mean_UF_by_sex_gam_prop)
 ```
@@
 
-# mean uncinate L - osex.L          -152.317    174.353  -0.874    0.383 ns
-disease_between_sexes_UF_mean <- lm(mean_UF_vol ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-summary(disease_between_sexes_UF_mean)
-
-```
-
-### Age*Disease
-
-#### Anxiety diagnosis
-```{r anxiety_dx_x_age}
-
-#purpose of this analysis is to evaluate the relationship between disease (cross sectional) by diagnosis as well as by anxiety dose
-#hypothesize that anxiety vs nonanxiety will have worse disease overall, and that this may be related to anxiety dose
-#start by defining new variables and a new data frame that contains anxiety dose (as factor and as ordinal), as well as diagnosis (no anxiety vs severe anxiety)
-
-#define group
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) %>%
-  mutate(anxiety_dose_factor = ordered(anxiety_dose)) %>%
-  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(Diagnosis = as.factor(Diagnosis)) #n=371
-
-### diagnosis by age interaction?
-#overall - DiagnosisMS+Anxiety  0.03966    0.02329   1.703   0.0893 .  NS for diagnosis
-diagnosis_by_age <- lm(proportion_volume_lost_per_total_network_size_sum ~ Diagnosis*PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-summary(diagnosis_by_age)
-
-#gam diagnosis - SPLINE SIGNIFICANT
-#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.581  1.930 5.026 0.01362 * 
-#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.994  2.385 5.249 0.00313 **
-diagnosis_by_age_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_gam)
-summary(diagnosis_by_age_gam)$s.table
-
-  #print summary stats
- gam_summary_stats(diagnosis_by_age_gam)
-
-#plot proportion_volume_lost_per_total_network_size_sum
-plot_smooths_proportion_volume_lost_per_total_network_size_sum <- plot_smooths(
-  model = diagnosis_by_age_gam,
-  series = PAT_AGE_AT_EXAM,
-  comparison = Diagnosis
-) +
-  theme(legend.position = "top")
-plot_smooths_proportion_volume_lost_per_total_network_size_sum
-
-#uncinate mean, DiagnosisMS+Anxiety    420.3      224.9   1.869   0.0624 . NS
-#s(PAT_AGE_AT_EXAM):DiagnosisMS-Anxiety 1.007  1.014 23.98 2.07e-06 ***
-#s(PAT_AGE_AT_EXAM):DiagnosisMS+Anxiety 1.000  1.000 17.15 4.36e-05 ***
-
-diagnosis_by_age_mean_UF_gam <- gam(mean_UF_vol ~ Diagnosis+s(PAT_AGE_AT_EXAM, by = Diagnosis, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_mean_UF_gam)
-summary(diagnosis_by_age_mean_UF_gam)$s.table
-#plot(diagnosis_by_age_UF_L_gam)
-
-  #print summary stats
- gam_summary_stats(diagnosis_by_age_mean_UF_gam)
-
-#gam UF mean plot
-
-plot_smooths_anxiety_diagnosis_by_age_mean_UF_vol <- plot_smooths(
-  model = diagnosis_by_age_mean_UF_gam,
-  series = PAT_AGE_AT_EXAM,
-  comparison = Diagnosis
-) +
-  theme(legend.position = "top")
-plot_smooths_anxiety_diagnosis_by_age_mean_UF_vol
-
-## Sex diff trajectories by age
-#overall - osex.L                  0.066402   0.075006   0.885  0.37658  NS
-sex_by_age <- lm(proportion_volume_lost_per_total_network_size_sum ~ osex*PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-summary(sex_by_age)
-
-```
-
-#### Anxiety DOSE 
-```{r anxietydosexage}
-
-#purpose of this analysis is to evaluate the relationship between disease (cross sectional) by diagnosis as well as by anxiety dose
-#hypothesize that anxiety vs nonanxiety will have worse disease overall, and that this may be related to anxiety dose
-#start by defining new variables and a new data frame that contains anxiety dose (as factor and as ordinal), as well as diagnosis (no anxiety vs severe anxiety)
-
-#define group
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) %>%
-  mutate(anxiety_dose_factor = ordered(anxiety_dose)) %>%
-  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(Diagnosis = as.factor(Diagnosis))
-
-### diagnosis by age interaction?
-#overall - NS
-diagnosis_by_age <- lm(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose*PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-summary(diagnosis_by_age)
-
-#gam dose; s(PAT_AGE_AT_EXAM):anxiety_dose 2.058  2.452 4.972 0.00315 **
-diagnosis_by_age_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_gam)
-summary(diagnosis_by_age_gam)$s.table
-#plot(diagnosis_by_age_gam)
-
-  #print summary stats
- gam_summary_stats(diagnosis_by_age_gam)
-
-#gam factor - there is a linear dose effect per network size sum, as well as a sig age by anxiety relationship, but only in sick people
-#anxiety_dose_factor.L  0.07788    0.03209   2.427   0.0157 * 
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.459  1.765 5.736  0.0138 *
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.972  2.372 2.128  0.1123  
-diagnosis_by_age_gam_factor <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_gam_factor)
-summary(diagnosis_by_age_gam_factor)$s.table
-#plot(diagnosis_by_age_gam_factor)
-
-  #print summary stats
- gam_summary_stats(diagnosis_by_age_gam_factor)
-
-#plot proportion_volume_lost_per_total_network_size_sum
-plot_smooths_proportion_volume_lost_per_total_network_size_sum <- plot_smooths(
-  model = diagnosis_by_age_gam_factor,
-  series = PAT_AGE_AT_EXAM,
-  comparison = anxiety_dose_factor
-) +
-  theme(legend.position = "top")
-plot_smooths_proportion_volume_lost_per_total_network_size_sum
-
-#uncinate mean
-#dose
-#s(PAT_AGE_AT_EXAM):anxiety_dose 1.003  1.005 12.59 0.000427 ***
-diagnosis_by_age_mean_UF_gam <- gam(mean_UF_vol ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_mean_UF_gam)
-summary(diagnosis_by_age_mean_UF_gam)$s.table
-
-#factor
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor1 1.002  1.004 17.462 3.69e-05 ***
-#s(PAT_AGE_AT_EXAM):anxiety_dose_factor2 1.002  1.005  0.029    0.872 
-diagnosis_by_age_mean_UF_gam_factor <- gam(mean_UF_vol ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor, k=4, fx = F), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
-summary(diagnosis_by_age_mean_UF_gam_factor)
-summary(diagnosis_by_age_mean_UF_gam_factor)$s.table
-#plot(diagnosis_by_age_UF_L_gam_factor)
-
-  #print summary stats
- gam_summary_stats(diagnosis_by_age_mean_UF_gam_factor)
-
-#gam mean
-
-plot_smooths_anxiety_dose_by_age_mean_UF_factor <- plot_smooths(
-  model = diagnosis_by_age_mean_UF_gam_factor,
-  series = PAT_AGE_AT_EXAM,
-  comparison = anxiety_dose_factor
-) +
-  theme(legend.position = "top")
-plot_smooths_anxiety_dose_by_age_mean_UF_factor
-
-## Sex diff trajectories by age
-#overall -osex.L                  0.066402   0.075006   0.885  0.37658  NS
-sex_by_age <- lm(proportion_volume_lost_per_total_network_size_sum ~ osex*PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-summary(sex_by_age)
-
-```
-
-### Individual Fascicle disease
-
-#### healthy vs super sick - values that fdr correct, most not anxiety net
-```{r individual_fascicle_disease_healthy_vs_super_sick}
-
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  mutate(anxiousAndMeds_or_healthy = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  filter(anxiousAndMeds_or_healthy %in% c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>%
-  mutate(anxiousAndMeds_or_healthy = factor(anxiousAndMeds_or_healthy, levels=c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
-
-#lm
-fascicle_lm <- lapply(fascicle_names_w_vol_suffix, function(x) 
-{
-  lm(substitute(i ~ anxiousAndMeds_or_healthy + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-})
-names(fascicle_lm) <- fascicle_names_w_vol_suffix
-
-#anova
-fascicle_lm_anova <- lapply(fascicle_lm, anova)
-
-#uncorrected, n=33
-fascicle_anova_lm_p <- sapply(fascicle_lm_anova, function(v) v$"Pr(>F)"[1])
-fascicle_anova_lm_p05_unc <- as.data.frame(fascicle_anova_lm_p[fascicle_anova_lm_p < 0.05])
-print(fascicle_anova_lm_p05_unc)
-
-#fdr corrected, n = 11
-fascicle_anova_lm_fdr <- fdr_anova_generic(fascicle_lm_anova, 1, print_unc_df = TRUE)
-print(fascicle_anova_lm_fdr)
-
-#gam
-fascicle_gam <- lapply(fascicle_names_w_vol_suffix, function(x) 
-{
-  gam(substitute(i ~ anxiousAndMeds_or_healthy + +osex+ s(PAT_AGE_AT_EXAM, k=4, fx=F), list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-})
-names(fascicle_gam) <- fascicle_names_w_vol_suffix
-
-#anova
-fascicle_anova_gam <- lapply(fascicle_gam, anova)
-
-#uncorrected (38 items)
-fascicle_anova_gam_p <- sapply(fascicle_anova_gam, function(v) v$p.pv[2])
-print(as.data.frame(fascicle_anova_gam_p))
-fascicle_anova_gam_p05_unc <- as.data.frame(fascicle_anova_gam_p[fascicle_anova_gam_p < 0.05])
-print(fascicle_anova_gam_p05_unc)
-
-#fdr corrected (18 items correct)
-fascicle_anova_gam_fdr <- round(p.adjust(fascicle_anova_gam_p, method = "fdr"),3)
-fascicle_anova_gam_fdr_p05 <- as.data.frame(fascicle_anova_gam_fdr[fascicle_anova_gam_fdr < 0.05])
-print(fascicle_anova_gam_fdr_p05) 
-```
-
-#### Parametric all fascicles
-```{r individual_fascicle_disease_anxiety_dose}
-
-### 
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) %>%
-  mutate(anxiety_dose_factor = ordered(anxiety_dose))
-
-#lm
-fascicle_lm <- lapply(fascicle_names_w_vol_suffix, function(x) 
-{
-  lm(substitute(i ~ anxiety_dose + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-})
-names(fascicle_lm) <- fascicle_names_w_vol_suffix
-
-#anova
-fascicle_anova_lm <- lapply(fascicle_lm, anova)
-
-#fdr corrected, n = 1
-fascicle_anova_lm_fdr <- fdr_anova_generic(fascicle_anova_lm, 1, print_unc_df = TRUE)
-print(fascicle_anova_lm_fdr)
-
-#uncorrected, n = 19
-fascicle_anova_lm_p <- sapply(fascicle_anova_lm, function(v) v$"Pr(>F)"[1])
-fascicle_anova_lm_p05_unc <- as.data.frame(fascicle_anova_lm_p[fascicle_anova_lm_p < 0.05])
-print(fascicle_anova_lm_p05_unc)
-
-#gam
-fascicle_gam <- lapply(fascicle_names_w_vol_suffix, function(x) 
-{
-  gam(substitute(i ~ anxiety_dose + osex+s(PAT_AGE_AT_EXAM, k=4, fx=F), list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
-})
-names(fascicle_gam) <- fascicle_names_w_vol_suffix
-
-#anova
-fascicle_anova_gam <- lapply(fascicle_gam, anova)
-
-#uncorrected, n = 30
-fascicle_anova_gam_p <- sapply(fascicle_anova_gam, function(v) v$p.pv[2])
-print(as.data.frame(fascicle_anova_gam_p))
-fascicle_anova_gam_p05_unc <- as.data.frame(fascicle_anova_gam_p[fascicle_anova_gam_p < 0.05])
-print(fascicle_anova_gam_p05_unc)
-
-#fdr corrected, n = 11
-fascicle_anova_gam_fdr <- round(p.adjust(fascicle_anova_gam_p, method = "fdr"),3)
-fascicle_anova_gam_fdr_p05 <- as.data.frame(fascicle_anova_gam_fdr[fascicle_anova_gam_fdr < 0.05])
-print(fascicle_anova_gam_fdr_p05) 
-```
+# mean uncinate L - osex.L          -0.019879   0.022675  -0.877    0.381  ns
+disease_between_sexes_UF_mean_prop <- lm(mean_UF_prop ~ osex+ PAT_AGE_AT_EXAM, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+summary(disease_between_sexes_UF_mean_prop)
+```
+
 ### Plots
 
-##### Overall disease, within and outside anxiety net
+##### Overall disease in brain
 ```{r}
@@
 
-#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety   -187.4      885.1  -0.212    0.835 N.S.
-disease_mean_UF_vol_gam <- gam(mean_UF_vol ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
-summary(disease_mean_UF_vol_gam)
+#bilateral UF prop ~ Diagnosis: DiagnosisMS+Anxiety -0.02490    0.11510  -0.216   0.8317 
+disease_mean_UF_prop_gam <- gam(mean_UF_prop ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
+summary(disease_mean_UF_prop_gam)
 
     #print summary stats
- gam_summary_stats(disease_mean_UF_vol_gam)
+ gam_summary_stats(disease_mean_UF_prop_gam)
 
@@
 
-  #bilat anxiety dose -anxiety_dose   -46.71     423.41  -0.110 0.912524   NS
-  anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_mean_UF_by_sex_gam)
+  #bilat anxiety dose -anxiety_dose   -0.006261   0.055025  -0.114 0.909793       NS
+  anxietyGrouping_mean_UF_by_sex_gam_prop <- gam(mean_UF_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxietyGrouping_mean_UF_by_sex_gam_prop)
 
     #print summary stats
- gam_summary_stats(anxietyGrouping_mean_UF_by_sex_gam)
-
-```
+
+ gam_summary_stats(anxietyGrouping_mean_UF_by_sex_gam_prop)
+
+```

### 2024-08-29 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL.Rmd
Add files via upload

--- 2024-08-29 scripts/MSAnxiety_manuscript_audrey_replication_prop.Rmd
@@
 #figure brainstorming
-1. Flowchart of inclusion/exclusion
-2. Demographics (age, sex, race, +/- PHQ2, PHQ9, has anxiety dx, on anxiety meds, both, on dmt) 
-3. Some sort of schematic of pipeline - 
+1. Flowchart of inclusion/exclusion (825 participants -> 11 lost for poor streamline filtering -> 814 go into phenotyping) -> Elena
+   A. Anxiety diagnosis
+    I. Yes
+       - Anxiety Med
+          a. Yes -> MS+severeA (24 individuals)
+          b. No  -> MS+mildA (87 indiv)
+     II. No
+        - Anxiety Med
+          a. Yes -> MS+mildA (162)
+          b. No
+            - Has PHQ2 or 9 and 0 
+              i. Yes-> MS+noA (99 individuals)
+              ii. No -> Unclassified (442 individuals)
+
+Final groups (MS+noA = 99, MS+mildA = 249, MS+severeA = 24)
+
+2. Demographics (age, sex, race, +/- PHQ2, PHQ9, has anxiety dx, on anxiety meds, both, on dmt) -> elena to make all the csvs into tables
+3. PROMIS scores (each type of measure is a line, y axis is score, x axis is anxiety dose)
+4. Some sort of schematic of pipeline (Maggie) - 
   a. amygdala - mpfc blobs
@@
   e. mean of both side
-4. Mean UF Anxiety diagnosis either violin or bar
-5. Mean Anxiety dose either violin or bar
-6. PROMIS scores (each type of measure is a line, y axis is score, x axis is anxiety dose)
+5. Mean UF Anxiety diagnosis either violin or bar
+6. Mean Anxiety dose either violin or bar
+
 7. Supplement: 
@@
   left_join(fascicle_proportions, by = c("EMPI", "EXAM_DATE")) %>%
-  filter(!is.na(CNII_L)) %>% #this is a sample fascicle that should have a value. if it does not, it means something is usually wrong with whole person. Remove rows with NAs, n=854, lost 13
-  filter(!is.na(Has.MS.Provider))  #remove people who don't have MS provider, n=814 (lost 53)
+    filter(!is.na(Has.MS.Provider)) %>% #remove people who don't have MS provider, n=825 (lost 52) 
+    filter(!is.na(CNII_L))# %>% #this is a sample fascicle that should have a value. if it does not, it means something is usually wrong with whole person. Remove rows with NAs, n=814, lost 11
 
@@
 
-#drop unnecessary columns c("DE_PAT_ID", "EMPI", "HUP_MRN", "SEX", "RACE")
-promis_info_closest_proximity_just_scores <- promis_info_closest_proximity[,6:dim(promis_info_closest_proximity)[2]]
-
-#combine with df_people_with_promis_data
-df_people_with_promis_data_scores_added = cbind(df_people_with_promis_data, promis_info_closest_proximity_just_scores)
+#drop unnecessary columns c("DE_PAT_ID", "HUP_MRN", "SEX", "RACE")
+promis_info_closest_proximity_just_scores <- promis_info_closest_proximity %>% 
+	select(-c(DE_PAT_ID, HUP_MRN, SEX, RACE)) # include EMPI
+
+df_people_with_promis_data_scores_added <- merge(df_people_with_promis_data, 
+	promis_info_closest_proximity_just_scores, by = "EMPI")
 
@@
 #this will display a demographics table comparing age, race, sex between healthy and depressed groups, using the first presentation to treatment
-#demo
-make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
-
-make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[((df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
+#demo simple, all groups
+simple_demo_all_groups <- make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
+
+#save 
+simple_demo_all_groups_df <- print(simple_demo_all_groups, as.data.frame = TRUE)
+write.csv(simple_demo_all_groups_df, file = paste0(homedir, "/results/simple_demo_all_groups_df.csv"), row.names = TRUE)
+
+#demo simple, just MS+noA and MS+severeA
+simple_demo_diagnosis <- make_demographics_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[((df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
+
+#save 
+simple_demo_diagnosis_df <- print(simple_demo_diagnosis, as.data.frame = TRUE)
+write.csv(simple_demo_diagnosis_df, file = paste0(homedir, "/results/simple_demo_diagnosis_df.csv"), row.names = TRUE)
 ```
@@
   ungroup() 
-make_demographics_table_ms_w_promis_anxiety(data_frame = df_people_with_promis_data_scores_added_unique)
-
-make_demographics_table_ms_w_promis_anxiety(data_frame = df_people_with_promis_data_scores_added_unique[(df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds"),])
+simple_demo_promis_all_groups <- make_demographics_table_ms_w_promis_anxiety(data_frame = df_people_with_promis_data_scores_added_unique)
+
+#save 
+simple_demo_promis_all_groups_df <- print(simple_demo_promis_all_groups, as.data.frame = TRUE)
+write.csv(simple_demo_promis_all_groups_df, file = paste0(homedir, "/results/simple_demo_promis_all_groups_df.csv"), row.names = TRUE)
+
+simple_demo_promis_diagnosis <- make_demographics_table_ms_w_promis_anxiety(data_frame = df_people_with_promis_data_scores_added_unique[(df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds"),])
+
+#save 
+simple_demo_promis_diagnosis_df <- print(simple_demo_promis_diagnosis, as.data.frame = TRUE)
+write.csv(simple_demo_all_groups_df, file = paste0(homedir, "/results/simple_demo_promis_diagnosis_df.csv"), row.names = TRUE)
+
+#------
 
@@
 
-#first number is # with depression, second is number without depression
-num_w_promis <- c(sum(df_people_with_promis_data_scores_added_unique$depGroupVar == 2), sum(df_people_with_promis_data_scores_added_unique$depGroupVar == 1))
-
-#first number is # with depression, second is number without depression
-num_total <- c(sum(df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"), sum(df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy"))
-
-df_2x2_promis_score_by_total_people_per_diagnosis <- data.frame(cbind(num_w_promis, num_total), row.names = c("MS+NoA", "MS+severeA"))
-
-#X-squared = 0.21, p = 0.65, not significant)
+#first number is # with severeA, second is number without anxiety
+num_total <- c(sum(df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"), sum(df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy"))
+
+#first number is # with severeA, second is number without anxiety
+num_w_promis <- c(sum(df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"), sum(df_people_with_promis_data_scores_added_unique$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy"))
+
+df_2x2_promis_score_by_total_people_per_diagnosis <- data.frame(cbind(num_w_promis, num_total), row.names = c("MS+severeA", "MS+NoA"))
+
+#X-squared = 1.9699, df = 1, p-value = 0.1605, not significant); 
 chisq <- chisq.test(df_2x2_promis_score_by_total_people_per_diagnosis)
 print(chisq)
+
+#fishers exact:  p-value = 0.1313, 95 % CI 0.7169704 7.4524239, OR 2.388734 
+fisher_test <- fisher.test(df_2x2_promis_score_by_total_people_per_diagnosis)
+print(fisher_test)
 ```
@@
 
-#"Percent overlap 53.4%"
+#"Percent overlap 53.2%"
 print(paste0("Percent overlap ", round(sum(df_disease_burden_unc_and_anx_net_collapsed_variables$EMPI_in_dep_group)/length(df_disease_burden_unc_and_anx_net_collapsed_variables$EMPI), 3) * 100, "%"))
@@
   dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, volume_of_mimosa_lesions) %>%
-  ungroup() #n=122
+  ungroup() #n=123
 
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter (anxiety_dose != -1) #n=371
+  filter (anxiety_dose != -1) #n=372
 
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) %>% #n=371
+  filter(anxiety_dose != -1) %>% #n=372
   mutate(has.uncinate.lesion = ifelse(mean_UF_prop >0, 1, 0)) #anywhere where there is *some* overlap counts as a 1 - they have an uncinate lesion, otherwise 0
@@
   mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  ungroup() #n=122
+  ungroup() #n=123
 
@@
   mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  ungroup() #n=22
+  ungroup() #n=19
 
@@
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) #n=79
+  filter(anxiety_dose != -1) #n=64
 

### 2024-08-29 scripts/FINAL_scripts_clean/clean_dac_pull_icd10_codes_and_make_clean_df_post_replication.R

@@ -1,0 +1,190 @@
+### Clean data frame up
+
+##pre: dac pulls from 2023 with full psychiatric ICD10 codes
+##post: rds that contains beautifully curated all_icd10_dx column. 
+## uses: Takes the dac pull, combines csvs, adds column with beautifully curated icd10 codes
+## dependencies: dplyr
+
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(purrr)
+
+
+######################
+## FUNCTIONS #########
+######################
+####Extract unique ICD10 codes
+### takes an empi, returns all the unique diagnostic codes.
+### steps: 1) filter data frame by EMPI; 2) separate into 1 column per diagnosis; 3) remove doubles; 4) combine/paste into 1 column separated by semicolons; 5) return
+get_all_unique_ICD10_diagnoses <- function(indiv_empi) {
+  data_frame<-data_pull
+  all_unique_diagnoses <- data_frame %>% 
+    filter(str_detect(EMPI, indiv_empi)) %>% 
+    dplyr::select(ICD10) %>%
+    separate_rows(ICD10, sep = ";") %>%
+    summarize(all_icd_codes = paste(unique(ICD10), collapse = ";"))
+  #print(all_unique_diagnoses$all_icd_codes)
+  return(all_unique_diagnoses$all_icd_codes)
+}
+
+
+
+######################
+## CODE ##############
+######################
+
+#this goes through dac pulls, combines them, cleans them, and saves them as rds that can be loaded in other analyses. To clean up. 
+
+#############################################################################################################################
+### ***** MUST CHANGE THE HOMEDIR  AND THE PATHS TO DATA AND OUTPUT IN ORDER FOR THIS TO WORK ON A NEW PULL> THIS IS REALLY IMPORTANT ###
+#############################################################################################################################
+
+homedir <- "/Users/eballer/BBL/msanxiety/"
+
+## output directory
[…]

### 2024-08-29 scripts/FINAL_scripts_clean/ms_functions.R

@@ -1,0 +1,1763 @@
+require('visreg')
+require('mgcv')
+require('tableone')
+require('dplyr')
+require('plm')
+require('MatchIt')
+require('tidyr')
+require('ggplot2')
+require('reshape')
+require('emmeans')
+require('cowplot')
+require('stringr')
+require('visreg')
+require('rasterVis')
+require('lattice')
+require('circlize')
+## set directories ##
+#local_wkdir <- '~/Google Drive/TDSlab/SCZ_gene_imaging/'
+#remote_wkdir <- '~/Desktop/BBL/data/joy/BBL/studies/pnc/'
+
+#############################
+###Make Demographics Table###
+#############################
+
+#############################
+####### Demographics ########
+#############################
+
+#### anxiety demographics
+
+make_demographics_table_ms_anxiety_simple<- function(data_frame) {
+  #subset demographics
+  
+  listVars <- c("Race", 
+                "Sex",
+                "Age",
+                "Has.anxietydx", 
+                "On.Anxiolytics",
+                "oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed",
+                "anxiety_dose",
+                "on_anti_cd20",
+                "on_interferon",
+                "on_steroids",
+                "on_dmt",
+                "PHQ2",
+                "PHQ9",
+                "volume_of_mimosa_lesions", 
+                "mean_UF_vol",
+                "proportion_volume_lost_per_total_network_size_sum") #Race 1 = caucasian, Sex 1 = M age = years
+  
+  
+  #for_parse <- paste0("data.frame(data_frame$race_binarized, data_frame$sex_binarized, data_frame$PAT_AGE_AT_EXAM, data_frame$depGroupVar, data_frame$PHQ.2, data_frame$PHQ.9)")
+  # for_parse <- paste0(data.frame(data_frame$race_binarized,
+  for_parse <- paste0("data.frame(data_frame$RACE, 
+                      data_frame$sex_binarized, 
+                      data_frame$PAT_AGE_AT_EXAM, 
+                      data_frame$Has.anxietydx, 
+                      data_frame$On.Anxiolytics,
+                      data_frame$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed,
+                      data_frame$anxiety_dose,
+                      data_frame$On.Anti_cd20,
+                      data_frame$On.Interferon,
[…]

### 2024-08-30 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL.Rmd
added. new plots

@@
 library(tidymv)
-
+library(viridis)  # Ensure you have the viridis package
 #functions
@@
 
-#### Plot promis x anxiety dose, group by mental vs physical health
+#### Plot 
+#####Promis x anxiety dose, group by mental vs physical health
 ```{r plot_Promis_x_anxiety}
@@
   group_by(EMPI) %>%
-  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
-  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
+  mutate("Physical Health Burden" = sum(across(physical_domains))/length(physical_domains)) %>%
+  mutate("Mental Health Burden" = sum(across(mood_domains))/length(mood_domains)) %>%
   dplyr::select(EMPI,
                 anxiety_dose,
-                physical_health_score,
-                mental_health_score) %>%
+                "Physical Health Burden",
+                "Mental Health Burden") %>%
   gather(health_variable, PROMIS_Score, -anxiety_dose, -EMPI) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
@@
 
-custom_colors <- c("physical_health_score" = "#9ACD32","mental_health_score" =  "#4B0082")
-
-custom_colors_simple <- c("#9ACD32", "#4B0082") #done in alphabetical order.
+#custom_colors_simple <- c("#9ACD32", "#4B0082") #done in alphabetical order.
+
+# Define the desired order of legend items
+desired_order <- c("Physical Health Burden", "Mental Health Burden")
+
+# Ensure the factor levels are set to match the desired order
+df_for_promis_plot_mental_vs_physical_healthy$health_variable <- factor(
+  df_for_promis_plot_mental_vs_physical_healthy$health_variable,
+  levels = desired_order
+)
+
+# Define custom colors, ensuring the names match the levels of the factor
+custom_colors_simple <- c("Physical Health Burden" = "#4B0082",  # Purple
+                          "Mental Health Burden" = "#9ACD32")  # Green
 
@@
   geom_line(size = 1.2) +
-  scale_x_continuous(breaks = c(0, 1, 2)) +
+  scale_x_continuous(breaks = c(0, 1, 2),  # Keep numeric values on x-axis
+                     labels = c("MS+noA", "MS+mildA", "MS+severeA")) +  # Set custom labels for each numeric value
   scale_y_continuous(limits = c(0, 7)) +
@@
   theme(
-       # plot.title = element_text(size=16, hjust = 0.55),
-      #  axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
-      #  axis.title.y = element_text(size=16),
+        axis.text.y = element_text(size=12, colour = "black"),
+        axis.title.y = element_text(size=16),
         axis.line = element_line(size = 1.5, colour = "black", linetype=1),
-      #  legend.position = "none",
+        axis.title.x = element_blank(),
+        axis.text.x = element_text(size=12, colour = "black"),
+        legend.title = element_blank(),
+        legend.position = c(0.8, 0.95),  # Move legend to upper right of plot area (0.9, 0.9 corresponds to top-right)
+        legend.background = element_rect(fill = "white"),  # Set legend background to white
+        legend.key = element_rect(fill = "white", color = "white"),  # Set legend key background to white
         aspect.ratio=7/5,
         panel.background = element_rect(colour = "white", fill = "white")) +
-  labs(x = "Anxiety Dose", y = "Mean PROMIS Score", 
-       title = "PROMIS Scores by Anxiety Dose") +
-#  scale_color_brewer(palette = "Set3") 
-  scale_color_manual(values = custom_colors_simple)
+  labs(y= "Mean PROMIS Score") +
+  scale_color_manual(values = custom_colors_simple, breaks = desired_order)
+
 promis_with_post_op_mental_vs_physical
-
-# Create the ggplot -> bar
-promis_with_post_op_mental_vs_physical_bar <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, fill = health_variable)) +
-  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +  
-  geom_errorbar(aes(ymin = mean_promis_score - sem_promis_score, ymax = mean_promis_score + sem_promis_score), 
-                width = 0.2, size = 0.8, color = "black", position = position_dodge(width = 0.9)) +
-  scale_x_continuous(breaks = c(0, 1, 2)) +
-  scale_y_continuous(limits = c(0, 7)) +
-  theme_minimal() +
-  labs(x = "Anxiety Dose", y = "Mean PROMIS Score", 
-       title = "PROMIS Scores by Anxiety Dose") +
-  scale_fill_manual(values = custom_colors)
-
-promis_with_post_op_mental_vs_physical_bar
-
-```
-
-####Test promis*anxiety dose  stats
-#####Physical and Mental Health together
-```{r phsy_and_mental_step_x_anxiety_dose}
-###
-df_for_promis_plot_mental_vs_physical_healthy_test <- df_people_with_promis_data_scores_added_unique %>%
-  group_by(EMPI) %>%
-  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
-  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
-  mutate(phys_mental_diff_score = physical_health_score-mental_health_score) %>%
-  dplyr::select(EMPI,
-                anxiety_dose,
-                physical_health_score,
-                mental_health_score,
-                phys_mental_diff_score)
-
-#anxiety_dose  -0.7345     0.2946  -2.493   0.0153 * 
-anxiety_dose_x_phys_score <- lm(physical_health_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
-summary(anxiety_dose_x_phys_score)
-
-#anxiety_dose  -1.1181     0.2681  -4.171 9.59e-05 ***
-anxiety_dose_x_mental_score <- lm(mental_health_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
-summary(anxiety_dose_x_mental_score)
-
-#anxiety_dose   0.3836     0.2391   1.605    0.114
-anxiety_dose_x_diff_score <- lm(phys_mental_diff_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
-summary(anxiety_dose_x_diff_score)
-
-#looking at anxiety_dose = 2 only, 0.22 -> sample size too small
-
-mental_vs_physical_health_t <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
-mental_vs_physical_health_t
-
-#looking at physical health and mental health in sick vs healthy
-
-#physical health, sick vs healthy - t = 2.0048, df = 8.6555, p-value = 0.07722
-physical_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
-physical_health_t_sick_vs_healthy
-
-#mental health, sick vs healthy - t = 3.6838, df = 8.1324, p-value = 0.006011
-mental_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
-mental_health_t_sick_vs_healthy
+#save pdf
+pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/promis_with_post_op_mental_vs_physical.pdf"))
+  promis_with_post_op_mental_vs_physical
+dev.off()
+
 ```
@@
 
-#### Uncinate by Anxiety Dose (vol and prop)
+#### Uncinate by Anxiety Dose 
 ```{r uncinateByAnxietyDose}
@@
 
-#### Plots Uncinate R,L,mean Prop
+#### Plots 
+#####Uncinate R,L,mean Prop
 ```{r plots_uncinate}
   #proportion injured over R Uncinate prop
-  # Of note, PROP AND VOL ARE LINEARLY RELATED -> USE PROP FOR ANALYSIS OTHERWISE THE GRAPHS BECOME CONFUSING TO LOOK AT. PROP is proportion of total fascicle injury
-
-#n=371
+
+#n=372
+df_mean_UF_mean_by_anxiety_severity <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) %>%
+  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
+                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
+  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
+  mutate(mean_UF_prop = mean_UF_prop*100) %>%
+  group_by(anxiety_severity) %>%
+  summarise(mean_UF_mean = round(mean(mean_UF_prop , na.rm = TRUE),0),
+            sd_UF = sd(mean_UF_prop, na.rm = TRUE),
+            sem_UF = sd(mean_UF_prop, na.rm = TRUE) / sqrt(n())) %>%
+  mutate(anxiety_severity = factor(anxiety_severity, levels = unique(anxiety_severity))) %>%
+  ungroup()
+
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_mean_UF_mean_by_anxiety_severity, aes(x=anxiety_severity, y=mean_UF_mean, fill=anxiety_severity)) +
+  geom_bar(stat="identity", width = .6) +  
+  geom_errorbar(aes(ymin = mean_UF_mean - sem_UF, ymax = mean_UF_mean + sem_UF), width = 0.2, size = 0.8)  +
+  scale_fill_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
+  ylim(0,45)+
+  theme(axis.text.x = element_text(size=12, colour = "black"),
+        axis.text.y = element_text(size=12, colour = "black"),
+        axis.title.y = element_text(size=16, colour = "black"),
+        axis.title.x = element_blank(),
+        axis.line = element_line(linewidth = 1.5, colour="black"),
+        legend.position = "none",
+        panel.background = element_rect(colour = "white", fill = "white")) + 
+  labs(y = "Percent (%) of Uncinate Injured")
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
+
+#save pdf
+pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_bar.pdf"))
+  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
+dev.off()
+
+```
+##### Uncinate Violin Plot
+```{r uncinate_violin}
+#### trying prettier things
 df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
   filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1)
-
-prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_R_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
+  filter(anxiety_dose != -1) %>%
+  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
+                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
+  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
+  mutate(mean_UF_prop = mean_UF_prop*100)
+
+# Create the plot with narrower violins and error bars
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, fill = anxiety_severity)) +
+  geom_violin(width = 0.6, alpha =1.5, color = "black", trim = FALSE) +  # Adjust violin width and transparency
   geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot
-
- #proportion injured over R Uncinate prop - geom_bar
-means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_R_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
-
-df_UF_R_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
-
-names(df_UF_R_mean_by_anxiety_dose) <- c("mean_UF_R", "Anxiety_dose")
-
-df_UF_R_mean_by_anxiety_dose <- df_UF_R_mean_by_anxiety_dose %>%
-  mutate(mean_UF_R = as.numeric(mean_UF_R)) %>%
-  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
-
-prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_UF_R_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_R, fill=Anxiety_dose)) +
-  geom_bar(stat="identity") +  
-  ylim(0,0.5)+
-#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
-        panel.background = element_rect(colour = "white", fill = "white"))
-prop_injured_R_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
-
-  #proportion injured over L Uncinate prop
-prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=UF_L_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot
-
- #proportion injured over L Uncinate prop - geom_bar
-means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$UF_L_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
-
-df_UF_L_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
-
-names(df_UF_L_mean_by_anxiety_dose) <- c("mean_UF_L", "Anxiety_dose")
-
-df_UF_L_mean_by_anxiety_dose <- df_UF_L_mean_by_anxiety_dose %>%
-  mutate(mean_UF_L = as.numeric(mean_UF_L)) %>%
-  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
-
-prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_UF_L_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_L, fill=Anxiety_dose)) +
-  geom_bar(stat="identity") +  
-  ylim(0,0.5)+
-#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
-        panel.background = element_rect(colour = "white", fill = "white"))
-prop_injured_L_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
-
-#mean UF
-
-  #proportion injured over mean Uncinate prop
-prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, y=mean_UF_prop, fill=oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed)) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
+  ylim(0,100) +
+  #geom_errorbar(aes(ymin = mean_UF_prop - sem_UF_prop, ymax = mean_UF_prop + sem_UF_prop), width = 0.2, color = "black") +  # Add error bars
+  scale_fill_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
+  #theme_minimal(base_size = 14) +  # Use a minimal theme with a base font size
+  theme(
+    axis.text.x = element_text(size = 12, colour = "black"),  # Rotate x-axis labels for better readability
+    axis.text.y = element_text(size = 12, colour = "black"),
+    axis.title.y = element_text(size = 16, colour = "black"),
+    axis.title.x = element_blank(),
+    axis.line = element_line(linewidth = 1.5, colour = "black"),
+    legend.position = "none",
+    panel.background = element_rect(colour = "white", fill = "white"),
+    plot.margin = margin(10, 10, 10, 10)  # Add margins around the plot
+  ) + 
+  labs(y = "Percent (%) of Uncinate Injured")
+
 prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
 
- #proportion injured over mean Uncinate prop - geom_bar
-means_by_anxiety_dose <- c(mean(df_disease_burden_unc_and_anx_net_collapsed_variables$mean_UF_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$mean_UF_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxietydx.OR.Antianxiety.Meds"]),
-                                mean(df_disease_burden_unc_and_anx_net_collapsed_variables$mean_UF_prop[df_disease_burden_unc_and_anx_net_collapsed_variables$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep"]))
-
-df_mean_UF_mean_by_anxiety_dose <- data.frame(cbind(means_by_anxiety_dose, c("true_healthy", "Has.Anxietydx.OR.Antianxiety.Meds", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))
-
-names(df_mean_UF_mean_by_anxiety_dose) <- c("mean_UF_mean", "Anxiety_dose")
-
-df_mean_UF_mean_by_anxiety_dose <- df_mean_UF_mean_by_anxiety_dose %>%
-  mutate(mean_UF_mean = as.numeric(mean_UF_mean)) %>%
-  mutate(Anxiety_dose = factor(Anxiety_dose, levels = unique(Anxiety_dose)))
-
-prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_mean_UF_mean_by_anxiety_dose, aes(x=Anxiety_dose, y=mean_UF_mean, fill=Anxiety_dose)) +
-  geom_bar(stat="identity") +  
-  ylim(0,0.5)+
-#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5),
-        panel.background = element_rect(colour = "white", fill = "white"))
-prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
+#save pdf
+pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_violin.pdf"))
+  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
+dev.off()
+
+```
+##### Geom point
+```{r geom_point}
+#### trying prettier things
+df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) %>%
+  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
+                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
+  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
+  mutate(mean_UF_prop = mean_UF_prop*100)
+
+# Create the plot with narrower violins, viridis colors, and horizontal lines at means
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
+  geom_point(position = position_jitter(.1), size = 2, alpha = 0.8) +  # Add points with jitter using viridis colors
+  stat_summary(fun = "mean", geom = "crossbar", width = 0.3, color = "black", size = 0.5) +  # Add horizontal lines at means
+  scale_color_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale for points
+  theme(
+    axis.text.x = element_text(size = 12, colour = "black"),  # X-axis labels
+    axis.text.y = element_text(size = 12, colour = "black"),  # Y-axis labels
+    axis.title.y = element_text(size = 16, colour = "black"),  # Y-axis title
+    axis.title.x = element_blank(),  # Remove X-axis title
+    axis.line = element_line(linewidth = 1.5, colour = "black"),  # Axis lines
+    legend.position = "none",  # Remove legend
+    panel.background = element_rect(colour = "white", fill = "white")  # Background
+  ) + 
+  labs(y = "Percent (%) of Uncinate Injured")  # Y-axis label
+
+# Display the plot
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
+
+#save pdf
+pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_dot.pdf"))
+  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
+dev.off()
+
 ```

### 2024-08-30 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL.Rmd
added back the promis analysis

@@
 ```
-#### Plot promis x anxiety dose
+
+#### Plot 
+##### Plot promis x anxiety dose
 ```{r plot_Promis_x_anxiety}
@@
 
-#### Plot 
 #####Promis x anxiety dose, group by mental vs physical health
@@
 ```
+####Test promis*anxiety dose  stats
+#####Physical and Mental Health together
+```{r phsy_and_mental_step_x_anxiety_dose}
+###
+df_for_promis_plot_mental_vs_physical_healthy_test <- df_people_with_promis_data_scores_added_unique %>%
+  group_by(EMPI) %>%
+  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
+  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
+  mutate(phys_mental_diff_score = physical_health_score-mental_health_score) %>%
+  dplyr::select(EMPI,
+                anxiety_dose,
+                physical_health_score,
+                mental_health_score,
+                phys_mental_diff_score)
+
+#looking at anxiety_dose = 2 only, 0.22 -> sample size too small
+
+mental_vs_physical_health_t <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
+mental_vs_physical_health_t
+
+#looking at physical health and mental health in sick vs healthy
+
+#physical health, sick vs healthy - t = 2.0048, df = 8.6555, p-value = 0.07722
+physical_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
+physical_health_t_sick_vs_healthy
+
+#mental health, sick vs healthy - t = 3.6838, df = 8.1324, p-value = 0.006011
+mental_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
+mental_health_t_sick_vs_healthy
+
+###linear models
+#anxiety_dose  -0.7345     0.2946  -2.493   0.0153 * ; (T = -2.493, P = 0.015, Cohen's f2 =  0.1, Effect size = small)
+anxiety_dose_x_phys_score <- lm(physical_health_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
+summary(anxiety_dose_x_phys_score)
+lm_summary_stats(lm_model = anxiety_dose_x_phys_score, which_variable = 2)
+
+#anxiety_dose  -1.1181     0.2681  -4.171 9.59e-05 ***; (T = -4.171, P = 0, Cohen's f2 =  0.281, Effect size = medium)
+anxiety_dose_x_mental_score <- lm(mental_health_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
+summary(anxiety_dose_x_mental_score)
+lm_summary_stats(lm_model = anxiety_dose_x_mental_score, which_variable = 2)
+
+#anxiety_dose   0.3836     0.2391   1.605    0.114; (T = 1.605, P = 0.114, Cohen's f2 =  0.042, Effect size = small) - delta between physical and mental health NS
+anxiety_dose_x_diff_score <- lm(phys_mental_diff_score ~ anxiety_dose, df_for_promis_plot_mental_vs_physical_healthy_test)
+summary(anxiety_dose_x_diff_score)
+lm_summary_stats(lm_model = anxiety_dose_x_diff_score, which_variable = 2)
+
+```
 
@@
 
-#### Uncinate by anxiety diagnosis (vol and prop)
+#### Uncinate by anxiety diagnosis (prop)
 ```{r uncinate_by_dx}

### 2024-08-30 scripts/FINAL_scripts_clean/ms_functions.R

@@ -1183,6 +1183,32 @@ gam_summary_stats <- function(gam_model) {
   return(text)
 }
 
+lm_summary_stats <- function(lm_model, which_variable) {
+  ### Extract T, P, Eff size, eff size size
+  #picks whatever variable you want, intercept is 1, first actual variable would be 2, etc
+  #t val
+  t <- round(summary(lm_model)[["coefficients"]][, "t value"][which_variable], 3)
+  
+  #p
+  p <- round(summary(lm_model)[["coefficients"]][, "Pr(>|t|)"][which_variable],3)
+
+
+  #f2 - R2/1-R2
+  r2 <- summary(lm_model)$r.squared
+  f2 <- round(r2/(1-r2), 3)
+  
+  #eff size summary
+  eff_size = case_when(
+    f2 >=0.35 ~ "large",
+    f2 >= 0.15 & f2 < 0.35 ~ "medium",
+    f2 >= 0.02 & f2 < 0.15 ~ "small",
+    f2 >= 0 & f2 < 0.02 ~"minimal"
+  )
+  
+  text = paste0("(T = ", t, ", P = ", p, ", Cohen's f2 =  ", f2, ", Effect size = ", eff_size, ")")
+  return(text)
+}
+
 #for hydra k3
 cohen_d_onepair <- function(data_frame, subtypeA, subtypeB, measure, hydra_cluster) {
   grpA_for_parse <- paste0("data_frame$", measure, "[which(data_frame$Hydra_k", hydra_cluster, " == ", subtypeA, ")]")

### 2024-09-03 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL.Rmd
Add files via upload

@@
   geom_errorbar(aes(ymin = mean_UF_mean - sem_UF, ymax = mean_UF_mean + sem_UF), width = 0.2, size = 0.8)  +
-  scale_fill_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
+  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale
   ylim(0,45)+
@@
         legend.position = "none",
+        aspect.ratio = 7/5,
         panel.background = element_rect(colour = "white", fill = "white")) + 
@@
 dev.off()
+
+### try horizontal
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar_horiz <-  ggplot(df_mean_UF_mean_by_anxiety_severity, aes(y=anxiety_severity, x=mean_UF_mean, fill=anxiety_severity)) +
+  geom_bar(stat="identity", width = .6) +  
+  geom_errorbar(aes(xmin = mean_UF_mean - sem_UF, xmax = mean_UF_mean + sem_UF), width = 0.2, size = 0.8)  +
+  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale
+  xlim(0,45)+
+  theme(axis.text.x = element_text(size=12, colour = "black"),
+        axis.text.y = element_text(size=12, colour = "black"),
+        axis.title.x = element_text(size=16, colour = "black"),
+        axis.title.y = element_blank(),
+        axis.line = element_line(linewidth = 1.5, colour="black"),
+        legend.position = "none",
+        aspect.ratio = 7/5,
+        panel.background = element_rect(colour = "white", fill = "white")) + 
+  labs(x = "Percent (%) of Uncinate Injured")
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar_horiz
 
@@
 prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, fill = anxiety_severity)) +
-  geom_violin(width = 0.6, alpha =1.5, color = "black", trim = FALSE) +  # Adjust violin width and transparency
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
+  geom_violin(width = 0.5, alpha =.5, color = "black", trim = FALSE) +  # Adjust violin width and transparency
+  stat_summary(fun = "mean", geom = "crossbar", width = 0.3, color = "black", size = 0.5) +  # Add horizontal lines at means
+  #geom_point(position = position_jitter(seed = 1, width = 0.2)) +
+
+#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
   ylim(0,100) +
   #geom_errorbar(aes(ymin = mean_UF_prop - sem_UF_prop, ymax = mean_UF_prop + sem_UF_prop), width = 0.2, color = "black") +  # Add error bars
-  scale_fill_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
+  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale
   #theme_minimal(base_size = 14) +  # Use a minimal theme with a base font size
@@
     panel.background = element_rect(colour = "white", fill = "white"),
-    plot.margin = margin(10, 10, 10, 10)  # Add margins around the plot
+    plot.margin = margin(10, 10, 10, 10),  # Add margins around the plot
+    aspect.ratio = 5/5
   ) + 
@@
 prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
-  geom_point(position = position_jitter(.1), size = 2, alpha = 0.8) +  # Add points with jitter using viridis colors
+  geom_point(position = position_jitter(width=.1, height = 0), size = 2, alpha = 0.8) +  # Add points with jitter using viridis colors
   stat_summary(fun = "mean", geom = "crossbar", width = 0.3, color = "black", size = 0.5) +  # Add horizontal lines at means
-  scale_color_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale for points
+  scale_color_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale for points
   theme(
@@
 
+##### Box plot with jitter ND OTHERS
+```{r box_jitter}
+#### trying prettier things
+df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) %>%
+  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
+                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
+  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
+  mutate(mean_UF_prop = mean_UF_prop*100)
+
+##BOX PLOT WITH JITTER
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
+  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.3, outlier.size = 0) +  # Add boxplots with some transparency
+  geom_jitter(width = 0.2, size = 2, alpha = 0.8) +  # Add jittered points for individual observations
+  scale_color_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
+  scale_fill_viridis(discrete = TRUE, option = "D") +
+  theme(
+    axis.text.x = element_text(size = 12, colour = "black"),
+    axis.text.y = element_text(size = 12, colour = "black"),
+    axis.title.y = element_text(size = 16, colour = "black"),
+    axis.title.x = element_blank(),
+    axis.line = element_line(linewidth = 1.5, colour = "black"),
+    legend.position = "none",
+    panel.background = element_rect(colour = "white", fill = "white")
+  ) + 
+  labs(y = "Percent (%) of Uncinate Injured")
+
+# Display the plot
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
+
+##### BOX PLOT NO JITTER
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
+  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.3, outlier.size = 0) +  # Add boxplots with some transparency
+#  geom_jitter(width = 0.2, size = 2, alpha = 0.8) +  # Add jittered points for individual observations
+  scale_color_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
+  scale_fill_viridis(discrete = TRUE, option = "D") +
+  theme(
+    axis.text.x = element_text(size = 12, colour = "black"),
+    axis.text.y = element_text(size = 12, colour = "black"),
+    axis.title.y = element_text(size = 16, colour = "black"),
+    axis.title.x = element_blank(),
+    axis.line = element_line(linewidth = 1.5, colour = "black"),
+    legend.position = "none",
+    panel.background = element_rect(colour = "white", fill = "white")
+  ) + 
+  labs(y = "Percent (%) of Uncinate Injured")
+
+# Display the plot
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
+
+###dot plot
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
+  geom_point(position = position_jitter(width = 0.2, height = 0), size = 2, alpha = 0.8) +  # Individual data points with jitter
+  stat_summary(fun = "mean", geom = "point", size = 4, shape = 21, fill = "black") +  # Mean points
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, color = "black") +  # Confidence intervals
+  scale_color_viridis(discrete = TRUE, option = "D") +
+  theme(
+    axis.text.x = element_text(size = 12, colour = "black"),
+    axis.text.y = element_text(size = 12, colour = "black"),
+    axis.title.y = element_text(size = 16, colour = "black"),
+    axis.title.x = element_blank(),
+    axis.line = element_line(linewidth = 1.5, colour = "black"),
+    legend.position = "none",
+    panel.background = element_rect(colour = "white", fill = "white")
+  ) + 
+  labs(y = "Percent (%) of Uncinate Injured")
+
+# Display the plot
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
+
+### bar with error
+summary_stats <- df_disease_burden_unc_and_anx_net_collapsed_variables %>%
+  group_by(anxiety_severity) %>%
+  summarize(mean_UF_prop = mean(mean_UF_prop, na.rm = TRUE),
+            sd_UF_prop = sd(mean_UF_prop, na.rm = TRUE),
+            n = n(),
+            se_UF_prop = sd_UF_prop / sqrt(n))
+
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(summary_stats, aes(y = anxiety_severity, x = mean_UF_prop, fill = anxiety_severity)) +
+  geom_bar(stat = "identity", position = position_dodge(), width = 0.7) +  # Bar plot
+  geom_errorbar(aes(xmin = mean_UF_prop - se_UF_prop, xmax = mean_UF_prop + se_UF_prop), width = 0.2) +  # Error bars
+  scale_fill_viridis(discrete = TRUE, option = "D") +
+  theme(
+    axis.text.x = element_text(size = 12, colour = "black"),
+    axis.text.y = element_text(size = 12, colour = "black"),
+#    axis.title.y = element_text(size = 16, colour = "black"),
+    axis.title.y = element_blank(),
+    axis.line = element_line(linewidth = 1.5, colour = "black"),
+    legend.position = "none",
+    panel.background = element_rect(colour = "white", fill = "white")
+  ) + 
+  labs(x = "Percent (%) of Uncinate Injured")
+
+# Display the plot
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
+```
+
 ### Sex Differences lm and chisq - N.S.

### 2024-09-04 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL.Rmd
adding new figures

@@
 simple_demo_promis_diagnosis_df <- print(simple_demo_promis_diagnosis, as.data.frame = TRUE)
-write.csv(simple_demo_all_groups_df, file = paste0(homedir, "/results/simple_demo_promis_diagnosis_df.csv"), row.names = TRUE)
+write.csv(simple_demo_promis_diagnosis_df, file = paste0(homedir, "/results/simple_demo_promis_diagnosis_df.csv"), row.names = TRUE)
 
@@
 prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
+```
+
+##### Box plot no jitter
+```{r box_plot_no_jitter}
+
+####
+df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) %>%
+  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
+                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
+  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
+  mutate(mean_UF_prop = mean_UF_prop*100)
+
+# Define a custom palette
+custom_colors <- c(
+
+  #"MS+noA" = "#1F968B",
+  #"MS+mildA" = "#39568C",
+  #"MS+severeA" = "#482677" 
+    #"MS+noA" = "#55C667",
+  #"MS+mildA" = "#238A8D",
+  #"MS+severeA" = "#404788" 
+    #  "MS+noA" = "#404788",
+#  "MS+mildA" = "#482677",
+#  "MS+severeA" = "#440154" 
+  #      "MS+noA" = "#1f968abf",
+  #"MS+mildA" = "#33638d",
+  #"MS+severeA" = "#482677" 
+ #         "MS+noA" = "#29af7f",
+#  "MS+mildA" = "#33638d",
+#  "MS+severeA" = "#440154" 
+            "MS+noA" = "#55c667",
+  "MS+mildA" = "#2d708e",
+  "MS+severeA" = "#440154" 
+ # "MS+mildA" = viridis::viridis(3, option = "C")[2],  # Use green from 'D' for MS+noA
+#  "MS+severeA" = viridis::viridis(3, option = "D")[1],  # Use a different color from 'D'
+#  "MS+noA" = viridis::viridis(3, option = "D")[2]  # Use the last color from 'D'
+)
 
@@
 prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
-  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.3, outlier.size = 0) +  # Add boxplots with some transparency
+  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.65, outlier.size = 0) +  # Add boxplots with some transparency
+    scale_color_manual(values = custom_colors) +  # Apply custom color scale
+  scale_fill_manual(values = custom_colors) +  # Apply custom fill scale
 #  geom_jitter(width = 0.2, size = 2, alpha = 0.8) +  # Add jittered points for individual observations
-  scale_color_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
-  scale_fill_viridis(discrete = TRUE, option = "D") +
+  #scale_color_viridis(discrete = TRUE, option = "C", direction = -1) +  # Use Viridis color scale
+  #scale_fill_viridis(discrete = TRUE, option = "C", direction = -1) +
   theme(
@@
     legend.position = "none",
+    aspect.ratio = 7/6,
     panel.background = element_rect(colour = "white", fill = "white")
@@
 
-###dot plot
+#save pdf
+pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_box_plot_no_jitter.pdf"))
+  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
+dev.off()
+
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_horiz <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(y = anxiety_severity, x = mean_UF_prop, color = anxiety_severity)) +
+  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.65, outlier.size = 0) +  # Add boxplots with some transparency
+#  geom_jitter(width = 0.2, size = 2, alpha = 0.8) +  # Add jittered points for individual observations
+  scale_color_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale
+  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1) +
+  theme(
+    axis.text.x = element_text(size = 12, colour = "black"),
+    axis.text.y = element_text(size = 12, colour = "black"),
+    axis.title.x = element_text(size = 16, colour = "black"),
+    axis.title.y = element_blank(),
+    axis.line = element_line(linewidth = 1.5, colour = "black"),
+    legend.position = "none",
+    aspect.ratio = 5/6,
+    panel.background = element_rect(colour = "white", fill = "white")
+  ) + 
+  labs(x = "Percent (%) of Uncinate Injured")
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_horiz
+
+```
+
+###### dot plot
+```{r dot_plot_and_others}
+
+df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) %>%
+  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
+                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
+  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
+  mutate(mean_UF_prop = mean_UF_prop*100)
+
+##plot
 prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +

### 2024-09-06 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL_updated_figs.Rmd
added cohen's d and figures

--- 2024-08-30 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL.Rmd
@@
         legend.key = element_rect(fill = "white", color = "white"),  # Set legend key background to white
+        legend.text = element_text(size=10),
         aspect.ratio=7/5,
@@
 promis_with_post_op_mental_vs_physical
+
 #save pdf
@@
 
-#looking at anxiety_dose = 2 only, 0.22 -> sample size too small
-
-mental_vs_physical_health_t <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
-mental_vs_physical_health_t
-
-#looking at physical health and mental health in sick vs healthy
-
-#physical health, sick vs healthy - t = 2.0048, df = 8.6555, p-value = 0.07722
-physical_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
-physical_health_t_sick_vs_healthy
-
-#mental health, sick vs healthy - t = 3.6838, df = 8.1324, p-value = 0.006011
-mental_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
-mental_health_t_sick_vs_healthy
-
 ###linear models
@@
 lm_summary_stats(lm_model = anxiety_dose_x_diff_score, which_variable = 2)
+
+#post-hoc pairwise t-tests
+#looking at anxiety_dose = 0, 1 and 2
+
+# dose 2, "(T = 2.88, df = 6, P = 0.028, Cohen's d =  -0.69, Effect size = medium)"
+physical_vs_mental_health_anxiety_severeA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired = "T")
+print(physical_vs_mental_health_anxiety_severeA[1])
+
+#dose 1, "(T = 2.97, df = 44, P = 0.005, Cohen's d =  -0.38, Effect size = small)"
+
+physical_vs_mental_health_anxiety_mildA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==1], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==1], paired = "T")
+print(physical_vs_mental_health_anxiety_mildA[1])
+
+#dose 0, "(T = 0.68, df = 11, P = 0.513, Cohen's d =  -0.22, Effect size = small)"
+
+physical_vs_mental_health_anxiety_noA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], paired = "T")
+print(physical_vs_mental_health_anxiety_noA[1])
+
+#looking at physical health and mental health in sick vs healthy
+
+###physical health, sick vs healthy - "(T = 2.00, df = 8.66, P = 0.077, Cohen's d =  -1.01, Effect size = large)"
+
+physical_health_noAvsSevereA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired = "F")
+print(physical_health_noAvsSevereA[1])
+
+###mental health, sick vs healthy - (T = 3.68, df = 8.13, P = 0.006, Cohen's d =  -1.87, Effect size = large)
+mental_health_noAvsSevereA <- t_and_cohen_d(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
+print(mental_health_noAvsSevereA[1])
+
+#construct df of p values
+p_and_cohen_values <- t(data.frame(rbind(c(physical_vs_mental_health_anxiety_noA[2],
+                         physical_vs_mental_health_anxiety_mildA[2],
+                         physical_vs_mental_health_anxiety_severeA[2],
+                         mental_health_noAvsSevereA[2],
+                         physical_health_noAvsSevereA[2]),
+                         c(physical_vs_mental_health_anxiety_noA[3],
+                         physical_vs_mental_health_anxiety_mildA[3],
+                         physical_vs_mental_health_anxiety_severeA[3],
+                         mental_health_noAvsSevereA[3],
+                         physical_health_noAvsSevereA[3])), 
+                         row.names = c("p", "cohen_d")))
+
+#construct vector of names
+t_test_names <- c("Physical vs Emotional Functioning MS+noA", 
+"Physical vs Emotional Functioning MS+mildA",
+"Physical vs Emotional Functioning MS+severeA",
+"Emotional Functioning MS+severeA vs MS+noA",
+"Physical Functioning MS+severeA vs MS+noA")
+
+rownames(p_and_cohen_values) <- t_test_names
+
+#fdr correct
+p_and_cohen_values <- as.data.frame(p_and_cohen_values) %>%
+  mutate(fdr = round(p.adjust(p, method = "fdr"),3)) %>%
+  mutate(p = as.numeric(p)) %>%
+  mutate(cohen_d = as.numeric(cohen_d)) %>%
+  relocate(cohen_d, .after = fdr)
+
+print(p_and_cohen_values)
+
+#write output, will be used in supplement
+write.csv(p_and_cohen_values, file = paste0(homedir, "/results/promis_pairwise_p_and_cohen_d_values.csv"), row.names = TRUE)
+
+#save ones that meet correction
+pfdr_0.05 <- p_and_cohen_values %>%
+  filter(fdr <0.05)
+
+print(pfdr_0.05)
+
+#bonferroni correct
+#pbonf <- round(p.adjust(p_values, method = "bonferroni"),3)
+#pbonf_0.05 <- pbonf[pbonf < 0.05]
+#print(pbonf_0.05)
 
@@
 #### Plots 
-#####Uncinate R,L,mean Prop
-```{r plots_uncinate}
-  #proportion injured over R Uncinate prop
-
-#n=372
-df_mean_UF_mean_by_anxiety_severity <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) %>%
-  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
-                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
-  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
-  mutate(mean_UF_prop = mean_UF_prop*100) %>%
-  group_by(anxiety_severity) %>%
-  summarise(mean_UF_mean = round(mean(mean_UF_prop , na.rm = TRUE),0),
-            sd_UF = sd(mean_UF_prop, na.rm = TRUE),
-            sem_UF = sd(mean_UF_prop, na.rm = TRUE) / sqrt(n())) %>%
-  mutate(anxiety_severity = factor(anxiety_severity, levels = unique(anxiety_severity))) %>%
-  ungroup()
-
-prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_mean_UF_mean_by_anxiety_severity, aes(x=anxiety_severity, y=mean_UF_mean, fill=anxiety_severity)) +
-  geom_bar(stat="identity", width = .6) +  
-  geom_errorbar(aes(ymin = mean_UF_mean - sem_UF, ymax = mean_UF_mean + sem_UF), width = 0.2, size = 0.8)  +
-  scale_fill_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
-  ylim(0,45)+
-  theme(axis.text.x = element_text(size=12, colour = "black"),
-        axis.text.y = element_text(size=12, colour = "black"),
-        axis.title.y = element_text(size=16, colour = "black"),
-        axis.title.x = element_blank(),
-        axis.line = element_line(linewidth = 1.5, colour="black"),
-        legend.position = "none",
-        panel.background = element_rect(colour = "white", fill = "white")) + 
-  labs(y = "Percent (%) of Uncinate Injured")
-prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
-
-#save pdf
-pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_bar.pdf"))
-  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
-dev.off()
-
-```
-##### Uncinate Violin Plot
-```{r uncinate_violin}
-#### trying prettier things
+##### Box plot no jitter
+```{r box_plot_no_jitter}
+
+####
 df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
@@
 
-# Create the plot with narrower violins and error bars
-prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, fill = anxiety_severity)) +
-  geom_violin(width = 0.6, alpha =1.5, color = "black", trim = FALSE) +  # Adjust violin width and transparency
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  ylim(0,100) +
-  #geom_errorbar(aes(ymin = mean_UF_prop - sem_UF_prop, ymax = mean_UF_prop + sem_UF_prop), width = 0.2, color = "black") +  # Add error bars
-  scale_fill_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
-  #theme_minimal(base_size = 14) +  # Use a minimal theme with a base font size
+# Define a custom palette
+custom_colors <- c(
+
+  "MS+noA" = "#1F968B",
+  "MS+mildA" = "#39568C",
+  "MS+severeA" = "#482677" 
+)
+
+#fade colors at three different fade levels
+#custom_colors_faded <- addFade(col = custom_colors, fade = c(0.1, 0.5, 1))
+
+#change fill colors with progressive fades
+#custom_color_fill <- c(
+#  custom_colors_faded[1,1],
+#  custom_colors_faded[2,2],
+#  custom_colors_faded[3,3] 
+#)
+
+##### BOX PLOT NO JITTER
+prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
+  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.65, outlier.size = 0, linewidth=0.8, width = 0.5) +  # Add boxplots with some transparency
+  scale_color_manual(values = custom_colors) +  # Apply custom color scale
+  scale_fill_manual(values = custom_colors) +  # Apply custom fill scale
   theme(
-    axis.text.x = element_text(size = 12, colour = "black"),  # Rotate x-axis labels for better readability
+    axis.text.x = element_text(size = 12, colour = "black"),
     axis.text.y = element_text(size = 12, colour = "black"),
@@
     legend.position = "none",
-    panel.background = element_rect(colour = "white", fill = "white"),
-    plot.margin = margin(10, 10, 10, 10)  # Add margins around the plot
+    aspect.ratio = 7/6,
+    panel.background = element_rect(colour = "white", fill = "white")
   ) + 
@@
 
-prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
-
-#save pdf
-pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_violin.pdf"))
-  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
-dev.off()
-
-```
-##### Geom point
-```{r geom_point}
-#### trying prettier things
-df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) %>%
-  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
-                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
-  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
-  mutate(mean_UF_prop = mean_UF_prop*100)
-
-# Create the plot with narrower violins, viridis colors, and horizontal lines at means
-prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
-  geom_point(position = position_jitter(.1), size = 2, alpha = 0.8) +  # Add points with jitter using viridis colors
-  stat_summary(fun = "mean", geom = "crossbar", width = 0.3, color = "black", size = 0.5) +  # Add horizontal lines at means
-  scale_color_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale for points
-  theme(
-    axis.text.x = element_text(size = 12, colour = "black"),  # X-axis labels
-    axis.text.y = element_text(size = 12, colour = "black"),  # Y-axis labels
-    axis.title.y = element_text(size = 16, colour = "black"),  # Y-axis title
-    axis.title.x = element_blank(),  # Remove X-axis title
-    axis.line = element_line(linewidth = 1.5, colour = "black"),  # Axis lines
-    legend.position = "none",  # Remove legend
-    panel.background = element_rect(colour = "white", fill = "white")  # Background
-  ) + 
-  labs(y = "Percent (%) of Uncinate Injured")  # Y-axis label
-
 # Display the plot
@@
 #save pdf
-pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_dot.pdf"))
+pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_box_plot_no_jitter.pdf"))
   prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot

### 2024-09-06 scripts/FINAL_scripts_clean/ms_functions.R

@@ -1209,6 +1209,43 @@ lm_summary_stats <- function(lm_model, which_variable) {
   return(text)
 }
 
+# cohen_d_for_ttest
+t_and_cohen_d <- function(sample_1, sample_2, paired = "F"){
+  
+  #run t test
+  t_test <- t.test(sample_1, sample_2, paired=paired)
+  
+  #extract statistics
+  t <- round(t_test$statistic,2)
+  p <- round(t_test$p.value,3)
+  
+  #degrees of freedom
+  df <- round(t_test$parameter, 2)
+  
+  #find means and variances
+  mean_of_sample_1 <- mean(sample_1)
+  mean_of_sample_2 <- mean(sample_2)
+  variance_sample_1 <- var(sample_1)
+  variance_sample_2 <- var(sample_2)
+  
+  #calculate cohen's D
+  cohen_d <- round((mean_of_sample_2-mean_of_sample_1)/sqrt((variance_sample_1 + variance_sample_2)/2),2)
+  
+  #score effect size
+  eff_size = case_when(
+    abs(cohen_d) >=0.8 ~ "large",
+    abs(cohen_d) >= 0.5 & cohen_d < 0.8 ~ "medium",
+    abs(cohen_d) >= 0.2 & cohen_d < 0.5 ~ "small",
+    abs(cohen_d) >= 0 & cohen_d < 0.2 ~"minimal"
+  )
+  
+  #put in text output
+  text = paste0("(T = ", t, ", df = ", df, ", P = ", p, ", Cohen's d =  ", cohen_d, ", Effect size = ", eff_size, ")")
+  return(list(text, p, cohen_d))
+
+}
+  
+
 #for hydra k3
 cohen_d_onepair <- function(data_frame, subtypeA, subtypeB, measure, hydra_cluster) {
   grpA_for_parse <- paste0("data_frame$", measure, "[which(data_frame$Hydra_k", hydra_cluster, " == ", subtypeA, ")]")

### 2024-09-11 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_FINAL_20240911.Rmd
final, with figs, verifying T with promis

--- 2024-09-06 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL_updated_figs.Rmd
@@
   e. mean of both side
-5. Mean UF Anxiety diagnosis either violin or bar
-6. Mean Anxiety dose either violin or bar
-
-7. Supplement: 
- - More detailed streamline filtering
- - Depression group uncinate burden
- - Fornix diagnosis and dose; depression group 
- - Corr mean_UF with social problems?
-
+5. Mean Anxiety dose either violin or bar
+
+6. Supplement: 
+ - Promis tables
+#Rstduio Version: 2024.04.1+748 (2024.04.1+748)
 ## Make final data frame for analysis
@@
 # dose 2, "(T = 2.88, df = 6, P = 0.028, Cohen's d =  -0.69, Effect size = medium)"
-physical_vs_mental_health_anxiety_severeA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired = "T")
+physical_vs_mental_health_anxiety_severeA <- t_p_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired = "T")
 print(physical_vs_mental_health_anxiety_severeA[1])
@@
 
-physical_vs_mental_health_anxiety_mildA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==1], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==1], paired = "T")
+physical_vs_mental_health_anxiety_mildA <- t_p_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==1], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==1], paired = "T")
 print(physical_vs_mental_health_anxiety_mildA[1])
@@
 
-physical_vs_mental_health_anxiety_noA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], paired = "T")
+physical_vs_mental_health_anxiety_noA <- t_p_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], paired = "T")
 print(physical_vs_mental_health_anxiety_noA[1])
@@
 
-physical_health_noAvsSevereA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired = "F")
+physical_health_noAvsSevereA <- t_p_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired = "F")
 print(physical_health_noAvsSevereA[1])
@@
 ###mental health, sick vs healthy - (T = 3.68, df = 8.13, P = 0.006, Cohen's d =  -1.87, Effect size = large)
-mental_health_noAvsSevereA <- t_and_cohen_d(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
+mental_health_noAvsSevereA <- t_p_and_cohen_d(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired="F")
 print(mental_health_noAvsSevereA[1])
@@
 #construct df of p values
-p_and_cohen_values <- t(data.frame(rbind(c(physical_vs_mental_health_anxiety_noA[2],
+t_p_and_cohen_values <- t(data.frame(rbind(c(physical_vs_mental_health_anxiety_noA[2],
                          physical_vs_mental_health_anxiety_mildA[2],
@@
                          mental_health_noAvsSevereA[3],
-                         physical_health_noAvsSevereA[3])), 
-                         row.names = c("p", "cohen_d")))
+                         physical_health_noAvsSevereA[3]),
+                         c(physical_vs_mental_health_anxiety_noA[4],
+                         physical_vs_mental_health_anxiety_mildA[4],
+                         physical_vs_mental_health_anxiety_severeA[4],
+                         mental_health_noAvsSevereA[4],
+                         physical_health_noAvsSevereA[4])), 
+                         row.names = c("t", "p", "cohen_d")))
 
@@
 
-rownames(p_and_cohen_values) <- t_test_names
+rownames(t_p_and_cohen_values) <- t_test_names
 
 #fdr correct
-p_and_cohen_values <- as.data.frame(p_and_cohen_values) %>%
+t_p_and_cohen_values <- as.data.frame(t_p_and_cohen_values) %>%
+  mutate(t = as.numeric(t)) %>%
   mutate(fdr = round(p.adjust(p, method = "fdr"),3)) %>%
@@
 
-print(p_and_cohen_values)
+print(t_p_and_cohen_values)
 
 #write output, will be used in supplement
-write.csv(p_and_cohen_values, file = paste0(homedir, "/results/promis_pairwise_p_and_cohen_d_values.csv"), row.names = TRUE)
+write.csv(t_p_and_cohen_values, file = paste0(homedir, "/results/promis_pairwise_t_p_and_cohen_d_values.csv"), row.names = TRUE)
 
 #save ones that meet correction
-pfdr_0.05 <- p_and_cohen_values %>%
+pfdr_0.05 <- t_p_and_cohen_values %>%
   filter(fdr <0.05)

### 2024-09-11 scripts/FINAL_scripts_clean/ms_functions.R

@@ -1246,6 +1246,43 @@ t_and_cohen_d <- function(sample_1, sample_2, paired = "F"){
 }
   
 
+# cohen_d_for_ttest
+t_p_and_cohen_d <- function(sample_1, sample_2, paired = "F"){
+  
+  #run t test
+  t_test <- t.test(sample_1, sample_2, paired=paired)
+  
+  #extract statistics
+  t <- round(t_test$statistic,2)
+  p <- round(t_test$p.value,3)
+  
+  #degrees of freedom
+  df <- round(t_test$parameter, 2)
+  
+  #find means and variances
+  mean_of_sample_1 <- mean(sample_1)
+  mean_of_sample_2 <- mean(sample_2)
+  variance_sample_1 <- var(sample_1)
+  variance_sample_2 <- var(sample_2)
+  
+  #calculate cohen's D
+  cohen_d <- round((mean_of_sample_2-mean_of_sample_1)/sqrt((variance_sample_1 + variance_sample_2)/2),2)
+  
+  #score effect size
+  eff_size = case_when(
+    abs(cohen_d) >=0.8 ~ "large",
+    abs(cohen_d) >= 0.5 & cohen_d < 0.8 ~ "medium",
+    abs(cohen_d) >= 0.2 & cohen_d < 0.5 ~ "small",
+    abs(cohen_d) >= 0 & cohen_d < 0.2 ~"minimal"
+  )
+  
+  #put in text output
+  text = paste0("(T = ", t, ", df = ", df, ", P = ", p, ", Cohen's d =  ", cohen_d, ", Effect size = ", eff_size, ")")
+  return(list(text, t, p, cohen_d))
+  
+}
+
+
 #for hydra k3
 cohen_d_onepair <- function(data_frame, subtypeA, subtypeB, measure, hydra_cluster) {
   grpA_for_parse <- paste0("data_frame$", measure, "[which(data_frame$Hydra_k", hydra_cluster, " == ", subtypeA, ")]")

### 2024-09-12 scripts/FINAL_scripts_clean/clean_dac_pull_icd10_codes_and_make_clean_df_post_replication.R
Add files via upload

@@ -83,7 +83,8 @@ bcp <- read.csv("/Users/eballer/BBL/medication_data/BCP_est_and_prog_levels_and_
 bcp$bcp_name <- toupper(bcp$bcp_name)
 
 #read in ms med info, names of meds, mechanism, and whether or not dmt
-msmeds <- read.csv("/Users/eballer/BBL/medication_data/ms_medications_brand_and_generic.csv", sep = ",", header = TRUE)
+msmeds <- read.csv("/Users/eballer/BBL/medication_data/ms_medications_brand_and_generic_cleaned.csv", sep = ",", header = TRUE)
+#msmeds <- read.csv("/Users/eballer/BBL/medication_data/ms_medications_brand_and_generic.csv", sep = ",", header = TRUE)
 msmeds$Medication <- toupper(msmeds$Medication)
 
 #depression/psych meds from NAMI website 

### 2024-09-12 scripts/FINAL_scripts_clean/clean_dac_pull_icd10_codes_and_make_clean_df_post_replication.R
cleaned ms meds

@@ -84,7 +84,6 @@ bcp$bcp_name <- toupper(bcp$bcp_name)
 
 #read in ms med info, names of meds, mechanism, and whether or not dmt
 msmeds <- read.csv("/Users/eballer/BBL/medication_data/ms_medications_brand_and_generic_cleaned.csv", sep = ",", header = TRUE)
-#msmeds <- read.csv("/Users/eballer/BBL/medication_data/ms_medications_brand_and_generic.csv", sep = ",", header = TRUE)
 msmeds$Medication <- toupper(msmeds$Medication)
 
 #depression/psych meds from NAMI website 

### 2024-10-10 scripts/MSAnxiety_manuscript_FINAL_20241009_expanded_MSmeds.Rmd
Add files via upload

--- 2024-09-11 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_FINAL_20240911.Rmd
@@
 ---
-title: "ACNP 2024 MS ANXIETY"
+title: "MS ANXIETY"
 author: "Erica Baller"
@@
 ```
+### MS med summaries by group
+```{r demographics}
+
+#this will display a demographics table comparing age, race, sex between healthy and depressed groups, using the first presentation to treatment
+#msmeds simple, all groups
+msmeds_table_all_groups <- make_ms_med_summary_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
+
+#save 
+msmeds_table_all_groups_df <- print(msmeds_table_all_groups, as.data.frame = TRUE)
+write.csv(msmeds_table_all_groups_df, file = paste0(homedir, "/results/msmeds_table_all_groups_df.csv"), row.names = TRUE)
+
+#msmeds simple, just MS+noA and MS+severeA
+msmeds_table_diagnosis <- make_ms_med_summary_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[((df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
+
+#save 
+msmeds_table_diagnosis_df <- print(msmeds_table_diagnosis, as.data.frame = TRUE)
+write.csv(msmeds_table_diagnosis_df, file = paste0(homedir, "/results/msmeds_table_diagnosis_df.csv"), row.names = TRUE)
+```
 
@@
   group_by(EMPI) %>%
-  mutate("Physical Health Burden" = sum(across(physical_domains))/length(physical_domains)) %>%
-  mutate("Mental Health Burden" = sum(across(mood_domains))/length(mood_domains)) %>%
+  mutate("Physical Functioning" = sum(across(physical_domains))/length(physical_domains)) %>%
+  mutate("Emotional Functioning" = sum(across(mood_domains))/length(mood_domains)) %>%
   dplyr::select(EMPI,
                 anxiety_dose,
-                "Physical Health Burden",
-                "Mental Health Burden") %>%
+                "Physical Functioning",
+                "Emotional Functioning") %>%
   gather(health_variable, PROMIS_Score, -anxiety_dose, -EMPI) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
@@
 # Define the desired order of legend items
-desired_order <- c("Physical Health Burden", "Mental Health Burden")
+desired_order <- c("Physical Functioning", "Emotional Functioning")
 
@@
 # Define custom colors, ensuring the names match the levels of the factor
-custom_colors_simple <- c("Physical Health Burden" = "#4B0082",  # Purple
-                          "Mental Health Burden" = "#9ACD32")  # Green
+custom_colors_simple <- c("Physical Functioning" = "#4B0082",  # Purple
+                          "Emotional Functioning" = "#9ACD32")  # Green
 
@@
 ###
+
 df_for_promis_plot_mental_vs_physical_healthy_test <- df_people_with_promis_data_scores_added_unique %>%

### 2024-10-10 scripts/clean_dac_pull_icd10_codes_and_make_clean_df_post_replication_expanded_MSmeds.R

@@ -1,0 +1,196 @@
+### Clean data frame up
+
+##pre: dac pulls from 2023 with full psychiatric ICD10 codes
+##post: rds that contains beautifully curated all_icd10_dx column. 
+## uses: Takes the dac pull, combines csvs, adds column with beautifully curated icd10 codes
+## dependencies: dplyr
+
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(purrr)
+
+
+######################
+## FUNCTIONS #########
+######################
+####Extract unique ICD10 codes
+### takes an empi, returns all the unique diagnostic codes.
+### steps: 1) filter data frame by EMPI; 2) separate into 1 column per diagnosis; 3) remove doubles; 4) combine/paste into 1 column separated by semicolons; 5) return
+get_all_unique_ICD10_diagnoses <- function(indiv_empi) {
+  data_frame<-data_pull
+  all_unique_diagnoses <- data_frame %>% 
+    filter(str_detect(EMPI, indiv_empi)) %>% 
+    dplyr::select(ICD10) %>%
+    separate_rows(ICD10, sep = ";") %>%
+    summarize(all_icd_codes = paste(unique(ICD10), collapse = ";"))
+  #print(all_unique_diagnoses$all_icd_codes)
+  return(all_unique_diagnoses$all_icd_codes)
+}
+
+
+
+######################
+## CODE ##############
+######################
+
+#this goes through dac pulls, combines them, cleans them, and saves them as rds that can be loaded in other analyses. To clean up. 
+
+#############################################################################################################################
+### ***** MUST CHANGE THE HOMEDIR  AND THE PATHS TO DATA AND OUTPUT IN ORDER FOR THIS TO WORK ON A NEW PULL> THIS IS REALLY IMPORTANT ###
+#############################################################################################################################
+
+homedir <- "/Users/eballer/BBL/msanxiety/"
+
+## output directory
[…]

### 2024-10-10 scripts/ms_functions.R

@@ -90,7 +90,72 @@ make_demographics_table_ms_anxiety_simple<- function(data_frame) {
   print(demo_table_by_on_depAndAnxiety_true_healthy , showAllLevels = TRUE)
   
   
+  return(demo_table_by_on_depAndAnxiety_true_healthy)
+}
+
+make_ms_med_summary_table_ms_anxiety_simple<- function(data_frame) {
+  #subset demographics
+  listVars <- c("oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed",
+                "anxiety_dose",
+                "on_anti_cd20",
+                "on_interferon",
+                "on_steroids",
+                "on_DHODH_inhibitor",
+                "on_a4_integrin_inhibitor",
+                "on_anti_metabolite",
+                "on_mbp_analog",
+                "on_nrf_2",
+                "on_s1p_agonist")
+                
   
+  #for_parse <- paste0("data.frame(data_frame$race_binarized, data_frame$sex_binarized, data_frame$PAT_AGE_AT_EXAM, data_frame$depGroupVar, data_frame$PHQ.2, data_frame$PHQ.9)")
+  # for_parse <- paste0(data.frame(data_frame$race_binarized,
+  for_parse <- paste0("data.frame(
+                      data_frame$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed,
+                      data_frame$anxiety_dose,
+                      data_frame$On.Anti_cd20,
+                      data_frame$On.Interferon,
+                      data_frame$On.Steroids,
+                      data_frame$On.DHODH_inhibitor,
+                      data_frame$On.a4_integrin_inhibitor,
+                      data_frame$On.anti_metabolite,
+                      data_frame$On.mbp_analog,
+                      data_frame$On.nrf_2,
+                      data_frame$On.s1p_agonist)")
+  
+  
+  demo <- eval(parse(text = for_parse)) 
+  names(demo) <- c(listVars)
+  
+  #Change categorical values to have names
+  
+  ### uncomment the line below if you want to binarize race
[…]

### 2025-01-18 scripts/jama_scripts/get_fast_total_brain_volume_all_subjs.sh
Add files via upload

@@ -1,0 +1,30 @@
+#!/bin/bash
+
+#### Welcome to the fast party #########
+### Pre: Must have a file with full paths to the lesioned data 
+### Post: Within each directory specified by the lesioned data, we will have a bunch of fast files that we can use to calculate total volumes
+### Uses: For use in MS depression - iterates through each subject and session
+#dependencies: Using fsl
+
+default='/project/msdepression/data/melissa_martin_files/csv/mimosa_binary_masks_hcp_space_20211026_n2336'
+num_cores=1
+
+if [ $# == 0 ]
+then
+    echo "We will use the default mimosa path file" $default
+    lesion_file=$default
+else  
+    lesion_file=$1
+fi
+echo "File being read is "$lesion_file
+echo "... Starting to fast ..."
+
+lesion_paths=$(cat $lesion_file)
+
+job_count=1
+for lesion in ${lesion_paths}; do
+    echo "Working on file" $lesion
+    bsub -J "job+${job_count}" -n ${num_cores} -o /project/msdepression/scripts/logfiles/fast_${job_count}.out /project/msdepression/scripts/make_fast_files_single_subj_pmacs.sh $lesion
+    ((job_count+=1))
+done
+

### 2025-01-18 scripts/jama_scripts/make_fast_files_single_subj_pmacs.sh

@@ -1,0 +1,70 @@
+#!/bin/bash
+##########################
+### Total brain volume ###
+##########################
+
+##Pre: list of full paths to mimosa files, which are in same directory as their n4 skull-stripped t1
+##Post: in /results/total_brain_volume.csv, each EMPI and and total brain volumewill be listed
+##Uses: To address JAMA, will go through each person, calculate tbv with fslstats <.nii.gz> -V | cut -f 1 -d ' ', and store in output file
+## Dependencies: need fsl to be installed
+
+set -euf -o pipefail
+
+export ITK_GLOBAL_DEFAULT_NUMBER_OF_THREADS=$LSB_DJOB_NUMPROC
+num_cores=1
+
+#set default paths 
+#directory='/project/msdepression/'
+#default="${directory}/data/melissa_martin_files/csv/mimosa_binary_masks_hcp_space_20211026_n2336"
+output_csv="total_fast_brain_volume_values.csv"
+#default='/project/msdepression/data/melissa_martin_files/csv/erica_mini_mimosa_paths_n3'
+output_prefix="fast"
+#fascicle_directory='/project/msdepression/templates/dti/HCP_YA1065_tractography/'
+
+
+if [ $# == 0 ]
+then
+    echo "no file, something is wrong"
+else  
+    lesion=$1
+fi
+echo "File being read is "$lesion
+echo "... Starting to calculate total brain volume ..."
+
+	echo "working on ${lesion} ..."  
+	skull_stripped_file=`echo ${lesion} | perl -pe 's/mimosa_binary_mask_0.25_mni_hcp.nii.gz/t1_n4_reg_brain_ws.nii.gz/'`
+	echo "skullstripped file ${skull_stripped_file}"
+
+	directory=$(echo ${lesion} | perl -pe 's/(.*run-001).*/$1/')
+	echo $directory
+
+	#initialize output file
+	output_csv="${directory}/total_fast_brain_volume_values.csv"
+	
+	#remove it if it exists
+	rm -f $output_csv
+	touch $output_csv
+	echo "EMPI,EXAM_DATE,gm_volume,wm_volume,total_volume" >> $output_csv
+
+	#run fast
[…]

### 2025-01-19 scripts/jama_scripts/MSAnxiety_manuscript_JAMA_revision_20250116.Rmd
w/steiger

--- 2024-10-10 scripts/MSAnxiety_manuscript_FINAL_20241009_expanded_MSmeds.Rmd
@@
 library(ggpubr)
-library(tidymv)
+library(tidygam)
+library(psych)
+#library(tidymv)
+library(aod)
 library(viridis)  # Ensure you have the viridis package
 #functions
-source("~/BBL/msanxiety/scripts/ms_functions.R")
+source("~/Library/CloudStorage/Box-Box/BBL/ms_generic_scripts/msdepression_functions.R")
 ```
@@
 ```{r read_in_df}
-homedir <- "/Users/eballer/BBL/msanxiety/"
+homedir <- "~/Library/CloudStorage/Box-Box/BBL/msanxiety/"
 
@@
 #read in mimosa data
-mimosa_qc <- read.csv("/Users/eballer/BBL/msdepression/data/melissa_martin_files/csv/mimosa_dataframe", sep = ",", header = FALSE) #n=2841
+mimosa_qc <- read.csv("~/Library/CloudStorage/Box-Box/BBL/msdepression/data/melissa_martin_files/csv/mimosa_dataframe", sep = ",", header = FALSE) #n=2841
 
@@
 
-fascicle_proportions <- read.csv(paste0("/Users/eballer/BBL/msdepression//results/fascicle_volumes_all_subjects_roi_n2336.csv"), header = T, sep = ",") #n = 2336
+fascicle_proportions <- read.csv(paste0("~/Library/CloudStorage/Box-Box/BBL/msdepression//results/fascicle_volumes_all_subjects_roi_n2336.csv"), header = T, sep = ",") #n = 2336
 fascicle_proportions <- fascicle_proportions %>%
@@
 
-lesion_volumes <- read.csv("/Users/eballer/BBL/msdepression/results/mimosa_binary_masks_hcp_space_20211026_n2336_volumes", sep = ",", header = TRUE) #n=2336, 958 unique, identical to fascicle unique
+lesion_volumes <- read.csv("~/Library/CloudStorage/Box-Box/BBL/msdepression/results/mimosa_binary_masks_hcp_space_20211026_n2336_volumes", sep = ",", header = TRUE) #n=2336, 958 unique, identical to fascicle unique
 lesion_volumes <- lesion_volumes %>%
@@
 
+### read in brain volume size
+```{r read_in_brain_volumes}
+##########################################################
+#             Read in Brain Volumes                     #
+##########################################################
+
+# contains the volume of lesioned voxels, i.e. a sum of all the areas of each individual's binary mask that are 1
+
+brain_volumes <- read.csv(paste0(homedir, "/results/total_fast_brain_volumes_all_subjs.csv"), sep = ",", header = TRUE) #n=2336, 
+brain_volumes <- brain_volumes %>%
+  mutate(EMPI = as.character(EMPI)) %>%
+  mutate(EXAM_DATE = as.character(EXAM_DATE))
+
+```
+
+### merge brain vol with data frame with good mimosas
+```{r merge_brain_volume_w_mimosa_df}
+##########################################################
+#             Merge lesion volumes with mimosa df        #
+##########################################################
+#merge whole data set with fascicle proportions, n = 814
+df_demo_and_fascicles <- df_demo_and_fascicles %>%
+  left_join(brain_volumes, by = c("EMPI", "EXAM_DATE"))
+
+#test to make sure age is correlated with gm and tbv
+gmv_cor_age <- cor.test(df_demo_and_fascicles$PAT_AGE_AT_EXAM, df_demo_and_fascicles$gm_volume)
+print(gmv_cor_age) #Yup: t = -6.9769, df = 812, p-value = 6.264e-12 (higher age, lower gmv); cor = -0.237817
+
+tbv_cor_age <- cor.test(df_demo_and_fascicles$PAT_AGE_AT_EXAM, df_demo_and_fascicles$total_volume)
+print(tbv_cor_age) #Yup: t = -4.5874, df = 812, p-value = 5.196e-06 (higher age, lower tbv); cor = -0.158941 
+```
+
 ### make separate columns for proportional injury (prop), total volume injury (vol)
@@
 #read in fiber volume values
-fiber_volume_values <- read.csv("/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fiber_volume_values.csv", sep=",", header = T)
+fiber_volume_values <- read.csv("~/Library/CloudStorage/Box-Box//BBL/msdepression/templates/dti/HCP_YA1065_tractography/fiber_volume_values.csv", sep=",", header = T)
 
@@
 ```{r read_in_neurosynth_anxiety_network}
-neurosynth_anxiety_network_fascicle_overlap <- read.csv("/Users/eballer/BBL/msanxiety/results/streamline_volume_within_anxiety_network_association_neuro_maps_FDR_01.csv", header = T, sep = ",") %>% 
+neurosynth_anxiety_network_fascicle_overlap <- read.csv(paste0(homedir, "/results/streamline_volume_within_anxiety_network_association_neuro_maps_FDR_01.csv"), header = T, sep = ",") %>% 
   filter(fascicle %in% fascicle_names_no_cranial_nerves) %>%
@@
 #msmeds simple, all groups
-msmeds_table_all_groups <- make_ms_med_summary_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
+#msmeds_table_all_groups <- make_ms_med_summary_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified",])
 
 #save 
-msmeds_table_all_groups_df <- print(msmeds_table_all_groups, as.data.frame = TRUE)
-write.csv(msmeds_table_all_groups_df, file = paste0(homedir, "/results/msmeds_table_all_groups_df.csv"), row.names = TRUE)
+#msmeds_table_all_groups_df <- print(msmeds_table_all_groups, as.data.frame = TRUE)
+#write.csv(msmeds_table_all_groups_df, file = paste0(homedir, "/results/msmeds_table_all_groups_df.csv"), row.names = TRUE)
 
 #msmeds simple, just MS+noA and MS+severeA
-msmeds_table_diagnosis <- make_ms_med_summary_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[((df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
+#msmeds_table_diagnosis <- make_ms_med_summary_table_ms_anxiety_simple(data_frame = df_demo_and_fascicles[((df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") & (df_demo_and_fascicles$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds")),])
 
 #save 
-msmeds_table_diagnosis_df <- print(msmeds_table_diagnosis, as.data.frame = TRUE)
-write.csv(msmeds_table_diagnosis_df, file = paste0(homedir, "/results/msmeds_table_diagnosis_df.csv"), row.names = TRUE)
+#msmeds_table_diagnosis_df <- print(msmeds_table_diagnosis, as.data.frame = TRUE)
+#write.csv(msmeds_table_diagnosis_df, file = paste0(homedir, "/results/msmeds_table_diagnosis_df.csv"), row.names = TRUE)
 ```
@@
 ####Test promis*anxiety dose  stats
+#####NEW JAMA ANALYSIS: Testing for Normality - all normally distributed
+```{r normality_testing}
+###
+
+df_for_promis_plot_mental_vs_physical_healthy_test <- df_people_with_promis_data_scores_added_unique %>%
+  group_by(EMPI) %>%
+  mutate(physical_health_score = sum(across(physical_domains))/length(physical_domains)) %>%
+  mutate(mental_health_score = sum(across(mood_domains))/length(mood_domains)) %>%
+  mutate(phys_mental_diff_score = physical_health_score-mental_health_score) %>%
+  dplyr::select(EMPI,
+                anxiety_dose,
+                physical_health_score,
+                mental_health_score,
+                phys_mental_diff_score)
+
+### Normality tests
+
+### MS noA
+## MS+noA, Physical -> W = 0.87548, p-value = 0.07673 (normal)
+ms_noa_physical_normality <- shapiro.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose == 0])
+print(ms_noa_physical_normality)
+## MS+noA, Emotional -> W = 0.92006, p-value = 0.2864 (normal)
+ms_noa_emotional_normality <- shapiro.test(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose == 0])
+print(ms_noa_emotional_normality)
+
+### MS MILD
+## MS+mildA, Physical -> W = 0.96068, p-value = 0.1297 (normal)
+ms_milda_physical_normality <- shapiro.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose == 1])
+print(ms_milda_physical_normality)
+## MS+mildA, Emotional -> W = 0.97038, p-value = 0.299 (normal)
+ms_milda_emotional_normality <- shapiro.test(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose == 1])
+print(ms_milda_emotional_normality)
+
+### MS SEVERE
+## MS+severeA, Physical -> W = 0.96162, p-value = 0.8325 (normal)
+ms_severea_physical_normality <- shapiro.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose == 2])
+print(ms_severea_physical_normality)
+## MS+severeA, Emotional -> W = 0.89898, p-value = 0.3248 (normal)
+ms_severea_emotional_normality <- shapiro.test(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose == 2])
+print(ms_severea_emotional_normality)
+
+normality_stats_table <- data.frame(matrix(nrow = 6, ncol = 5))
+names(normality_stats_table) <- c("Anxiety Severity", "PROMIS Functioning Domain", "W", "P", "Normality")
+normality_stats_table$`Anxiety Severity` <- rep(c("MS+noA", "MS+mildA", "MS+severeA"), 2)
+normality_stats_table$`PROMIS Functioning Domain` <- rep(c("Physical", "Emotional"), 3)
+
+count = 1
+for (anxiety_dose in 0:2){
+  for (promis in c("physical_health_score", "mental_health_score"))
+  {
+    normality_test <- eval(parse(text = paste0("shapiro.test(df_for_promis_plot_mental_vs_physical_healthy_test$", promis, "[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose == ", anxiety_dose, "])")))
+    print(normality_test)
+    normality_stats_table$W[count] = round(normality_test$statistic, 3)
+    normality_stats_table$P[count] = round(normality_test$p.value, 3)
+    normality_stats_table$Normality = ifelse(normality_test$p.value < 0.05, "NON-NORMAL", "NORMAL")
+    count = count + 1
+  }
+}
+print(normality_stats_table)
+
+write.csv(normality_stats_table, paste0(homedir, "results/normality_table_promis.csv"), row.names = F, sep = ",", col.names = T)
+
+```
+
 #####Physical and Mental Health together
@@
 #read csv of empis from depression paper
-depression_empis <- read.table(file="/Users/eballer/BBL/msanxiety/data/empis_of_people_in_BP_depression_paper.csv")
+depression_empis <- read.table(file=paste0(homedir, "/data/empis_of_people_in_BP_depression_paper.csv"))
 names(depression_empis) <- "EMPI"
@@
 
+### Whole brain volumes 
+#### Diagnosis 
+  - sick > healthy in vol of lesions
+```{r lesion_volumes_dx}
+ df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, total_volume) %>%
+  ungroup() #n=123
+
+##### healthy vs sick
+
+#gam brain volume; DiagnosisMS+Anxiety     3359      25590   0.131    0.896    
+#(T = 0.131, P = 0.896, Cohen's f2 =  0.4, Effect size = large)
+total_brain_volume_gam <- gam(total_volume ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+summary(total_brain_volume_gam)
+
+ #print summary stats
+ gam_summary_stats(total_brain_volume_gam)
+```
+
+#### Anxiety dose
+  - anxiety dose correlates with disease burden (total brain volume )
+```{r lesion_volumes_anxiety_dose}
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter (anxiety_dose != -1) #n=372
+
+ #brain volume anxiety dose + sex + age: anxiety_dose     3948      11484   0.344    0.731  
+#(T = 0.344, P = 0.731, Cohen's f2 =  0.311, Effect size = medium)
+
+  anxiety_dose_total_brain_volume_by_sex_gam <- gam(total_volume ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(anxiety_dose_total_brain_volume_by_sex_gam)
+
+   #print summary stats
+ gam_summary_stats(anxiety_dose_total_brain_volume_by_sex_gam)
+
+```
+
 ### Uncinate **ACNP**
@@
 #### Sensitivity
-###### UF by depGroupVar (vol and prop, N.S)
+###### UF by depGroupVar (vol/prop, N.S)
 ```{r UF_by_depGroupVar}
@@
  gam_summary_stats(dep_mean_UF_gam_prop)
+
+```
+
+###### Lesion & brainvol by depGroupVar (lesion vol - Y, tbv - N, N.S)
+```{r UF_by_depGroupVar}
+# Specificity - want to make sure the lesion and brain vol findings are nonspecific t so check to see if same findings exist in depression
+### Reviewed previous pull from BP paper, finding was also consistent there -> no diff in uncinate in depressed vs non depressed
+
+df_dep <- df_demo_and_fascicles %>%
+  filter(depGroupVar != 0) %>%
+  mutate(depDiagnosis = as.factor(ifelse(depGroupVar ==2, "MS+Depression", "MS+noDepression")))
+
+table(df_dep$depDiagnosis) #MS+Dep n = 207; MS+noDep n = 99
+
+ #mean vol mimosa lesions, depDiagnosisMS+noDepression 
+#(T = -3.164, P = 0.002, Cohen's f2 =  0.128, Effect size = small)
+dep_mean_lesion_vol_gam_prop <- gam(volume_of_mimosa_lesions ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
+summary(dep_mean_lesion_vol_gam_prop)
+
+  #print summary stats
+ gam_summary_stats(dep_mean_lesion_vol_gam_prop)
+
+  #mean brain vol mimosa lesions, depDiagnosisMS+noDepression  
+ #(T = 0.016, P = 0.988, Cohen's f2 =  0.333, Effect size = medium)
+dep_mean_total_brain_vol_gam_prop <- gam(total_volume ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
+summary(dep_mean_total_brain_vol_gam_prop)
+
+  #print summary stats
+ gam_summary_stats(dep_mean_total_brain_vol_gam_prop)
+
 ```
@@
  gam_summary_stats(anxietyGrouping_mean_F_by_sex_gam_prop)
+```
+
+###### JAMA ANALYSIS- UF Anxiety diagnosis + lesion vol
+```{r uncinate_by_dx}
+### Having found that there is no association between the number of uncinate lesions and the anxiety dose, I next explored whether the *burden* of uncinate lesions differs by diagnosis/group
+
+#### Fx = F gives better results than FX = T
+
+### Results:  
+#define group
+  uncinate_by_dx_df <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  mutate(mean_UF_vol_scaled_total_vol_lesions = mean_UF_vol/volume_of_mimosa_lesions) %>%
+  ungroup() #n=123
+
+#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety   0.10624    0.05255   2.022   0.0455  * original result
+
+#First, test if they are related. If so, they can't really be modeled together ->
+
+  corr_LV_to_UF <- cor.test(uncinate_by_dx_df$volume_of_mimosa_lesions,uncinate_by_dx_df$mean_UF_vol) #corr 0.69; 
+  print(corr_LV_to_UF)
+
+  lesion_vol_UF_lm <- lm(uncinate_by_dx_df$volume_of_mimosa_lesions~ uncinate_by_dx_df$mean_UF_vol) #P <2.2*10^-16, they are colinear
+  summary(lesion_vol_UF_lm) #T=10.585
+
+  #how about in fornix
+
+  corr_LV_to_fornix <- cor.test(uncinate_by_dx_df$volume_of_mimosa_lesions,uncinate_by_dx_df$mean_fornix_volume) #corr 0.69; 
+  print(corr_LV_to_fornix) #0.3452654
+
+  lesion_vol_fornix_lm <- lm(uncinate_by_dx_df$volume_of_mimosa_lesions~ uncinate_by_dx_df$mean_fornix_volume)
+  summary(lesion_vol_fornix_lm) #T = 4.047
+
+  ## Try scaling mean volume
+  disease_mean_scaled_UF_vol_gam <- gam(mean_UF_vol_scaled_total_vol_lesions ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
+  summary(disease_mean_scaled_UF_vol_gam) #- N.S.
+
+  #print summary stats; (T = -0.556, P = 0.579, Cohen's f2 =  0.007, Effect size = minimal)"
+  gam_summary_stats(disease_mean_scaled_UF_vol_gam)
+
+  #How about predicting Diagnosis? - nope
+  diagnosis_prediction <- glm(Diagnosis ~ mean_UF_prop + Diagnosis + osex+PAT_AGE_AT_EXAM + volume_of_mimosa_lesions, data = uncinate_by_dx_df, family = "binomial")
+  summary(diagnosis_prediction)
+  confint(diagnosis_prediction)
+
+  #how about predicting diagnosis with scaled UF? N.S.
+  diagnosis_prediction_scaled <- glm(Diagnosis ~ mean_UF_vol_scaled_total_vol_lesions + Diagnosis + osex+PAT_AGE_AT_EXAM, data = uncinate_by_dx_df, family = "binomial")
+  summary(diagnosis_prediction_scaled)
+  confint(diagnosis_prediction_scaled)
+
+## modeling this doesn't make sense
+#disease_mean_UF_prop_w_LV_gam <- gam(mean_UF_prop ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F) + volume_of_mimosa_lesions, data = uncinate_by_dx_df)
+#summary(disease_mean_UF_prop_w_LV_gam)
+
+ #print summary stats
+ # gam_summary_stats(disease_mean_UF_prop_w_LV_gam)
+```
+###### JAMA ANALYSIS-  UF Anxiety dose + lesion vol
+```{r uncinateByAnxietyDose}
+
+#### Fx = F gives better results than FX = T
+#results: Anxiety dose related to UF_R when covarying for linear effects of age and sex, just barely
+# Additionally - taking the mean of both UF and UR, LM for bilat anxiety dose + sex + age: anxiety_dose most sig P= 0.0367 *  (fx=T)
+
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) #n=372
+
+    #bilat anxiety dose + sex + age: anxiety_dose    0.04989    0.02397   2.082   0.0381 * original result
+
+  #How about predicting Diagnosis? volume_of_mimosa_lesions  1.518e-05  7.147e-06   2.124   0.0357 *
+  diagnosis_prediction <- lm(anxiety_dose ~ mean_UF_prop + osex+PAT_AGE_AT_EXAM + volume_of_mimosa_lesions, data = uncinate_by_dx_df)
+  summary(diagnosis_prediction)
+  confint(diagnosis_prediction)
+
+### modeling volume of mimosa lesions like this doesn't make sense
+ #anxietyGrouping_mean_UF_by_sex_w_LV_gam_prop <- gam(mean_UF_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F) + volume_of_mimosa_lesions, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+ # summary(anxietyGrouping_mean_UF_by_sex_w_LV_gam_prop)
+
+  #print summary stats
+  #gam_summary_stats(anxietyGrouping_mean_UF_by_sex_w_LV_gam_prop)
+
+```
+###### JAMA ANALYSIS- UF Anxiety diagnosis + total brain vol
+```{r uncinate_by_dx}
+### Having found that there is no association between the number of uncinate lesions and the anxiety dose, I next explored whether the *burden* of uncinate lesions differs by diagnosis/group
+
+#### Fx = F gives better results than FX = T
+
+### Results:  
+#define group
+  uncinate_by_dx_df <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(Diagnosis = as.factor(Diagnosis)) %>%
+  ungroup() #n=123
+
+#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety   0.10624    0.05255   2.022   0.0455  * original result
+
+#First, test if they are related. If so, they can't really be modeled together ->
+
+ # t = -0.34681, df = 121, p-value = 0.7293; corr -0.03151255
+
+  corr_tbv_to_UF <- cor.test(uncinate_by_dx_df$total_volume,uncinate_by_dx_df$mean_UF_vol) #corr 0.69; 
+  print(corr_tbv_to_UF)
+
+  total_vol_UF_lm <- lm(uncinate_by_dx_df$total_volume~ uncinate_by_dx_df$mean_UF_vol) #P <2.2*10^-16, they are colinear
+  summary(total_vol_UF_lm)
+
+  #can covary, no change: "(T = 2.009, P = 0.047, Cohen's f2 =  0.19, Effect size = medium)"
+  disease_UF_cov_brain_vol_gam <- gam(mean_UF_prop ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F) + total_volume, data = uncinate_by_dx_df)
+  summary(disease_UF_cov_brain_vol_gam) #- N.S.
+  gam_summary_stats(disease_UF_cov_brain_vol_gam)
+```
+
+###### JAMA ANALYSIS-  UF Anxiety dose + total brain volume
+```{r uncinateByAnxietyDose}
+
+#### Fx = F gives better results than FX = T
+#results: Anxiety dose related to UF_R when covarying for linear effects of age and sex, just barely
+# Additionally - taking the mean of both UF and UR, LM for bilat anxiety dose + sex + age: anxiety_dose most sig P= 0.0367 *  (fx=T)
+
+#define group
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) #n=372
+
+#check correlations  
+# cor: -0.06590961 ; t = -1.2706, df = 370, p-value = 0.2047
+  corr_tbv_to_UF <- cor.test(df_demo_and_fascicles_no_unclass_anxiety_dose$total_volume,df_demo_and_fascicles_no_unclass_anxiety_dose$mean_UF_vol) #corr 0.69; 
+  print(corr_tbv_to_UF)
+
+  total_vol_UF_lm <- lm(df_demo_and_fascicles_no_unclass_anxiety_dose$total_volume~ df_demo_and_fascicles_no_unclass_anxiety_dose$mean_UF_vol) #P <2.2*10^-16, they are colinear
+  summary(total_vol_UF_lm)
+
+  #can covary, no change: (T = 2.089, P = 0.037, Cohen's f2 =  0.102, Effect size = small)
+  disease_UF_cov_brain_vol_dose_gam <- gam(mean_UF_prop ~ anxiety_dose + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F) + total_volume, data = df_demo_and_fascicles_no_unclass_anxiety_dose)
+  summary(disease_UF_cov_brain_vol_dose_gam) #- N.S.
+  gam_summary_stats(disease_UF_cov_brain_vol_dose_gam)
+
+```
+##### JAMA Analysis: Residuals vs UF
+```{r dep_anxiety_UF}
+
+## Definte data frams
+################
+## depression ##
+################
+df_dep <- df_demo_and_fascicles %>%
+  filter(depGroupVar != 0) %>%
+  mutate(depDiagnosis = as.factor(ifelse(depGroupVar ==2, "MS+Depression", "MS+noDepression")))
+
+####################### 
+## anxiety diagnosis ##
+#######################
+df_anxiety_dx <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
+  mutate(subject = as.factor(EMPI)) %>%
+  mutate(anxiety_Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
+  mutate(anxiety_Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
+  mutate(anxiety_Diagnosis = as.factor(anxiety_Diagnosis)) %>%
+  ungroup()
+
+##################
+## anxiety dose ##
+################## 
+df_anxiety_dose <-  df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1) #n=372
+
+### stats
+# Step 1: Fit the three models
+
+# Model 1: depDiagnosis with df_dep
+model_depDiagnosis <- gam(mean_UF_prop ~ depDiagnosis + s(PAT_AGE_AT_EXAM, k=4, fx=F) + osex, data = df_dep)
+
+# Model 2: anxiety_Diagnosis with df_anxiety_dx
+model_anxiety_Diagnosis <- gam(mean_UF_prop ~ anxiety_Diagnosis + s(PAT_AGE_AT_EXAM, k=4, fx=F) + osex, data = df_anxiety_dx)
+
+# Model 3: anxiety_dose with df_anxiety_dose
+model_anxiety_dose <- gam(mean_UF_prop ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k=4, fx=F) + osex, data = df_anxiety_dose)
+
+# Step 2: Extract residuals from each model (mean_UF_prop adjusted for age and sex)
+residuals_depDiagnosis <- residuals(model_depDiagnosis)
+residuals_anxiety_Diagnosis <- residuals(model_anxiety_Diagnosis)
+residuals_anxiety_dose <- residuals(model_anxiety_dose)
+
+# Step 3: Calculate the correlation between mean_UF_prop and the predictors (residuals)
+cor_depDiagnosis <- cor(df_dep$mean_UF_prop, residuals_depDiagnosis)
+cor_anxiety_Diagnosis <- cor(df_anxiety_dx$mean_UF_prop, residuals_anxiety_Diagnosis)
+cor_anxiety_dose <- cor(df_anxiety_dose$mean_UF_prop, residuals_anxiety_dose)
+
+# Print the correlation results
+cat("Correlation between mean_UF_prop and depDiagnosis: ", cor_depDiagnosis, "\n")
+cat("Correlation between mean_UF_prop and anxiety_Diagnosis: ", cor_anxiety_Diagnosis, "\n")
+cat("Correlation between mean_UF_prop and anxiety_dose: ", cor_anxiety_dose, "\n")
+
+# Step 4: Perform Steiger's test for comparing the correlations
+# Create a function for Steiger's test (comparison of two correlated correlations)
+steiger_test <- function(r12, r13, n) {
+  # r12: correlation between variable1 and variable2
+  # r13: correlation between variable1 and variable3
+  # n: sample size
+
+  # Calculate the Z score for comparison
+  z <- (r12 - r13) / sqrt((1 - r12^2) / (n - 3) + (1 - r13^2) / (n - 3))
+  p_value <- 2 * (1 - pnorm(abs(z)))  # Two-tailed p-value
+
+  return(list(Z_score = z, p_value = p_value))
+}
+
+# Sample size (number of subjects)
+n = length(Reduce(intersect, list(df_dep$EMPI, df_anxiety_dx$EMPI, df_anxiety_dose$EMPI)))
+
+# Step 5: Test for differences between correlations
+# Test if the correlation between anxiety_Diagnosis and mean_UF_prop is stronger than depression
+steiger_test_anxiety_vs_dep <- steiger_test(cor_anxiety_Diagnosis, cor_depDiagnosis, n)
+
+# Test if the correlation between anxiety_dose and mean_UF_prop is stronger than depression
+steiger_test_anxiety_dose_vs_dep <- steiger_test(cor_anxiety_dose, cor_depDiagnosis, n)
+
+# Output the results of Steiger's test; Z score:  -0.7806441 ; p-value:  0.4350118 
+cat("Steiger's Test: Anxiety Diagnosis vs Depression Diagnosis\n")
+cat("Z score: ", steiger_test_anxiety_vs_dep$Z_score, "\n")
+cat("p-value: ", steiger_test_anxiety_vs_dep$p_value, "\n")
+
+#Z score:  0.07445476 ; p-value:  0.9406485 
+cat("Steiger's Test: Anxiety Dose vs Depression Diagnosis\n")
+cat("Z score: ", steiger_test_anxiety_dose_vs_dep$Z_score, "\n")
+cat("p-value: ", steiger_test_anxiety_dose_vs_dep$p_value, "\n")
+```
+
+```
+##### JAMA ANALYSIS - compare correlations w/wout uncinate
+```{r other_injured_fascicles}
+df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
+  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
+  filter(anxiety_dose != -1)  %>% #n=372 
+  mutate(total_lesion_burden_no_UF = sum_fascicle_vol_lost - (UF_L_vol + UF_R_vol))
+
+#almost identical because uncinate is small
+#t=2.05, p = 0.04083
+cor_lesion_burden_by_anxiety = cor.test(df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose, df_demo_and_fascicles_no_unclass_anxiety_dose$sum_fascicle_vol_lost)
+print(cor_lesion_burden_by_anxiety)
+
+#t=2.05, p = 0.04075
+cor_lesion_burden_no_UF_by_anxiety = cor.test(df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose, df_demo_and_fascicles_no_unclass_anxiety_dose$total_lesion_burden_no_UF)
+print(cor_lesion_burden_no_UF_by_anxiety)
+
 ```
@@
 ```
+
+```{r ants}
+
+```

### 2025-01-19 scripts/jama_scripts/ms_functions.R

@@ -1,0 +1,1863 @@
+require('visreg')
+require('mgcv')
+require('tableone')
+require('dplyr')
+require('plm')
+require('MatchIt')
+require('tidyr')
+require('ggplot2')
+require('reshape')
+require('emmeans')
+require('cowplot')
+require('stringr')
+require('visreg')
+require('rasterVis')
+require('lattice')
+require('circlize')
+## set directories ##
+#local_wkdir <- '~/Google Drive/TDSlab/SCZ_gene_imaging/'
+#remote_wkdir <- '~/Desktop/BBL/data/joy/BBL/studies/pnc/'
+
+#############################
+###Make Demographics Table###
+#############################
+
+#############################
+####### Demographics ########
+#############################
+
+#### anxiety demographics
+
+make_demographics_table_ms_anxiety_simple<- function(data_frame) {
+  #subset demographics
+  
+  listVars <- c("Race", 
+                "Sex",
+                "Age",
+                "Has.anxietydx", 
+                "On.Anxiolytics",
+                "oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed",
+                "anxiety_dose",
+                "on_anti_cd20",
+                "on_interferon",
+                "on_steroids",
+                "on_dmt",
+                "PHQ2",
+                "PHQ9",
+                "volume_of_mimosa_lesions", 
+                "mean_UF_vol",
+                "proportion_volume_lost_per_total_network_size_sum") #Race 1 = caucasian, Sex 1 = M age = years
+  
+  
+  #for_parse <- paste0("data.frame(data_frame$race_binarized, data_frame$sex_binarized, data_frame$PAT_AGE_AT_EXAM, data_frame$depGroupVar, data_frame$PHQ.2, data_frame$PHQ.9)")
+  # for_parse <- paste0(data.frame(data_frame$race_binarized,
+  for_parse <- paste0("data.frame(data_frame$RACE, 
+                      data_frame$sex_binarized, 
+                      data_frame$PAT_AGE_AT_EXAM, 
+                      data_frame$Has.anxietydx, 
+                      data_frame$On.Anxiolytics,
+                      data_frame$oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed,
+                      data_frame$anxiety_dose,
+                      data_frame$On.Anti_cd20,
+                      data_frame$On.Interferon,
[…]

### 2025-01-20 scripts/jama_scripts/MSAnxiety_manuscript_JAMA_revision_20250116.Rmd
clean

@@
 ### Lesion volumes 
-#### Diagnosis 
-  - sick > healthy in vol of lesions
+#### Diagnosis - sick > healthy in vol of lesions
 ```{r lesion_volumes_dx}
@@
 
- #print summary stats
+ #print summary stats; (T = 3.04, P = 0.003, Cohen's f2 =  0.342, Effect size = medium)
  gam_summary_stats(volume_of_mimosa_lesions_gam)
@@
 
-#### Anxiety dose
-  - anxiety dose correlates with disease burden (volume of lesions)
+#### Anxiety dose- anxiety dose correlates with disease burden (volume of lesions)
 ```{r lesion_volumes_anxiety_dose}
@@
 
-   #print summary stats
+   #print summary stats; (T = 3.084, P = 0.0022, Cohen's f2 =  0.12, Effect size = small)
  gam_summary_stats(anxiety_dose_volume_of_mimosa_lesions_by_sex_gam)
@@
 ### Whole brain volumes 
-#### Diagnosis 
-  - sick > healthy in vol of lesions
+#### Diagnosis - sick > healthy in vol of lesions
 ```{r lesion_volumes_dx}
@@
 
-#bilateral UF ~ Diagnosis: DiagnosisMS+Anxiety   0.10624    0.05255   2.022   0.0455  * original result
-
 #First, test if they are related. If so, they can't really be modeled together ->
 
-  corr_LV_to_UF <- cor.test(uncinate_by_dx_df$volume_of_mimosa_lesions,uncinate_by_dx_df$mean_UF_vol) #corr 0.69; 
+  corr_LV_to_UF <- cor.test(uncinate_by_dx_df$volume_of_mimosa_lesions,uncinate_by_dx_df$mean_UF_vol) #corr 0.69; p-value < 2.2e-16
   print(corr_LV_to_UF)
-
-  lesion_vol_UF_lm <- lm(uncinate_by_dx_df$volume_of_mimosa_lesions~ uncinate_by_dx_df$mean_UF_vol) #P <2.2*10^-16, they are colinear
-  summary(lesion_vol_UF_lm) #T=10.585
 
@@
   ## Try scaling mean volume
-  disease_mean_scaled_UF_vol_gam <- gam(mean_UF_vol_scaled_total_vol_lesions ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
-  summary(disease_mean_scaled_UF_vol_gam) #- N.S.
+ # disease_mean_scaled_UF_vol_gam <- gam(mean_UF_vol_scaled_total_vol_lesions ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
+  #summary(disease_mean_scaled_UF_vol_gam) #- N.S.
 
   #print summary stats; (T = -0.556, P = 0.579, Cohen's f2 =  0.007, Effect size = minimal)"
-  gam_summary_stats(disease_mean_scaled_UF_vol_gam)
-
-  #How about predicting Diagnosis? - nope
-  diagnosis_prediction <- glm(Diagnosis ~ mean_UF_prop + Diagnosis + osex+PAT_AGE_AT_EXAM + volume_of_mimosa_lesions, data = uncinate_by_dx_df, family = "binomial")
-  summary(diagnosis_prediction)
-  confint(diagnosis_prediction)
-
-  #how about predicting diagnosis with scaled UF? N.S.
-  diagnosis_prediction_scaled <- glm(Diagnosis ~ mean_UF_vol_scaled_total_vol_lesions + Diagnosis + osex+PAT_AGE_AT_EXAM, data = uncinate_by_dx_df, family = "binomial")
-  summary(diagnosis_prediction_scaled)
-  confint(diagnosis_prediction_scaled)
+  #gam_summary_stats(disease_mean_scaled_UF_vol_gam)
 
@@
 
-    #bilat anxiety dose + sex + age: anxiety_dose    0.04989    0.02397   2.082   0.0381 * original result
-
-  #How about predicting Diagnosis? volume_of_mimosa_lesions  1.518e-05  7.147e-06   2.124   0.0357 *
-  diagnosis_prediction <- lm(anxiety_dose ~ mean_UF_prop + osex+PAT_AGE_AT_EXAM + volume_of_mimosa_lesions, data = uncinate_by_dx_df)
-  summary(diagnosis_prediction)
-  confint(diagnosis_prediction)
-
-### modeling volume of mimosa lesions like this doesn't make sense
- #anxietyGrouping_mean_UF_by_sex_w_LV_gam_prop <- gam(mean_UF_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F) + volume_of_mimosa_lesions, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
- # summary(anxietyGrouping_mean_UF_by_sex_w_LV_gam_prop)
-
-  #print summary stats
-  #gam_summary_stats(anxietyGrouping_mean_UF_by_sex_w_LV_gam_prop)
+corr_LV_to_UF_anxiety_dose <- cor.test(df_demo_and_fascicles_no_unclass_anxiety_dose$volume_of_mimosa_lesions,df_demo_and_fascicles_no_unclass_anxiety_dose$mean_UF_vol) #
+  print(corr_LV_to_UF_anxiety_dose)
 
@@
 
-  total_vol_UF_lm <- lm(uncinate_by_dx_df$total_volume~ uncinate_by_dx_df$mean_UF_vol) #P <2.2*10^-16, they are colinear
-  summary(total_vol_UF_lm)
-
   #can covary, no change: "(T = 2.009, P = 0.047, Cohen's f2 =  0.19, Effect size = medium)"
@@
 
-  total_vol_UF_lm <- lm(df_demo_and_fascicles_no_unclass_anxiety_dose$total_volume~ df_demo_and_fascicles_no_unclass_anxiety_dose$mean_UF_vol) #P <2.2*10^-16, they are colinear
-  summary(total_vol_UF_lm)
-
   #can covary, no change: (T = 2.089, P = 0.037, Cohen's f2 =  0.102, Effect size = small)
@@
   gam_summary_stats(disease_UF_cov_brain_vol_dose_gam)
-
-```
-##### JAMA Analysis: Residuals vs UF
-```{r dep_anxiety_UF}
-
-## Definte data frams
-################
-## depression ##
-################
-df_dep <- df_demo_and_fascicles %>%
-  filter(depGroupVar != 0) %>%
-  mutate(depDiagnosis = as.factor(ifelse(depGroupVar ==2, "MS+Depression", "MS+noDepression")))
-
-####################### 
-## anxiety diagnosis ##
-#######################
-df_anxiety_dx <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
-  mutate(subject = as.factor(EMPI)) %>%
-  mutate(anxiety_Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  mutate(anxiety_Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(anxiety_Diagnosis = as.factor(anxiety_Diagnosis)) %>%
-  ungroup()
-
-##################
-## anxiety dose ##
-################## 
-df_anxiety_dose <-  df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) #n=372
-
-### stats
-# Step 1: Fit the three models
-
-# Model 1: depDiagnosis with df_dep
-model_depDiagnosis <- gam(mean_UF_prop ~ depDiagnosis + s(PAT_AGE_AT_EXAM, k=4, fx=F) + osex, data = df_dep)
-
-# Model 2: anxiety_Diagnosis with df_anxiety_dx
-model_anxiety_Diagnosis <- gam(mean_UF_prop ~ anxiety_Diagnosis + s(PAT_AGE_AT_EXAM, k=4, fx=F) + osex, data = df_anxiety_dx)
-
-# Model 3: anxiety_dose with df_anxiety_dose
-model_anxiety_dose <- gam(mean_UF_prop ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k=4, fx=F) + osex, data = df_anxiety_dose)
-
-# Step 2: Extract residuals from each model (mean_UF_prop adjusted for age and sex)
-residuals_depDiagnosis <- residuals(model_depDiagnosis)
-residuals_anxiety_Diagnosis <- residuals(model_anxiety_Diagnosis)
-residuals_anxiety_dose <- residuals(model_anxiety_dose)
-
-# Step 3: Calculate the correlation between mean_UF_prop and the predictors (residuals)
-cor_depDiagnosis <- cor(df_dep$mean_UF_prop, residuals_depDiagnosis)
-cor_anxiety_Diagnosis <- cor(df_anxiety_dx$mean_UF_prop, residuals_anxiety_Diagnosis)
-cor_anxiety_dose <- cor(df_anxiety_dose$mean_UF_prop, residuals_anxiety_dose)
-
-# Print the correlation results
-cat("Correlation between mean_UF_prop and depDiagnosis: ", cor_depDiagnosis, "\n")
-cat("Correlation between mean_UF_prop and anxiety_Diagnosis: ", cor_anxiety_Diagnosis, "\n")
-cat("Correlation between mean_UF_prop and anxiety_dose: ", cor_anxiety_dose, "\n")
-
-# Step 4: Perform Steiger's test for comparing the correlations
-# Create a function for Steiger's test (comparison of two correlated correlations)
-steiger_test <- function(r12, r13, n) {
-  # r12: correlation between variable1 and variable2
-  # r13: correlation between variable1 and variable3
-  # n: sample size
-
-  # Calculate the Z score for comparison
-  z <- (r12 - r13) / sqrt((1 - r12^2) / (n - 3) + (1 - r13^2) / (n - 3))
-  p_value <- 2 * (1 - pnorm(abs(z)))  # Two-tailed p-value
-
-  return(list(Z_score = z, p_value = p_value))
-}
-
-# Sample size (number of subjects)
-n = length(Reduce(intersect, list(df_dep$EMPI, df_anxiety_dx$EMPI, df_anxiety_dose$EMPI)))
-
-# Step 5: Test for differences between correlations
-# Test if the correlation between anxiety_Diagnosis and mean_UF_prop is stronger than depression
-steiger_test_anxiety_vs_dep <- steiger_test(cor_anxiety_Diagnosis, cor_depDiagnosis, n)
-
-# Test if the correlation between anxiety_dose and mean_UF_prop is stronger than depression
-steiger_test_anxiety_dose_vs_dep <- steiger_test(cor_anxiety_dose, cor_depDiagnosis, n)
-
-# Output the results of Steiger's test; Z score:  -0.7806441 ; p-value:  0.4350118 
-cat("Steiger's Test: Anxiety Diagnosis vs Depression Diagnosis\n")
-cat("Z score: ", steiger_test_anxiety_vs_dep$Z_score, "\n")
-cat("p-value: ", steiger_test_anxiety_vs_dep$p_value, "\n")
-
-#Z score:  0.07445476 ; p-value:  0.9406485 
-cat("Steiger's Test: Anxiety Dose vs Depression Diagnosis\n")
-cat("Z score: ", steiger_test_anxiety_dose_vs_dep$Z_score, "\n")
-cat("p-value: ", steiger_test_anxiety_dose_vs_dep$p_value, "\n")
-```
-
-```
-##### JAMA ANALYSIS - compare correlations w/wout uncinate
-```{r other_injured_fascicles}
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1)  %>% #n=372 
-  mutate(total_lesion_burden_no_UF = sum_fascicle_vol_lost - (UF_L_vol + UF_R_vol))
-
-#almost identical because uncinate is small
-#t=2.05, p = 0.04083
-cor_lesion_burden_by_anxiety = cor.test(df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose, df_demo_and_fascicles_no_unclass_anxiety_dose$sum_fascicle_vol_lost)
-print(cor_lesion_burden_by_anxiety)
-
-#t=2.05, p = 0.04075
-cor_lesion_burden_no_UF_by_anxiety = cor.test(df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose, df_demo_and_fascicles_no_unclass_anxiety_dose$total_lesion_burden_no_UF)
-print(cor_lesion_burden_no_UF_by_anxiety)
 
@@
 ##### Overall disease in brain
-```{r}
+```{r overall_disease_bruden}
 #n = 372

### 2025-01-23 scripts/jama_scripts/MSAnxiety_manuscript_JAMA_revision_20250123_FINAL.Rmd
Add files via upload

--- 2025-01-20 scripts/jama_scripts/MSAnxiety_manuscript_JAMA_revision_20250116.Rmd
@@
 library(ggpubr)
-library(tidygam)
-library(psych)
-#library(tidymv)
 library(aod)
@@
 #functions
-source("~/Library/CloudStorage/Box-Box/BBL/ms_generic_scripts/msdepression_functions.R")
-```
-
-## MS anxiety analyses
-
-## R Markdown
-
-The first chunk here is reading in appropriate data frames and preprocessing.
-Two big data frames are read in.
-The first is the demographic, drug, lab info for the MS patients (from the DAC pull).
-The second is the data frame of fascicle proportion affected for people with good mimosa (# volume affected/total volume of fascicle).
-The most important preprocessing occurs in a series of mutate commands.
-These essentially add new columns to the data frame that can later be used.
-The thrust of these mutate commands is to define who has depression and who does not.
-
-Of note, in prior iterations of this analysis, we did not consider psychiatric medications in determining group inclusion/exclusion.
-Turns out it makes a difference, as a lot of people on psychotropic medications were counted as "controls/healthy" in previous analyses.
-For these preliminary analysis, our inclusion/exclusion are more stringent.
-Of note, the graph below is irrespective of whether they had good/bad MIMoSA.
-As such, the MIMoSA subset is smaller.
-It does however highlight the
-
-<img width="70%" src="/Users/eballer/BBL/msdepression/data/drugs_data/MS_Patient_Depression_Categorizations.png"/>
-
-Inclusion criteria below:
-
-Inclusion MS Criteria (dataframe read in here has already been filtered down using the exclusions below previously)
-  1) Scanned under MS protocol (42K)
-  2) MS Diagnosis (17K)
-  3) Seen by MS doctor (16K)
-
-Inclusion criteria for Anxious Group
-  1) Have an ICD10 F4* code (in our sample, people have F41.1; 41.3; 41.8; 41.9)
-        (may use this later)- https://www.nami.org/About-Mental-Illness/Treatments/Mental-Health-Medications
-
-Inclusion criteria for Healthy Group
-  1) No F* diagnoses
-  2) At least 1 PHQ2 or PHQ9 with a documented 0
-  3) Free of psychiatric medications per NAMI website (plus editions per Dr. Baller)
-
-Exclusions
-  If you received the MS protocol or had a diagnosis of MS but never actually saw an MS provider, we cannot be sure that the diagnosis of MS is truly valid, as it is hard to diagnose anyway.
-  If you did not have a diagnosis of depression and never completed a PHQ2 or 9, and had no history of medications, we could not safely confirm nor deny the presence of anxiety.
-These subjects were excluded from future analyses.
-We could consider adding these to the healthy group maybe, but not too inclined to do that right now.
-
-Imaging exclusion
-  We are currently only using people who had good MIMOSA (75 or 100). That severely limits our numbers, but that is okay! When we re-QC, we will probably get a lot more into this group.
-
-Groups:
-1. Total unique individuals who also have MS - 1026
-2. Total unique who had good MIMoSA - 867 (lost 159)
-3. Remove people without MS provider, n=814 (lost 53)
-
-#figure brainstorming
-1. Flowchart of inclusion/exclusion (825 participants -> 11 lost for poor streamline filtering -> 814 go into phenotyping) -> Elena
-   A. Anxiety diagnosis
-    I. Yes
-       - Anxiety Med
-          a. Yes -> MS+severeA (24 individuals)
-          b. No  -> MS+mildA (87 indiv)
-     II. No
-        - Anxiety Med
-          a. Yes -> MS+mildA (162)
-          b. No
-            - Has PHQ2 or 9 and 0 
-              i. Yes-> MS+noA (99 individuals)
-              ii. No -> Unclassified (442 individuals)
-
-Final groups (MS+noA = 99, MS+mildA = 249, MS+severeA = 24)
-
-2. Demographics (age, sex, race, +/- PHQ2, PHQ9, has anxiety dx, on anxiety meds, both, on dmt) -> elena to make all the csvs into tables
-3. PROMIS scores (each type of measure is a line, y axis is score, x axis is anxiety dose)
-4. Some sort of schematic of pipeline (Maggie) - 
-  a. amygdala - mpfc blobs
-  b. uncinate connecting the two
-  c. white matter lesion dropped in uncinates
-  d. streamline filtering
-  e. mean of both side
-5. Mean Anxiety dose either violin or bar
-
-6. Supplement: 
- - Promis tables
-#Rstduio Version: 2024.04.1+748 (2024.04.1+748)
-## Make final data frame for analysis
+source("~/Library/CloudStorage/Box-Box/BBL/msanxiety/scripts/FINAL/ms_functions.R")
+```
+
 ### read in emr data
@@
 ### MS med summaries by group
-```{r demographics}
+```{r demographics_meds}
 
@@
 #####Promis x anxiety dose, group by mental vs physical health
-```{r plot_Promis_x_anxiety}
+```{r plot_Promis_x_anxiety_mental_vs_phys}
 #set mood versus physical domains
@@
 
+#save eps
+postscript(file = paste0(homedir, "/results/Figures_for_msanxiety_paper/promis_with_post_op_mental_vs_physical.eps"), width = 2, height = 1.5)
+  promis_with_post_op_mental_vs_physical
+dev.off()
 ```
@@
   mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  dplyr::select(subject, osex, Diagnosis, PAT_AGE_AT_EXAM, volume_of_mimosa_lesions) %>%
   ungroup() #n=123
@@
 
-#gam lesion volumes; DiagnosisMS+Anxiety   8215.7     2702.7   3.040  0.00292 ** 
-volume_of_mimosa_lesions_gam <- gam(volume_of_mimosa_lesions ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+#gam lesion volumes; DiagnosisMS+Anxiety 8.262e+03  2.691e+03   3.070  0.00266 **
+volume_of_mimosa_lesions_gam <- gam(volume_of_mimosa_lesions ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T) + total_volume, data = df_empi_dx_network_proportions)
 summary(volume_of_mimosa_lesions_gam)
 
- #print summary stats; (T = 3.04, P = 0.003, Cohen's f2 =  0.342, Effect size = medium)
+ #print summary stats; (T = 3.07, P = 0.003, Cohen's f2 =  0.354, Effect size = large)
  gam_summary_stats(volume_of_mimosa_lesions_gam)
@@
 
- #bilat anxiety dose + sex + age: anxiety_dose     3866       1254   3.084   0.0022 **
-
-  anxiety_dose_volume_of_mimosa_lesions_by_sex_gam <- gam(volume_of_mimosa_lesions ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+ #bilat anxiety dose + sex + age:  anxiety_dose  3.955e+03  1.228e+03   3.221  0.00139 **
+
+  anxiety_dose_volume_of_mimosa_lesions_by_sex_gam <- gam(volume_of_mimosa_lesions ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T) + total_volume, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxiety_dose_volume_of_mimosa_lesions_by_sex_gam)
 
-   #print summary stats; (T = 3.084, P = 0.0022, Cohen's f2 =  0.12, Effect size = small)
+   #print summary stats; (T = 3.221, P = 0.001, Cohen's f2 =  0.168, Effect size = medium)
  gam_summary_stats(anxiety_dose_volume_of_mimosa_lesions_by_sex_gam)
@@
 ### Whole brain volumes 
-#### Diagnosis - sick > healthy in vol of lesions
-```{r lesion_volumes_dx}
+#### Diagnosis - sick > healthy 
+```{r tbv_dx}
  df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
@@
  gam_summary_stats(total_brain_volume_gam)
+
 ```
@@
   - anxiety dose correlates with disease burden (total brain volume )
-```{r lesion_volumes_anxiety_dose}
+```{r tbv_anxiety_dose}
 df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
@@
 #### Uncinate by anxiety diagnosis (prop)
-```{r uncinate_by_dx}
+```{r uncinate_by_dx_prop}
 ### Having found that there is no association between the number of uncinate lesions and the anxiety dose, I next explored whether the *burden* of uncinate lesions differs by diagnosis/group
-
-#### Fx = F gives better results than FX = T
 
@@
 
- #print summary stats
+ #print summary stats; (T = 2.022, P = 0.045, Cohen's f2 =  0.192, Effect size = medium)
   gam_summary_stats(disease_mean_UF_prop_gam)
@@
 #### Fx = F gives better results than FX = T
-#results: Anxiety dose related to UF_R when covarying for linear effects of age and sex, just barely
-# Additionally - taking the mean of both UF and UR, LM for bilat anxiety dose + sex + age: anxiety_dose most sig P= 0.0367 *  (fx=T)
+#results: Anxiety dose related to UF_R when covarying for linear effects of age and sex
 
@@
 
-    #bilat anxiety dose + sex + age: anxiety_dose    0.04989    0.02397   2.082   0.0381 * 
+    #bilat anxiety dose + sex + age + total volume: anxiety_dose  0.04989    0.02397   2.082   0.0381 * 
  anxietyGrouping_mean_UF_by_sex_gam_prop <- gam(mean_UF_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
@@
 
-  #print summary stats
+  #print summary stats; (T = 2.082, P = 0.038, Cohen's f2 =  0.105, Effect size = small)
   gam_summary_stats(anxietyGrouping_mean_UF_by_sex_gam_prop)
@@
 #### Sensitivity
-###### UF by depGroupVar (vol/prop, N.S)
-```{r UF_by_depGroupVar}
-# Specificity - want to make sure the UF findings are specific to anxiety, so check to see if same findings exist in depression
-### Reviewed previous pull from BP paper, finding was also consistent there -> no diff in uncinate in depressed vs non depressed
-
-df_dep <- df_demo_and_fascicles %>%
-  filter(depGroupVar != 0) %>%
-  mutate(depDiagnosis = as.factor(ifelse(depGroupVar ==2, "MS+Depression", "MS+noDepression")))
-
-table(df_dep$depDiagnosis) #MS+Dep n = 207; MS+noDep n = 99
-
- #mean UF, depDiagnosisMS+noDepression   -0.05029    0.03028  -1.661   0.0978 . 
-dep_mean_UF_gam_prop <- gam(mean_UF_prop ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
-summary(dep_mean_UF_gam_prop)
-
-  #print summary stats
- gam_summary_stats(dep_mean_UF_gam_prop)
-
-```
-
-###### Lesion & brainvol by depGroupVar (lesion vol - Y, tbv - N, N.S)
-```{r UF_by_depGroupVar}
-# Specificity - want to make sure the lesion and brain vol findings are nonspecific t so check to see if same findings exist in depression
-### Reviewed previous pull from BP paper, finding was also consistent there -> no diff in uncinate in depressed vs non depressed
-
-df_dep <- df_demo_and_fascicles %>%
-  filter(depGroupVar != 0) %>%
-  mutate(depDiagnosis = as.factor(ifelse(depGroupVar ==2, "MS+Depression", "MS+noDepression")))
-
-table(df_dep$depDiagnosis) #MS+Dep n = 207; MS+noDep n = 99
-
- #mean vol mimosa lesions, depDiagnosisMS+noDepression 
-#(T = -3.164, P = 0.002, Cohen's f2 =  0.128, Effect size = small)
-dep_mean_lesion_vol_gam_prop <- gam(volume_of_mimosa_lesions ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
-summary(dep_mean_lesion_vol_gam_prop)
-
-  #print summary stats
- gam_summary_stats(dep_mean_lesion_vol_gam_prop)
-
-  #mean brain vol mimosa lesions, depDiagnosisMS+noDepression  
- #(T = 0.016, P = 0.988, Cohen's f2 =  0.333, Effect size = medium)
-dep_mean_total_brain_vol_gam_prop <- gam(total_volume ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
-summary(dep_mean_total_brain_vol_gam_prop)
-
-  #print summary stats
- gam_summary_stats(dep_mean_total_brain_vol_gam_prop)
-
-```
-
 ###### Fornix by Anxiety Diagnosis and Dose (vol and prop, N.S)
@@
  ##### healthy vs sick - prop
-#Fornix gam Diagnosis; DiagnosisMS+Anxiety    0.03690    0.05405   0.683   0.4961    - NS
-anxietyDiagnosis_mean_F_by_sex_gam_prop <- gam(mean_fornix_prop ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+#Fornix gam Diagnosis; DiagnosisMS+Anxiety   (T = 0.67, P = 0.504, Cohen's f2 =  0.025, Effect size = small)
+anxietyDiagnosis_mean_F_by_sex_gam_prop <- gam(mean_fornix_prop ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T) + total_volume, data = df_empi_dx_network_proportions)
 summary(anxietyDiagnosis_mean_F_by_sex_gam_prop)
 
-#define group for dose
+#define group for dose; 
 df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
@@
 
-  #gam, Fornix anxiety_dose   0.02303    0.02401   0.959    0.338    - NS
-  anxietyGrouping_mean_F_by_sex_gam_prop <- gam(mean_fornix_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  #gam, Fornix anxiety_dose  ; anxiety_dose  2.305e-02  2.404e-02   0.959   0.3383
+
+  anxietyGrouping_mean_F_by_sex_gam_prop <- gam(mean_fornix_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T) + total_volume, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_mean_F_by_sex_gam_prop)
@@
  #print summary stats
- gam_summary_stats(anxietyDiagnosis_mean_F_by_sex_gam_prop)
- gam_summary_stats(anxietyGrouping_mean_F_by_sex_gam_prop)
+ gam_summary_stats(anxietyDiagnosis_mean_F_by_sex_gam_prop) #"(T = 0.67, P = 0.504, Cohen's f2 =  0.025, Effect size = small)
+ gam_summary_stats(anxietyGrouping_mean_F_by_sex_gam_prop) #(T = 0.959, P = 0.338, Cohen's f2 =  -0.003, Effect size = NA
+```
+
+###### UF by depGroupVar (vol/prop, N.S)
+```{r UF_by_depGroupVar}
+# Specificity - want to make sure the UF findings are specific to anxiety, so check to see if same findings exist in depression
+### Reviewed previous pull from BP paper, finding was also consistent there -> no diff in uncinate in depressed vs non depressed
+
+df_dep <- df_demo_and_fascicles %>%
+  filter(depGroupVar != 0) %>%
+  mutate(depDiagnosis = as.factor(ifelse(depGroupVar ==2, "MS+Depression", "MS+noDepression")))
+
+table(df_dep$depDiagnosis) #MS+Dep n = 207; MS+noDep n = 99
+
+ #mean UF, depDiagnosisMS+noDepression  T = -1.659, P = 0.098, Cohen's f2 =  0.105
+dep_mean_UF_gam_prop <- gam(mean_UF_prop ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F) + total_volume, data = df_dep)
+summary(dep_mean_UF_gam_prop)
+
+  #print summary stats: (T = -1.659, P = 0.098, Cohen's f2 =  0.105, Effect size = small)
+ gam_summary_stats(dep_mean_UF_gam_prop)
+
+```
+
+###### JAMA ANALYSIS: Lesion & brainvol by depGroupVar (lesion vol - Y, tbv - N, N.S)
+```{r UF_by_depGroupVar_lesion_tbv}
+# Specificity - want to make sure the lesion and brain vol findings are nonspecific t so check to see if same findings exist in depression
+### Reviewed previous pull from BP paper, finding was also consistent there -> no diff in uncinate in depressed vs non depressed
+
+df_dep <- df_demo_and_fascicles %>%
+  filter(depGroupVar != 0) %>%
+  mutate(depDiagnosis = as.factor(ifelse(depGroupVar ==2, "MS+Depression", "MS+noDepression")))
+
+table(df_dep$depDiagnosis) #MS+Dep n = 207; MS+noDep n = 99
+
+ #mean vol mimosa lesions, depDiagnosisMS+noDepression; depDiagnosisMS+noDepression -5.608e+03  1.753e+03  -3.200 0.001522 **
+
+dep_mean_lesion_vol_gam_prop <- gam(volume_of_mimosa_lesions ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F) + total_volume, data = df_dep)
+summary(dep_mean_lesion_vol_gam_prop)
+
+  #print summary stats; #(T = -3.2, P = 0.002, Cohen's f2 =  0.178, Effect size = medium)
+ gam_summary_stats(dep_mean_lesion_vol_gam_prop)
+
 ```
@@
 ###### JAMA ANALYSIS- UF Anxiety diagnosis + lesion vol
-```{r uncinate_by_dx}
+```{r uncinate_by_dx_lesion_vol}
 ### Having found that there is no association between the number of uncinate lesions and the anxiety dose, I next explored whether the *burden* of uncinate lesions differs by diagnosis/group
@@
 
-  #how about in fornix
-
-  corr_LV_to_fornix <- cor.test(uncinate_by_dx_df$volume_of_mimosa_lesions,uncinate_by_dx_df$mean_fornix_volume) #corr 0.69; 
-  print(corr_LV_to_fornix) #0.3452654
-
-  lesion_vol_fornix_lm <- lm(uncinate_by_dx_df$volume_of_mimosa_lesions~ uncinate_by_dx_df$mean_fornix_volume)
-  summary(lesion_vol_fornix_lm) #T = 4.047
-
-  ## Try scaling mean volume
- # disease_mean_scaled_UF_vol_gam <- gam(mean_UF_vol_scaled_total_vol_lesions ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
-  #summary(disease_mean_scaled_UF_vol_gam) #- N.S.
-
-  #print summary stats; (T = -0.556, P = 0.579, Cohen's f2 =  0.007, Effect size = minimal)"
-  #gam_summary_stats(disease_mean_scaled_UF_vol_gam)
-
-## modeling this doesn't make sense
-#disease_mean_UF_prop_w_LV_gam <- gam(mean_UF_prop ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F) + volume_of_mimosa_lesions, data = uncinate_by_dx_df)
-#summary(disease_mean_UF_prop_w_LV_gam)
-
- #print summary stats
- # gam_summary_stats(disease_mean_UF_prop_w_LV_gam)
-```
-###### JAMA ANALYSIS-  UF Anxiety dose + lesion vol
-```{r uncinateByAnxietyDose}
+```
+###### JAMA ANALYSIS-  UF Anxiety severity + lesion vol
+```{r uncinateByAnxietyDose_lesion_vol}
 
@@
 
+#cor = 0.6282121; t = 15.531, df = 370, p-value < 2.2e-16
 corr_LV_to_UF_anxiety_dose <- cor.test(df_demo_and_fascicles_no_unclass_anxiety_dose$volume_of_mimosa_lesions,df_demo_and_fascicles_no_unclass_anxiety_dose$mean_UF_vol) #
@@
 ###### JAMA ANALYSIS- UF Anxiety diagnosis + total brain vol
-```{r uncinate_by_dx}
+```{r uncinate_by_dx_tbv}
 ### Having found that there is no association between the number of uncinate lesions and the anxiety dose, I next explored whether the *burden* of uncinate lesions differs by diagnosis/group
@@
 ###### JAMA ANALYSIS-  UF Anxiety dose + total brain volume
-```{r uncinateByAnxietyDose}
+```{r uncinateByAnxietyDose_tbv}
 
@@
   gam_summary_stats(disease_UF_cov_brain_vol_dose_gam)
+
+```
+
+##### JAMA ANALYSIS- correction for multiple comparisons
+```{r sensi_correction}
+#uf dep group
+#fornix by anxiety diag
+#fornix by anxiety dose
+#lesion vol anxiety diag
+#lesion vol anxiety dose
+
+anxiety_dx_vol_mimosa_lesions = summary(volume_of_mimosa_lesions_gam)$p.table[2,4]
+anxiety_dose_vol_mimosa_lesions = summary(anxiety_dose_volume_of_mimosa_lesions_by_sex_gam)$p.table[2,4]
+dep_mean_lesion_vol_gam = summary(dep_mean_lesion_vol_gam_prop)$p.table[2,4]
+dep_uf_gam = summary(dep_mean_UF_gam_prop)$p.table[2,4]
+anxiety_dx_fornix = summary(anxietyDiagnosis_mean_F_by_sex_gam_prop)$p.table[2,4]
+anxiety_dose_fornix = summary(anxietyGrouping_mean_F_by_sex_gam_prop)$p.table[2,4]
+
+p_vals <- array(c(anxiety_dx_vol_mimosa_lesions,
+                 anxiety_dose_vol_mimosa_lesions,
+                 dep_mean_lesion_vol_gam,
+                 dep_uf_gam,
+                 anxiety_dx_fornix,
+                 anxiety_dose_fornix))
+
+#0.005324721 0.004567230 0.004567230 0.147282059 0.496139621 0.405577736
+p_val_fdr <- p.adjust(method = "fdr", p_vals)
+names(p_val_fdr) = c("anxiety_dx_vol_mimosa_lesions", "anxiety_dose_vol_mimosa_lesions", "dep_mean_lesion_vol_gam", "dep_uf_gam", "anxiety_dx_fornix", "anxiety_dose_fornix")
+print(p_val_fdr)
 
@@
 
+postscript(file = paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_box_plot_no_jitter.eps"), width = 2, height = 1.5)
+  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
+dev.off()
+
 ```
@@
 ```
-
-### Plots
-
-##### Overall disease in brain
-```{r overall_disease_bruden}
-#n = 372
-
-df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified")
-
-prop_injured_by_anxiety_burden_collapsed_vars_plot <-  ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x= oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed , y=proportion_volume_lost_per_total_network_size_sum, fill= oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed )) +
-  geom_violin() +  
-  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
-  theme(axis.text.x = element_text(size=8, angle = 45, vjust = 0.5))
-prop_injured_by_anxiety_burden_collapsed_vars_plot
-```
-
-###Promis data in UF - groups too small
-#### Uncinate by anxiety diagnosis (N.S) 
-```{r uncinate_by_dx}
-
-### Results:  
-#define group
-  uncinate_by_dx_df <- df_people_with_promis_data_scores_added_unique %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
-  mutate(subject = as.factor(EMPI)) %>%
-  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  ungroup() #n=19
-
-#bilateral UF prop ~ Diagnosis: DiagnosisMS+Anxiety -0.02490    0.11510  -0.216   0.8317 
-disease_mean_UF_prop_gam <- gam(mean_UF_prop ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
-summary(disease_mean_UF_prop_gam)
-
-    #print summary stats
- gam_summary_stats(disease_mean_UF_prop_gam)
-
-```
-
-#### Uncinate by Anxiety Dose (N.S.)
-```{r uncinateByAnxietyDose}
-
-#define group
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_people_with_promis_data_scores_added_unique %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) #n=64
-
-  #bilat anxiety dose -anxiety_dose   -0.006261   0.055025  -0.114 0.909793       NS
-  anxietyGrouping_mean_UF_by_sex_gam_prop <- gam(mean_UF_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_mean_UF_by_sex_gam_prop)
-
-    #print summary stats
-
- gam_summary_stats(anxietyGrouping_mean_UF_by_sex_gam_prop)
-
-```
-
-```{r ants}
-
-```

### 2025-01-23 scripts/MSAnxiety_manuscript_JAMA_revision_20250116.Rmd
Add files via upload

--- 2025-01-20 scripts/jama_scripts/MSAnxiety_manuscript_JAMA_revision_20250116.Rmd
@@
 #functions
-source("~/Library/CloudStorage/Box-Box/BBL/ms_generic_scripts/msdepression_functions.R")
+source("~/Library/CloudStorage/Box-Box/BBL/msanxiety/scripts/FINAL/ms_functions.R")
 ```
@@
 As such, the MIMoSA subset is smaller.
-It does however highlight the
-
-<img width="70%" src="/Users/eballer/BBL/msdepression/data/drugs_data/MS_Patient_Depression_Categorizations.png"/>
 
@@
 #### Uncinate by anxiety diagnosis (prop)
-```{r uncinate_by_dx}
+```{r uncinate_by_dx_prop}
 ### Having found that there is no association between the number of uncinate lesions and the anxiety dose, I next explored whether the *burden* of uncinate lesions differs by diagnosis/group
@@
 
- #mean UF, depDiagnosisMS+noDepression   -0.05029    0.03028  -1.661   0.0978 . 
-dep_mean_UF_gam_prop <- gam(mean_UF_prop ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
+ #mean UF, depDiagnosisMS+noDepression  T = -1.659, P = 0.098, Cohen's f2 =  0.105
+dep_mean_UF_gam_prop <- gam(mean_UF_prop ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F) + total_volume, data = df_dep)
 summary(dep_mean_UF_gam_prop)
@@
 ###### Lesion & brainvol by depGroupVar (lesion vol - Y, tbv - N, N.S)
-```{r UF_by_depGroupVar}
+```{r UF_by_depGroupVar_lesion_tbv}
 # Specificity - want to make sure the lesion and brain vol findings are nonspecific t so check to see if same findings exist in depression
@@
  #mean vol mimosa lesions, depDiagnosisMS+noDepression 
-#(T = -3.164, P = 0.002, Cohen's f2 =  0.128, Effect size = small)
-dep_mean_lesion_vol_gam_prop <- gam(volume_of_mimosa_lesions ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
+#(T = -3.2, P = 0.002, Cohen's f2 =  0.178, Effect size = medium)
+dep_mean_lesion_vol_gam_prop <- gam(volume_of_mimosa_lesions ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F) + total_volume, data = df_dep)
 summary(dep_mean_lesion_vol_gam_prop)
@@
  #(T = 0.016, P = 0.988, Cohen's f2 =  0.333, Effect size = medium)
-dep_mean_total_brain_vol_gam_prop <- gam(total_volume ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
-summary(dep_mean_total_brain_vol_gam_prop)
+#dep_mean_total_brain_vol_gam_prop <- gam(total_volume ~ depDiagnosis + osex + s(PAT_AGE_AT_EXAM, k=4, fx=F), data = df_dep)
+#summary(dep_mean_total_brain_vol_gam_prop)
 
   #print summary stats
- gam_summary_stats(dep_mean_total_brain_vol_gam_prop)
+ #gam_summary_stats(dep_mean_total_brain_vol_gam_prop)
 
@@
  ##### healthy vs sick - prop
-#Fornix gam Diagnosis; DiagnosisMS+Anxiety    0.03690    0.05405   0.683   0.4961    - NS
-anxietyDiagnosis_mean_F_by_sex_gam_prop <- gam(mean_fornix_prop ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data = df_empi_dx_network_proportions)
+#Fornix gam Diagnosis; DiagnosisMS+Anxiety    (T = 0.683, P = 0.496, Cohen's f2 =  0.024, Effect size = small)
+anxietyDiagnosis_mean_F_by_sex_gam_prop <- gam(mean_fornix_prop ~ Diagnosis + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T) + total_volume, data = df_empi_dx_network_proportions)
 summary(anxietyDiagnosis_mean_F_by_sex_gam_prop)
@@
 
-  #gam, Fornix anxiety_dose   0.02303    0.02401   0.959    0.338    - NS
-  anxietyGrouping_mean_F_by_sex_gam_prop <- gam(mean_fornix_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
+  #gam, Fornix anxiety_dose   (T = 0.959, P = 0.338, Cohen's f2 =  0, Effect size = minimal)"
+  anxietyGrouping_mean_F_by_sex_gam_prop <- gam(mean_fornix_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T) + total_volume, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
   summary(anxietyGrouping_mean_F_by_sex_gam_prop)
@@
 
-  #how about in fornix
-
-  corr_LV_to_fornix <- cor.test(uncinate_by_dx_df$volume_of_mimosa_lesions,uncinate_by_dx_df$mean_fornix_volume) #corr 0.69; 
-  print(corr_LV_to_fornix) #0.3452654
-
-  lesion_vol_fornix_lm <- lm(uncinate_by_dx_df$volume_of_mimosa_lesions~ uncinate_by_dx_df$mean_fornix_volume)
-  summary(lesion_vol_fornix_lm) #T = 4.047
-
-  ## Try scaling mean volume
- # disease_mean_scaled_UF_vol_gam <- gam(mean_UF_vol_scaled_total_vol_lesions ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
-  #summary(disease_mean_scaled_UF_vol_gam) #- N.S.
-
-  #print summary stats; (T = -0.556, P = 0.579, Cohen's f2 =  0.007, Effect size = minimal)"
-  #gam_summary_stats(disease_mean_scaled_UF_vol_gam)
-
-## modeling this doesn't make sense
-#disease_mean_UF_prop_w_LV_gam <- gam(mean_UF_prop ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F) + volume_of_mimosa_lesions, data = uncinate_by_dx_df)
-#summary(disease_mean_UF_prop_w_LV_gam)
-
- #print summary stats
- # gam_summary_stats(disease_mean_UF_prop_w_LV_gam)
 ```
 ###### JAMA ANALYSIS-  UF Anxiety dose + lesion vol
-```{r uncinateByAnxietyDose}
+```{r uncinateByAnxietyDose_lesion_vol}
 
@@
   gam_summary_stats(disease_UF_cov_brain_vol_dose_gam)
+
+```
+
+##### JAMA ANALYSIS- correction for multiple comparisons
+```{r sensi_correction}
+#uf dep group
+#fornix by anxiety diag
+#fornix by anxiety dose
+#lesion vol anxiety diag
+#lesion vol anxiety dose
+
+anxiety_dx_vol_mimosa_lesions = summary(volume_of_mimosa_lesions_gam)$p.table[2,4]
+anxiety_dose_vol_mimosa_lesions = summary(anxiety_dose_volume_of_mimosa_lesions_by_sex_gam)$p.table[2,4]
+dep_mean_lesion_vol_gam = summary(dep_mean_lesion_vol_gam_prop)$p.table[2,4]
+dep_mean_gam = summary(dep_mean_UF_gam_prop)$p.table[2,4]
+anxiety_dx_fornix = summary(anxietyDiagnosis_mean_F_by_sex_gam_prop)$p.table[2,4]
+anxiety_dose_fornix = summary(anxietyGrouping_mean_F_by_sex_gam_prop)$p.table[2,4]
+
+p_vals <- array(c(anxiety_dx_vol_mimosa_lesions,
+                 anxiety_dose_vol_mimosa_lesions,
+                 dep_mean_lesion_vol_gam,
+                 dep_mean_gam,
+                 anxiety_dx_fornix,
+                 anxiety_dose_fornix))
+
+#0.005324721 0.004567230 0.004567230 0.147282059 0.496139621 0.405577736
+p_val_fdr <- p.adjust(method = "fdr", p_vals)
+print(p_val_fdr)
 
@@
 ```
-
-###Promis data in UF - groups too small
-#### Uncinate by anxiety diagnosis (N.S) 
-```{r uncinate_by_dx}
-
-### Results:  
-#define group
-  uncinate_by_dx_df <- df_people_with_promis_data_scores_added_unique %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "Has.Anxietydx.OR.Antianxiety.Meds") %>%
-  mutate(subject = as.factor(EMPI)) %>%
-  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
-  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
-  mutate(Diagnosis = as.factor(Diagnosis)) %>%
-  ungroup() #n=19
-
-#bilateral UF prop ~ Diagnosis: DiagnosisMS+Anxiety -0.02490    0.11510  -0.216   0.8317 
-disease_mean_UF_prop_gam <- gam(mean_UF_prop ~ Diagnosis + osex+s(PAT_AGE_AT_EXAM, k = 4, fx = F), data = uncinate_by_dx_df)
-summary(disease_mean_UF_prop_gam)
-
-    #print summary stats
- gam_summary_stats(disease_mean_UF_prop_gam)
-
-```
-
-#### Uncinate by Anxiety Dose (N.S.)
-```{r uncinateByAnxietyDose}
-
-#define group
-df_demo_and_fascicles_no_unclass_anxiety_dose <- df_people_with_promis_data_scores_added_unique %>%
-  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
-  filter(anxiety_dose != -1) #n=64
-
-  #bilat anxiety dose -anxiety_dose   -0.006261   0.055025  -0.114 0.909793       NS
-  anxietyGrouping_mean_UF_by_sex_gam_prop <- gam(mean_UF_prop ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
-  summary(anxietyGrouping_mean_UF_by_sex_gam_prop)
-
-    #print summary stats
-
- gam_summary_stats(anxietyGrouping_mean_UF_by_sex_gam_prop)
-
-```
-
-```{r ants}
-
-```
